\documentclass[12pt]{article}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}
\usepackage{mathptmx,multicol,common}
\parindent 0pt
\parskip
\baselineskip
\setlength{\topmargin}{-0.30in}
\setlength{\oddsidemargin}{-0.30in}
\setlength{\evensidemargin}{-0.30in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0.25in}
\setlength{\topskip}{0.25in}
\setlength{\textwidth}{6.9in}
\setlength{\textheight}{9.25in}
\pagestyle{myheadings}
\newcommand{\myhead}{Cavagnolo, Expertise}

\begin{document}

\begin{center}
{\Large\sc{Description of Research Activities}}
\end{center}

The description should make clear the applicant’s role in the
activities presented, and the research results should also be
described within an international perspective. The description should
include an assessment of the applicant’s independence and
productivity.

\end{document}

Description of research activities:

External research grants received:

List major grants that have been received. Specify the body awarding
the grant, the amount, and date of the award. The applicant is to
state whether the grant has been awarded to the applicant in the role
of principal researcher or as co-applicant. The principal researcher
and other co-applicants are to be specified in the latter case.

Scientific distinctions, prizes, academy memberships, etc.

Other scientific expertise:

Appointment as opponent at doctoral disputations or member of
examination board. Appointment as a member of an expert panel. Work
abroad, postdoctoral periods (if any). National and international
collaborative projects. Participation in national and international
conferences related to the field of research. Memberships of
editorial/advisory boards for international journals and referee
commissions for journals. Specify the journals and the number of
commissions per year. Other expertise.
