%%%%%%%%%%
% Header %
%%%%%%%%%%

\documentclass{emulateapj}
\usepackage{apjfonts,graphicx,here}
\shorttitle{X-ray Band Dependent Temperature}
\shortauthors{Cavagnolo et al.}
\bibliographystyle{apj}

%%%%%%%%%%%%%%%%%%%%%
% Title and Authors %
%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\title{Bandpass Dependence of X-ray Temperatures in Galaxy Clusters}
\author{Kenneth W. Cavagnolo\altaffilmark{1,2}, Megan
Donahue\altaffilmark{1}, G. Mark Voit\altaffilmark{1}, and Ming
Sun\altaffilmark{1}}
\altaffiltext{1}{Department of Physics and Astronomy, Michigan State
University, BPS Building, East Lansing, MI 48824}
\altaffiltext{2}{cavagnolo@pa.msu.edu}

%%%%%%%%%%%%
% Abstract %
%%%%%%%%%%%%

\begin{abstract}

We explore the band dependence of the inferred X-ray temperature of
the intracluster medium (ICM) for 193 well-observed galaxy clusters
selected from the {\it Chandra} Data Archive. If
the hot gas in a cluster is nearly isothermal in the projected region
of interest, the X-ray temperature inferred from a broad-band
(0.7-7.0 keV) spectrum should be identical to the X-ray temperature
inferred from a hard-band (2.0-7.0 keV) spectrum. However, if there are
unresolved cool lumps of gas contributing soft X-ray emission, the
temperature of a best-fit single-component thermal model will be
cooler for a broad-band spectrum than for a hard-band spectrum. Using
this difference as a diagnostic, the ratio of best-fitting hard-band
and broad-band temperatures may indicate presence of cooler gas even
when the X-ray spectrum itself may not have sufficient signal-to-noise
to resolve multiple temperature components. To test this possible
diagnostic, we extract X-ray spectra from core-excised annular regions
for each cluster in our archival sample. We compare the X-ray
temperatures inferred from single-temperature fits of global spectra
when the energy range of the fit is 0.7-7.0 keV (broad) and when the
energy range is 2.0/(1+$z$)-7.0 keV (hard). We find that the hard-band
temperature is significantly higher, on average, than the broad-band
temperature. Upon further exploration, we find this temperature ratio
is enhanced preferentially for clusters which are known merging
systems. Clusters with temperature decrements in their cores (known as
cool-core clusters) tend to have best-fit hard-band temperatures that
are statistically consistent with their best-fit broad-band
temperatures. We show, using simulated spectra, that this test is
sensitive to cool components with emission measures $> 10\%$ of the
hot component.
\end{abstract}

%%%%%%%%%%%%
% Keywords %
%%%%%%%%%%%%

\keywords{catalogs -- galaxies: clusters: general -- X-rays: galaxies:
clusters -- cosmology: observations -- methods: data analysis}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The normalization, shape, and evolution of the cluster mass function
are useful for measuring cosmological parameters
(e.g. \citealt{1989ApJ...341L..71E, 1998ApJ...508..483W,
2001ApJ...553..545H,  2004PhRvD..70l3008W}). The evolution of large
scale structure formation, and clusters in particular, is a test of
how dark matter and dark energy effect the evolution of dark
matter haloes, and therefore provides a complementary and distinct
constraint on cosmological parameters to those tests which constrain
them geometrically (e.g. supernovae \citealt{1998AJ....116.1009R,
2007ApJ...659...98R} and baryon acoustic oscillations
\citealt{2005ApJ...633..560E}).

However, clusters are a useful cosmological tool only if we can infer
cluster masses from observable properties such as X-ray luminosity,
X-ray temperature, lensing shear, optical luminosity, or galaxy
velocity dispersion. Empirically, the correlation of mass to these
observable properties is well-established
\citep{2005RvMP...77..207V}. However, if we could identify a ``2nd
parameter" -- possibly reflecting the degree of relaxation in the
cluster -- we could improve the utility of clusters as cosmological
probes by parameterizing and reducing the scatter in mass-observable
scaling relations.

Toward this end, we desire to quantify the dynamical state of a
cluster rather than simply identifying which clusters appear to be
relaxed and those which appear to be unrelaxed. Most clusters are
likely to have a dynamical state which is somewhere in between
\citep{2006ApJ...639...64O, 2006ApJ...650..128K}. The degree to which
a cluster is virialized must be quantified within simulations that
correctly predict the observable properties of the cluster. This
prediction may then be tested and possibly calibrated with
observations of an unbiased sample of clusters.

One study that examined how relaxation might affect the observable
properties of clusters was conducted by \citealt{2001ApJ...546..100M}
(hereafter ME01) using the ensemble of simulations by
\citealt{1997ApJ...491...38M}. ME01 found that most clusters which had
experienced a recent merger were cooler than the cluster
mass-observable scaling relations predicted. They attributed this to the
presence of cool, spectroscopically unresolved accreting subclusters
which introduced energy into the ICM and which have a long timescale for
dissipation. The consequence was an under-prediction of cluster
binding masses of $15-30\%$ \citep{2001ApJ...546..100M}.

An empirical method of quantifying cluster substructure employs the ratios of
X-ray surface brightness moments to quantify the degree of relaxation
\citep{1995ApJ...452..522B, 1996ApJ...458...27B,
2005ApJ...624..606J}. Although an excellent tool, power ratios suffer
from being aspect-dependent \citep{2007arXiv0708.1518J, VV08}. The
work of ME01 suggested a complementary measure of substructure which
does not depend on projected perspective. They found hard-band
(2.0-9.0 keV) temperatures were $\sim 20\%$ hotter than broad-band
(0.5-9.0 keV) temperatures. This result can be interpreted in several
ways. One interpretation is that the cooler broad-band temperature is
caused by unresolved accreting cool subclusters which are contributing
significant amounts of line emission to the soft-band ($E < 2$
keV). This effect has been studied and confirmed by
\cite{2004MNRAS.354...10M} and \cite{2006ApJ...640..710V} using
simulated {\it Chandra} and {\textit{XMM-Newton}} spectra. The other
way to view this temperature ratio skewing is that a hotter hard-band
temperature is being caused by shock heating from accretion.

ME01 suggested that this temperature skewing, and consequently the
fingerprint of merging, could be detected utilizing the energy
resolution and soft-band sensitivity of {\it Chandra}. They proposed
selecting a sufficiently large sample of clusters covering a broad
dynamical range, fitting a single-component temperature to the hard
band and broad-band, and then checking for a net skew above unity in
the hard-band to broad-band temperature ratio.

In this paper we present the findings of just such a temperature-ratio
test using {\it Chandra} archival data. We find the hard-band
temperature exceeds the broad-band temperature, on average, by
$\sim16\%$ in multiple flux-limited samples of X-ray clusters from the
{\it Chandra} archive. This mean excess is somewhat weaker than the
$20\%$ predicted by ME01, but is significant at the $12\sigma$ level
nonetheless. Hereafter, we refer to the hard-band to broad-band
temperature ratio as $T_{HBR}$. We also find that non-cool core
systems and mergers tend to have higher values of $T_{HBR}$. This
study suggests that $T_{HBR}$ is an indicator of a cluster's temporal
proximity to the most recent merger event.

This paper proceeds in the following manner. In \S\ref{sec:selection}
we outline sample-selection criteria and {\it Chandra}
observations selected under these criteria. Data reduction and
handling of the X-ray background is discussed in
\S\ref{sec:data}. Spectral extraction is discussed in
\S\ref{sec:extraction} while fitting and simulated spectra are
discussed in \S\ref{sec:specan}. Results and discussion of our
analysis are presented in \S\ref{sec:r&d}. A summary of our work
is presented in \S\ref{sec:summary}. For this work we have assumed a
flat $\Lambda$CDM Universe with cosmology $\Omega_{M} = 0.3$,
$\Omega_{\Lambda} = 0.7$, and $H_{0} = 70$ km s$^{-1}$ Mpc$^{-1}$. All
quoted uncertainties are at the 1.6$\sigma$ level (90\% confidence).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sample Selection} \label{sec:selection}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Our sample is selected from observations publicly available in the
{\it Chandra} X-ray Telescope's Data Archive (CDA). Our initial
selection pass came from the {\textit{ROSAT}} Brightest Cluster Sample
\citep{1998MNRAS.301..881E}, RBC Extended Sample
\citep{2000MNRAS.318..333E}, and {\textit{ROSAT}} Brightest 55 Sample
\citep{1990MNRAS.245..559E, 1998MNRAS.298..416P}. The portion of our
sample at $z \gtrsim 0.4$ can also be found in a combination of the
{\textit{Einstein}} Extended Medium Sensitivity Survey
\citep{1990ApJS...72..567G}, North Ecliptic Pole Survey
\citep{2006ApJS..162..304H}, {\textit{ROSAT}} Deep Cluster Survey
\citep{1995ApJ...445L..11R}, {\textit{ROSAT}} Serendipitous Survey
\citep{1998ApJ...502..558V}, and Massive Cluster Survey
\citep{2001ApJ...553..668E}. We later extended our sample to include
clusters found in the REFLEX Survey \citep{2004A&A...425..367B}. Once
we had a master list of possible targets, we cross-referenced this
list with the CDA and gathered observations where a minimum of
$R_{5000}$ (defined below) is fully within the CCD field of
view.

$R_{\Delta_c}$ is defined as the radius at which the average cluster
density is $\Delta_c$ times the critical density of the Universe,
$\rho_c=3H(z)^2/8\pi G$. For our calculations of $R_{\Delta_c}$ we
adopt the relation from \cite{2002A&A...389....1A}:
\begin{eqnarray}
R_{\Delta_c} &=& 2.71 \mathrm{~Mpc~}
\beta_T^{1/2}
\Delta_{\mathrm{z}}^{-1/2}
(1+z)^{-3/2}
\left(\frac{kT_X}{10 \mathrm{~keV}}\right)^{1/2}\\
\Delta_z &=& \frac{\Delta_c \Omega_M}{18\pi^2\Omega_z} \nonumber \\
\Omega_z &=& \frac{\Omega_M (1+z)^3}{[\Omega_M
(1+z)^3]+[(1-\Omega_M-\Omega_{\Lambda})(1+z)^2]+\Omega_{\Lambda}} \nonumber
\end{eqnarray}
where $R_{\Delta_c}$ is in units of $h_{70}^{-1}$, $\Delta_c$ is
the assumed density contrast of the cluster at $R_{\Delta_c}$, and
$\beta_T$ is a numerically determined, cosmology-independent
($\lesssim \pm 20\%$) normalization for the virial relation $GM/2R =
\beta_TkT_{vir}$. We use $\beta_T = 1.05$ taken from
\cite{1996ApJ...469..494E}.

The result of our CDA search is a total of 374 observations of which
we use 244 for 193 clusters. The bolometric ($E = 0.1-100$ keV)
luminosities, $L_{bol}$, for our sample clusters plotted as a function of
redshift are shown in Figure \ref{fig:lx_z}. These $L_{bol}$ values
are calculated from our best-fit spectral models and are limited to
the region of the spectral extraction (from $R=70$ kpc to
$R=R_{2500}$, or $R_{5000}$ in the cases where no $R_{2500}$ fit was
possible).

Basic properties of our sample are listed in Table
\ref{tab:sample}. For the sole purpose of defining extraction regions
based on fixed overdensities as discussed in \S\ref{sec:extraction},
fiducial temperatures and redshifts were taken from the Ph.D. thesis
of Don
Horner\footnote{http://asd.gsfc.nasa.gov/Donald.Horner/thesis.html}
(all redshifts confirmed with NED\footnote{http://nedwww.ipac.caltech.edu/}).
We will show later the {\it ASCA} temperatures are
sufficiently close to the {\it Chandra} temperatures that $R_{\Delta_c}$
is reliably estimated within 20\%. Note that $R_{\Delta_c}$ is only
proportional to $T^{1/2}$, so a 20\% error in the temperature leads to
only a 10\% error in $R_{\Delta_c}$, which in turn affects our final
results imperceptibly. For clusters not listed in Horner's thesis, we
used a literature search to find previously measured temperatures. If
no published value could be located, we measured the global temperature by
recursively extracting a spectrum in the region 0.1 $< r <$ 0.2
$R_{500}$ fitting a temperature and recalculating $R_{500}$. This
process was repeated until three consecutive iterations produced
$R_{500}$ values which differed by $\leq 1\sigma$. This method of
temperature determination has been employed in other studies, see
\cite{2006MNRAS.tmp.1068S} and \cite{2006ApJS..162..304H} as
examples.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{{\it Chandra} Data}\label{sec:data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Reprocessing and Reduction}\label{sec:reprocessing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

All datasets were reduced utilizing the {\it Chandra} Interactive Analysis of
Observations package ({\tt CIAO}) and accompanying Calibration
Database ({\tt CALDB}). Using {\tt CIAO v3.3.0.1} and {\tt
CALDB v3.2.2}, standard data analysis was followed for each
observation to apply the most up-to-date time-dependent gain
correction and charge transfer inefficiency (CTI) correction (when
appropriate) \citep{2000ApJ...534L.139T}.

Point sources were identified in an exposure-corrected events file
using the adaptive wavelet tool {\tt wavdetect}
\citep{2002ApJS..138..185F}. All point sources were then visually
confirmed. A $2\sigma$ region surrounding each point source was
automatically output by {\tt wavdetect} to define an exclusion
mask. We then added regions for point sources which were missed by
{\tt wavdetect} and deleted regions for spuriously detected
``sources''. Spurious sources are typically faint CCD features (chip
gaps and chip edges) not fully removed after dividing by the exposure
map. This process results in an events file (at "level 2") that has
been cleaned of point sources.

To check for contamination from background flares or periods of
excessively high background, light curve analyses were performed using
Maxim Markevitch's contributed {\tt CIAO} script {\tt
lc\_clean.sl}\footnote{http://cxc.harvard.edu/contrib/maxim/acisbg/}.
Periods with count rates $\geq 3\sigma$ and/or a factor $\geq 1.2$ of
the mean background level of the observation were removed from the
good time interval file. As prescribed by Markevitch's
cookbook\footnote{http://cxc.harvard.edu/contrib/maxim/acisbg/COOKBOOK},
ACIS front-illuminated (FI) chips were analyzed in the $0.3-12.0$ keV
range, and for the ACIS back-illuminated (BI) chips, $2.5-7.0$ keV
energy range.

When a FI and BI chip were both active during an observation, we
compared light curves from both chips to detect long duration,
soft-flares which can go undetected on the FI chips but show up on the
BI chips. While rare, this class of flare must be filtered out of the
data as it introduces a spectral component which artificially
increases the best-fit temperature via a high energy tail. We find
evidence for a long duration soft flare in the observations of Abell
1758 \citep{2004ApJ...613..831D}, CL J2302.8+0844, and IRAS
09104+4109. These flares were handled by removing the time period of
the flare from the GTI file.

Defining the cluster ``center'' is essential for the later purpose of
excluding cool cores from our spectral analysis (see
\S\ref{sec:extraction}). To determine the cluster center, we
calculated the centroid of the flare cleaned, point-source
free level-2 events file filtered to include only photons in the
$0.7-7.0$ keV range. Before centroiding, the events file is
exposure-corrected and ``holes'' created by excluding point sources
are filled using interpolated values taken from a narrow annular region just
outside the hole (``holes'' are not filled during spectral extraction
discussed in \S\ref{sec:extraction}). Prior to centroiding we define
the emission peak by heavily binning the image, finding the peak value
within a circular region extending from the peak to the chip edge
(defined by the radius $R_{max}$), reducing $R_{max}$ by 5\%,
reducing the binning by a factor of two, and finding the peak
again. This process is repeated until the image is unbinned (binning
factor of one). We then return to an unbinned image with an aperture
centered on the emission peak with a radius $R_{max}$ and find the
centroid using {\tt CIAO}'s {\tt dmstat}. The centroid, ($x_c$,$y_c$),
for a distribution of $N$ good pixels with coordinates ($x_i$,$y_j$)
and values f($x_i$,$y_j$) is defined as:
\begin{eqnarray}
Q &=& \sum_{i,j=1}^N f(x_i,y_i) \\
x_c &=& \frac{\sum_{i,j=1}^N x_i \cdot f(x_i,y_i)}{Q} \nonumber \\
y_c &=& \frac{\sum_{i,j=1}^N y_i \cdot f(x_i,y_i)}{Q}. \nonumber
\end{eqnarray}

If the centroid was within 70 kpc of the emission peak the emission
peak was selected as the center, otherwise the centroid was used
as the center. This selection was made to ensure all ``peaky'' cool
cores are at the cluster center thus maximizing their exclusion later
in our analysis. All cluster centers are verified by-eye.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{X-ray Background} \label{sec:background}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Because we measured a global cluster temperature, specifically looking
for a temperature ratio shift in energy bands which can be
contaminated by the high-energy particle background or the soft local
background, it was important to carefully analyze the background and
subtract it from our resulting spectra. Below we outline three steps
taken in handling the background: customization of blank-sky backgrounds,
re-normalization of these backgrounds for variation of hard-particle
count rates, and fitting of soft background residuals.

We used the blank-sky observations of the X-ray background from
\cite{2001ApJ...562L.153M} and supplied within the CXC {\tt
CALDB}. First, we compared the flux from the diffuse soft X-ray
background of the {\textit{ROSAT}} All-Sky Survey ({\it RASS})
combined bands $R12$, $R45$, and $R67$ to the 0.7-2.0 keV flux in each
extraction aperture for each observation. {\it RASS} combined bands
give fluxes for energy ranges of 0.12-0.28 keV, 0.47-1.21 keV, and
0.76-2.04 keV respectively corresponding to $R12$, $R45$, and $R67$. For
the purpose of simplifying subsequent analysis, we discarded
observations with an $R45$ flux $\geq 10\%$ of the total cluster X-ray
flux.

The appropriate blank-sky dataset for each observation was
selected from the {\tt CALDB}, reprocessed exactly as the
observation was, and then reprojected using the aspect solutions provided
with each observation. For observations on the ACIS-I array, we
reprojected blank-sky backgrounds for chips I0-I3 plus chips S2 and/or
S3. For ACIS-S observations, we created blank-sky backgrounds only for
the target chip plus chips I2 and/or I3. The additional off-aimpoint
chips were included only if they were active during the observation
and had available blank-sky data sets for the observation time
period. Off-aimpoint chips were cleaned for point sources and diffuse
sources using the method outlined in \S\ref{sec:reprocessing}.

The additional off-aimpoint chips were included in data reduction
since they contain data which is farther from the cluster center and
are therefore more useful in analyzing the observation background. For
observations which did not have a matching off-aimpoint blank-sky
background in the CALDB a source-free region of the active chips is
located and used for background normalization. To normalize the hard
particle component we measured fluxes for identical regions in the
blank-sky field and target field in the 9.5-12.0 keV range. The
effective area of the ACIS arrays above 9.5 keV is zero and thus the
collected photons there are exclusively from the particle background.

A histogram of the ratios of the 9.5-12.0 keV count rate from an
observation's off-aimpoint chip to that of the observation specific
blank-sky background are presented in Figure \ref{fig:bgd}. The
majority of the observations are in agreement to $\lesssim 20\%$ of
the blank-sky background rate, which is small enough to not affect our
analysis. Even so, we re-normalized all blank-sky backgrounds to match
the observed background.

Normalization brings the observation background and blank-sky
background into agreement for $E > 2$ keV, but even after
normalization, typically, there may exist a soft excess/deficit
associated with the spatially varying soft Galactic
background. Following the technique detailed in
\cite{2005ApJ...628..655V} we constructed and fit soft residuals for
this component. For each observation we subtracted a spectrum of the
blank-sky field from a spectrum of the off-aimpoint field to create a
soft residual. The residual was fit with a solar abundance, zero
redshift {\tt MeKaL} model \citep{1985A&AS...62..197M,
1986A&AS...65..511M, 1992SRON, 1995ApJ...438L.115L} where the
normalization was allowed to be negative. The resulting best-fit
temperatures for all of the soft residuals identified here were
between 0.2-1.0 keV, which is in agreement with results of
\cite{2005ApJ...628..655V}. The model normalization of this background
component was then scaled to the cluster sky area. The re-scaled
component was included as a fixed background component during fitting
of a cluster's spectra.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Spectral Extraction} \label{sec:extraction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The simulated spectra calculated by ME01 were analyzed in the energy
ranges $0.5-9.0$ keV and $2.0_{rest}-9.0$ keV, but to make a reliable
comparison with {\it Chandra} data we restricted our focus to a
broad energy band, $0.7-7.0$ keV, and a hard energy band,
$2.0_{rest}-7.0$ keV. We excluded data below $0.7$ keV to avoid the
effective area and quantum efficiency variations of the ACIS
detectors, and excluded energies above $7.0$ keV in which diffuse source
emission is dominated by the background and {\it Chandra}'s
effective area is small. We also accounted for cosmic redshift by
shifting the lower energy boundary of the hard-band from 2.0 keV to
$2.0/(1+z)$ keV (henceforth, assume the 2.0 keV cut is in the rest
frame).

ME01 calculated the relation between $T_{0.5-9.0}$ and $T_{2.0-9.0}$
using apertures of $R_{200}$ and $R_{500}$ in size. While it is
trivial to calculate a temperature out to $R_{200}$ or $R_{500}$ for
a simulation, such a measurement at these scales is extremely
difficult with {\it Chandra} observations (see \cite{2005ApJ...628..655V} for
a detailed example). Thus, we chose to extract spectra from regions
with radius $R_{5000}$ and $R_{2500}$ when possible. Clusters analyzed
only within $R_{5000}$ are denoted in Table \ref{tab:sample} by a
dagger.

The cores of some clusters are dominated by gas at $< T_{vir}/2$ which
can greatly affect the global temperature, therefore we excised the
central 70 kpc of each aperture. These excised apertures are denoted
by ``-CORE'' in the text. Recent work by \citealt{2007astro.ph..3504M}
has shown excising 0.15 $R_{500}$ rather than a static 70 kpc reduces
scatter in mass-observable scaling relations. But such a reduction
does not affect this work as the conclusions drawn from our spectral
analysis are strongly related to the uncertainties of $T_{2.0-7.0}$
and not on the best-fit value of $T_{0.7-7.0}$ where the effect of a
cool core is the strongest.

Although some clusters are not circular in projection, but rather are
elliptical or asymmetric, we found that assuming sphericity and
extracting spectra from a circular annulus did not significantly
change the best-fit values. For another such example see
\cite{2005MNRAS.359.1481B}.

After defining annular apertures, we extracted source spectra from the
target cluster and background spectra from the corresponding
normalized blank-sky dataset. By standard {\tt CIAO} means we created
effective area functions (ARF files) and redistribution matrices (RMF
files) for each cluster using a flux-weighted map (WMAP) across the
entire extraction region. The WMAP was calculated over the energy
range 0.3-2.0 keV to weight calibrations that vary as a function of
position on the chip. Each spectrum was then binned to contain a
minimum of 25 counts per channel.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Spectral Analysis} \label{sec:specan}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fitting} \label{sec:fitting}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Spectra were fit with {\tt XSPEC 11.3.2ag} \citep{1996ASPC..101...17A}
using a single-temperature {\tt MeKaL} model in combination with the
photoelectric absorption model {\tt WABS} \citep{1983ApJ...270..119M}
to account for Galactic absorption. Galactic absorption values,
$N_{HI}$, are taken from \cite{1990ARA&A..28..215D}. The potentially
free parameters of the absorbed thermal model are
$N_{HI}$, X-ray temperature ($T_{X}$), metal abundance normalized to Solar
(elemental ratios taken from \cite{1989GeCoA..53..197A}), and a
normalization proportional to the integrated emission measure of the
cluster. Results from the fitting are presented in Table
\ref{tab:r2500specfits} and Table \ref{tab:r5000specfits}. No
systematic error is added during fitting and thus all quoted errors
are statistical only. Clusters with multiple independent observations
had their spectra fit simultaneously and are denoted by a dagger.

Additional statistical error was introduced into the fits because of
uncertainty associated with the soft local background component
discussed in \S\ref{sec:background}. To estimate the sensitivity of
our best-fit temperatures to this uncertainty, we used the differences
between $T_{X}$ for a model using the best-fit soft background
normalization and $T_{X}$ for models using $\pm1\sigma$ of the soft
background normalization. The statistical uncertainty of the original
fit and the additional uncertainty inferred from the range of
normalizations to the soft X-ray background component were then added
in quadrature to produce a final error. In all cases this additional
background error on the temperature was less than 10\% of the total
statistical error and therefore represents a minor inflation of the
error budget.

When comparing fits with fixed Galactic column density with those
where it was a free parameter, we found that neither the goodness of
fit per free parameter nor the best-fit $T_{X}$ were significantly
different. Thus, $N_{HI}$ was fixed at the Galactic value with the
exception of three cases: Abell 399 \citep{2004MNRAS.351.1439S}, Abell
520, and Hercules A. For these three clusters $N_{HI}$ is a free
parameter. In all fits the metal abundance was a free parameter.

After fitting we rejected several datasets as their best-fit $T_{2.0-7.0}$
had no upper bound in the 90\% confidence interval and thus were
insufficient for our analysis. All fits for the clusters Abell 781,
Abell 1682, CL J1213+0253, CL J1641+4001, IRAS 09104+4109, Lynx E,
MACS J1824.3+4309, MS 0302.7+1658, and RX J1053+5735 were rejected. We
also removed Abell 2550 from our sample after finding it to be a an
anomalously cool ($T_{X} \sim$ 2 keV) ``cluster''. In fact it is a
line-of-sight set of groups as discussed by
\cite{2004cgpc.sympE..31M}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Simulated Spectra}\label{sec:simulated}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To quantify the effect a second, cooler gas component would have on the fit
of a single-component spectral model, we created an ensemble of simulated
spectra for each real spectrum in our entire sample using {\tt
XSPEC}. With these simulated spectra we sought to answer the question:
Given the count level in each observation of our sample, how bright
must a second temperature component be for it to affect the observed
temperature ratio, $T_{HBR}$? Put another way, we asked at what flux
ratio a second gas phase produces a temperature ratio, $T_{HBR}$, of
greater than unity at the 1$\sigma$ level.

We began by adding the observation-specific background to a convolved,
absorbed thermal model with two temperature components for a time
period equal to the observation exposure time and adding Poisson
noise. For each realization of an observation's simulated spectrum we
defined the primary component to have the best-fit temperature and
metallicity of the $R_{2500-\mathrm{CORE}}$ (or $R_{5000-\mathrm{CORE}}$
if no $R_{2500-\mathrm{CORE}}$ fit was performed), 0.7-7.0 keV fit, and
we stepped the secondary component temperature over the values 0.5,
0.75, and 1.0 keV. The metallicity of the secondary component was
fixed and set equal to the metallicity of the primary component.

We adjusted the normalization of the simulated two-component spectra to
achieve equivalent count rates to those in the real spectra. We set
the primary component normalization to $K_1 = \xi \cdot K_{bf}$ where
$K_{bf}$ is the best-fit normalization of the appropriate
0.7-7.0 keV fit and $\xi$ is a preset factor having the values 0.8,
0.85, 0.9, 0.95, 0.96, 0.97, 0.98, and 0.99. The secondary component
normalization was determined through an iterative process to make real
and simulated spectral count rates match.

We also simulated a control sample of single-temperature models. The
control sample is a simulated version of the best-fit model. This
control provides us with a statistical test of how often the actual
hard-component temperature might differ from a broad-band temperature
fit if calibration effects are under control.

For each observation, we have 59 total simulated spectra: 35
single-temperature control spectra and 24 two-component simulated
spectra (three second temperatures, each with 8 different $\xi$). Our
resulting ensemble of simulated spectra contains $11,387$
spectra. After generating all the spectra we followed the same fitting
routine detailed in \S\ref{sec:fitting}.

There are three important results from the analysis of these simulated
spectra:
\begin{enumerate}
\item In the control sample, a single-temperature model rarely
($\sim 2\%$ of the time) gives a significantly different $T_{0.7-7.0}$ and
$T_{2.0-7.0}$. The weighted average for the control sample is 1.001$\pm
0.002$ and the standard deviation is $\pm0.06$. The $T_{HBR}$
distribution for the control sample appears to have an intrinsic width
which is likely associated with statistical noise of fitting in {\tt
XSPEC} (Dupke, private communication). This result indicates our
remaining set of observations is statistically sound: our finding that
$T_{HBR}$ significantly differs from 1.0 cannot result from
statistical fluctuations alone.
\item A second temperature component representing $> 10\%$ of the total
emission must be present in order to obtain $T_{HBR} > 1.1$ as we find
in the real data.
\item As redshift increases, gas cooler than 1.0 keV is slowly
redshifted out of the observable X-ray band. As expected, we find from
our simulated spectra that for $z \geq 0.6$, $T_{HBR}$ is no longer
statistically distinguishable from unity. For the 14 clusters with $z
\geq 0.6$ in our real sample we can safely conclude we are not
overestimating the contribution of cool gas to the spectra and we are
most likely underestimating the temperature inhomogeneity.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and Discussion} \label{sec:r&d}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Temperature Ratios} \label{sec:tfresults}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

For each cluster we have measured a temperature ratio $T_{HBR}$ =
$T_{2.0-7.0}$/$T_{0.7-7.0}$. We find that the mean $T_{HBR}$ for our
entire sample is greater than unity at more than $12\sigma$
significance. The weighted mean values for our sample are shown in
Table \ref{tab:wavg}. Presented in Figure  \ref{fig:ftx} are the binned
weighted means and raw $T_{HBR}$ values for $R_{2500-\mathrm{CORE}}$,
$R_{5000-\mathrm{CORE}}$, and the simulated control sample. The peculiar
points with $T_{HBR} <$ 1 are all statistically consistent with
$T_{HBR}$ = 1. The presence of clusters with $T_{HBR}$ = 1 suggests
that systematic calibration uncertainties are not the sole reason for
deviations of $T_{HBR}$ from 1. We also find that the temperature
ratio does not depend on the best-fit broad-band temperature, and that
the observed dispersion of $T_{HBR}$ is greater than the predicted
dispersion arising from systematic uncertainties.

The uncertainty associated with each value of $T_{HBR}$ is dominated by
the larger error in $T_{2.0-7.0}$, and on average, $\Delta T_{2.0-7.0} \approx
2.3\Delta T_{0.7-7.0}$. This error interval discrepancy naturally results
from excluding the bulk of a cluster's emission which occurs below 2
keV. While choosing a temperature-sensitive cut-off energy for the
hard-band (other than 2.0 keV) might maintain a more consistent
error budget across our sample, we do not find any systematic trend in
$T_{HBR}$ or the associated errors with cluster temperature.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Systematics} \label{sec:sys}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In this study we have found the average value of $T_{HBR}$ is significantly
greater than one and that $\sigma_{HBR} > \sigma_{control}$, the
latter result being robust against systematic uncertainties. As
predicted by ME01, both of these results are expected to arise
naturally from hierarchical formation of clusters. But systematic
uncertainty related to {\it Chandra} instrumentation or other sources could
shift the average value of $T_{HBR}$ one would get from ``perfect'' data. In
this section we consider some additional sources of uncertainty.

First, the disagreement between {\it XMM-Newton} and {\it Chandra}
cluster temperatures has been noted in several independent studies,
i.e. \citealt{2005ApJ...628..655V,chanxmmdis}. But the source of this
discrepancy is not well understood and efforts to perform
cross-calibration between {\it XMM-Newton} and {\it Chandra} have thus
far not been conclusive. One possible explanation is poor calibration
of {\it Chandra} at soft X-ray energies which may arise from a
hydrocarbon contaminant on the High Resolution Mirror Assembly (HRMA)
similar in nature to the contaminant on the ACIS detectors
\citep{aciscontaminant}. We have assessed this possibility by looking
for systematic trends in $T_{HBR}$ with time or temperature, as such a
contaminant would most likely have a temperature and/or time
dependence.

As noted in \S\ref{sec:tfresults} and seen in Figure \ref{fig:ftx} we
find no systematic trend with temperature either for the full sample
or for a sub-sample of single-observation clusters with $> 75\%$ of
the observed flux attributable to the source (higher signal-to-noise
observations will be more affected by calibration
uncertainty). Plotted in Figure \ref{fig:sys} is $T_{HBR}$ versus time
for single observation clusters (clusters with multiple observations
are fit simultaneously and any time effect would be washed out) and
where the spectral flux is $> 75\%$ from the source. We find no
systematic trend in $T_{HBR}$ with time, which suggests that if
$T_{HBR}$ is affected by any contamination of {\it Chandra}'s HRMA,
then the contaminant is not changing with time. Our conclusion on this
matter is that the soft calibration uncertainty is not playing a
dominant role in our results.

% Even if the uncertainty in $T_{0.7-7.0}$ were very large and drove
%$T_{HBR}$ systematically down by 10\%, the correlation between clusters with
%the highest significant values of $T_{HBR}$ and their relaxation state would
%persist. It may be the case that we are observing a superposition of
%effects: 1) physics within the cluster associated with mergers and 2)
%uncalibrated soft emission uncertainty.

Aside from instrumental and calibration effects, some other possible
sources of systematic error are signal-to-noise (S/N), redshift
selection, and Galactic absorption. Presented in Figure \ref{fig:sys}
are these three parameters versus $T_{HBR}$. The trend in $T_{HBR}$ with redshift
is expected as the 2.0/(1+$z$) keV hard-band lower boundary nears
convergence with the 0.7 keV broad-band lower boundary at
$z \approx 1.85$. We find no systematic trends with S/N or Galactic
absorption, which might occur if the skew in $T_{HBR}$ were a consequence of
poor count statistics, inaccurate Galactic absorption, or very poor
calibration. Also shown in panel four of Fig. \ref{fig:sys} is the
ratio of $T_{HBR}$ for $R_{2500-\mathrm{CORE}}$ and
$R_{5000-\mathrm{CORE}}$. For every cluster in our sample both apertures
result in $T_{HBR}$ values which are not significantly different from
one another. Our results are robust to changes in aperture size.

Also shown in Figure \ref{fig:sys} is the ratio of {\it ASCA}
temperatures taken from Don Horner's thesis to {\it Chandra}
temperatures derived in this work. The spurious point below 0.5 with
very large error bars is MS 2053.7-0449 which has a poorly
constrained {\it ASCA} temperature of $10.03^{+8.73}_{-3.52}$. Our value of
$\sim 3.5$ keV for this cluster is in agreement with the recent work of
\cite{2007astro.ph..3156M}. Not all our sample clusters have an {\it ASCA}
temperature, but a sufficient number (53) are available to make this
comparison reliable. Apertures used in the extraction of {\it ASCA} spectra
had no core region removed and were substantially larger than
$R_{2500}$. {\it ASCA} spectra were also fit over a broader energy range
(0.6-10 keV) than we use here. Thus, we make the temperature
comparison using our unexcised $R_{2500}$, 0.7-7.0 keV fits as
these get us the closest to replicating the {\it ASCA} apertures and energy
range. Our temperatures are in good agreement with those from {\it ASCA},
but we do note a trend of comparatively hotter {\it Chandra} temperatures for
$T_{Chandra} > 10$ keV. The clusters with $T_{Chandra} > 10$ keV are
Abell 1758, Abell 2163, Abell 2255, and RX J1347.5-1145.

Based on this trend, we test excluding the hottest clusters
($T_{Chandra} > 10$ keV where {\it ASCA} and {\it Chandra} disagree) from our sample.
The mean temperature ratio for $R_{2500-\mathrm{CORE}}$ remains $1.16$ and the error
of the mean increases from $\pm 0.014$ to $\pm 0.015$, while for $R_{5000-\mathrm{CORE}}$
$T_{HBR}$ increases by a negligible $0.9\%$ to $1.15\pm 0.014$. Our results
are not being influenced by the inclusion of hot clusters.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Using $T_{HBR}$ to Select for Relaxation} \label{sec:relax}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Cool Core Versus Non-Cool Core}\label{sec:ccncc}

The process of cluster formation and virialization may robustly result
in the formation of a cool core
\citep{2006ApJ...640..673O,2007arXiv0708.1954B}. Flux-limited surveys
have found the prevalence of CCs to be $34-60\%$ \citep{1997MNRAS.292..419W,
1998MNRAS.298..416P, 2005MNRAS.359.1481B, 2007A&A...466..805C}
depending upon classification criteria, completeness, and possible
selection biases. As discussed in \S\ref{sec:intro}, ME01 give us
reason to believe the observed skewing of $T_{HBR}$ to greater than unity is
related to the dynamic state of a cluster. We thus sought to identify
which clusters in our sample have cool cores (CC), which do not (NCC),
and if the presence or absence of a cool core is correlated to $T_{HBR}$. We
also asked about the number of CC and NCC clusters as a function of
$T_{HBR}$. Recall that we excluded the cool core itself during spectral
extraction.

To identify a CC we extracted spectra for the 50 kpc region
surrounding the cluster center and then defined a temperature
decrement 
\begin{equation}
T_{dec} = T_{50}/T_{cluster}
\label{eqn:tdec}
\end{equation}
where $T_{50}$ is the temperature of the inner 50 kpc and
$T_{cluster}$ is the $R_{2500-\mathrm{CORE}}$ temperature (clusters
without $R_{2500-\mathrm{CORE}}$ fits were excluded from this
analysis). If $T_{dec}$ was 2$\sigma$ less than unity, we defined the
cluster as having a CC, otherwise the cluster was defined as NCC. We
find CCs in 35\% of our sample and when we lessen the significance
needed for CC classification from 2$\sigma$ to 1$\sigma$, we find 46\%
of our sample clusters have CCs. It's important to note the frequency
of CCs in our study is consistent with other more detailed studies of
CC/NCC populations.

When fitting for $T_{50}$ we altered the method outlined
in \S\ref{sec:fitting} to use {\tt XSPEC}'s modified Cash statistic
\citep{1979ApJ...228..939C}, {\tt cstat}, on ungrouped
spectra. This choice was made because the distribution of counts per
bin in low count spectra is not Gaussian but instead
Poisson. As a result, the best-fit temperature using $\chi^2$ is
typically cooler \citep{1989ApJ...342.1207N, 2007A&A...462..429B}. We
have explored this systematic in {\bfseries\em{all}} our fits and
found it to be significant only in the lowest count spectra of the
inner 50 kpc apertures discussed here. But for consistency, we fit all
inner 50 kpc spectra using the modified Cash statistic.

With each cluster classified, we then took cuts in $T_{HBR}$ 
and asked how many CC and NCC clusters were above these cuts. 
Figure \ref{fig:cc_ncc_bin} shows the normalized number of CC and NCC
clusters as a function of cuts in $T_{HBR}$. If $T_{HBR}$ were insensitive to
the dynamical state of a cluster we expect, for normally
distributed $T_{HBR}$ values, to see the number of CC and NCC clusters
decreasing in the same way. However, the number of CC clusters falls off
more rapidly than the number of NCC clusters. This effect
is dramatically reduced -- as expected -- if the core is included.
If the presence of a CC is indicative of a cluster's advancement
towards complete virialization, then the significantly steeper
fall-off of CC clusters as a function of $T_{HBR}$ that we observe indicates
higher values of $T_{HBR}$ are associated with a less relaxed state. This
result is insensitive to our choice of significance level in the core
classification.

Because of the CC/NCC definition we selected, our identification of
CCs and NCCs was only as robust as the errors on $T_{50}$ allowed. One can
thus ask the question, did our loose definition bias us towards
finding more NCCs than CCs? To explore this question we simulated 20
spectra for each observation following the method outlined in
\S\ref{sec:simulated} for the control sample but using the inner 50
kpc spectral best-fit values as input. For each simulated spectrum we
calculated a temperature decrement (Eq. \ref{eqn:tdec}) and
re-classified the cluster as having a CC or NCC. Using the new set of
mock classifications we assigned a reliability factor, $\psi$, to each
real classification which is simply the fraction of mock
classifications which agree with the real classification. A value of
$\psi = 1.0$ indicates complete agreement, and $\psi = 0.0$ indicating no
agreement. When we removed clusters with $\psi < 0.9$ and repeated the
analysis above, we found no significant change in the number of CC
clusters as a function of $T_{HBR}$.

Recall that the coolest ICM gas is being redshifted out of the
observable band as $z$ increases and becomes a significant effect at
$z \geq 0.6$ (\S\ref{sec:simulated}). Thus, we are likely not detecting
``weak'' CCs in the highest redshift clusters of our sample and
consequently these cores are classified as NCCs artificially increasing
the NCC population. When we excluded the 14 clusters at $z \geq 0.6$
from this core classification analysis we found no significant change
in our results.

\subsubsection{Mergers Versus Non-Mergers}\label{sec:merge}

To further investigate trends in $T_{HBR}$ we now examine a subclass of
clusters with $T_{HBR} > 1.1$ at the 1$\sigma$ level and which are
identified in Table \ref{tab:tf11}. $T_{HBR} > 1.1$ is an arbitrary
threshold selected to limit the number of clusters to which we pay
individual attention, but which is still representative of mid to high
$T_{HBR}$ values. All of these 29 clusters have core classifications 
with $\psi > 0.9$. We define a further subclass of these culled
clusters which have been identified as mergers in the literature. From Figure
\ref{fig:ftx_tx} and Table \ref{tab:tf11} we can see clusters
exhibiting the highest significant values of $T_{HBR}$ tend to be ongoing or
recent mergers. At the 2$\sigma$ level, we find increasing values of
$T_{HBR}$ favor merger systems with NCCs over relaxed, CC clusters. Mergers
have left a spectroscopic imprint on the ICM which is predicted by
ME01 and which we observe in our sample.

Of the 29 clusters with $T_{HBR}$ significantly $> 1.1$, only six have
CCs. Three of those, MKW3S, 3C 28.0, and RX J1720.1+2638 have their
apertures centered on the bright, dense cores in confirmed
mergers. Two more clusters, Abell 2384 and RX J1525+0958, while
not confirmed mergers, have morphologies which are consistent with
powerful ongoing mergers. Abell 2384 has a long gas tail extending out
to a gaseous clump which has presumably passed through the cluster
recently. RXJ1525 has a core which is shaped like an arrowhead and is
reminiscent of the bow shock seen in 1E0657-56. Abell 907 is the
remaining CC of the six listed. It has no signs of being a merger
system but the highly compressed surface brightness contours to the
west of the core are indicative of a prominent cold front which are
tell-tale signs of a subcluster merger event
\citep{2007PhR...443....1M}.

The unclassified systems -- RX J0439.0+0715, MACS J2243.3-0935, MACS
J0547.0-3904, ZWCL 1215, MACS J2311+0338, and Abell 267 -- have NCCs and
X-ray morphologies consistent with an ongoing or post-merger
scenario. Two clusters, Abell 1204 and MACS J1427.6-2521, show no
signs of recent or ongoing merger activity, however, they reside at
the bottom of the arbitrary $T_{HBR}$ cut, and as evidenced by Abell 401 and
Abell 1689, exceptional spherical symmetry is no guarantee of
relaxation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Conclusions}\label{sec:summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We have explored the band dependence of the inferred X-ray temperature
of the ICM for 193 well-observed ($N_{counts} > 1500$) clusters of
galaxies selected from the {\it Chandra} Data Archive.

We extracted spectra from the annulus between $R=70$ kpc and
$R=R_{2500}$, $R_{5000}$ for each cluster. We compared the X-ray
temperatures inferred for single-component fits to global spectra
when the energy range of the fit was 0.7-7.0 keV (broad) and when the
energy range was $2.0/(1+z)$-7.0 keV (hard). We found that, on
average, the hard-band temperature is significantly higher than
the broad-band temperature. For the $R_{2500-\mathrm{CORE}}$ aperture we measured a
weighted average of $T_{HBR} = 1.16$ with $\sigma = \pm 0.10$ and
$\sigma_{mean} = \pm 0.01$, for the $R_{5000-\mathrm{CORE}}$ aperture,
$T_{HBR} = 1.14$ with $\sigma = \pm 0.12$ and $\sigma_{mean} = \pm
0.01$. We also found no systematic trends with signal-to-noise,
redshift selection, or Galactic absorption in the value of $T_{HBR}$
or the dispersion of $T_{HBR}$.

In addition, we simulated an ensemble of $11,387$ observation-specific
control spectra and spectra with two thermal components. From analysis
of these simulations we found the observed scatter, $\sigma_{HBR}$, is
consistent with the presence of unresolved cool ($T_X < 1.0$ keV) gas,
and we also found the observational scatter is greater than the
statistical scatter, $\sigma_{control}$. As discussed in ME01 both of
these results are consistent with the process of hierarchical cluster
formation.

Upon further exploration, we found that $T_{HBR}$ is enhanced
preferentially for clusters which are known merger systems and for
clusters without cool cores. Clusters with temperature decrements in
their cores (known as cool-core clusters) tend to have best-fit
hard-band temperatures that are consistently closer to their
best-fit broad-band temperatures. The correlation of $T_{HBR}$ with
the type of cluster core is insensitive to our choice of
classification scheme and is robust against redshift effects. Our
results qualitatively support the finding by ME01 that the temperature
ratio $T_{HBR}$ might therefore be useful for statistically
quantifying the degree of cluster relaxation/virialization.

An additional robust test of the ME01 finding should be made with
simulations by tracking $T_{HBR}$ during hierarchical assembly of a
cluster. If $T_{HBR}$ is tightly correlated with a cluster's degree of
relaxation then it, along with other methods of substructure measure,
may provide a powerful metric for predicting (and therefore reducing)
a cluster's expected deviation from mean mass-scaling relations. The
task of reducing scatter in scaling relations will be very important
if we are to reliably and accurately measure the mass of clusters.

%%%%%%%%%%%%%%%%%%%
% Acknowledgments %
%%%%%%%%%%%%%%%%%%%

\acknowledgements
Kenneth Cavagnolo was supported in this work by the National
Aeronautics and Space Administration through {\it Chandra} X-ray
Observatory Archive grants AR-6016X and AR-4017A, with additional
support from a start-up grant for Megan Donahue from Michigan State
University. Megan Donahue and Michign State University acknowledge
support from the NASA LTSA program NNG-05GD82G. The {\it Chandra}
X-ray Observatory Center is operated by the Smithsonian Astrophysical
Observatory for and on behalf of the National Aeronautics Space
Administration under contract NAS8-03060. This research has made use
of software provided by the {\it Chandra} X-ray Center (CXC) in the
application packages CIAO, ChIPS, and Sherpa. We thank Alexey
Vikhlinin for helpful insight and expert advice, attendees of the
``Eight Years of Science with {\it Chandra} Calibration
Workshop'' for stimulating discussion regarding {\it XMM}-{\it
Chandra} cross-calibration, and especially Keith Arnaud for personally
providing support/advice for using {\tt XSPEC}. This research has made use
of the NASA/IPAC Extragalactic Database (NED) which is operated by the
Jet Propulsion Laboratory, California Institute of Technology, under
contract with the National Aeronautics and Space Administration. This
research has also made use of NASA's Astrophysics Data System. {\it
ROSAT} data and software were obtained from the High Energy
Astrophysics Science Archive Research Center (HEASARC), provided by
NASA's Goddard Space Flight Center.

%%%%%%%%%%%%%%%%
% Bibliography %
%%%%%%%%%%%%%%%%

\bibliography{cavagnolo}

%%%%%%%%%%%%%%%%%%%%%
% Figures and Tables%
%%%%%%%%%%%%%%%%%%%%%

\input{figs.tex}

%%%%%%%%%%
% Tables %
%%%%%%%%%%

\LongTables
\clearpage
\input{sample.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Comparison of THBR for wavg %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\input{tfwav.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Clusters with thfr > 1.1 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{cc_nccdesc.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% R2500 Spectral fit results %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\input{r2500.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% R5000 Spectral fit results %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\input{r5000.tex}

%%%%%%%%%%%%%%%%%%%%
% End the document %
%%%%%%%%%%%%%%%%%%%%

\end{document}
