%%%%%%%%%%
% Header %
%%%%%%%%%%
%\documentclass[12pt, preprint]{aastex}
%\documentclass[onecolumn]{emulateapj}
\documentclass{emulateapj}
\usepackage{apjfonts}
\usepackage{graphicx}
\usepackage{here,lscape}
\shorttitle{X-ray Band Dependent Temperature}
\shortauthors{Cavagnolo et al.}
\bibliographystyle{apj}
\newcommand{\tf}{T$_{HFR}$ }
\newcommand{\hard}{T$_{2.0-7.0}$ }
\newcommand{\full}{T$_{0.7-7.0}$ }
\newcommand{\tx}{T$_{X}$}

%%%%%%%%%%%%%%%%%%%%%
% Title and Authors %
%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\title{X-ray Band Dependence of X-ray \\
	Temperatures in Galaxy Clusters}
\author{Kenneth W. Cavagnolo\altaffilmark{1,2}, Megan
Donahue\altaffilmark{1}, G. Mark Voit\altaffilmark{1}, and Ming
Sun\altaffilmark{1}}
\altaffiltext{1}{Department of Physics and Astronomy, Michigan State
University, BPS Building, East Lansing, MI 48824}
\altaffiltext{2}{cavagnolo@pa.msu.edu}

%%%%%%%%%%%%
% Abstract %
%%%%%%%%%%%%

\begin{abstract}

We explore the band-dependence of the inferred X-ray temperature of
the intracluster medium (ICM) for 179 well-observed ($N_{photons} >
1500$) clusters of galaxies selected from the Chandra data archive. If
the hot gas in a cluster is nearly isothermal in the projected region
of interest, the  X-ray temperature inferred from a broad-band
(0.7-7.0 keV) spectrum should be identical to the X-ray temperature
inferred from a hard-band (2.0-7.0 keV) spectrum. However,  if there are
excess soft X-ray photons contributed by cooler lumps of gas or by
non thermal processes, the temperature of a best-fit 
single-temperature thermal model will be cooler for a broad-band
spectrum than for a hard-band spectrum. Such a diagnostic may
indicate such contamination even when the X-ray spectrum itself may
not have sufficient signal-to-noise to resolve multiple temperature
components. To test this possible diagnostic, we extract X-ray spectra
from annular regions between $R=70$ kpc and $R=R_{2500}$, $R_{5000}$ for
each cluster in our archival sample. We compare the X-ray temperatures
inferred for single-temperature fits of global spectra when the energy
range of the fit is 0.7-7.0 keV (full) and when the energy range is
2.0/(1+z)-7.0 keV (hard). We find, on average, the hard-band
temperature is significantly higher than the full-band 
temperature. Upon further exploration, we find the ratio
\tf = \hard/\full is enhanced preferentially for clusters which are
known merger systems and for clusters which are isothermal. Clusters
with temperature decrements in their cores (known as cool-core
clusters) tend to have best-fit hard-band temperatures that are
statistically consistent with their best fit full-band
temperatures. We show, using simulated spectra, that this test is
sensitive to cool components with emission measures $> 4\%$ of the
hot component for $2.0 \leq $\tx$ \leq 15.0$ keV and for $z < 0.6$.

We show this test is relatively insensitive to second components
in an individual cluster when the total counts in the spectrum are $<
2500$, but that investigation of a sample of low-count clusters may
still reveal interesting trends. A comparison to the predicted
distribution of temperature ratios and their relationship to putative
cool lumps and/or non-thermal soft X-ray emission in cluster simulations would be a very useful next step.
\end{abstract}

%%%%%%%%%%%%
% Keywords %
%%%%%%%%%%%%

\keywords{catalogs -- galaxies: clusters: general -- X-rays: galaxies:
clusters -- cosmology: observations -- methods: data analysis}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Cluster mass functions and the evolution of the cluster mass function
are useful for measuring cosmological parameters
\citep{1989ApJ...341L..71E, 1998ApJ...508..483W, 2001ApJ...553..545H,
2003PhRvD..67h1304H, 2004PhRvD..70l3008W}. Cluster evolution tests the
effect of dark matter and dark energy on the evolution of dark matter
halos, and therefore provide a complementary and distinct constraint
on cosmological parameters to those tests which constrain
them geometrically (e.g. supernovae \citep{1998AJ....116.1009R,
2007ApJ...659...98R} and baryon acoustic oscillations
\citep{2005ApJ...633..560E}).

However, clusters are a useful cosmological tool only if we can infer
cluster masses -- the fundamental cluster property inferred from
cosmological simulations \citep{1990ApJ...363..349E} -- from
observable properties such as X-ray luminosity, X-ray temperature,
lensing shear, optical luminosity, and galaxy velocity
dispersion. Empirically, the relationship of mass and these observable
properties is well-established \citep{2005RvMP...77..207V}. However,
if we could identify a ``3rd parameter" -- possibly reflecting the
degree of relaxation in the cluster -- we could improve the utility of
clusters as cosmological probes.

Toward this end, we desire to understand the dynamical state of a
cluster beyond identifying which clusters appear to be relaxed and
those which appear to be unrelaxed. More likely, clusters have a
dynamical state which is somewhere in between
\citep{2006ApJ...639...64O, 2006ApJ...650..128K}. The degree to which
a cluster is virialized must be quantified within simulations and then
observationally calibrated with an unbiased statistical sample of
clusters.

One such study to quantify the dynamical state of
clusters was performed by \cite{2001ApJ...546..100M} (hereafter ME01)
using the ensemble of simulations by \cite{1997ApJ...491...38M}. ME01
found clusters which had experienced a recent merger were much cooler
than the cluster mass-observable scaling relations predict. They
attribute this to the presence of cool, spectroscopically unresolved
accreting subclusters which introduce energy into the ICM which
requires a long timescale to dissipate. The consequence being an
under-prediction of cluster binding masses of $15-30\%$
\citep{2001ApJ...546..100M}.

One method of quantifying the underestimate of the cluster temperature
(and therefore cluster mass) employs the ratios of X-ray surface
brightness moments to quantify the degree of relaxation
\citep{1995ApJ...452..522B, 1996ApJ...458...27B,
2005ApJ...624..606J}. Although an excellent tool, power ratios suffer
from being aspect dependent. ME01 found an auxiliary measure of
substructure which does not depend on perspective and could be
combined with power ratio to yield a more robust metric for
quantifying a cluster's degree of relaxation. They found hard-band
(2.0$_{rest}$-9.0 keV) temperatures were $\sim 20\%$ hotter than
broad-band (0.5-9.0 keV) temperatures. The cooler broad-band
temperature being caused by unresolved accreting cool subclusters
contributing significant amounts of line emission to the
soft-band ($E<2$ keV). Work by \cite{2004MNRAS.354...10M} and
\cite{2006ApJ...640..710V} have confirmed this effect in simulated
{\textit{Chandra}} and {\textit{XMM-Newton}} spectra.

ME01 proposed this temperature skewing, and consequently the fingerprint of
accretion, could be detected utilizing the energy resolution and
soft-band sensitivity of {\textit{Chandra}}. They proposed comparing
single-phase temperature fits to a hard band and full band for a
sufficiently large sample of clusters covering a broad dynamical range
then checking for a net skew in the ratio of hard and full
temperatures above unity.

In this paper we present our findings of just such a temperature ratio
test using {\textit{Chandra}} archival data. We find on average, the
hard-band temperature exceeds the broad-band temperature by $\sim15\%$
in multiple flux-limited samples of X-ray clusters from the Chandra
archive. This mean excess is weaker than the $20\%$
predicted by ME01, but is significant at the $11\sigma$ level
nonetheless. Hereafter, we refer to the hard-band to broad-band
temperature ratio as \tf. 

This paper proceeds in the following manner. In \S\ref{sec:selection}
we outline sample selection criteria and {\textit{Chandra}}
observations selected under these criteria. Data reduction and
handling of the X-ray background is discussed in
\S\ref{sec:data}. Spectral extraction is discussed in
\S\ref{sec:extraction} while fitting and simulated spectra are
discussed in \S\ref{sec:specan}. Results and discussion of our
analysis are presented in \S\ref{sec:r&d}. A final summary of our work
is presented in \S\ref{sec:summary}. For this work we have assumed a
flat $\Lambda$CDM Universe with cosmology $\Omega_{M} = 0.3$,
$\Omega_{\Lambda} = 0.7$, and $H_{0} = 70$ km s$^{-1}$ Mpc$^{-1}$. All
quoted uncertainties are at the 1.6$\sigma$ level (90\% confidence).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sample Selection} \label{sec:selection}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Our sample is selected from observations publicly available in the
{\textit{Chandra}} X-ray Telescope's Data Archive (CDA). Our initial
selection pass came from the {\textit{ROSAT}} Brightest Cluster Sample
\citep{1998MNRAS.301..881E}, RBC Extended Sample
\citep{2000MNRAS.318..333E}, and {\textit{ROSAT}} Brightest 55 Sample
\citep{1990MNRAS.245..559E, 1998MNRAS.298..416P}. The portion of our
sample at z $\gtrsim 0.4$ can also be found in a combination of the
{\textit{Einstein}} Extended Medium Sensitivity Survey
\citep{1990ApJS...72..567G}, North Ecliptic Pole Survey
\citep{2006ApJS..162..304H}, {\textit{ROSAT}} Deep Cluster Survey
\citep{1995ApJ...445L..11R}, {\textit{ROSAT}} Serendipitous Survey
\citep{1998ApJ...502..558V}, and Massive Cluster Survey
\citep{2001ApJ...553..668E}. We later extended our sample to include
clusters found in the REFLEX Survey \citep{2004A&A...425..367B}. Once
we had a master list of possible targets, we cross-referenced this
list with the CDA and gathered observations where a minimum of
R$_{5000}$ (defined below) is fully within the aimpoint CCD's field of
view.

R$_{\Delta_c}$ is defined as the radius at which the average cluster
density is $\Delta_c$ times the critical density of the Universe,
$\rho_c=3H_{0}^2/8\pi G$. For our calculations of R$_{\Delta_c}$ we adopt the relation
from \cite{2002A&A...389....1A}:

\begin{eqnarray}
R_{\Delta_c} &=& 2.71 \text{ Mpc }
\beta_T
\Delta_{\text{z}}^{-1/2}
(1+z)^{3/2}
(\frac{kT_X}{10 \text{ keV}})^{1/2}\\
\Delta_z &=& \frac{\Delta_c \Omega_M}{18\pi^2\Omega_z} \nonumber \\
\Omega_z &=& \frac{\Omega_M (1+z)^3}{[\Omega_M
(1+z)^3]+[(1-\Omega_M-\Omega_{\Lambda})(1+z)^2]+\Omega_{\Lambda}} \nonumber
\end{eqnarray}

where R$_{\Delta_c}$ is in units of h$_{70}^{-1}$, $\Delta_c$ is
the assumed density contrast of the cluster at R$_{\Delta_c}$, and
$\beta_T$ is a numerically determined, cosmology-independent
($\lesssim \pm 20\%$) normalization for the virial relation $GM/2R =
\beta_TkT$. We use $\beta_T = 1.05$ taken from
\cite{1996ApJ...469..494E}.

The result of our CDA search is a total of 374 observations of which
224 are used from 179 clusters. The bolometric ($E \sim 0.1-100$ keV)
luminosities, L$_{bol}$, for our sample clusters plotted as a function of
redshift are shown in Figure \ref{fig:lx_z}. These L$_{bol}$ values
are limited to the region of the spectral extraction (from $R=70$ kpc
to $R=R_{2500}$).

Basic properties of our sample are listed in Table
\ref{tab:sample}. For the sole purpose of computing extraction regions
as is discussed in \S\ref{sec:extraction}, fiducial temperatures and
redshifts were taken from the Ph.D. thesis of Don Horner\footnote{Available at
http://asd.gsfc.nasa.gov/Donald.Horner/thesis.html} (all redshifts confirmed with
NED\footnote{http://nedwww.ipac.caltech.edu/}). For clusters not
observed with {\textit{ASCA}} and thus not listed in Horner's thesis,
we used a literature search to locate temperature values. If no published value
could be located, we approximated a temperature by recursively
extracting a spectrum in the region 0.1 $<$ r $<$ 0.2 R$_{500}$
fitting a temperature and recalculating R$_{500}$. This process was
repeated until three consecutive iterations produced R$_{500}$ values
which differed by $\leq 1\sigma$. This method of temperature
determination has been employed in other studies, see
\cite{2006MNRAS.tmp.1068S} and \cite{2006ApJS..162..304H} as
examples.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\textit{Chandra} Data}\label{sec:data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Reprocessing and Reduction}\label{sec:reprocessing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

All datasets were reduced utilizing the Chandra Interactive Analysis of
Observations package ({\tt CIAO}) and accompanying Calibration
Database ({\tt CALDB}). Using {\tt CIAO v3.3.0.1} and {\tt
CALDB v3.2.2}, standard data analysis was followed for each
observation to apply the most up-to-date time-dependent gain
correction and charge transfer inefficiency (CTI) correction (when
appropriate) \citep{2000ApJ...534L.139T}. Observations taken in {\tt
VFAINT} mode had possible background events flagged using the {\tt
check\_vf\_pha} mode switch in {\tt acis\_process\_events}.

The X-ray events were then filtered for bad grades. Only events
recorded during the good time intervals (GTI) were used. For
observations taken prior to standard data processing version (SDP)
7.4, we flagged, inspected, and then removed the afterglow correction
applied as part of the older SDP pipeline. For observations taken
prior to SDP 7.4 and using {\tt FAINT} mode, or SDP 7.6 and {\tt
VFAINT} mode, a new bad pixel file was constructed.

To detect and remove point sources we used the adaptive wavelet 
tool {\tt wavdetect} \citep{2002ApJS..138..185F} on events files
filtered in the energy range $0.3-9.0$ keV. This energy window extends
below and above the energy range of interest for our spectral analysis
as the photons below $0.7$ keV and above $7.0$ keV, while useless
for diffuse emission studies, are a good diagnostic for detecting
point sources \citep{2000SPIE.4012...17J}. 

After visually inspecting an image of the observation overlaid with
the source regions generated by {\tt wavdetect}, we added regions for point
sources which were missed by wavdetect and deleted regions for
spuriously detected ``sources'' thus creating a point source
mask. Spurious sources are typically CCD features not fully removed by
dividing out the exposure map. Each remaining source was then masked out using
$2\sigma$ ellipses as calculated from {\tt wavdetect}. This process
results in an events file (at "level 2") that has been cleaned of
point sources.

To check for contamination from background flares or periods of
excessively high background, light curve analyses were performed using
Maxim Markevitch's contributed {\tt CIAO} script {\tt
lc\_clean.sl}\footnote{Available at
http://cxc.harvard.edu/contrib/maxim/acisbg/}. Periods with count
rates $\geq 3\sigma$ and/or a factor $\geq 1.2$ of the mean background
level of the observation were removed from the GTI file. As prescribed
by Markevitch's
cookbook\footnote{http://cxc.harvard.edu/contrib/maxim/acisbg/COOKBOOK},
ACIS front-illuminated (FI) chips were analyzed in the $0.3-12.0$ keV
range with time bins of $259.28$ sec in length, and for the ACIS
back-illuminated (BI) chips, $2.5-7.0$ keV energy range with time bins
of $1037.12$ sec.

If possible, we compared light curves from a FI and BI chip in an
effort to detect long duration, soft-flares which can go undetected on
the FI chips but show up on the BI chips. While rare, this class of
flare needs to be filtered out of the data as it introduces a spectral
component which artificially increases the best-fit temperature via a
high energy tail.

Determining a cluster ``center'' is essential for the later purpose of
removing cool cores from our spectral analysis (see
\S\ref{sec:extraction}). To determine the cluster center, we
calculated the centroid of the resulting flare clean, point source
free level-2 events file filtered to include only photons in the
$0.7-7.0$ keV range. Before centroiding, the events file is exposure
corrected and ``holes'' created by excluding point sources are filled
using interpolated values taken from a narrow annular region just
outside the hole. This last step is implemented using the Poisson
method of the {\tt CIAO} tool {\tt dmfilth}. Prior to centroiding we define
the emission peak by heavily binning the image, finding the peak value
within a circular region extending from the peak to the chip edge
(defined by the radius, R$_{max}$), reducing R$_{max}$ by 5\%
and the binning by a factor of two, and finding the peak again. This
process is repeated until the image is unbinned (binning factor of
one). We then return to an unbinned image with an aperture centered on
the emission peak with a radius R$_{max}$ and find the centroid using
{\tt CIAO}'s {\tt dmstat}. The centroid, (x$_c$,y$_c$), for a
distribution of $N$ good pixels with coordinates (x$_i$,y$_j$) and
values f(x$_i$,y$_j$) is defined as:

\begin{eqnarray}
Q &=& \sum_{i,j=1}^N f(x_i,y_i) \\
x_c &=& \frac{\sum_{i,j=1}^N x_i \cdot f(x_i,y_i)}{Q} \nonumber \\
y_c &=& \frac{\sum_{i,j=1}^N y_i \cdot f(x_i,y_i)}{Q} \nonumber \\
\end{eqnarray}

If the centroid was within 70 kpc of the emission peak the emission
peak is selected as the center, otherwise the centroid is used
as the center. This selection was made to ensure all ``peaky'' cool
cores are at the cluster center thus maximizing their exclusion later
in our analysis. All cluster centers are verified by-eye.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{X-ray Background} \label{sec:background}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Because we are attempting to measure a global cluster temperature,
specifically looking for a temperature ratio shift in energy bands
which can be contaminated by the high-energy particle background or
the soft local background, it is important to carefully analyze the
background and subtract it from our resulting spectra.

We use blank-sky observations of the X-ray background from
\cite{2001ApJ...562L.153M} supplied within the CXC {\tt CALDB}. First, we
compare the flux from the diffuse soft X-ray background of the
{\textit{ROSAT}} All-Sky Survey ({\textit{RASS}}) combined
bands\footnote{RASS combined bands give fluxes for energy ranges of
0.12-0.28 keV, 0.47-1.21 keV, and 0.76-2.04 keV respectively
corresponding to R12, R45, and R67.} R12, R45, and R67 to the 0.7-7.0
keV flux in each extraction aperture for each observation. For the
purpose of simplifying the subsequent analysis, we discarded
observations with an R45 flux $\geq 10\%$ of the total cluster X-ray
flux.

The appropriate blank-sky dataset for each observation was
selected from the {\tt CALDB}, reprocessed exactly as the
observation, and then reprojected using the aspect solutions provided
with each observation. For observations on the ACIS-I array, we
constructed blank-sky backgrounds for chips I0-I3 plus chips S2 and/or
S3. For ACIS-S observations, we created blank-sky backgrounds only for
the S3 chip plus chips I2 and/or I3. The additional off-aimpoint
chips were included only if they were active during the observation
and had available blank-sky data sets for the observation time
period. For observations which did not have a matching off-aimpoint
blank-sky background in the CALDB a source-free region of the active
chips is located and used for background normalization. Off-aimpoint
chips were cleaned for point sources and diffuse sources using the
method outlined in \S\ref{sec:reprocessing}.

The additional off-aimpoint chips were included in data reduction
since they contain data which is farther from the cluster center and
are therefore more useful in analyzing the observation background. To
normalize the hard particle component we measured fluxes for identical
chips in the blank-sky field and target field in the 9.5-12.0 keV
range. The effective area of the ACIS arrays above 9.5 keV is zero and
thus the collected photons there are exclusively from the particle
background. 

A histogram of the ratios of the 9.5-12.0 keV count rate from an
observation's off-aimpoint chip to that of the observation specific
blank-sky background are presented in Figure \ref{fig:bgd}. The
majority of the observations are in agreement to $\lesssim 20\%$ of
the blank-sky background rate, which is small enough to not affect our
analysis; regardless, we re-normalize all blank-sky backgrounds. 

Normalization brings the observation background and blank-sky
background into agreement for energies $> 2$ keV, but even after
normalization, typically, there still exists a soft excess/deficit
associated with the spatially varying soft Galactic
background. Following the technique detailed in
\cite{2005ApJ...628..655V} we construct and fit soft residuals for
this component. For each observation we first compare the 0.3-2.0 keV
flux of the blank-sky field and off-aimpoint field. We then
subtract a spectrum of the blank-sky field from a spectrum of the
off-aimpoint field to create a residual. The residual is fit
with a solar abundance, zero redshift {\tt MeKaL} model
\citep{1985A&AS...62..197M, 1986A&AS...65..511M, 1992SRON,
1995ApJ...438L.115L} where the normalization is allowed to be
negative. The resulting best-fit temperatures for all of the soft
residuals identified here were between 0.2-1.0 keV, which is in
agreement with results of \cite{2005ApJ...628..655V}. The
normalization of this background component was then scaled to the
cluster sky area. The re-scaled component is included as a fixed
background component during fitting of a cluster's spectra.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Notes for Individual Clusters} \label{sec:indnotes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We find evidence for long duration soft flares in the observations of
Abell 1758 \citep{2004ApJ...613..831D}, CL J2302.8+0844, and IRAS
09104+4109. These flares were handled by adding the {\tt XSPEC}
CUTOFFPL/b model during spectral analysis, freezing the spectral index
at $\Gamma=-0.15$, freezing the high energy exponential cut-off at 5.6
keV, and allowing the normalization to be the only free
parameter. This procedure follows directly from the recommendations of
\cite{2003ApJ...583...70M}. IRAS 09104+4109 presented a special, 
troubling circumstance which resulted in its removal from the sample.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Spectral Extraction} \label{sec:extraction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The simulated spectra calculated by ME01 were analyzed in the energy
ranges $0.5-9.0$ keV and $2.0_{rest}-9.0$ keV, but to make a reliable
comparison with {\textit{Chandra}} data we restrict our focus to a
full energy band, $0.7-7.0$ keV, and a hard energy band,
$2.0_{rest}-7.0$ keV. We exclude data below $0.7$ keV to avoid the
effective area and quantum efficiency variations of the ACIS
detectors, and exclude energies above $7.0$ keV in which diffuse
emission is dominated by the background and {\textit{Chandra}'s}
effective area is small. We also account for cosmic redshift by
shifting our hard energy band from 2.0 keV to $2.0/(1+z)$
keV (henceforth, assume the 2.0 keV cut is in the rest frame unless
otherwise stated).

ME01 calculated the relation between
T$_{0.5-9.0}$ and T$_{2.0-9.0}$ using apertures of R$_{200}$ and
R$_{500}$ in size. While it is trivial to calculate a temperature out
to R$_{200}$ or R$_{500}$ from a simulation, such a measurement at
these scales is extremely difficult with {\textit{Chandra}}
observations (see \cite{2005ApJ...628..655V} for a detailed
explanation).  However, in typical Chandra fields of view, apertures
with $R=R_{200}$ or even $R_{500}$ are not fully included. Thus we
chose to extract spectra from regions with radius R$_{2500}$ when
possible and R$_{5000}$ otherwise. Clusters analyzed only within
R$_{5000}$ are denoted in Table \ref{tab:sample} by a dagger.

The cores of some clusters are dominated by cool cores which affect
the global temperature, therefore we excise the central 70 kpc of each
aperture. These excised apertures are denoted by ``-CORE'' in the
text. Recent work by \cite{2007astro.ph..3504M} has shown excising
0.15 R$_{500}$ rather than 70 kpc reduces scatter in mass-observable
scaling relations. But such a reduction does not effect this work as
the conclusions drawn from our spectral analysis are strongly related
to the uncertainties of \hard and not on the best-fit value of \full
where the effect of a cool core is the strongest.

Although some clusters are not circular in projection, but rather are
elliptical or asymmetric, we find that extracting from a circular
annulus does not significantly change the best-fit values. For another
such example see \cite{2005MNRAS.359.1481B}.

After defining annular apertures, we extracted source spectra from the
target cluster and background spectra from the corresponding
normalized blank-sky dataset. By standard {\tt CIAO} means we created
effective area functions (ARF files) and redistribution matrices (RMF
files) for each cluster using a flux-weighted map (WMAP) across the
entire extraction region. The WMAP was calculated over the energy
range 0.3-2.0 keV to  weight calibrations that vary as a function of
position on the chip. Each spectrum was then binned to contain a
minimum of 25 counts per channel.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Spectral Analysis} \label{sec:specan}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fitting} \label{sec:fitting}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Spectra were fit with {\tt XSPEC 11.3.2ag} \citep{1996ASPC..101...17A}
using a single-temperature {\tt MeKaL} model in combination with the
photoelectric absorption model {\tt WABS} \citep{1983ApJ...270..119M}
for Galactic absorption. Galactic absorption values, $N_{HI}$, are taken from
\cite{1990ARA&A..28..215D}. The parameters which can be fit in the
{\tt WABS(MeKaL)} model are $N_{HI}$, X-ray temperature (\tx),
metal abundance ($Z/Z_{\sun}$), and a normalization proportional to the
integrated emission measure of the cluster. The spectra from
clusters with multiple observations were fit simultaneously. Results
from the fitting are presented in Table \ref{tab:r2500specfits} and
Table \ref{tab:r5000specfits}. No systematic error is added during
fitting and thus all quoted errors are statistical only.

Additional statistical error is introduced into our fitting through
inclusion of the soft local background component discussed in
\S\ref{sec:background}. To account for this error we use the
differences between \tx of the model using the scaled 
normalization and \tx of the model using $\pm1\sigma$ of the
scaled normalization as the errors associated with this additional
component. The statistical error and the error inferred from the range
of normalization to the soft X-ray background component are then
added in quadrature to produce a final error. In all cases this
additional background error on the temperature is $< 10\%$ of the
total statistical error and represents a minor inflation of the error
budget.

In all fits the metal abundance is allowed to be free. When comparing
fits using $N_{HI}$-free and $N_{HI}$-fixed we find the best-fit
$N_{HI}$ values did not significantly alter \tx or improve the
goodness of fit, thus $N_{HI}$ is fixed at the Galactic value with the
exception of three cases: Abell 399 \citep{2004MNRAS.351.1439S},
Abell 520, and Hercules A.

After fitting we reject several datasets as their best-fit \hard
had no upper bound in the 90\% confidence interval and thus we gain
nothing from their inclusion in the final analysis. All R$_{5000}$ and
R$_{5000-\text{CORE}}$ fits of the clusters Abell 781, Abell 1682, CL
J1213+0253, CL J1641+4001, MS 0302.7+1658, RX J1053+5735, and RX
J1525+0958 are rejected; we also reject all fits for R$_{2500}$ and
R$_{2500-\text{CORE}}$ apertures of Lynx E and MACS J1824.3+4309.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Simulated Spectra}\label{sec:simulated}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To quantify the effect a second, cooler gas component has on a
single-phase spectral model, we used the {\tt fakeit} command within
{\tt XSPEC} to create an ensemble of simulated spectra for our entire
sample. With these simulated spectra we are attempting to answer the
question: How bright must a second temperature component be to see it
in the 2.0-7.0 over the 0.7-7.0 keV bandpass?  Put another
way, we are asking at what flux ratio a second gas phase skews
\tf to greater than unity at the 1$\sigma$ level.

We began by convolving the observation-specific background, ARF, and RMF
with a {\tt WABS(MeKaL$_{1}$+MeKaL$_{2}$)} model for a time period equal to
the observation exposure time and adding Poisson noise. We define the
{\tt MeKaL$_1$} component to have the best-fit temperature and metallicity of
the R$_{2500-\text{CORE}}$, 0.7-7.0 keV fit for that observation.

For each realization of an observation's simulated spectrum, we vary
the {\tt MeKaL$_2$} component temperature over values 0.5, 0.75, and
1.0 keV. The {\tt MeKaL$_2$} metallicity is assumed to be equal to the
value of {\tt MeKaL$_1$}.

We adjust the normalization of the simulated two-component spectra to
achieve equivalent count rates to that in the real spectra. We
increment the {\tt MeKaL$_1$} normalization, $K_1$, away from the
best-fit value by a prescribed factor, $\xi$, while leaving the {\tt
MeKaL$_2$} normalization, $K_2$, free. We explore
a wide variety of $K_2$ by using $\xi$ values of 0.8, 0.85, 0.9, 0.95,
0.96, 0.97, 0.98, and 0.99 $K_1$.

We also simulate a control sample of single-temperature models. The
control sample is essentially a simulated version of the best-fit
model. This control provides us with a check of how often a hard
component temperature might differ from a broad-band temperature
statistically (i.e. calibration effects under control).

For each observation, we have 59 total simulated spectra-- 35
single-temperature control spectra and 24 two-component simulated
spectra (three second temperatures, each with 8 different $\xi$). Our
resulting simulated spectra ensemble contains 11269 spectra. After
generating all the spectra we follow the same fitting routine detailed
in \S\ref{sec:fitting}.

There are two important results taken away from the analysis of these
simulated spectra:\\
1. A single temperature component rarely (frequency $\sim 2\%$) gives
a significantly different \full and \hard temperature as demonstrated
with the control sample shown in the first panel of Figure
\ref{fig:ft_histo}. The two real data distributions are qualitatively
in agreement with the distribution of the multicomponent simulated
distribution, while the control sample distribution is roughly
Gaussian and peaked around \tf = 1.0. This is a strong indication the
calibration of {\textit{Chandra}} is under control and will not be the
driver for any measured temperature skew.\\
2. A significantly bright second temperature component, for
example $\xi > 0.96$ where the effect of a second spectral temperature
diminishes to $< 10\%$, must be present in order to get
significant deviations of \tf from 1.0 as large as 1.1-1.2, as seen in
the real data. Figure \ref{fig:fak_tx} highlights this fact further. Even
in the extreme case of a second component only accounting for $1\%$ of
the observed flux, the weighted-average of \tf still registers a
skew of $1.06\pm0.005$. The control sample however has a \tf
weighted-average of $1.00\pm0.001$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and Discussion} \label{sec:r&d}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Temperature Ratios} \label{sec:tspecresults}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We estimate a temperature ratio \tf = \hard/\full for each
cluster. We find a clear departure of the mean \tf from unity for
our entire sample at greater than $11\sigma$. The weighted mean values
for our sample are shown in Table \ref{tab:wavg}. Presented in Figure
\ref{fig:ftx} are the binned weighted-means and raw \tf values of
R$_{2500-\text{CORE}}$ and R$_{5000-\text{CORE}}$. Each bin contains
25 clusters with the exception of the highest temperature bins which
have 6 and 20 for the  R$_{2500-\text{CORE}}$ and
R$_{5000-\text{CORE}}$, respectively. The peculiar points with \tf
$<$ 1 are all statistically consistent with \tf = 1. In addition,
ratios less than one in the real data occur at nearly the same
frequency in the simulated data, $\sim 0.3\%$, suggesting that these
ratios are consistent with statistical uncertainties in the data. The
presence of clusters where \tf = 1 suggests that the calibration is
not the sole reason for deviations of \tf from 1. We also do not
find the temperature ratio depends on the best-fit full-band
temperature.

The uncertainty associated with each value of \tf is dominated by
the larger error in \hard, and on average, $\Delta$\hard$\approx
2.3\Delta$\full. This error interval discrepancy naturally results
from excluding the bulk of a cluster's emission occurring below 2
keV. While choosing a temperature-sensitive cut-off energy for the
hard-band (other than $2.0_{rest}$ keV) might maintain a more consistent
error budget across our sample (see Figure \ref{fig:ftxerr}), we do not
find any systematic TREND in the ratio with cluster temperature. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Systematics} \label{sec:sys}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Aside from instrumental and calibration effects there may be
additional systematics in our analysis which do not present themselves
on an individual basis but emerge as underlying trends in the sample
as a whole. Three possible sources of these systematics
are signal-to-noise (S/N), redshift selection, and Galactic
absorption. Presented in Figure \ref{fig:sys} are these three
parameters versus \tf. The trend in \tf with redshift is expected
as the 2.0/(1+z) keV hard-band lower boundary nears convergence with
the 0.7 keV full-band lower boundary which occurs at z $\sim 1.85$. We
find no systematic trends with S/N or Galactic absorption, which might
occur if the ratio skew were a consequence of poor calibration. Also
shown in panel four of Fig. \ref{fig:sys} is a comparison of the best-fit
results for R$_{2500-\text{CORE}}$ and R$_{5000-\text{CORE}}$. Our
results are robust at the 1$\sigma$ level against change in aperture
size.

Shown in Figure \ref{fig:asch} is the ratio of {\textit{ASCA}}
temperatures taken from Don Horner's thesis to {\textit{Chandra}}
temperatures derived in this work. Not all of our sample clusters have
an {\textit{ASCA}} temperature, but a sufficient number (57) are
available to make this comparison reliable. Apertures used in the
extraction of {\textit{ASCA}} spectra had no core region removed and
were substantially larger than R$_{2500}$. Thus we compare the the
unexcised R$_{2500}$ temperatures as it gets us the closest to
replicating the {\textit{ASCA}} apertures. We note a trend of
comparatively hotter {\textit{Chandra}} temperatures for clusters $>
10$ keV.

If we exclude the hottest clusters (\tx$ > 10$ keV where
{\textit{ASCA}} and {\textit{Chandra}} disagree) from our sample, the
mean temperature ratio for the sample remains $1.16$ and the error
increases from $\pm 0.014$ to $\pm 0.015$ for R$_{2500-\text{CORE}}$;
\tf increases by $0.9\%$ for R$_{5000-\text{CORE}}$ from $1.14\pm
0.013$ to $1.15\pm 0.014$. Our results are not being influenced by the
inclusion of hot clusters.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Using \tf to Select for Relaxation} \label{sec:relax}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Cool Core Versus Non-Cool Core}\label{sec:ccncc}

The process of virialization may robustly result in the formation of a
cool core \citep{2006ApJ...640..673O}. Flux-limited surveys have found
the prevalence of CCs to be $34-60\%$ \citep{1997MNRAS.292..419W,
1998MNRAS.298..416P, 2005MNRAS.359.1481B, 2007A&A...466..805C}
depending upon definition, completeness, and possible selection
biases. As discussed in \S\ref{sec:intro}, ME01 give us reason to
believe the observed skewing of \tf to greater than unity is related
to the dynamic state of a cluster. We thus seek to identify which
clusters in our sample have cool cores (CC), which have (NCC), and if
the presence or absence of a cool core is correlated to \tf. We also
ask about the number of cool core (CC) and non-cool core (NCC)
clusters as a function of \tf. Recall that we exclude the cool core
itself from the cluster spectrum.

To identify a CC cluster, we extract spectra for a 50 kpc region
surrounding the cluster center, then we define a temperature decrement
using the ratio of temperatures for the inner 50 kpc, T$_{50}$, and
the R$_{2500-\text{CORE}}$ aperture, T$_{dec} =
$T$_{50}/$T$_{R_{5000-\text{CORE}}}$ (clusters without
R$_{2500-\text{CORE}}$ fits are excluded from this analysis). When
finding T$_{50}$ we alter the fitting method outlined in
\S\ref{sec:fitting} to use {\tt XSPEC}'s modified Cash statistic
\citep{1979ApJ...228..939C}, {\tt cstat}, on ungrouped
spectra. This choice is made because the distribution of counts per
bin in low count spectra is not Gaussian but instead
Poisson. As a result the best-fit temperature using $\chi^2$ is
typically cooler \citep{1989ApJ...342.1207N, 2007A&A...462..429B}. We
have explored this systematic in {\bfseries\em{all}} our fits and
only found it to be significant in the lowest count spectra of the
inner 50 kpc apertures discussed here. But for consistency, we fit all
inner 50 kpc spectra using the modified Cash statistic.

If T$_{dec} < 1$ at the 2$\sigma$ level then we define it
as a CC cluster, otherwise it is a NCC cluster. We find CCs in 46\% of
our sample using 1$\sigma$ and 35\% using 2$\sigma$ thus indicating we
are consistent with more detailed studies of CC/NCC populations.

With each cluster classified we then take cuts in \tf at the $1\sigma$
level and ask how many CC and NCC clusters are above these cuts. 
Figure \ref{fig:cc_ncc_bin} shows the normalized number of CC and NCC
clusters as a function of cuts in \tf. If \tf were insensitive to
the dynamical state of a cluster we would expect, for normally
distributed \tf values, to see the number of CC and NCC clusters
monotonically decreasing. However, the number of CC clusters falls off
more rapidly than the number of NCC clusters. This effect
is dramatically reduced - as expected - if the core is included. All
curves demonstrate linear behavior in the region $0.9 \leq
$T$_{HFR,cut} \leq 1.2$. The slope of the linear curve segment for
R$_{2500-\text{CORE}}$ CC is $-3.10\pm 0.26$ and for NCC is $-2.41\pm
0.07$. For R$_{5000-\text{CORE}}$ the CC slope is $-2.55\pm 0.21$ and
for NCC is $-2.37\pm 0.13$. All fits have excellent goodness of fit.
This steeper fall-off of CCs indicates the contribution of soft
emission is indeed playing a role in affecting \tf. This result is
insensitive to our choice of significance level in both the core
classification and \tf cuts.

However, cluster redshift is playing a role in our ability to classify
CCs and NCCs. As redshift increases cool gas is shifted out of the
observable X-ray band and we lose spectral information about the core
which would aid in its classification. An analog of this effect can be
seen in our spectral simulations. Shown in Figure \ref{fig:fak_z} is
\tf plotted against redshift. The first three panels of
Fig. \ref{fig:fak_z} are the most interesting as they clearly show
this effect in the extreme cases of a second, cooler temperature
component which is $10-20\%$ the brightness of the hot gas phase. At
redshifts $> 0.6$ \tf begins to scatter about unity and a skew in
\tf only shows up under weight averaging making a cluster by cluster
detection of the coolest cluster gas difficult. Thus we are likely
not detecting weak CCs in the highest redshift clusters of our sample.

Because of the CC/NCC definition we've selected, our identification of
CCs and NCCs is only as robust as the errors on T$_{50}$ allow. One can
thus ask the question, does our loose definition bias us towards
finding more NCCs than CCs? Aside from the redshift effect, how often
would a CC be classified as a NCC because of low S/N? To explore these
questions we simulated 20 spectra for each observation following the
method outlined in \S\ref{sec:simulated} for the control sample but
using the inner 50 kpc spectral best-fit values as input. For each
simulated spectrum we then calculate the temperature decrement as
described above and re-classify the cluster as a CC or NCC. These
classifications based on simulated data are then compared to the
classification made from the real data. Based on this comparison we
can assign a reliability factor to each real classification. This
reliability factor is simply the percent of simulated spectra which
agree with the real classification. Values of 1.0 mean complete
agreement and 0.0 mean no agreement.

If we remove clusters with reliability factors less than 0.9 and
repeat the analysis above we find no significant change in the number
of CC clusters as a function of \tf.

\subsubsection{Mergers Versus Non-Mergers}\label{sec:merge}

We further define a subclass of NCC clusters as known mergers. Known
mergers are NCC clusters which have been identified as mergers in the
cluster literature. From Figure \ref{fig:ftx_tx} we can see clusters
exhibiting the highest significant values of \tf are all ongoing or
recent mergers. At the 2$\sigma$ level, we find increasing values of
\tf favor merger systems with NCCs over relaxed, CC clusters. Mergers
have left a spectroscopic imprint on the ICM which is predicted by
ME01 and which we observe in our sample.

To further investigate \tf we list the identities of 
clusters with T$_{frac} > 1.1$ at the 1$\sigma$ level. These are
presented in Table \ref{tab:tf11}. Of the 29 clusters, only six have
CCs. Three of those, MKW3S, 3C 28.0, and RX J1720.1+2638 have their
apertures centered on the bright, dense cores in confirmed
mergers. Two more clusters, Abell 2384 and RX J1525+0958, while
unconfirmed mergers have morphologies which are consistent with
powerful ongoing mergers. Abell 2384 has a long gas tail extending out
to a gaseous clump which has presumably passed through the cluster
recently. RXJ1525 has a core which is shaped like an arrowhead and is
reminiscent of the bow shock seen in 1E0657-56. Abell 907 is the
remaining CC of the six listed. It has no signs of being a merger
system but the highly compressed surface brightness contours to the
west of the core are indicative of a prominent cold
front which are tell-tale signs of a subcluster merger event
\citep{2007PhR...443....1M}.

The unclassified systems, RX J0439.0+0715, MACS J2243.3-0935, MACS
J0547.0-3904, ZWCL 1215, MACS J2311+0338, and Abell 267, have NCCs and
X-ray morphologies consistent with an ongoing or post-merger
scenario. Two clusters, Abell 1204 and MACS J1427.6-2521, show no
signs of recent or ongoing merger activity, however, they reside at
the bottom of the arbitrary \tf cut, and as evidenced by Abell 401 and
Abell 1689, exceptional spherical symmetry is no guarantee of
relaxation.

Returning to the discussion in \S\ref{sec:ccncc}, we find no cluster
with \tf $> 1.1$ has a reliability factor $< 0.9$. The correlation of
\tf with a cluster's dynamical state is robust.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Conclusions}\label{sec:summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We have explored the band-dependence of the inferred X-ray temperature
of the intracluster medium (ICM) for 179 well-observed ($N_{counts} >
1500$) clusters of galaxies selected from the Chandra data archive.

We extracted spectra from the annulus between $R=70$ kpc and
$R=R_{2500}$, R$_{5000}$ for each cluster. We compare the X-ray
temperatures inferred for single-temperature fits to global spectra
when the energy range of the fit is 0.7-7.0 keV (full) and when the
energy range is $2.0/(1+z)$-7.0 keV (hard). We find that, on
average, the hard-band temperature is significantly higher than
the full-band temperature. Upon further exploration, we find that
the ratio \tf is enhanced preferentially for clusters which are known
merger systems and for clusters which are isothermal. Clusters with
temperature decrements in their cores (known as as cool-core clusters)
tend to have best-fit hard-band temperatures that are statistically
consistent with their best fit full-band temperatures.

As was the original motivation from ME01, we suggest \tf can be
utilized as an indicator for the degree of relaxation/virialization. A
test for this prediction can be made with simulations by tracking \tf
during hierarchical assembly of clusters.

If \tf is correlated with a cluster's degree of relaxation then along
with other methods of substructure measure, such as power ratio, axial
ratio, and centroid shift, we can assemble a powerful metric for
measuring a cluster's expected deviation from mean scaling relations
such as L$_X$-\tx and L$_X$-M. Because \tf is aspect independent
this metric will have two components, spatial and spectroscopic,
by adding spectroscopic information to our understanding of cluster
virialization we may be able to reduce the scatter introduced into
observational studies of scaling relations which will in turn yield
smaller uncertainties in cosmological studies. However, to reach such
a lofty goal we need to expand our observational sample and begin
getting information about the underlying distribution of \tf and the
intrinsic scatter in \tf which was not possible with this sample.

%%%%%%%%%%%%%%%%%%%
% Acknowledgments %
%%%%%%%%%%%%%%%%%%%

\acknowledgements
This work was supported through {\textit{Chandra}} grant
XXX-YYY-123456. We thank the Chandra X-Ray Observatory Science Center,
operated for the National Aeronautics and Space Administration (NASA)
by the Smithsonian Astrophysical Observatory (SAO), for maintaining
the Chandra Data Archive (CDA) and for supplying and supporting the
Chandra Interactive Analysis of Observations (CIAO) software and
Calibration Database (CALDB). This project also utilized the NASA/IPAC
Extragalactic Database (NED), which is operated by the Jet Propulsion
Laboratory, California Institute of Technology, under contract with
NASA, and of NASA's Astrophysical Data System Bibliographic
Services. We also extend a special thanks to Keith Arnaud for
personally providing support for {\tt XSPEC}, obtained from the High
Energy Astrophysics Science Archive Research Center (HEASARC) and
supported by NASA's Goddard Space Flight Center.

%%%%%%%%%%%%%%%%
% Bibliography %
%%%%%%%%%%%%%%%%

\bibliography{cavagnolo}

%%%%%%%%%%%%%%%%%%%%%
% Figures and Tables%
%%%%%%%%%%%%%%%%%%%%%

\input{figs.tex}

%%%%%%%%%%
% Tables %
%%%%%%%%%%

\clearpage
\LongTables
\input{sample.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Comparison of Tfrac for wavg %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\input{tfwav.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Clusters with thfr > 1.1 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{cc_nccdesc.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% R2500 Spectral fit results %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\input{r2500.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% R5000 Spectral fit results %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\input{r5000.tex}

%%%%%%%%%%%%%%%%%%%%
% End the document %
%%%%%%%%%%%%%%%%%%%%

\end{document}
