\documentclass[11pt]{cv}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}
\usepackage{mathptmx,multicol,common}
\parindent 0pt
\parskip
\baselineskip
\setlength{\topmargin}{-0.30in}
\setlength{\oddsidemargin}{-0.30in}
\setlength{\evensidemargin}{-0.30in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0.25in}
\setlength{\topskip}{0.25in}
\setlength{\textwidth}{6.9in}
\setlength{\textheight}{9.25in}
\pagestyle{myheadings}
\newcommand{\myhead}{Cavagnolo, Publications}

\begin{document}

\begin{center}
{\Large Kenneth W. Cavagnolo\\Publications}
\rule{\linewidth}{1pt}
\normalsize
\end{center}

\begin{llist}
\vspace{-0.5cm}
%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Submitted}

{\sc {\textit{``Direct Evidence of Radiative and Mechanical Feedback from the Quasar in IRAS 09104+4109''}}}\\
{\bf K. Cavagnolo}, M. Donahue, B. McNamara, G.~M. Voit, \& M. Sun\\
Submitted to MNRAS

{\sc {\textit{``A Powerful, Line-of-Sight AGN Outburst in RBS 797''}}}\\
{\bf K. Cavagnolo}, B. McNamara, M. Wise, P. Nulsen, M. Br\"uggen, M. Gitti, \& D. Rafferty\\
Submitted to ApJ

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{In\\Preparation}

{\sc {\textit{``Identifying AGN Feedback Relics Via Steep Spectrum Radio Sources''}}}\\
{\bf{K. Cavagnolo}}, A. Edge, H. R\"ottgering, B. McNamara, M. Wise, M. Br\"uggen, R. van Weeren, G. Brunetti, \& J. Croston\\
In prep. for A\&A

{\sc {\textit{``Entropy Scaling Relations of ACCEPT Galaxy Clusters''}}}\\
{\bf K. Cavagnolo}, G.~M. Voit, M. Donahue, \& S. Bruch\\
In prep. for ApJL

{\sc {\textit{``How Difficult is SMBH Spin Axis Reorientation? Implications for AGN Feedback Models''}}}\\
{\bf K. Cavagnolo} \& N. Afshordi\\
In prep. for ApJL

{\sc {\textit{``The Radio Halo-Merger-Cooling Connection in Galaxy Clusters at $z\sim0.5$''}}}\\
E. Orr\`u, C. Ferrari, M. Arnaud, {\bf K. Cavagnolo}, J. Croston, N. Jetha, G. Pratt, E. Pointecouteau, \& S. Raychaudhury\\
In prep. for A\&A

{\sc{\textit{``Redistribution of Metals in Galaxy Clusters via AGN Feedback''}}}\\
C. Kirkpatrick, B. McNamara, {\bf K. Cavagnolo}, P. Nulsen, \& M. Wise\\
In prep. for ApJ

{\sc {\textit{``Normalization and Scatter of the $M \dash T$ Relation for Supermassive Galaxy Clusters''}}}\\
R. Mandelbaum, R. Nakajima, N. Bahcall, G. Bernstein, {\bf K. Cavagnolo}, M. Donahue, J. Hughes, C. Keeton, A. Kravtsov, S. Miyazaki, N. Padmanabhan, \& T. Schrabback\\
In prep. for ApJ

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{First\\Author\\Refereed}

{\sc {\textit{``A Relationship Between AGN Jet Power and Radio Luminosity''}}}\\
{\bf K. Cavagnolo}, B. McNamara, P. Nulsen, C. Carilli, C. Jones, \& L. B\^irzan\\
\href{http://adsabs.harvard.edu/abs/2010ApJ...720.1066C}{ApJ Published, 2010}

{\sc {\textit{``Intracluster Medium Entropy Profiles for a Chandra Archival Sample Of Galaxy Clusters''}}}\\
{\bf K. Cavagnolo}, M. Donahue, G.~M. Voit, \& M. Sun\\
\href{http://adsabs.harvard.edu/abs/2009ApJS..182...12C}{ApJ Published, 2009}

{\sc {\textit{``An Entropy Threshold for Strong H$\alpha$ and Radio Emission in the Cores of Galaxy Clusters''}}}\\
{\bf K. Cavagnolo}, M. Donahue, G.~M. Voit, \& M. Sun\\
\href{http://adsabs.harvard.edu/abs/2008ApJ...683L.107C}{ApJ Published, 2008}

{\sc {\textit{``Bandpass Dependence of X-Ray Temperatures in Galaxy Clusters''}}}\\
{\bf K. Cavagnolo}, M. Donahue, G.~M. Voit, \& M. Sun\\
\href{http://adsabs.harvard.edu/abs/2008ApJ...682..821C}{ApJ Published, 2008}

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Co-Author\\Refereed}

{\sc {\textit{``Direct Evidence for an Outflow of Metal-Enriched Gas Along the Radio Jets of 
Hydra A''}}}\\
C. Kirkpatrick, M. Gitti, {\bf K. Cavagnolo}, B. McNamara, L. David, P. Nulsen, \& M. Wise\\
\href{http://adsabs.harvard.edu/abs/2009arXiv0909.2252K}{ApJL Published, 2009}

{\sc {\textit{``A Chandra X-ray Analysis of Abell 1664: Cooling, Feedback and Star Formation in the Central Cluster Galaxy''}}}\\
C. Kirkpatrick, B. McNamara, D. Rafferty, P. Nulsen, L. Birzan, F. Kazemzadeh, M. Wise, M. Gitti, \& {\bf K. Cavagnolo}\\
\href{http://adsabs.harvard.edu/abs/2009ApJ...697..867K}{ApJ Published, 2009}

{\sc {\textit{``Conduction and the Star Formation Threshold in Brightest Cluster Galaxies''}}}\\
G.~M. Voit, {\bf K. Cavagnolo}, M. Donahue, D. Rafferty, B. McNamara, \& P. Nulsen\\
\href{http://adsabs.harvard.edu/abs/2008ApJ...681L...5V}{ApJ Published, 2008}

{\sc {\textit{``Star Formation, Radio Sources, Cooling X-Ray Gas and Galaxy Interactions in the Brightest Cluster Galaxy in 2A0335+096''}}}\\
M. Donahue, M. Sun, C. O'Dea, G.~M. Voit, \& {\bf K. Cavagnolo}\\
\href{http://adsabs.harvard.edu/abs/2007AJ....134...14D}{AJ Published, 2007}

{\sc {\textit{``s-Process Abundances in Planetary Nebulae''}}}\\
B. Sharpee, Y. Zhang, R. Williams, E. Pellegrini, {\bf K. Cavagnolo}, J. Baldwin, M. Phillips, \& X. Liu\\
\href{http://adsabs.harvard.edu/abs/2007ApJ...659.1265S}{ApJ Published, 2007}

{\sc {\textit{``Entropy Profiles in the Cores of Cooling Flow Clusters of Galaxies''}}}\\
M. Donahue, D. Horner, {\bf K. Cavagnolo}, \& G.~M. Voit\\
\href{http://adsabs.harvard.edu/abs/2006ApJ...643..730D}{ApJ Published, 2006}

\markright{\myhead}

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Presented\\Work}

{\sc Invited Talk: {\textit{``Exploring the Radio-mode/Quasar-mode Feedback Dichotomy''}}}\\
Nov. 2010 -- CNRS Colloquium; Observatoire de la C\^ote d'Azur

{\sc Talk: {\textit{``The AGN Jet Power and Radio Power Relationship''}}}\\
Jun. 2009 -- The Monster's Fiery Breath Meeting; University of Wisconsin-Madison

{\sc Invited Talk: {\textit{``Using Galaxy Clusters as Galaxy Formation Labs''}}}\\
Oct. 2008 -- Undergraduate Seminar Series; University of Waterloo

{\sc Invited Talk: {\textit{``Understanding Cluster Cores: The Role of Core Entropy''}}}\\
Sept. 2008 -- The Cool, Cooler, and Cold Meeting; Leiden University

{\sc Invited Talk: {\textit{``Investigating Feedback and Relaxation in Clusters of Galaxies''}}}\\
Jul. 2008 -- Center for Study of Cosmic Evolution; Michigan State University

{\sc Invited Talk: {\textit{``From Cluster Cosmology to Galaxy Formation in Under One Hour''}}}\\
Mar. 2008 -- Astrophysics Seminar; University of Waterloo

{\sc Invited Talk: {\textit{``The Effect of Cluster Feedback on High-Precision Cosmology''}}}\\
Feb. 2008 -- NASA Space Science and Technology Center; University of Alabama-Huntsville

{\sc Invited Talk: {\textit{``Understanding Feedback in Galaxy Clusters''}}}\\
Jan. 2008 -- Center for Study of Cosmic Evolution; Michigan State University

{\sc Invited Talk: {\textit{``Band Dependence of X-ray Temperatures''}}}\\
Oct. 2007 -- Astrophysics Seminar; University of Michigan

{\sc Poster: {\textit{``The Entropy-Feedback Connection and Quantifying Cluster Virialization''}}}\\
Oct. 2007 -- Eight Years of Science with Chandra; University of Alabama-Huntsville

{\sc Poster: {\textit{``Chandra Studies of Dark Matter and Galaxy Formation: Signatures from the Intracluster Medium''}}}\\
Dec. 2006 -- American Astronomical Society Meeting

{\sc Proceeding: {\textit{``Abundances of s-process elements in planetary nebulae: Br, Kr \& Xe''}}}\\
Jul. 2006 -- International Astronomical Union Symposium

{\sc Poster: {\textit{``Studies of Entropy Distributions in X-ray Luminous Clusters of Galaxies''}}}\\
Dec. 2005 -- American Astronomical Society Meeting

{\sc Poster: {\textit{``Entropy Distributions in the Cores of Nearby X-ray Luminous Clusters of Galaxies''}}}\\
Dec. 2004 -- American Astronomical Society Meeting

{\sc Poster: {\textit{``Radio-Free Cluster Cooling Flows''}}}\\
Dec. 2004 -- American Astronomical Society Meeting

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\markright{\myhead}
\end{llist}
\end{document}
