\documentclass[11pt]{cv}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}
\usepackage[T1]{fontenc}
\usepackage{mathptmx,multicol,common,color}
\pagestyle{empty}
\parindent 0pt
\parskip
\baselineskip
\setlength{\topmargin}{-0.30in}
\setlength{\oddsidemargin}{-0.30in}
\setlength{\evensidemargin}{-0.30in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0.25in}
\setlength{\topskip}{0.25in}
\setlength{\textwidth}{6.9in}
\setlength{\textheight}{9.25in}
\pagestyle{myheadings}

\begin{document}

\begin{center}
{\large \textbf{Dr. Kenneth W. Cavagnolo\\List of Publications}}\\
\rule{17.35cm}{2pt}\\
\footnotesize
{\it Last updated \today; \textcolor{blue}{Hyperlinks colored blue}}
\normalsize
\end{center}

\begin{llist}

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{In\\Preparation}

{\sc {\textit{``A Relationship Between AGN Jet Power and Radio Luminosity''}}}\\
{\bf K. Cavagnolo}, B. McNamara, P. Nulsen, C. Carilli, C. Jones, W. Forman, \& L. B\^irzan\\
Submitted to ApJ

{\sc {\textit{``Mechanical Feedback from the Obscured Quasar in IRAS 09104+4109''}}}\\
{\bf K. Cavagnolo}, M. Donahue, B. McNamara, G.~M. Voit, \& M. Sun\\
Submitted to MNRAS

{\sc {\textit{``A Multiwavelength Analysis of the Galaxy Cluster RBS 797: Evidence for a Cluster-scale Line-of-Sight AGN Outburst''}}}\\
{\bf K. Cavagnolo}, B. McNamara, P. Nulsen, M. Wise, M. Gitti, \& M. Br\"uggen\\
In prep. for ApJ

{\sc {\textit{``Entropy Scaling Relations of ACCEPT Galaxy Clusters''}}}\\
{\bf K. Cavagnolo}, G.~M. Voit, M. Donahue, \& S. Bruch\\
In prep. for ApJL

{\sc {\textit{``The Complications of SMBH Spin Axis Reorientation and Implications for AGN Feedback Models''}}}\\
{\bf K. Cavagnolo}, B. McNamara, \& N. Afshordi\\
In prep. for ApJL

{\sc {\textit{``Normalization and Scatter of the Mass-Temperature relation for Supermassive Galaxy Clusters''}}}\\
R. Mandelbaum, R. Nakajima, G. Bernstein, {\bf K. Cavagnolo}, M. Donahue, C. Keeton, J. Hughes, N. Bahcall, T. Schrabback, N. Padmanabhan, S. Miyazaki, \& A. Kravtsov\\
In prep. for ApJ

{\sc {\textit{``Constraining the Spin of Supermassive Black Holes Using Measured AGN Jet Powers''}}}\\
M. Rohanizadegan, B. McNamara, F. Kazemzadeh, P. Nulsen, \& {\bf K. Cavagnolo}\\
In prep. for ApJ

{\sc {\textit{``Identifying AGN Feedback Relics Via Steep Spectrum Radio Sources''}}}\\
A. Edge, {\bf{K. Cavagnolo}}, H. R\"ottgering, B. McNamara, M. Wise, M. Br\"uggen, R. van Weeren, G. Brunetti, \& J. Croston\\
In prep. for MNRAS

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{First\\Author\\Refereed\\Papers}

{\sc {\textit{``Intracluster Medium Entropy Profiles for a Chandra Archival Sample Of Galaxy Clusters''}}}\\
{\bf K. Cavagnolo}, M. Donahue, G.~M. Voit, \& M. Sun\\
\href{http://adsabs.harvard.edu/abs/2009ApJS..182...12C}{ApJ Accepted, 2009}

{\sc {\textit{``An Entropy Threshold for Strong H$\alpha$ and Radio Emission in the Cores of Galaxy Clusters''}}}\\
{\bf K. Cavagnolo}, M. Donahue, G.~M. Voit, \& M. Sun\\
\href{http://adsabs.harvard.edu/abs/2008ApJ...683L.107C}{ApJ Accepted, 2008}

{\sc {\textit{``Bandpass Dependence of X-Ray Temperatures in Galaxy Clusters''}}}\\
{\bf K. Cavagnolo}, M. Donahue, G.~M. Voit, \& M. Sun\\
\href{http://adsabs.harvard.edu/abs/2008ApJ...682..821C}{ApJ Accepted, 2008}

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Co-Author\\Refereed\\Papers}

{\sc {\textit{``Direct Evidence for an Outflow of Metal-Enriched Gas Along the Radio Jets of 
Hydra A''}}}\\
C. Kirkpatrick, M. Gitti, {\bf K. Cavagnolo}, B. McNamara, L. David, P. Nulsen, \& M. Wise\\
\href{http://adsabs.harvard.edu/abs/2009arXiv0909.2252K}{ApJL Accepted, 2009}

{\sc {\textit{``A Chandra X-ray Analysis of Abell 1664: Cooling, Feedback and Star Formation in the Central Cluster Galaxy''}}}\\
C. Kirkpatrick, B. McNamara, D. Rafferty, P. Nulsen, L. Birzan, F. Kazemzadeh, M. Wise, M. Gitti, \& {\bf K. Cavagnolo}\\
\href{http://adsabs.harvard.edu/abs/2009ApJ...697..867K}{ApJ Accepted, 2009}

{\sc {\textit{``Conduction and the Star Formation Threshold in Brightest Cluster Galaxies''}}}\\
G.~M. Voit, {\bf K. Cavagnolo}, M. Donahue, D. Rafferty, B. McNamara, \& P. Nulsen\\
\href{http://adsabs.harvard.edu/abs/2008ApJ...681L...5V}{ApJ Accepted, 2008}

{\sc {\textit{``Star Formation, Radio Sources, Cooling X-Ray Gas and Galaxy Interactions in the Brightest Cluster Galaxy in 2A0335+096''}}}\\
M. Donahue, M. Sun, C. O'Dea, G.~M. Voit, \& {\bf K. Cavagnolo}\\
\href{http://adsabs.harvard.edu/abs/2007AJ....134...14D}{AJ Accepted, 2007}

{\sc {\textit{``s-Process Abundances in Planetary Nebulae''}}}\\
B. Sharpee, Y. Zhang, R. Williams, E. Pellegrini, {\bf K. Cavagnolo}, J. Baldwin, M. Phillips, \& X. Liu\\
\href{http://adsabs.harvard.edu/abs/2007ApJ...659.1265S}{ApJ Accepted, 2007}

{\sc {\textit{``Entropy Profiles in the Cores of Cooling Flow Clusters of Galaxies''}}}\\
M. Donahue, D. Horner, {\bf K. Cavagnolo}, \& G.~M. Voit\\
\href{http://adsabs.harvard.edu/abs/2006ApJ...643..730D}{ApJ Accepted, 2006}

\markright{K.W.C., Publications}

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Presented\\Work\\\& Talks}

{\sc Poster: {\textit{``IRAS 09104+4109: At the Cross-roads of Massive Galaxy Formation?''}}}\\
Jun. 2010 -- From Massive Galaxy Formation to Dark Energy; University of Tokyo-Kashiwa

{\sc Poster: {\textit{``Probing SMBH Accretion History Via Radio Luminosities''}}}\\
Apr. 2010 -- What drives the growth of black holes?; Durham University

{\sc Talk: {\textit{``The AGN Jet Power and Radio Power Relationship for Isolated Giant Elliptical Galaxies''}}}\\
Jun. 2009 -- The Monster's Fiery Breath: Feedback in galaxies, groups, and clusters; University of Wisconsin-Madison

{\sc Invited Talk: {\textit{``Using Galaxy Clusters as Galaxy Formation Labs''}}}\\
Oct. 2008 -- Undergraduate Seminar Series; University of Waterloo

{\sc Invited Talk: {\textit{``Understanding Cluster Cores: The Role of Core Entropy''}}}\\
Sep. 2008 -- The Cool, Cooler and Cold - Cluster Cooling Flows in a New Light; Leiden University

{\sc Invited Talk: {\textit{``Investigating Feedback and Relaxation in Clusters of Galaxies''}}}\\
Jul. 2008 -- Center for Study of Cosmic Evolution; Michigan State University

{\sc Invited Talk: {\textit{``From Cluster Cosmology to Galaxy Formation in Under One Hour''}}}\\
Mar. 2008 -- Astrophysics Seminar; University of Waterloo

{\sc Invited Talk: {\textit{``The Effect of Cluster Feedback on High-Precision Cosmology''}}}\\
Feb. 2008 -- NASA Space Science and Technology Center; University of Alabama-Huntsville

{\sc Invited Talk: {\textit{``Understanding Feedback in Galaxy Clusters''}}}\\
Jan. 2008 -- Center for Study of Cosmic Evolution; Michigan State University

{\sc Invited Talk: {\textit{``Band Dependence of X-ray Temperatures''}}}\\
Oct. 2007 -- Astrophysics Seminar; University of Michigan

{\sc Poster: {\textit{``The Entropy-Feedback Connection and Quantifying Cluster Virialization''}}}\\
Oct. 2007 -- Eight Years of Science with Chandra; University of Alabama-Huntsville

{\sc Poster: {\textit{``Chandra Studies of Dark Matter and Galaxy Formation: Signatures from the Intracluster Medium''}}}\\
Dec. 2006 -- American Astronomical Society Meeting

{\sc Proceeding: {\textit{``Abundances of s-process elements in planetary nebulae: Br, Kr \& Xe''}}}\\
Jul. 2006 -- International Astronomical Union Symposium

{\sc Poster: {\textit{``Studies of Entropy Distributions in X-ray Luminous Clusters of Galaxies''}}}\\
Dec. 2005 -- American Astronomical Society Meeting

{\sc Poster: {\textit{``Entropy Distributions in the Cores of Nearby X-ray Luminous Clusters of Galaxies''}}}\\
Dec. 2004 -- American Astronomical Society Meeting

{\sc Poster: {\textit{``Radio-Free Cluster Cooling Flows''}}}\\
Dec. 2004 -- American Astronomical Society Meeting

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\markright{K.W.C., Publications}

\end{llist}

\end{document}
