\documentclass[12pt]{cv}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}
\usepackage{mathptmx,multicol,common}
\parindent 0pt
\parskip
\baselineskip
\setlength{\topmargin}{-0.30in}
\setlength{\oddsidemargin}{-0.30in}
\setlength{\evensidemargin}{-0.30in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0.25in}
\setlength{\topskip}{0.25in}
\setlength{\textwidth}{6.9in}
\setlength{\textheight}{9.25in}
\pagestyle{myheadings}
\pagestyle{empty}
\newcommand{\myhead}{Cavagnolo, Curriculum Vitae}

\begin{document}

\begin{center}
{\Large\sc{Kenneth W. Cavagnolo\\Curriculum Vitae}}\vspace{-0.3cm}
\end{center}
Observatoire de la C\^ote d'Azur \hfill Citizenship: U.S.A.\\
Boulevard de l'Observatoire \hfill Birthdate: Jan. 27\ths, 1980\\
B.P. 4229 \hfill Languages: English, Latin, French\\
F-06304, Nice, France \hfill \href{http://www.oca.eu/~cavagnolo/}{www.oca.eu/cavagnolo}\\
+33(0)687098367 \hfill \href{mailto:cavagnolo@oca.eu}{cavagnolo@oca.eu}

{\large\sc{Education}}\vspace{-0.3cm}\\
\rule{\linewidth}{0.5pt}
Ph.D. Astrophysics, Michigan State University \hfill 2008\\
M.S. Astrophysics, \textit{magna cum laude}, Michigan State University \hfill 2005\\
B.S. Physics, \textit{magna cum laude}, Georgia Institute of Technology \hfill 2002

{\large\sc{Employment}}\vspace{-0.3cm}\\
\rule{\linewidth}{0.5pt}
ANR Opales Postdoctoral Fellow, Observatoire de la C\^ote d'Azur \hfill 2010--Present\\
Waterloo Scholars Postdoctoral Fellow, University of Waterloo \hfill 2008--10\\
Research Assistant, X-ray astrophysics, Michigan State University \hfill 2003--08\\
Research Assistant, Planetary nebulae, Michigan State University \hfill 2002--03\\
Research Assistant, Eclipsing stellar binaries, Georgia Institute of Technology \hfill 2000--02

{\large\sc{Awards \& Honors}}\vspace{-0.3cm}\\
\rule{\linewidth}{0.5pt}
{\scriptsize{$\bullet$}} Referee for AJ, ApJ, ApJL, CanTAC, \& MNRAS\\
{\scriptsize{$\bullet$}} Sherwood K. Haynes Award for Outstanding Graduate Student\\
{\scriptsize{$\bullet$}} MSU College of Natural Science Dissertation Fellow\\
{\scriptsize{$\bullet$}} Georgia Institute of Technology President's List\\
{\scriptsize{$\bullet$}} Georgia Institute of Technology Four Year Dean's List\\
{\scriptsize{$\bullet$}} Perimeter Institute Black Hole Reading Group

{\large\sc{Collaborations \& Memberships}}\vspace{-0.3cm}\\
\rule{\linewidth}{0.5pt}
{\scriptsize{$\bullet$}} IXO Science Associate \hfill 2011--Present\\
{\scriptsize{$\bullet$}} Consortiums: LOFAR, ASKAP ({\it{EMU, POSSUM}}), \& SKA-Africa ({\it{MeerKAT}}) \hfill 2010--Present\\
{\scriptsize{$\bullet$}} $\Sigma \Xi$ National Scientific Research Society \hfill 2009--Present\\
{\scriptsize{$\bullet$}} American Astronomical Society \hfill 2002--Present\\
{\scriptsize{$\bullet$}} American Physical Society \hfill 2002--Present\\
{\scriptsize{$\bullet$}} $\Sigma \Pi \Sigma$ National Physics Honor Society \hfill 2001--Present
%{\scriptsize{$\bullet$}} International Astronomical Union \hfill 2011--Present\\

{\large\sc{Scientific Skills}}\vspace{-0.3cm}\\
\rule{\linewidth}{0.5pt}
{\scriptsize{$\bullet$}} Expert of radio and X-ray data reduction, analysis and interpretation\\
{\scriptsize{$\bullet$}} Extensive experience analyzing IR, optical, UV, and $\gamma$-ray data\\
{\scriptsize{$\bullet$}} Mastery of \aips, \casa, \ciao, \iraf, \osa, and \sas\ analysis software\\
{\scriptsize{$\bullet$}} Fluent in \html, \idl, \LaTeX, \perl, and \python\ programming languages\\
{\scriptsize{$\bullet$}} Familiar with \clang, \fortran, \meq, \mysql, \supmo, and \tickle\\
{\scriptsize{$\bullet$}} Command of DOS, Linux, Macintosh, and Windows computing architectures

{\large\sc{Observing Experience}}\vspace{-0.3cm}\\
\rule{\linewidth}{0.5pt}
ASKAP-Boolardy Engineering Test Array (BETA) \hfill 2011\\
Low Frequency Array (LOFAR) \hfill 2011\\
Very Long Baseline Array (VLBA) \hfill 2011\\
Giant Metrewave Radio Telescope (GMRT) \hfill 2010\\
Very Large Array Radio Telescope (VLA) \hfill 2009

{\large\sc{Grants \& Proposals}}\vspace{-0.3cm}\\
\rule{\linewidth}{0.5pt}
PI, VLBA, {\it{``Imaging the Misdirected QSO of IRAS 09104+4109''}} \hfill 2010\\
Co-I, GMRT, {\it{``Power and Particle Content of Extragalactic Radio Sources \Rmnum{1}--\Rmnum{3}''}} \hfill 2008--10\\
Co-I, GMRT, {\it{``Morphology of Steepest Spectrum Radio Sources in Galaxy Cluster Cores''}} \hfill 2009\\
Co-I, NOAO, {\it{``The Supermassive Cluster Survey \Rmnum{1}--\Rmnum{5}''}} \hfill 2008--10\\
PI, CXO, {\it{``IRAS 09104+4109: An Extreme Brightest Cluster Galaxy''}} \hfill 2008\\
Co-I, CXO, {\it``{Conduction and Multiphase Structure in the ICM''}} \hfill 2008\\
Co-I, Spitzer, {\it{``Star Formation and AGN Feedback in BCGs''}} \hfill 2008\\
Co-I, Spitzer, {\it{``Infrared Properties of a Control Sample of Brightest Cluster Galaxies''}} \hfill 2008\\
Co-I, NSF, {\it{``Star Formation in the Universe's Largest Galaxies''}} \hfill 2008\\
Co-I, CXO, {\it{``Quantifying Cluster Temperature Substructure''}} \hfill 2007\\
Co-I, NRAO, {\it{``Radio Feedback in Clusters and Galaxies''}} \hfill 2007

{\large\sc{Student Advisement}}\vspace{-0.3cm}\\
\rule{\linewidth}{0.5pt}
C. Kirkpatrick, Ph.D., ICM Abundance Distributions \hfill 2008--10\\
M. Rohanizadegan, Ph.D., Understanding SMBH Accretion and Spin \hfill 2008--10\\
J. King, NSERC REU, Quantifying Scatter in the \pjet-\prad\ Relation \hfill 2010\\
B. Whuiska, NSERC REU, The Largest BCG Cores in the \hst\ Archive \hfill 2009\\
R. Myers, NSERC REU, Galaxy Cluster Radio Sources in the 400 deg$^2$ Survey \hfill 2009

{\large\sc{Service \& Teaching}}\vspace{-0.3cm}\\
\rule{\linewidth}{0.5pt}
%Volunteer Astronomer, ``Barred Galaxies'' Prisoner education program \hfill 2011\\
Local Organizing Committee, {\it{``Non-thermal Phenomena in Colliding Galaxy Clusters''}} \hfill 2010\\
Local Organizing Committee, UW International Year of Astronomy \hfill 2009\\
Physics Tutor, {\it{``Introductory Honors Physics I \& II''}} \hfill 2003\\
Substitute Instructor \& Teaching Assistant, {\it{``Visions of the Universe''}} \hfill 2002,`03,`06

\markright{\myhead}
{\large\sc{References}}\vspace{-0.3cm}\\
\rule{\linewidth}{0.5pt}
Megan Donahue, Michigan State University \hfill \href{mailto:donahue@pa.msu.edu}{donahue@pa.msu.edu}; +00(1)5178845618\\
Mark Voit, Michigan State University \hfill \href{mailto:voit@pa.msu.edu}{voit@pa.msu.edu}; +00(1)5178845619\\
Brian McNamara, University of Waterloo \hfill \href{mailto:mcnamara@uwaterloo.ca}{mcnamara@uwaterloo.ca}; +00(1)5198884567\\
Chiara Ferrari, Observatoire de la C\^ote d'Azur \hfill \href{mailto:ferrari@oca.eu}{ferrari@oca.eu}; +33(0)492003028\\
Jack Baldwin, Michigan State University \hfill \href{mailto:baldwin@pa.msu.edu}{baldwin@pa.msu.edu}; +00(1)5178845611\\
Chris Carilli, NRAO \hfill \href{mailto:ccarilli@nrao.edu}{ccarilli@nrao.edu}; +00(1)5758357306\\
Paul Nulsen, CfA \hfill \href{mailto:pnulsen@cfa.harvard.edu}{pnulsen@cfa.harvard.edu}; +00(1)6174957043\\
Mike Wise, University of Amsterdam \hfill \href{mailto:wise@science.uva.nl}{wise@science.uva.nl}; +31(0)521595564
\end{document}

{\large\sc{Personal\\Interests}}\vspace{-0.3cm}\\
\rule{\linewidth}{0.5pt}
{\scriptsize{$\bullet$}} Academic: Environmental sciences, ``Cradle2Cradle'' design, and urban planning.\\
{\scriptsize{$\bullet$}} Athletics: Triathlons, running, baseball, and Georgia Tech athletics.\\
{\scriptsize{$\bullet$}} Hobbies: Backpacking, reading, building model airplanes, and raising bonsai trees.

{\large\sc{Research\\Program\\\& Interests}}\vspace{-0.3cm}\\
\rule{\linewidth}{0.5pt}
My research program is focused on better understanding the physics of
the intracluster and intragroup medium, and the role of feedback from
active galactic nuclei \& quasars on the formation and evolution of
galaxies, galaxy groups, and galaxy clusters.

Specific areas of interest:\\
{\scriptsize{$\bullet$}} Cosmic magnetic fields\\
{\scriptsize{$\bullet$}} Non-thermal galaxy cluster emission\\
{\scriptsize{$\bullet$}} Black hole accretion physics\\
{\scriptsize{$\bullet$}} Relativistic jets\\
{\scriptsize{$\bullet$}} Cosmological studies of structure formation

{\large\sc{References}}\vspace{-0.3cm}\\
\rule{\linewidth}{0.5pt}
Prof. Megan Donahue \hfill \href{mailto:donahue@pa.msu.edu}{donahue@pa.msu.edu}\\
Physics and Astronomy Department \hfill 1-517-884-5618\\
Michigan State University\\
East Lansing, MI 48824, USA

Prof. Mark Voit \hfill \href{mailto:voit@pa.msu.edu}{voit@pa.msu.edu}\\
Physics and Astronomy Department \hfill 1-517-884-5619\\
Michigan State University\\
East Lansing, MI 48824, USA

Prof. Brian McNamara \hfill \href{mailto:mcnamara@uwaterloo.ca}{mcnamara@uwaterloo.ca}\\
Department of Physics and Astronomy \hfill 1-519-888-4567 ext. 3817\\
University of Waterloo\\
Waterloo, ON N2L 3G1, Canada

Dr. Chiara Ferrari \hfill \href{mailto:ferrari@oca.eu}{ferrari@oca.eu}\\
Observatoire de la C\^ote d’Azur \hfill 33-492003028\\
Boulevard de l’Observatoire, B.P. 4229\\
Nice, 06304, France

Prof. Jack Baldwin \hfill \href{mailto:baldwin@pa.msu.edu}{baldwin@pa.msu.edu}\\
Physics and Astronomy Department \hfill 1-517-884-5611\\
Michigan State University\\
East Lansing, MI 48824 USA

Dr. Chris Carilli \hfill \href{mailto:ccarilli@nrao.edu}{ccarilli@nrao.edu}\\
National Radio Astornomy Observatory, PO Box O \hfill 1-575-835-7306\\
Socorro, NM 87801 USA

Dr. Paul Nulsen \hfill \href{mailto:pnulsen@cfa.harvard.edu}{pnulsen@cfa.harvard.edu}\\
Harvard-Smithsonian Center for Astrophysics \hfill 1-617-495-7043\\
60 Garden Street\\
Cambridge, MA 02138 USA

Dr. Mike Wise \hfill \href{mailto:wise@astron.nl}{wise@astron.nl}\\
ASTRON Radio Observatory \hfill 31-521596564\\
P.O. Box 2\\
NL 7990 AA Dwingeloo, The Netherlands\\

PI, S. Raychaudhury, {\textit{Birmingham Univ.}}\\
PI, A. Edge, {\textit{Durham Univ.}}\\
PI, R. Mandelbaum, {\textit{Princeton}}
PI, Mark Voit, {\textit{Mich. St. Univ.}}
PI, Megan Donahue, {\textit{Mich. St. Univ.}}
PI, Megan Donahue, {\textit{Mich. St. Univ.}}
PI, Mark Voit, {\textit{Mich. St. Univ.}}
PI, Mark Voit, {\textit{Mich. St. Univ.}}
PI, Brian McNamara, {\textit{Univ. Waterloo}}
