\documentclass[11pt]{cv}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}
\usepackage[T1]{fontenc}
\usepackage{mathptmx,multicol,common}
\pagestyle{empty}
\parindent 0pt
\parskip
\baselineskip
\setlength{\topmargin}{-0.30in}
\setlength{\oddsidemargin}{-0.30in}
\setlength{\evensidemargin}{-0.30in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0.25in}
\setlength{\topskip}{0.25in}
\setlength{\textwidth}{6.9in}
\setlength{\textheight}{9.25in}
\pagestyle{myheadings}

\begin{document}

\begin{center}
{\large \textbf{Kenneth W. Cavagnolo}}
\rule{17.35cm}{2pt}
\end{center}

\addresses
{
Observatoire de la C\^ote d'Azur\\
Boulevard de l'Observatoire\\
B.P. 4229\\
F-06304, Nice Cedex 4, France
}
{
+33-0492003109\\
+33-0492003033 (fax)\\
\href{mailto:kencavagnolo@gmail.com}{\tt{kencavagnolo@gmail.com}}\\
\href{http://www.pa.msu.edu/people/cavagnolo/}{\tt www.pa.msu.edu/people/cavagnolo/}\\
}

\begin{llist}

\sectiontitle{Education}
Michigan State University, Ph.D., Astronomy \& Astrophysics
\location{2005 - 2008}
Michigan State University, M.S., Astronomy \& Astrophysics
\location{2002 - 2005}
Georgia Institute of Technology, B.S., Physics
\location{1998 - 2002}

\sectiontitle{Research\\Experience}
LOFAR Postdoctoral Fellow, {\textit{Observ. de la C\^ote d`Azur}}
\location{Sept. 2010 - 2012}
Postdoctoral Fellow, {\textit{Univ. of Waterloo}}
\location{2008 - Sept. 2010}
Graduate Research Assistant, {\textit{Mich. St. Univ.}}
\location{2002 - 2008}
Undergraduate Research Assistant, {\textit{Geor. Inst. of Tech.}}
\location{2000 - 2002}

\sectiontitle{Research\\Program\\\& Interests}
My research program is focused on better understanding the connection
between AGN and their host environments, with a specific interest in
the role of AGN feedback on the formation and evolution of galaxies,
galaxy groups, and galaxy clusters.

\sectiontitle{Selected\\Publications}
{\sc {\textit{``Intracluster Medium Entropy Profiles for a Chandra Archival Sample Of Galaxy Clusters''}}}\\
{\bf K. Cavagnolo}, M. Donahue, G.~M. Voit, \& M. Sun; \href{http://adsabs.harvard.edu/abs/2009ApJS..182...12C}{ApJ Published, 2009}

{\sc {\textit{``An Entropy Threshold for Strong H$\alpha$ and Radio Emission in the Cores of Galaxy Clusters''}}}\\
{\bf K. Cavagnolo}, M. Donahue, G.~M. Voit, \& M. Sun; \href{http://adsabs.harvard.edu/abs/2008ApJ...683L.107C}{ApJ Published, 2008}

{\sc {\textit{``Bandpass Dependence of X-Ray Temperatures in Galaxy Clusters''}}}\\
{\bf K. Cavagnolo}, M. Donahue, G.~M. Voit, \& M. Sun; \href{http://adsabs.harvard.edu/abs/2008ApJ...682..821C}{ApJ Published, 2008}

{\sc {\textit{``Direct Evidence for an Outflow of Metal-Enriched Gas Along the Radio Jets of 
Hydra A''}}}\\
C. Kirkpatrick, M. Gitti, {\bf K. Cavagnolo}, B. McNamara, L. David, P. Nulsen, \& M. Wise; \href{http://adsabs.harvard.edu/abs/2009arXiv0909.2252K}{ApJL Published, 2009}

{\sc {\textit{``A Chandra X-ray Analysis of Abell 1664: Cooling, Feedback and Star Formation in the Central Cluster Galaxy''}}}\\
C. Kirkpatrick, B. McNamara, D. Rafferty, P. Nulsen, L. Birzan, F. Kazemzadeh, M. Wise, M. Gitti, \& {\bf K. Cavagnolo}; \href{http://adsabs.harvard.edu/abs/2009ApJ...697..867K}{ApJ Published, 2009}

{\sc {\textit{``Conduction and the Star Formation Threshold in Brightest Cluster Galaxies''}}}\\
G.~M. Voit, {\bf K. Cavagnolo}, M. Donahue, D. Rafferty, B. McNamara, \& P. Nulsen; \href{http://adsabs.harvard.edu/abs/2008ApJ...681L...5V}{ApJ Published, 2008}

{\sc {\textit{``Star Formation, Radio Sources, Cooling X-Ray Gas and Galaxy Interactions in the Brightest Cluster Galaxy in 2A0335+096''}}}\\
M. Donahue, M. Sun, C. O'Dea, G.~M. Voit, \& {\bf K. Cavagnolo}; \href{http://adsabs.harvard.edu/abs/2007AJ....134...14D}{AJ Published, 2007}

{\sc {\textit{``Entropy Profiles in the Cores of Cooling Flow Clusters of Galaxies''}}}\\
M. Donahue, D. Horner, {\bf K. Cavagnolo}, \& G.~M. Voit; \href{http://adsabs.harvard.edu/abs/2006ApJ...643..730D}{ApJ Published, 2006}

\end{llist}

\end{document}
