\indent The University of Wisconsin-Madison (UW) is an ideal host for
this project. The UW Astronomy and Physics Departments, Center for
Plasma Theory \& Computation, and Center for Magnetic
Self-Organization are home to (to name but a few) Sebastian Heinz (the
sponsor), Alex Lazarian, Leonid Malyshkin, Dan McCammon, Sne\v{z}ana
Stanimirovi\'{c}, Eric Wilcots, and Ellen Zweibel: all are experts in
one, or several, of the areas of X-ray/radio/polarization studies of
clusters, AGN feedback, computational modeling, and plasma
physics. Their experience with the latest techniques in numerical
simulations, radio interferometry, and high-energy physics will be
invaluable. UW is a \ska\ Consortium member, with Dr. Wilcots serving
on the science steering committee. {\bf{Year one:}} Data acquisition
begins, the archival project and tool development continue, I initiate
a collaboration with the UW plasma physics group to undertake
simulations addressing questions like: How do MHD instabilities couple
with ICM cooling and the accretion powering AGN activity?  What is the
relation between these processes, ICM temperature \& density, and
thermal instability formation? {\bf{Year two:}} Data acquisition
continues, first round of archival-based results is published, and
observation-model comparisons begin. {\bf{Year three:}} Data
acquisition and analysis of REXCESS conclude, second round of results
published, and the investigation of CMF origins and non-thermal
pressure support is underway.

