%%%%%%%%%%%%%%%%%%%
% Custom commands %
%%%%%%%%%%%%%%%%%%%

\newcommand{\mytitle}{Direct Evidence of Quasar Radiative and Mechanical Feedback in \iras}
\newcommand{\mystitle}{Feedback in \iras}
\newcommand{\iras}{IRAS 09104+4109}
\newcommand{\irs}{IRAS09}
\newcommand{\rxj}{RX J0913.7+4056}
\newcommand{\tsync}{\ensuremath{t_{\mathrm{sync}}}}
\newcommand{\refl}{\ensuremath{r_{\mathrm{refl}}}}
\newcommand{\fekaew}{\ensuremath{\mathrm{EW}_{\mathrm{K}\alpha}}}
\newcommand{\cltx}{\ensuremath{T_{\mathrm{cl}}}}
\newcommand{\leff}{\ensuremath{\lambda_{\mathrm{Edd}}}}
\newcommand{\lqso}{\ensuremath{\lbol^{\mathrm{QSO}}}}

%%%%%%%%%%
% Header %
%%%%%%%%%%

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{graphicx, here, common, longtable, ifthen, amsmath,
amssymb, natbib, lscape, subfigure, mathptmx, url, times, array}
\usepackage[abs]{overpic}
\usepackage[pagebackref,
  pdftitle={\mytitle},
  pdfauthor={Dr. Kenneth W. Cavagnolo},
  pdfsubject={ApJ},
  pdfkeywords={},
  pdfproducer={LaTeX with hyperref},
  pdfcreator={LaTeX with hyperref}
  pdfdisplaydoctitle=true,
  colorlinks=true,
  citecolor=blue,
  linkcolor=blue,
  urlcolor=blue]{hyperref}

\title[\mystitle]{\mytitle}

\author[Cavagnolo et al.]{K. Cavagnolo$^{1}$\thanks{Email:
    kcavagno@uwaterloo.ca}, M. Donahue$^{2}$, B. McNamara$^{1,3,4}$,
  G. M. Voit$^{2}$, and M. Sun$^{5}$\\
$^{1}$Department of Physics and Astronomy, University of Waterloo,
Waterloo, ON N2L 3G1, Canada.\\
$^{2}$Department of Physics and Astronomy, Michigan State University,
East Lansing, MI, 48824-2320, USA.\\
$^{3}$Perimeter Institute for Theoretical Physics, 31 Caroline St. N.,
Waterloo, Ontario, N2L 2Y5, Canada\\
$^{4}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street,
Cambridge, MA 02138, USA\\
$^{5}$Department of Astronomy, University of Virginia,
Charlottesville, VA, 22904, USA.}

\begin{document}

\date{Accepted 2010 Month DD. Received 2010 Month DD; in original form 2010 Month DD}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2010}

\maketitle

\label{firstpage}

%%%%%%%%%%%%
% Abstract %
%%%%%%%%%%%%

\begin{abstract}
  We present a detailed study of the hyperluminous infrared brightest
  cluster galaxy \iras\ using a deep \chandra\ X-ray observation. The
  X-ray observations reveal interaction between the galaxy's halo and
  the mechanical outflow \& radiative emission of the central AGN. We
  show that the properties of the \iras\ nucleus are consistent with
  reflected emission from an AGN embedded in a moderately
  Compton-thick medium. The observations indicate that \iras\ may be
  in transition from a radiatively-dominated to a
  mechanically-dominated mode of AGN feedback. We highlight why
  \iras\ is an ideal test case of a very short-lived but highly active
  stage of galaxy cluster and central galaxy formation.
\end{abstract}

%%%%%%%%%%%%
% Keywords %
%%%%%%%%%%%%

\begin{keywords}
cooling flows -- galaxies: clusters: general -- galaxies: clusters:
individual (\iras)
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%

\iras\ (hereafter, \irs) is an uncommon low-redshift ($z = 0.4418$)
ultraluminous infrared galaxy (ULIRG; $L_{\mathrm{IR}} > 10^{12}
~\lsol$). Unlike most ULIRGs, \irs\ is the brightest cluster galaxy
(BCG) in a rich galaxy cluster, but unlike most BCGs, \irs\ is a
Seyfert-2 with 99\% of the bolometric luminosity emerging longward of
1 \mymicron\ due to a heavily-obscured ($\nhobs > 10^{24} ~\pcmsq$)
quasar \citep{1988ApJ...328..161K, 1993ApJ...415...82H,
  1994ApJ...436L..51F, 1998ApJ...506..205E, 2000A&A...353..910F,
  2001MNRAS.321L..15I}.

Reduction of X-ray and radio data is discussed in Section
\ref{sec:obs}. ICM global (Section \ref{sec:global}) and radial
(Section \ref{sec:rad}) properties are then analyzed. Details
regarding the BCG, the ICM cavities, SMBH fueling, and QSO heating of
the ICM are given in Sections \ref{sec:bcg}, \ref{sec:cavs},
\ref{sec:fuel}, and \ref{sec:excess}, respectively. The complex
nuclear source is discussed in Section \ref{sec:centsrc}. We provide
interpretation of the results throughout and a supply a brief summary
in Section \ref{sec:summ}. \LCDM\ For our assumed cosmography, the
cluster redshift of $z = 0.4418$ corresponds to $\approx 9.1$ Gyr for
the age of the Universe, $\da \approx 5.72$ kpc arcsec$^{-1}$, and
$\dl \approx 2.45~\Gpc$. All errors are 90\% confidence unless stated
otherwise.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Observations and Data Reduction}
\label{sec:obs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Unless otherwise noted, all spectral fits were performed with the
\chisq\ statistic in \xspec\ 12.4.0 \citep{xspec} using an absorbed
single-temperature \mekal\ model \citep{mekal1, mekal2} with abundance
as a free parameter (\citealt{ag89} solar abundance distribution
assumed) over the energy range 0.7-7.0 keV. All spectral models had
the Galactic absorbing column density fixed at $\nhgal = 1.58 \times
10^{20} ~\pcmsq$ \citep{lab}. We assumed a mean molecular weight of
$\mu = 0.597$ and adiabatic index $\gamma = 5/3$ in all calculations
involving ICM gas.

%%%%%%%%%%%%%%%%%%%%%
\subsection{\chandra}
\label{sec:xray}
%%%%%%%%%%%%%%%%%%%%%%

A 77.2 ks observation of \irs\ was taken on 2009 January 09 with the
ACIS-I instrument (\dataset [ADS/Sa.CXO#Obs/10445] {ObsID 10445}; PI
Cavagnolo). The 9 ks archival \chandra\ observation of \irs\ from 1999
November 03 taken with the ACIS-S array was included in our analysis
(\dataset [ADS/Sa.CXO#Obs/00509] {ObsID 509}; PI Fabian). Both
datasets were reprocessed and reduced using \ciao\ and
\caldb\ versions 4.2. X-ray events were selected using \asca\ grades,
and corrections for the ACIS gain change, charge transfer
inefficiency, and degraded quantum efficiency were applied. Point
sources were located and excluded using {\textsc{wavdetect}} and
visual inspection. Light curves from a source free region of each
observation were created for a front-illuminated and back-illuminated
CCD and compared to look for flares. Time intervals which fell outside
$20\%$ of the mean background count rate were excluded. After flare
exclusion, the final exposure times for ObsID 509 and 10445 were 7 ks
and 76 ks, respectively.

For imaging analysis, the flare-clean events files were reprojected to
a common tangent point and summed. The astrometry of the ObsID 509
dataset was improved using a new aspect solution created with the
\ciao\ tool {\textsc{reproject\_aspect}} and the positions of several
field sources. The positional uncertainty introduced by the strong
angle dependence of the off-axis \chandra\ point-spread function (PSF)
was minimized by using sources closest to the aim-point. After
correction of the astrometry, the positional accuracy between both
observations was comparable to the resolution limit of the ACIS
detectors. We refer to the final point source free, flare-clean,
exposure-corrected images as the ``clean'' images. In Figure
\ref{fig:imgs} are the 0.5-10.0 keV mosaiced clean image of \rxj, a
zoom-in of the core region harboring \irs, and photons in the energy
range 4.35-4.50 keV associated with the \feka\ fluorescence line from
the nucleus (discussed in Section \ref{sec:centsrc}). Unless stated
otherwise, the X-ray analysis in this paper relates to the
\chandra\ data only -- \xmm\ and \bepposax\ data were re-analyzed for
the purposes of cross checking our \chandra\ analysis.

%%%%%%%%%%%%%%%%%
\subsection{\xmm}
\label{sec:xmm}
%%%%%%%%%%%%%%%%%

\xmm\ observed \irs\ on 2003 April 23 for 14 ks with the EPIC PN and
MOS detectors (ObsID 0147671001; PI Fiore). Data was reprocessed using
SAS version 7.1 and CCF release 258. Events files were created using
the tools {\textsc{EMCHAIN}} and {\textsc{EPCHAIN}} for patterns
0-4. Light curves were extracted from the energy range 10-12 keV for
the full field after \chandra\ identified point sources and cluster
emission were removed. After flare exclusion, the effective exposure
times for PN and MOS were 10 ks and 12 ks, respectively. A source
spectrum grouped to 20 counts per energy channel was extracted from a
region centered on the X-ray peak and extending to \rf\ (defined in
Section \ref{sec:global}). A background spectrum was extracted from a
source-free region with an area equal to the source region. Instrument
responses were generated with the tools {\textsc{ARFGEN}} and
{\textsc{RMFGEN}}. The \xmm\ data is utilized in Section
\ref{sec:centsrc} to check our results for the nuclear source against
the analysis presented in \citet{2007A&A...473...85P}.

%%%%%%%%%%%%%%%%%%%%%%
\subsection{\bepposax}
\label{sec:beppo}
%%%%%%%%%%%%%%%%%%%%%%

Conclusions reached in previous studies regarding the nature of the
\irs\ nuclear absorber have relied on the \bepposax\ hard X-ray
detection discussed by \citet{2000A&A...353..910F}. Here, we repeat
and confirm that analysis in order to compare our results in Section
\ref{sec:centsrc} against \citet{2000A&A...353..910F}. We retrieved
and re-analyzed the \bepposax\ PDS X-ray data (15-220 keV) taken 1998
April 18 (ObsCode 50273002; PI Franceschini). The data was reduced and
analyzed with \saxdas\ version 2.3.1 using the calibration data and
cookbook available from
HEASARC\footnote{http://heasarc.nasa.gov/docs/sax/shp\_software.html}. PDS
data was accumulated, screened for good time intervals, and then a
light curve was extracted to look for spikes caused by fluorescence of
only one of the four PDS crystal scintillators. No spikes were
detected.

A PDS total spectrum was extracted from the on-axis data, and
background subtraction was performed using the variable rise time
threshold. The epoch appropriate response function used in fitting was
selected from the HEASARC database. Following the HEASARC cookbook,
LECS and MECS spectra were also generated for the \rf\ region with a
background spectrum taken from an annulus outside \rf. We measured a
PDS 15-80 keV count rate of $0.106 \pm 0.055$ ct \ps. Fitting the PDS
spectrum over the energy range 20-200 keV with an absorbed power-law
having fixed spectral index of $\Gamma = 1.7$ yields fluxes of $f_{10
  \dash 200} = 2.09^{+1.95}_{-1.95} \times 10^{-11} ~\flux$ and $f_{20
  \dash 100} = 1.10^{+1.57}_{-1.63} \times 10^{-11} ~\flux$. These
values are consistent with the results presented in
\citet{2000A&A...353..910F}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\integral\ \& \swift}
\label{sec:integral}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In the following section, we show that \integral\ and \swift\ data do
not reveal any hard X-ray sources at the location of \irs, but the
upper limits are consistent with the \bepposax\ detection. Between the
beginning of 2005 and end of 2006, \irs\ was within the
\integral\ field of view (FOV) during 85 pointings. For 81 pointings,
data was collected with the IBIS Soft Gamma-Ray Imager (ISGRI;
$E_{\mathrm{sens}}$ = 15 keV-1 MeV), and for 79 pointings data was
collected with detector-1 of the Joint European X-ray Monitor (JEM-X;
$E_{\mathrm{sens}}$ = 3-35 keV). Datasets were reduced using
\osa\ version 8.0 and version 8.0.1 of the Instrument
Characteristics. For each instrument, mosaiced images of intensity,
significance, variance, and exposure were generated from the
background-subtracted images of each pointing. The combined ISGRI and
JEM-X effective exposure times are 200 ks and 210 ks, respectively.

Versions 1 and 30 of the \integral\ Reference Catalogue were used for
source detection. The \osa\ source detection routines did not locate
any $5\sigma$ sources in the ISGRI and JEM-X mosaiced
images. Additional visual inspection of the mosaiced ISGRI and JEM-X
images did not reveal any features which might suggest emission from a
source. The ISGRI and JEM-X instrument responses have a strong energy
dependence, thus, upper limits calculated using only the variance
images (\ie\ assuming uniform sensitivity) will systematically
underestimate the flux limit. To account for this variation, flux
upper limits were derived by integrating the ISGRI and JEM-X response
matrix functions (RMFs) over a specified energy range and weighting by
an assumed spectral shape.

We assumed the \irs\ $E> 10$ keV spectrum goes as $S_{\nu} =
\nu^{-1.7}$ with no high-energy cut-off. Between 10-35 keV and 20-100
keV, we derive $3\sigma$ upper limits of $f_{10 \dash 35} = 1.28
\times 10^{-12} ~\flux$ and $f_{20 \dash 100} = 5.70 \times 10^{-11}
~\flux$, respectively. The \integral\ $1\sigma$ 20-100 keV flux limit
is narrowly higher than the \bepposax\ 20-100 keV PDS measured
flux. The \integral\ 20-100 keV upper limit is also consistent with a
$z = 0.442$ source which would not be detected in the IBIS
Extragalactic AGN Survey \citep{2006ApJ...636L..65B}.

As a check of this result, the \swift-BAT archive was searched for
sources. No sources within $5\mydeg$ of \irs\ were detected in the 22
month \swift-BAT survey \citep{2010ApJS..186..378T}. The \swift-BAT
survey has a 14-195 keV $4.8\sigma$ detection limit of $2.2 \times
10^{-11} ~\flux$, which is 14\% higher than the 14-195 keV \irs\ flux
expected based on the \bepposax\ detection. Assuming the
\integral\ and \swift-BAT upper limits are representative of a
$1\mydeg$ region around \irs\ (\ie\ the FWHM PDS FOV), the lack of
detected hard X-ray sources near \irs\ suggests that the PDS detection
did not originate from a brighter off-axis source, assuming the source
is/was not transient or a one-off event.

%%%%%%%%%%%%%%%%
\subsection{VLA}
\label{sec:vla}
%%%%%%%%%%%%%%%%

Between the years 1986 and 2000, \irs\ was observed at multiple
frequencies with varying resolutions using the VLA radio
observatory. An analysis of 1.4 and 5 GHz VLA data is also presented
in \citet[][hereafter H93]{1993ApJ...415...82H}. Continuum mode
observations were taken from the VLA archive and reduced using version
3.0 of the Common Astronomy Software Applications (\casa). Flagging of
bad data was performed using a combination of \casa's
{\textsc{flagdata}} tool in {\textsc{rfi}} mode and manual
inspection. Radio images were generated by Fourier transforming,
cleaning, self-calibrating, and restoring individual radio
observations. The additional steps of phase and amplitude
self-calibration were included to increase the dynamic range and
sensitivity of the radio maps. All sources within the primary beam and
first side-lobe detected with fluxes $> 5\sigma_{\mathrm{rms}}$ were
imaged to further maximize the sensitivity of the radio maps.

Resolved radio emission associated with \irs\ is detected at 1.4 GHz,
5.0 GHz, and 8.4 GHz, while a $3\sigma$ upper limit of $0.84$ mJy is
established at 14.9 GHz. Fluxes for unresolved emission at 74 MHz, 151
MHz, and 325 MHz were retrieved from VLSS \citep{vlss}, 7C Survey
\citep{1999MNRAS.306...31R}, and WENSS \citep{1997A&AS..124..259R},
respectively. No formal detection is found in VLSS, however, an
overdensity of emission at the location of \irs\ is evident. For
completeness, we measured a flux for the potential source, but
excluded the value during fitting of the radio spectrum. The combined
1.4 GHz image reveals the most extended structure, and thus our
discussion regarding radio morphology is guided using this frequency.

The resolution of the combined 1.4 GHz dataset is $0.37\arcs$
pixel$^{-1}$ with an average beam shape of $1.26\arcs \times
1.15\arcs$ inclined at $-37.16\mydeg$ from north and an off-source rms
noise of $0.027$ mJy beam$^{-1}$. The deconvolved, integrated 1.4 GHz
flux of the continuous extended structure coincident with \irs, and
having $S_{\nu} \ga 3\sigma_{\mathrm{rms}}$, is $14.0 \pm 0.51$ mJy. A
significant spur of radio emission northeast of the nucleus is
detected with flux $0.21 \pm 0.07$ mJy. Radio contours were generated
beginning at 3 times the rms noise and moving up in 6 log-space steps
to the peak intensity of 4.7 mJy beam$^{-1}$. These are the contours
referenced in all following discussion of the radio source morphology
and its interaction with the X-ray gas.

Below we determine properties of the radio source for the purpose of
constraining the AGN outflow properties which created X-ray cavities
in the \rxj\ halo (see Section \ref{sec:cavs}). The radio spectrum was
fitted between 151 MHz and 8.4 GHz for the full radio source (lobes,
jets, \& core) with the well-known KP \citep{1962SvA.....6..317K,
  pach}, JP \citep{1973A&A....26..423J}, and CI
\citep{1987MNRAS.225..335H} synchrotron models. The models vary by
assumption of pitch-angle distribution and number of electron
injections. The models were fitted to the radio spectrum using the
code of \citet{2005ApJ...624..656W}, which is based on the method of
\citet{1991ApJ...383..554C}. The JP model (single electron injection,
randomized but isotropic pitch-angle distribution) yields the best fit
with \chisq(DOF)$ = 0.491(3)$, a break frequency of $\nu_B = 12.9 \pm
1.0$ GHz, and a low-frequency ($\nu < 2$ GHz) spectral index of
$\alpha = -1.10 \pm 0.09$. The bolometric radio luminosity was
approximated by integrating under the JP curve between $\nu_1 = 10$
MHz and $\nu_2 =$ 10,000 MHz, giving $\lrad = 1.09 \times
10^{42}~\lum$. The radio spectrum and best-fit models are shown in
Figure \ref{fig:radio}.

Assuming inverse-Compton (IC) scattering and synchrotron emission are
the dominant radiative mechanisms of the radio source, the time since
acceleration for an isotropic particle population is given by
\citet{2001AJ....122.1172S} as
\begin{equation}
  \tsync = 1590 \left(\frac{B^{1/2}}{B^2 + B_{\mathrm{CMB}}^2}\right)~
  \left[\nu_{\mathrm{B}} (1+z)\right]^{-1/2} ~\Myr
\end{equation}
where $B$ [\mg] is magnetic field strength, $B_{\mathrm{CMB}} =
3.25(1+z)^2$ [\mg] is a correction for IC losses to the cosmic
microwave background, $\nu_{\mathrm{B}}$ [GHz] is the radio spectrum
break frequency, and $z$ is the dimensionless source redshift. Note
that this form for \tsync\ neglects energy lost to adiabatic expansion
of the radio plasma \citep{1968ARA&A...6..321S}. We assume that $B$ is
not significantly different from the equipartition magnetic field
strength, $B_{\mathrm{eq}}$, which is derived from the minimum energy
density condition as \citep{1980ARA&A..18..165M}
\begin{equation}
  B_{\mathrm{eq}} = \left[\frac{6 \pi ~c_{12}(\alpha,\nu_1, \nu_2)
      ~\lrad ~(1+k)}{V \Phi}\right]^{2/7} ~\mathrm{\mg}
\end{equation}
where $c_{12}(\alpha,\nu_1,\nu_2)$ is a dimensionless constant derived
in \citet{pach}, \lrad\ [$\lum$] is the integrated radio luminosity
from $\nu_1$ to $\nu_2$, $k$ is the dimensionless ratio of lobe energy
in non-radiating particles to that in relativistic electrons, $V$
[\cc] is the radio source volume, and $\Phi$ is a dimensionless
radiating population volume filling factor. Synchrotron age as a
function of $k$ and $\Phi$ for the full radio source is shown in
Figure \ref{fig:radio}. For various combinations of $k$ and $\Phi$,
$B_{\mathrm{eq}} \approx 4 \dash 57 ~\mg$, with associated synchrotron
ages in the range $\approx 1 \dash 12$ Myr. Repeating the above
analysis using only radio lobe emission at 1.4 GHz, 5.0 GHz, and an
8.4 GHz upper limit, \tsync\ could be as high as $30$ Myr as a result
of a significantly steeper spectral index and lower break frequency.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Global ICM Properties}
\label{sec:global}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Our analysis begins at the cluster scale with the integrated
properties of the \rxj\ ICM hosting \irs. We define the mean cluster
temperature, \cltx, as the ICM temperature within a core-excised
aperture extending to $R_{\Delta_c}$, the radius at which the average
cluster density is $\Delta_c$ times the critical density for a
spatially flat Universe. We chose $\Delta_c = 500$ and used the
relations from \cite{2002A&A...389....1A} to calculate
$R_{\Delta_c}$. \irs\ has a luminous, cool core which is not
representative of \cltx, thus, the convention of
\citet{2007ApJ...668..772M} was followed and emission inside $0.15
~\rf$ was excised. Source spectra were extracted from the region $0.15
\dash 1.0~\rf$ and background spectra were extracted from reprocessed
\caldb\ blank-sky backgrounds (see Section \ref{sec:rad}). Because
\cltx\ and $R_{\Delta_c}$ are correlated in the adopted definitions,
they were recursively determined until three consecutive iterations
produced \cltx\ values which agreed within the 68\% confidence
intervals. We measure $\cltx = 7.54^{+1.76}_{-1.15}$ keV corresponding
to $\rf = 1.16^{+0.27}_{-0.19}~\Mpc$. Measurements for a variety of
$R_{\Delta_c}$ apertures are summarized in Table \ref{tab:specfits}.
The BCG nucleus emits strong \feka\ emission which affects the
spectral fitting, and for any aperture including the core, the nucleus
was excluded using a region twice the size of the \chandra\ PSF 90\%
EEF (see Section \ref{sec:centsrc} for details).

The cluster gas and gravitational masses were derived using the
deprojected radial electron density and temperature profiles presented
in Section \ref{sec:rad}. Electron gas density, $\nelec$, was
converted to total gas density as $n_g = 1.92 \nelec \mu \mH$ where
\mH\ [g] is the mass of hydrogen. The gas density profile was fitted
with a $\beta$-model \citep{betamodel}, and the temperature profile
was fitted with the 3D-$T(r)$ model of \citet{2006ApJ...640..691V} to
ensure continuity and smoothness of the radial log-space derivatives
when solving the hydrostatic equilibrium equation. Total gas mass was
calculated by assuming spherical symmetry and integrating the best-fit
$\beta$-model out to \rt, giving $\mgas(r<\rt) = 7.99 ~(\pm 0.65)
\times 10^{13} ~\msol$. The gravitating mass was derived by solving
the hydrostatic equilibrium equation using the analytic density and
temperature profiles. We calculate $\mgrav(r<\rt) = 7.22 ~(\pm 1.44)
\times 10^{14} ~\msol$, giving a ratio of gas mass to gravitating mass
of $0.11 \pm 0.02$. The gas and gravitating mass errors were estimated
from 10,000 Monte Carlo realizations of the measured density and
temperature profiles and their associated uncertainties.

In terms of the galaxy cluster population, \rxj\ resides toward the
high-end of the mass distribution with a luminosity-temperature ratio
and gas fraction consistent with flux-limited and representative
cluster samples \citep{hiflugcs2, 2009A&A...498..361P}. Adjusted for
differences in assumed cosmology, our global measurements agree with
prior studies of \irs\ \citep[\eg][]{2000MNRAS.315..269A}. With the
exception of the strange ULIRG/QSO BCG at its heart, \rxj\ appears to
be a typical massive, relaxed galaxy cluster. None of the integrated
X-ray cluster properties suggest the system has undergone a recent
major merger or cluster-scale AGN outburst which may have dramatically
disrupted the ICM. The lack of a detected radio halo also suggests no
recent merger activity, previous powerful AGN outbursts, and possibly
no turbulent motions in the core \citep[\eg][]{2008SSRv..134...93F}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Radial ICM Properties}
\label{sec:rad}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Now we discuss the finer global structure of \rxj\ via radial ICM
properties. Consistent with the analysis of Section \ref{sec:global},
the BCG nucleus was excluded from all radial analysis. Temperature
(\tx) and abundance ($Z$) profiles were created using circular annuli
centered on the cluster X-ray peak and containing 2.5K and 5K source
counts per annulus, respectively. A deprojected temperature profile
was generated using the \textsc{deproj} method in \xspec. We use the
projected profile in all analysis as it does not significantly differ
from the deprojected profile. Spectra were grouped to 25 source counts
per energy channel. \caldb\ blank-sky backgrounds were reprocessed and
reprojected to match each observation, and then normalized for
variations of the hard-particle background using the ratio of
blank-sky and observation 9.5-12 keV count rates. Following the method
outlined in \citet{2005ApJ...628..655V}, a fixed background component
was included during spectral analysis to account for the
spatially-varying Galactic foreground \citep[see][for more
  detail]{xrayband}. The temperature and abundance profiles are shown
in the top row of Figure \ref{fig:gallery}. After masking out all
X-ray substructure (see Section \ref{sec:excess}) and the central
$2\arcs$, a grouped spectrum for the central 20 kpc was fitted with a
thermal model plus cooling flow component. The best-fit model had a
mass deposition rate of $\mdot = 206^{+87}_{-65} ~\msol$ for upper and
lower temperatures of 5.43 keV and 0.65 keV, respectively, with
abundance $0.51 ~\Zsol$.

A surface brightness (SB) profile was extracted using concentric
$1\arcs$ wide circular annuli centered on the cluster X-ray peak. From
the SB and temperature profiles, a deprojected electron density
(\nelec) profile was derived using the \citet{kriss83} technique
\citep[see][for more detail]{accept}. Errors for the density profile
were estimated from 10,000 Monte Carlo bootstrap resamplings of the SB
profile. The SB and electron gas density profiles are shown in the
second row of Figure \ref{fig:gallery}.

Total gas pressure ($P = 2.4 \tx \nelec$), entropy ($K =
\tx\nelec^{-2/3}$), cooling time ($\tcool = 3n\tx~[2\nelec \nH
  \Lambda(T,Z)]^{-1}$), and enclosed X-ray luminosity (\lx) profiles
were also created. These profiles are presented in the bottom two rows
of Figure \ref{fig:gallery}. Uncertainties for each profile were
calculated by propagating the individual parameter errors and then
summing in quadrature. The cooling functions, $\Lambda(T,Z)$, used to
calculate cooling times were derived from the best-fit spectral model
for each annulus of the temperature profile and interpolated onto the
grid of the higher resolution density profile. The function $K(r) =
\kna +\khun (r/100 ~\kpc)^{\alpha}$ was fitted to the entropy profile,
giving best-fit values of $\kna = 12.6 \pm 2.9 ~\ent$, $\khun = 139
\pm 8 ~\ent$, and $\alpha = 1.71 \pm 0.10$.

The \rxj\ ICM structure is typical of the cool core class of galaxy
clusters, with a temperature profile that rises with increasing radius
and an entropy profile with a relatively small, flattened core. There
are no resolved discontinuities in the \tx, \nelec, or $P$ profiles to
suggest the presence of a shock or cold front.  The entropy profile is
consistent with the cool core population as a whole \citep{accept},
and, in particular, with the population of $\kna < 30 ~\ent$ clusters
that have radio-loud AGN and star formation in the BCG
\citep{haradent}. The $\kna \la 30 ~\ent$ scale also defines an
entropy regime in which thermal electron conduction in cluster cores
is too inefficient to suppress widespread environmental cooling
\citep{conduction}. Therefore, core sub-systems, like gas ram pressure
stripped from merging companions or ICM thermal instabilities, should
be long-lived. There is an abundance of cool, gaseous sub-structure
surrounding \irs, and in Section \ref{sec:bcg} we discuss the possible
relation of this structure to the the \rxj\ core environment and the
state of \irs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{ICM Cavity System}
\label{sec:cavs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%

To aid investigation of ICM substructure, a residual X-ray image was
created by subtracting a SB model for the ICM from the mosaiced
\chandra\ clean image. The \chandra\ clean image was binned by a
factor of 2 and the SB isophotes fitted with ellipses. The geometric
parameters ellipticity ($\epsilon$), position angle ($\phi$), and
centroid ($C$) were initially free to vary, but the best-fit values
for each isophote converged to mean values of $\epsilon = 0.52$, $\phi
= 72.5\mydeg$, and $C$ [J2000] = (09:13:45.5; +40:56:28.2). These
values were fixed in the fitting routine to eliminate the isophotal
twisting resulting from statistical variation of the best-fit values
for each radial step.

A SB model normalized to the parent image was constructed from the
best-fit isophote ellipses and subtracted from the parent image. The
resulting residual image is shown in Figure \ref{fig:resid}. The faint
SB decrements NW and SE of the nucleus in the parent image are
resolved into cylindrical voids in the residual image. The void and
radio jet morphologies closely trace each other, confirming they share
a common origin in the AGN outburst. Cavities are a well-known feature
of groups and clusters \citep[\eg][]{birzan04, 2005MNRAS.364.1343D},
but currently, \irs\ is the highest redshift object where cavities
have been directly imaged. In addition, \irs\ is thus far the only
example of a QSO-dominated system with an unambiguous cavity
detection. Using a 1994 \rosat\ HRI observation,
\citet{1995MNRAS.274L..63F} found a ``hole'' in the core of
\rxj\ which they attributed to absorption by a cooling flow. When
juxtaposed with the \chandra\ residual image, the ``hole'' is clearly
not associated with the real cavities, neither of which is resolved in
the 1994 HRI image nor the longer 1995 HRI follow-up observation.

The AGN outburst energetics were investigated using properties of the
cavities \citep[see][for a review]{mcnamrev}. Cavity volumes were
calculated by approximating each void in the X-ray image with a right
circular cylinder projected onto the plane of the sky along the radial
axis. The axis of the cylinders were assumed to lie in a plane
perpendicular to the line of sight that passes through the central
AGN. The energy in each cavity, $\ecav = \gamma PV/(\gamma-1)$, was
estimated by assuming the contents are a relativistic plasma ($\gamma
= 4/3$), and then integrating the total gas pressure profile over the
surface of each cylinder. The radio source morphology, spectrum, and
age suggest the jets were recently, or still are, being fed by the
central AGN. Thus, we assumed the cavities were created on a timescale
dictated by the ambient gas sound speed,
\tsonic\ \citep[see][]{birzan04}, and the distance the AGN outflow
traveled to create the cavity was set to the cylinder length. The
power of each cavity is thus $\pcav = \ecav/\tsonic$. Cavity power is
often assumed to be a good estimate of the physical quantity jet
power, \pjet, but note that neither accounts for energy which may be
imparted to shocks. Properties of the individual cavities are listed
in Table \ref{tab:cylcavities}.

The total cavity energy and power are estimated at $\ecav = 5.71 ~(\pm
0.89) \times 10^{59}$ erg and $\pcav = 3.41 ~(\pm 0.89) \times 10^{44}
~\lum$, respectively, with a mean $\pcav = 1.70 ~(\pm 0.45) \times
10^{44} ~\lum$. Radio power has been shown to be a reasonable
surrogate for estimating mean jet power \citep{birzan08}. Thus, we
checked the \pcav\ calculation using the \citet{pjet} \pjet-\prad\ 1.4
GHz and 200-400 MHz scaling relations. The relations give $\pjet
\approx 2 \dash 6 \times 10^{44} ~\lum$, in agreement with the X-ray
measurements. Compared with other systems hosting cavities,
\irs\ resides between the middle and upper-end of the cavity power
distribution. The AGN outburst is powerful, but there is nothing
unusual about the energetics or the radiative efficiency (\prad/\pjet)
given the cluster mass and ICM properties.

Of interest is how the AGN energetics compare to the cooling rate of
the host X-ray halo. The cooling radius was set at the radius where
the ICM cooling time is equal to $H_0^{-1}$ at the redshift of
\irs. We calculate $R_{\mathrm{cool}} = 128$ kpc, and measure an
unabsorbed bolometric luminosity within this radius of
$L_{\mathrm{cool}} = 1.61^{+0.25}_{-0.20} \times 10^{45} ~\lum$. If
all of the cavity energy is thermalized over $4\pi$ sr, then $\approx
20\%$ of the energy radiated away by gas within $R_{\mathrm{cool}}$ is
replaced by energy coming from the AGN. Assuming the mean ICM cooling
rate does not vary significantly on a timescale of $\sim 1$ Gyr, this
highly optimistic scenario implies that 5 similar power AGN outbursts
will significantly suppress cooling of the cluster halo.

Our calculations neglect the influence of shocks, but the synchrotron
age and cavity age are useful in addressing this issue. If \tsync\ is
an accurate measure of the radio source age, then the age discrepency
$\tsonic \ga 42$ Myr versus $\tsync \la 30$ Myr implies the AGN
outflow is supersonic, otherwise the radio-loud plasma will radiate
away all its energy prior to reaching the end of the observed jet and
would be radio-silent. The implication being that some amount of
energy may have gone into gas shocking. Recall, however, that no
shocks are detected in the X-ray analysis, and that the properties of
\irs\ nebulae are inconsistent with excitation due to shocks
\citep{1996MNRAS.283.1003C, 2000AJ....120..562T}. But, the nebular
regions studied are $> 20$ kpc from the jet axis, and may not be
indicative of gas dynamics close to the outflow. Regardless, the
energy in shocks was crudely estimated by setting $t_{\mathrm{sonic}}
= 20$ Myr and adjusting \pcav\ by the Mach number: $\Delta \pcav =
\Delta P / \Delta t$ and $\Delta P \propto M^3$. Relative to the ICM
sound speed, the velocity needed to reach the end of the radio jet in
20 Myrs requires a Mach number of $M \approx 2.5$, which brings the
outburst power up to $\approx 1 \times 10^{46} ~\lum$ ($\ecav \sim
10^{61}$ erg for a 20 Myr duration). Within the formal uncertainties,
the AGN outburst power is on the order of a few times $10^{44} ~\lum$,
with the possibility of being as large as $10^{46} ~\lum$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fueling the AGN Outburst}
\label{sec:fuel}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

An estimate of black hole mass, \mbh, is key to investigating what
powers an AGN outburst. There are a variety of \mbh\ estimators, many
of which rely on infrared or optical emission line measurements. The
integrated IR and emission line properties of \irs, however, are
dominated by hot dust and complex nebulae, and may not be
representative of \mbh. Therefore, \mbh\ was constrained using a
variety of relations and the weighted mean was used in subsequent
calculations. Using a stellar velocity dispersion of $\sigma_s = 293
\pm 6 ~\kmps$, determined from the \citet{1976ApJ...204..668F}
relation and the corrected $B$-band magnitude from HyperLeda
\citep{hyperleda}, the \citet{2002ApJ...574..740T} relation gives
$\mbh = 0.63 ~(\pm 0.05) \times 10^9 ~\msol$. The
\citet{2007MNRAS.379..711G} relations relating absolute $[B,R,K]$-band
magnitudes to \mbh\ predict $\mbh = 0.64 \dash 4.1 \times 10^9
~\msol$. The weighted mean \mbh\ value we adopt is $1.05 ~(\pm 0.17)
\times 10^9 ~\msol$.

Some of the gravitational binding energy of the material accreting
onto the SMBH is transported outward via relativistic jets. Assuming
this conversion has an efficiency $\epsilon$, the energy deposited in
cavities by the jets implies an accretion mass expressed as $\macc =
\ecav/(\epsilon c^2)$ with a time-averaged mass accretion rate of
$\dmacc = \macc/t_{\mathrm{sonic}}$. Setting $\epsilon = 0.1$, the AGN
outburst resulted from the accretion of $3.19 ~(\pm 0.49) \times
10^{6} ~\msol$ of matter at a rate of $0.063 \pm 0.017 ~\msolpy$. If
the accretion flow feeding the SMBH is spherical symmetry, it can be
characterized in terms of the Eddington (Eqn. \ref{eqn:edd}) and Bondi
(Eqn. \ref{eqn:bon}) accretion rates,
\begin{eqnarray}
  \dmedd &=& \frac{2.2}{\epsilon} \left(\frac{\mbh}{10^9~\msol}\right)
  ~\msolpy  \label{eqn:edd}\\
  \dmbon &=& 0.013 ~K_{\mathrm{Bon}}^{-3/2} \left(\frac{\mbh}{10^9
    ~\msol}\right)^{2} ~\msolpy \label{eqn:bon}
\end{eqnarray}
where $K_{\mathrm{Bon}}$ [\ent] is the mean entropy of gas within the
Bondi radius. The Eddington rate defines the maximal inflow rate of
gas not expelled by radiation pressure, as where the Bondi rate
approximates the quantity of hot, ambient gas captured by the
SMBH. Assuming $K_{\mathrm{Bon}} = \kna$, the derived \mbh\ gives
$\dmedd \approx 23 ~\msolpy$ and $\dmbon \approx 3.2 \times 10^{-4}
~\msolpy$. Thus, the Eddington and Bondi ratios for the accretion
event which powered the AGN outburst are $\dmacc/\dmedd \approx 0.003$
and $\dmacc/\dmbon \approx 350$.

The Bondi radius for \irs\ is unresolved ($\rbon = 9$ pc), and
$K_{\mathrm{Bon}}$ is likely less than \kna. For a Bondi ratio of at
least unity, $K_{\mathrm{Bon}}$ must be $\le 0.34 ~\ent$, lower than
is measured for even galactic coronae \citep{coronae}. In terms of
entropy, $\tcool \propto K^{3/2} ~\tx^{-1}$ \citep{d06}. Assuming gas
close to \rbon\ is no cooler than 0.5 keV, the accreting material will
have $\tcool < 6$ Myr, a factor of 60 below the shortest ICM cooling
time and 1/4 the free-fall time in the core. But this creates the
problem that gas close to \rbon\ is disconnected from cooling at
larger radii, breaking the feedback loop
\citep{2006NewA...12...38S}. If instead cold-mode accretion dominates,
then the gas which becomes fuel for the AGN is distributed in the BCG
halo, \eg\ $R \la 30$ kpc, and falls into the BCG as a result of
cooling \citep{pizzolato05, 2010arXiv1003.4181P}. Indeed, radial
filaments and gaseous substructure within 30 kpc of \irs\ are seen
down to the resolution-limit of
\hst\ \citep{1999Ap&SS.266..113A}. This may indicate the presence of
cooling, overdense regions similar to the cold blobs expected in
cold-mode accretion. The process of cold-mode accretion is more
consistent with the nature of \irs, and though Bondi accretion cannot
be ruled out, it does not seem viable.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{QSO Irradiation of the ICM}
\label{sec:excess}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In Figure \ref{fig:resid}, three regions of X-ray emission in excess
of the best-fit SB model are highlighted. The regions are illustrative
and approximate the constant SB contours used to define the spectral
extraction regions. Each region is denoted by its location relative to
the nucleus: northern excess (NEx), eastern excess (EEx), and western
excess (WEx). The NEx and WEx appear to be part of a tenuous, arc-like
filament which may be gas displaced by the NW radio jet. In other
clusters, structures similar to the NEx-WEx are found to be cool rims
of gas \citep[\eg][]{2009ApJ...697L..95B}, but the \chandra\ data is
insufficient to determine if this is the case for \irs, hence we treat
the NEx and WEx as separate structures.

Spectral analysis was performed on each region. A background spectrum
was extracted from regions neighboring the excesses which did not show
enhanced emission in the residual image. The backgrounds were scaled
to correct for differences in sky area. For each region, the ungrouped
source and background spectra were differenced in \xspec\ to create a
residual spectrum. To avoid systematically cooler best-fit
temperatures resulting from low count rates
\citep{1989ApJ...342.1207N}, the modified Cash statistic
\citep{1979ApJ...228..939C} was used during fitting. The low
signal-to-noise ratio (SN) of each spectrum precluded setting metal
abundance as a free parameter when fitting a thermal model. The three
excesses reside within the two central annuli of the abundance
profile, thus abundance was fixed at $0.51 ~\Zsol$. Varying the fixed
abundance by $\pm 0.2 ~\Zsol$ changed the output temperatures and
normalizations within the statistical uncertainties when $0.51 ~\Zsol$
was assumed. A fixed thermal component scaled to sky area representing
the ICM emission for the coincident annulus was included in the
fitting.

The NEx residual spectrum had low-SN which resulted in poor resolution
of spectral features. Thus, the thermal model had an unconstrained
temperature of $\sim 7$ keV, and similarly the power-law model had an
unconstrained spectral index of $\Gamma \sim 1.9$. The northern radio
jet terminates in the NEx region, and the hardness ratio map (see
Section \ref{sec:centsrc} and Figure \ref{fig:resid}) shows a possible
hot spot in this same area. The NEx may result from non-thermal
emission in the hot spot, but we cannot confirm this
spectroscopically.

The EEx and WEx residual spectra have characteristics consistent with
thermal emission. The best-fit values for the thermal models are given
in Table \ref{tab:excess}, and the discussion now focuses on just the
EEx. The EEx spectrum has prominent features at $E < 2$ keV which were
poorly fit by a single-component thermal model. The thermal
\feka\ complex was also poorly fit because of an obvious asymmetry
toward lower energies. To reconcile the poor fit, three Gaussians were
added to the modeling. Comparison of fit statistics and goodness of
fits determined from 10,000 Monte Carlo simulations of the best-fit
spectra suggest the model with the Gaussians is preferred. The
strength of the features relative to the continuum suggest a thermal
origin is unlikely, and that the features may be emission line blends.

\citet[][hereafter H99]{1999ApJ...512..145H} suggests the AGN which
produced the large-scale jets has been reoriented within the last few
Myrs, resulting in a new beaming direction close to the line of sight
and at roughly a right angle to the previous beaming axis. The new AGN
axis suggested by H99 is coincident with the EEx, the radio spur
northeast of the radio core, a cone of UV ionization, an ionized
optical nebula, and highly polarized diffuse optical emission. These
respective features are outlined in Figure
\ref{fig:resid}. \citet{2010MNRAS.402.1561R} demonstrate that the QSO
in H1821+643, which is 2 times more luminous than \irs, is capable of
photoionizing gas up to 30 kpc from the nucleus, and we suspect a
similar process may be occurring in \irs.

To test this hypothesis, reflection and diffuse spectra were simulated
for the nebula and ICM coincident with the EEx using
\cloudy\ \citep{cloudy}. The nebular gas density and ionization state
were taken from \citet{2000AJ....120..562T}, while the initial ICM
temperature, density, and abundance were set at 3 keV, 0.04 \pcc, \&
0.51 \Zsol, respectively. No Ca or Fe lines are detected from the
nebula coincident with the EEx, but strong Mg, Ne, and O lines are
\citep{2000AJ....120..562T}, possibly as a result of metal depletion
onto dust grains \citep[\eg][]{1993ApJ...414L..17D}. Thus, a metal
depleted, grain-rich, 12 kpc thick nebular slab was placed 15 kpc from
an attenuated $\Gamma = 1.7$ power law source with power $1 \times
10^{47} ~\lum$. Likewise, a $17 ~\kpc \times 16 ~\kpc$ ICM slab was
placed 19 kpc from the same source. The QSO radiation was attenuated
using a 15 kpc column of density 0.06 \pcc, abundance 0.51 \Zsol, and
temperature 3 keV. The output models were summed, folded through the
\chandra\ responses using \xspec, and fitted to the observed EEx
spectrum (shown in Figure \ref{fig:qso}).

In the energy range 0.1-10.0 keV, the nebula emission lines which
exceed the thermal line emission originate from Si, Cl, O, F, K, Ne,
Co, Na, \& Fe and occur as blends around redshifted 0.4, 0.6, 0.9, \&
1.6 keV. The energies and strengths of these blends are in good
agreement with the EEx spectrum. Further, the \feka\ emission from the
nebula is 100 times fainter than that from the ICM, and the observed
asymmetry of the EEx \feka\ emission results from the 6.4 keV
\feka\ photoionized line of the ICM. We conclude that beamed QSO
radiation is responsible for the nature of the EEx.

One alternative explanation for the EEx is that it is low entropy gas
uplifted from deeper within the core along the new AGN beaming
axis. Scattered UV emission 32 kpc from the core places a minimum
lifetime of 73 kyr for the new beaming direction (H93), and, assuming
saturated heat flux across the EEx surface, the evaporation time is
exceedingly short, $< 1$ Myr. These short timescales suggest the EEx
was transported to the present location at $> 20$ times the ambient
sound speed, or $v \sim 0.06 \dash 0.1c$, well below typical jet bulk
flow velocities. The radio spur has a 1.4 GHz luminosity of $\approx 3
\times 10^{39} ~\lum$, suggesting an associated 1 Myr old jet would
have $\sim 10^{57}$ erg of kinetic energy, which is sufficient to lift
$\sim 10^{10} ~\msol$ to a distance of 19 kpc. It appears uplift is
feasible, particularly if the gas is magnetically-shielded and
conduction is staved-off.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Nucleus X-ray Emission}
\label{sec:centsrc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The precise location and extent of the nuclear X-ray source were
determined using the \ciao\ tool {\tt wavdetect} and confirmed with a
hardness ratio map calculated as $HR = f(2.0 \dash 9.0 ~\keV) / f(0.5
\dash 2.0 ~\keV)$, where $f$ is the flux in the denoted energy
band. The $HR$ map and spectral extraction regions are shown in Figure
\ref{fig:nucleus}. A source extraction region was defined using the
90\% enclosed energy fraction (EEF) of the normalized \chandra\ PSF
specific to the nuclear source median photon energy and off-axis
position. The elliptical source region had an effective radius of
$1.16\arcs$. A segmented elliptical annulus with the same central
coordinates, ellipticity, and position angle as the source region, but
having 5 times the area, was used for the background region. The
background annulus was broken into segments to avoid the regions of
excess X-ray emission discussed in Section \ref{sec:excess}.

Source and background spectra were created using the \ciao\ tool {\tt
  psextract}. The source spectrum was grouped to have 20 counts per
energy channel. The background-subtracted \chandra\ spectra and
best-fit models are presented in Figure \ref{fig:nucleus}. The spectra
have been corrected for soft Galactic emission and ICM emission. The
significant flux difference below 1.3 keV is a result of the greater
effective area of the ACIS-S3 CCD in 1999 versus ACIS-I3 in
2009. Approximately 72\% of the 2009 spectrum (hereafter, SP09) is
from the source, with a count rate of $1.63 ~(\pm 0.06) \times
10^{-2}$ ct \ps\ in the 0.5-9.0 keV band. For the 1999 spectrum
(hereafter, SP99), 67\% is source flux, with a 0.5-9.0 keV count rate
of $2.71 ~(\pm 0.26) \times 10^{-2}$ ct \ps. We confirm the findings
of \citet{2001MNRAS.321L..15I} that the ICM thermal
\feka\ contribution to the nuclear spectrum is negligible, and that
prominent blended line-like features around 0.8 keV and 1.3 keV are
superposed on the reflection continuum.

Previous studies have shown the nuclear spectrum is best modeled as
Compton reflection from cold matter with a strong \feka\ fluorescence
line ($E_{\rm{rest}} = 6.4$ keV). The SP99 and SP09 were fitted
separately in \xspec\ over the energy range 0.5-7.0 keV with an
absorbed \pexrav\ model \citep{pexrav} plus three Gaussians. The
disk-reflection geometry employed in the \pexrav\ model is not ideal
for fitting reflection from a Compton-thick torus
\citep{2009MNRAS.397.1549M}, but no other suitable \xspec\ model is
currently available. Hence, only the \pexrav\ reflection component was
fitted and no high energy cut-off for the power law was used. Fitting
separate SP99 and SP09 models allowed for source variation in the
decade between observations, however $\Gamma$ was poorly constrained
for SP99 and thus fixed at the SP09 value. Using constraints from
\citet{2000AJ....120..562T}, the model parameters for reflector
abundance and source inclination were fixed at $1.0 ~\Zsol$ and $i =
50\mydeg$, respectively. Setting abundance as a free parameter did not
statistically improve the fits. The best-fit model parameters are
presented in Table \ref{tab:nucspec}.

Using a solar abundance thermal component in place of the two
low-energy Gaussians yielded a statistically worse fit. The model
systematically underestimated the 1-1.5 keV flux and overestimated the
2-4 keV flux. Leaving the thermal component abundance as a free
parameter resulted in $0.1 ~\Zsol$, \ie\ the thermal component tended
toward a featureless skewed-Gaussian. Strong Mg, Ne, S, and Si
K$\alpha$ fluorescence lines at $E < 3.0$ keV can be present in
reflection spectra \citep{1991MNRAS.249..352G}, as can Fe L-shell
lines from photoionized gas \citep{1990ApJ...362...90B}. We conclude
that the soft X-ray emission modeled using the Gaussians is likely a
combination of emission line blends and low-level thermal continuum,
whether the thermal component is nuclear or ambient in origin is
unclear.

The unabsorbed 2-10 keV {\it{reflected}} flux is $4.24^{+0.57}_{-0.55}
\times 10^{-13} ~\flux$ corresponding to a rest-frame $L_{2-10} =
1.57^{+0.19}_{-0.19} \times 10^{44} ~\lum$. Adjusted for cosmology,
this agrees with the measurement from
\citet{2001MNRAS.321L..15I}. Since we have used a pure reflection
model, the intrinsic QSO luminosity can only be estimated as
$(\kappa/\eta) L_{2-10}$ where $\kappa = 40$ is a bolometric
correction factor \citep{2007MNRAS.381.1235V} and $\eta = 0.06$ is the
reflector albedo \citep{2009MNRAS.397.1549M}. This gives $\lqso = 1.05
~(\pm 0.13) \times 10^{47} ~\lum$.

As a check for acceptable agreement between our models and results of
prior studies, the \rf\ \chandra, \xmm, and \bepposax\ spectra were
jointly fitted with our best-fit nucleus and ICM models
simultaneously. There were no significant differences between our
models and those of \citet{2000A&A...353..910F},
\citet{2001MNRAS.321L..15I}, and the \citet{2007A&A...473...85P}
reflection model. The value for the \feka\ equivalent width (\fekaew),
which is a valuable diagnostic for probing the environment of an AGN
\citep[see][for a review]{2000PASP..112.1145F}, also agrees with
previous measurements which found $\fekaew \la 1$ keV. The large
uncertainties associated with the individual SP99, \xmm, and
\bepposax\ \fekaew\ values prevents us from determining if
\fekaew\ has varied since 1998.

Our results are consistent with models and observations which show
that $\fekaew \ga 0.5$ keV is correlated with $\Gamma \ga 1.7$ and
reflecting column densities $\nhref \sim 10^{24} ~\pcmsq$
\citep{1996MNRAS.280..823M, 1997ApJ...477..602N, 1999MNRAS.303L..11Z,
  2005A&A...444..119G}. Previous studies suggested the \bepposax\ PDS
detection resulted primarily from transmission of hard X-rays through
an obscuring screen with $\nhobs > 10^{24} ~\pcmsq$. Extrapolating our
best-fit model out to 10-80 keV reveals statistically acceptable
agreement with the PDS data (see Figure \ref{fig:resid}). The 10-200
keV model flux is $f_{10 \dash 200} = 8.15^{+0.21}_{-0.19} \times
10^{-12} ~\flux$, which is not significantly different from the $f_{10
  \dash 200}$ measured with \bepposax. Addition of a second power-law
component ($\Gamma = 1.7$) absorbed by a $\nhobs = 3 \times 10^{24}
\pcmsq$ screen at the \irs\ redshift to the model lowered \chisq\ but
with no statistical improvement to the fit. If transmitted hard X-ray
emission falls within the passband used for spectral analysis,
$\Gamma$ would be artifically lowered, and the extrapolated hard X-ray
flux thus increases. However, for $\Gamma \ge 1.7$, column densities
$> 3 \times 10^{24} ~\pcmsq$ are sufficient to suppress significant
transmitted emission below the 7 keV spectral analysis cut-off,
indicating the best-fit model should not have an artificially low
$\Gamma$.

That we find no need for an additional hard X-ray component does not
contradict the well-founded conclusion that \irs\ harbors a
Compton-thick AGN. On the contrary, the measured \fekaew\ suggests
reflecting column densities of $\nhref \sim 1 \dash 5 \times 10^{24}
~\pcmsq$ \citep{1993MNRAS.263..314L, 2005A&A...444..119G,
  2010arXiv1005.3253C}. Assuming the density of material surrounding
the AGN is mostly homogeneous, \ie\ $\nhref \approx \nhobs$, our
results are consistent with the presence of a moderately Compton-thick
screen.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Evolution of the feedback mode?}
\label{sec:bcg}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Cosmological simulations typically segregate radiatively- and
mechanically-dominated feedback into a distinct early-time quasar-mode
\citep[\eg][]{2005Natur.435..629S} and a late-time radio-mode
\citep[\eg][]{croton06}, respectively. These modes of feedback are
used to ensure that SMBH-host galaxy co-evolution is in accordance
with observations \citep[\eg][]{magorrian}. The quasar-mode is
expected to be brief, expelling large quantities of cold gas from the
host galaxy \citep{2006ApJ...642L.107N}; whereas the radio-mode is
prolonged \& intermittent, heating the extended hot halo such that
cooling is regulated indefinitely \citep[see][for a
  review]{mcnamrev}. Examples of mechanical feedback are many
\citep[\eg][]{perseus1, ms0735}, and the best evidence of cold gas
expulsion by QSOs comes from low-luminosity, low-redshift early-type
galaxies \citep[\eg][]{2009ApJ...690.1672S}. In a unified feedback
model, there must be a transition from one mode to the other, and we
suspect \irs\ is one such example. But aside from the obvious AGN
mechanical feedback and irradiation of the ICM by the QSO, are there
other indications of quasar-mode feedback in the host galaxy which
would strengthen the case?

The H$_2$ mass of \irs\ is $< 10^{10} ~\msol$
\citep{1998ApJ...506..205E}, there is $< 10^8 ~\msol$ of cold dust
\citep{2001MNRAS.326.1467D}, no polycyclic aromatic hydrocarbon or
silicate absorption features are detected \citep{2004ApJ...613..986P,
  2008ApJ...683..114S}, and the hot dust mass is $\sim 10^9 ~\msol$
\citep{1997A&A...318L...1T}. Additionally, the \halpha\ luminosity
exceeds $10^{42} ~\lum$ \citep{1996MNRAS.283.1003C,
  1998ApJ...506..205E}. Based on these measurements, and compared with
other BCGs \citep[\eg][]{2001MNRAS.328..762E}, \irs\ appears to be
gas-poor with a low gas-to-dust ratio. All told, the lack of strong
molecular gas indicators around such a powerful QSO is odd. One
possible explanation for the discrepency is that the QSO is driving
gas out of the galaxy via non-relativistic winds, radiation pressure,
or a combination of both. Indeed, integral field spectroscopy
indicates the presence of a $> 1000 ~\kmps$ emission line outflow
coincident with the nucleus \citep{1996MNRAS.283.1003C}. Further, the
CO observations used to infer the H$_2$ mass
\citep{1998ApJ...506..205E} were not sensitive to velocities $> 300
~\kmps$, the regime where molecular gas being expelled at
high-velocities ($\sim 1000 \kmps$) by QSO winds might be detected.
Given that rapid \& extensive dust formation is also expected in such
QSO winds \citep{2002ApJ...567L.107E}, this may further explain the
extreme dust richness of \irs.

\citet[][hereafter F09]{2009MNRAS.394L..89F} show that QSO/AGN
radiation pressure has a significant influence on dusty material in
the host galaxy. F09 define the effective Eddington ratio for dusty
gas to be $\leff = \lqso (1.38 \times 10^{38} ~\mbh)^{-1}$, and for
\irs, this has a value of $\approx 0.72$. F09 also present a plane for
\nhobs-\leff\ which is divided into regions where obscuring clouds are
either long-lived or experience the effects of a super-Eddington AGN,
\ie\ where clouds are efficiently expelled. In this plane,
\irs\ resides near the boundary of the two regions, close enough that
it is reasonable to suspect that the massive reservoir of dust-laden
gas in the galaxy is being heated, ionized, or accelerated away from
the QSO by radiation pressure. These conclusions are, however, at the
mercy of our choice for \mbh, \ie\ if $\mbh \ge 5 \times 10^9 ~\msol$,
then $\leff < 0.2$, as where $\mbh < 1 \times 10^9 ~\msol$ implies
$\leff > 1$.

All three of the primary channels for QSO/AGN feedback to influence
its environment (jets, winds, radiation) are conceivably active in
\irs, and it may be that these processes are simultaneously conspiring
to quench cooling within and around the host galaxy. But are we really
witnessing the evolution from one dominant form of feedback to
another? The mass accretion rate required to power the QSO is $\dmacc
= \lqso/(0.1 c^2) \approx 20 ~\msolpy$, 300 times larger than
\dmacc\ needed to power the jets. At this rate, the black hole mass
will double in $\approx 50$ Myr, and for the Magorrian relation to
hold, $> 10^{11} ~\msol$ of stars would need to form, $> 10\%$ of the
current bulge mass. This seems unlikely, and thus the current period
of QSO activity should be fleeting, giving way to a sustained period
of sub-Eddington accretion which can readily power an AGN but not a
QSO. The emergence of jets may be signaling this change. Further, H93
and H99 discuss in detail that the misalignment between the
large-scale radio jets and beamed nuclear radiation may be correlated
with the FR-II to FR-I evolution of the radio source, and that jet
axis realignment must have transpired in less than a few Myrs.

The origin of the misalignment and its relation to the feedback mode
cannot be determined with any certainty, but one can speculate. For
example, there may be multiple SMBHs in the nucleus, each with their
own beaming direction. In the following discussion we assume the jet
and spin axes of an AGN are aligned. One explanation for the
misalignment is that it was caused by a ``spin-flip''
\citep{2002Sci...297.1310M} of the \irs\ SMBH when a smaller black
hole merged with it. Given that \irs\ is a cD galaxy, which are known
for cannabilism, and that 6 possible companion galaxies reside within
a projected 80 kpc of the galaxy \citep{1996AJ....111..649S,
  1999Ap&SS.266..113A}, it is not unlikely that one or more mergers
have taken place in the last few Myrs. However, black hole mergers are
lengthy (few Gyrs) and difficult processes, and the spin axes of the
merging black holes may naturally align when in a gas-rich environment
\citep{2007ApJ...661L.147B}. But, in the spin evolution framework of
\citet{2010arXiv1004.1166G}, mergers are not needed to drastically
change the spin axis. \citet{2010arXiv1004.1166G} suggest that the
evolution of the black hole spin state relative to accreting matter
from retrograde to prograde may be correlated with a transition from
FR-II to FR-I. During this process, the black hole will naturally pass
through a state where the spin is small. At this point, if there is an
assymetric accretion flow, the spin axis can be dramatically realigned
on timescales of a few Myrs (Cavagnolo et al., in preparation),
possibly giving rise to the type of misalignment observed in \irs.

%%%%%%%%%%%%%%%%%
\section{Summary}
\label{sec:summ}
%%%%%%%%%%%%%%%%%

In this paper we show that the powerful BCG radio source is driving a
supersonic plasma outflow with mechanical power $\sim 10^{44}
~\lum$. We also show, via detection of an X-ray excess 13-26 kpc NE of
the nucleus, radiation from the $\sim 10^{47} ~\lum$ QSO is escaping
the nucleus and interacting with the ICM in the same region as
strongly photoionized \& polarized optical emission are detected.

We have presented analysis of the ULIRG \iras\ and the host galaxy
cluster \rxj\ using a new 75 ks \chandra\ X-ray observation. The
results presented in this paper are as follows:
\begin{itemize}
\item The \rxj\ ICM global and radial properties reveal no signs of
  shocks, cold fronts, or deviations from hydrostatic equilibrium to
  suggest disruption by a major merger or cluster-scale AGN
  outburst. \rxj\ is an unremarkable, massive, cool-core galaxy
  cluster with a 12 \ent\ core entropy, $M \propto T^{3/2}$, and mean
  gas fraction of 0.11.
\item We have discovered cavities in the X-ray halo of \irs\ which
  indicate an AGN outburst with mechanical power of at least $3 \times
  10^{44} ~\lum$, a hundredth of the QSO radiative power, $1 \times
  10^{47} ~\lum$. Comparison of cavity sound speed age and radio
  source age indicate the outflow may be supersonic, and if gas
  shocking has occurred, the total kinetic power of the AGN may be
  $\sim 10^{46} ~\lum$.
\item We have determined that cold-mode accretion is a preferable
  explanation for the nature of \irs. We also show that the QSO has a
  high effective Eddington luminosity of $\approx 0.7$, indicating
  radiation pressure should be expelling dusty clouds from \irs.
\item We have resolved substructure in the X-ray halo coincident with
  the [O \Rmnum{3}] nebula NE of the nucleus. The X-ray emission
  properties of this region are well-fit by a model where the nebula
  and ICM are being irradiated by the QSO.
\item The nuclear X-ray source is well-fit by a power law source
  obscured by Compton-thick material. The \fekaew\ indicates a
  reflecting column density, and presumably obscuring column density,
  of $> 10^{24} \pcmsq$. We also show that the \bepposax\ detected
  hard X-ray emission results from reflected nuclear emission.
\end{itemize}

In this paper, we explore the possibility that the QSO in \irs\ has
expelled, and/or sufficiently heated, the galactic gas reservoir which
has been providing fuel for the supermassive black hole (SMBH), and
that the associated jets are suppressing cooling of the X-ray halo
from which the galactic reservoir would be re-supplied. Further, we
confirm the conclusion of \citet{1996MNRAS.283.1003C} that the BCG
nebular velocities and gas masses are inconsistent with a scenario in
which the gas reservoir was deposited by stripping or tidal
interactions. Based on the AGN outburst energetics, it is shown that
Bondi accretion is unlikely to be responsible for fueling the AGN.

\irs\ simultaneously shows the characteristics of a system in quasar-
and radio-mode. The photoionized region NE of the nucleus, high \leff,
low gas-to-dust ratio, and strong nuclear optical outflow all suggest
the central 30 kpc of \rxj\ is dominated by radiative feedback from
the QSO in \irs. At the same time, the X-ray cavities and radio
outflow show an AGN actively suppressing cooling of the ICM. \irs\ may
be a local example of how massive galaxies at higher redshifts evolve
from quasar-mode into radio-mode.

%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%

KWC \& MD were supported by SAO grant GO9-0143X, and MD acknowledges
support through NASA LTSA grant NASA NNG-05GD82G. KWC \& BRM thank the
Natural Sciences and Engineering Research Council of Canada for
support. KWC thanks Alastair Edge \& Niayesh Afshordi for helpful
insight, and Guillaume Belanger \& Roland Walter for advice regarding
\integral\ data analysis. The \cxo\ Center is operated by the
Smithsonian Astrophysical Observatory for and on behalf of NASA under
contract NAS8-03060. The VLA (Very Large Array) is a facility of the
National Radio Astronomy Observatory (NRAO), which is a facility of
the National Science Foundation operated under cooperative agreement
by Associated Universities, Inc. This research has made use of: data
obtained from the Chandra Data Archive, the Chandra Source Catalog,
software provided by the Chandra X-ray Center (CXC), the NASA/IPAC
Extragalactic Database, and the NASA Astrophysics Data System.

%%%%%%%%%%%%%%%%
% Bibliography %
%%%%%%%%%%%%%%%%

\bibliographystyle{mn2e}
\bibliography{cavagnolo}

%%%%%%%%%%%%%%%%%%%%%%%
% Figures  and Tables %
%%%%%%%%%%%%%%%%%%%%%%%

%% \clearpage
%% \onecolumn
%% \input{specfits.tex}
%% \input{excess.tex}
%% \input{cylcavities.tex}
%% \input{nucspec.tex}
%% \clearpage
%% \input{figs.tex}

%%%%%%%%%%%%%%%%%%%%
% End the document %
%%%%%%%%%%%%%%%%%%%%

\label{lastpage}
\end{document}

%% -- if nothing else, multi smbhs, when they are qsos, could more
%% readily destory an obscuring cocoon?
%% AGN feedback implementation in models
%% - Quasar mode (Kauffmann \& Haehnelt 2000)
%% - Powerful outflow evacutes gas and quenches star formation
%% immediately (not clear required by observations)
%% - Tremonti et al 2007 find high velocity outflows in post starburst
%% (also post- AGN) systems
%% - Radio mode (Croton et al. 2006)
%% - Heating of hot gas envelope of galaxies stops further gas cooling
%% - Very successful qualitatively
%% - Particularly effective when have hot gas as working surface (Dekel,
%% Cattaneo)
%% - P. Hopkins et al. 2006-present
%% - good to have deep X-ray hi-res spectroscopy to directly determine
%% the mass deposition rate from the X-ray halo

%% \rbon &=& 32 \left(\frac{\tx}{\keV}\right) \left(\frac{\mbh}{10^9
%%   ~\msol}\right) ~\pc\\
%% \dmbon &=& 0.01 \left(\frac{\nelec}{\pcc}\right)
%% \left(\frac{\tx}{\keV}\right)^{-3/2} \left(\frac{\mbh}{10^9
%%   ~\msol}\right)^{2} ~\msolpy \label{eqn:edd}\\

%% \begin{equation}
%%   \mgrav(< r) = -\frac{r \tx(r)}{G \mu \mH}\left[\frac{d\ln
%%       \tx(r)}{d\ln r} - \frac{d\ln n_g(r)}{d\ln r}\right]
%% \end{equation}
%% where (all cgs) $k$ is the Boltzmann constant, $G$ is the
%% gravitational constant, \mH\ is hydrogen mass, $\tx(r)$ and
%% $\nelec(r)$ are the radial X-ray gas temperature and gas density
%% profiles, respectively.

%% Potentially emitting species were first identified using the
%% ATOMDB\footnote{http://cxc.harvard.edu/atomdb/WebGUIDE/}. The
%% strongest lines within 0.1 keV of the 0.91 keV feature belong to Mg
%% \Rmnum{11} and Fe \Rmnum{21}, while for the 1.31 keV feature Si
%% \Rmnum{13} is the strongest. The emission around 4.4 keV broadening
%% the thermal rest-frame \feka\ 6.7 and 6.9 keV complex is consistent
%% with the rest-frame 6.4 keV \feka\ line.

%% The mass-energy going into the SMBH and not the jets is expressed
%% as $\dmbh = (1-\epsilon) \macc$ with a time-averaged rate of
%% $\ddmbh = \dmbh/t_{\mathrm{sonic}}$. The black hole mass thus grew
%% by $2.87 ~(\pm 0.44) \times 10^{6} ~\msol$ (6\% of the original
%% \mbh) at a rate of $0.057 \pm 0.015 ~\msolpy$.

%% The \rxj\ ICM cooling rate is $\mdot > 100 ~\msolpy$. Even at $0.1
%% \mdot$, in $\approx 1$ Gyr a gas reservoir exceeding $10^{10}
%% ~\msol$ should condense out of the ICM onto the BCG.

%% \citet{2004ApJ...608...62S} model of QSO feedback requires that 5\%
%% of \lqso\ goes into kinetic power of an outflow, which is $5 \times
%% 10^{45} ~\lum$ in this case.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Megan's v1 comments

It will take me a little longer to really digest your intricate
arguments about feeding the AGN and the illumination spectra, but I
really do appreciate the intellectual efforts here!  I think the paper
has basically what it needs except for a real introduction and an
abstract. The current introduction jumps immediately into details
without giving context to a reader without cluster/AGN expertise
(think graduate students/ non-X-ray astronomers etc.). The next step
may be to write a draft of the abstract, with specifics about your
conclusions, and with that hovering over the intro, that will allow
you to write a more accessible intro, ending with something like ``To
investigate these questions, we present a case study of X-ray and
radio observations of an unusual brightest cluster galaxy and ULIRG,
IRAS 09...''

What's currently in the introduction belongs in a ``Review of known
properties of IRAS 09'' and complete with a really brief summary of
what we're going to claim about the source.

Input from the other authors will help refine & clarify your arguments
about the AGN - shall we pass this by Mark next?  (After a draft
abstract and intro are in place.)  He'd also have some good
suggestions about where to start, as well as applying some AGN
expertise to your AGN analysis.

Anyway, here's a start - see comments (more) and edits (few). I'll try
to read through it more carefully soon, but since I'm recommending
some macro re-organization, I figured that you'd like to hear about
sooner than details. In the AGN category I do not feel expert enough
to make canonical pronouncements :) but I'll definitely have more
questions -- some of them may be more naive than others, so have
patience on that.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
stripping
%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%

Using the \rxj\ radial density structure, the ram pressure stripping
analysis presented in \citet{a1664}
%% Elaborate on this a little more - it's a little too cryptic. The
%% next sentence does not follow at all, so help us readers out a
%% little.
was performed to investigate how much of the BCG gas reservoir could
be deposited by the 6 compact spheroids ($r < 2.5$ kpc;
$M_{\mathrm{V}} > -17$ mag) within a projected 80 kpc of the BCG
\citep{1996AJ....111..649S, 1999Ap&SS.266..113A}. We estimated a
cluster velocity dispersion of $\sigma_{\mathrm{gal}} \approx 1109 \pm
259 ~\kmps$ using the relations from \citet{2000MNRAS.318..715X}. The
ICM density dictates that only $10^{11 \dash 12} ~\msol$ spirals will
be efficiently stripped if they are traveling at $> 700 ~\kmps$ inside
of 37 kpc.
%% Not sure what you're saying here.  My confusion may be caused by
%% the position of the word ``only'' in the sentence.
Our analysis indicates even if 6 gas-rich galaxies ($M_{\mathrm{gas}}
= 2 \dash 5 \times 10^8 ~\msol$) were stripped bare, they still
contribute 5-10 times too little gas to explain the reservoir in \irs.
%% Then the stripping analysis is kind of unnecessary -- the extreme
%% approximation (requiring zero knowledge of velocities and
%% densities) that ALL of the gas-rich galaxies' gasses were removed
%% still doesn't explain the reservoir. But why limit the BCG's source
%% of gas to those within 80 kpc?
If the spheroids are instead tidally-truncated compact ellipticals
similar to M32, it is odd that the mean projected separation among
them is $30 \pm 15$ kpc, 8-15 times the expected tidal radius of each
object.
%% I'm not sure I understand this argument. What kinds of timescales
%% are you assuming?

If the spheroids have interacted with each other, or the BCG,
to the point of tidal truncation, then to have such large separations
requires huge relative velocities. Yet, the BCG nebulae which may have
been stripped from the spheroids have small velocities relative to the
BCG \citep{1996MNRAS.283.1003C}. But the relaxation and dynamical
friction time scales in the core are $\sim 10^{8-9}$ yr, 10-100 times
the free-fall time, so if the gas is old enough to have slowed, then
it should have fallen into the BCG, unless the gas has high angular
momentum or is in a stable orbit.
%% This paragraph is hard to follow.  I'm not sure I get the argument.

If mergers are responsible for the accumulation of cold gas in the
core, it is odd that the radio source is very linear. Bulk motion and
turbulence induced by mergers would disrupt the radio plasma
\citep[\eg][]{2009A&A...495..721S, 2010arXiv1002.0395S}, indicating
that the core has been mostly undisturbed for $> 12$
Myr. Alternatively, mergers could have been very gentle so as not to
stir the core gas, but then how was gas stripped from the galaxies?
We thus conclude that the gas reservoir likely did not result from
mergers, but most likely from a cooling flow.
%% The counter argument to this is: how did the gas get dusty then? If
%% the gas is ex-cooling flow gas, it was recently at X-ray emitting
%% temperatures, and such gas has a very short sputtering time. So if the
%% gas came from a hot ICM, the dust must have come from somewhere
%% else...

%% I'm uncomfortable with the conclusive tone of this sentence.  You've
%% presented some circumstantial evidence suggesting that the gas
%% reservoir cannot come from other galaxies, but it's not quantitatively
%% airtight.  In particular, 12 Myr is an eyeblink compared with the
%% timescale of a merger. There's also another potential source of gas:
%% normal stellar mass loss from the BCG, which I think has been woefully
%% underinvestigated.

\item Using the \rxj\ gas density profile, we have determined that the
  measured BCG gas mass appears to exceed the amount of gas which can
  be efficiently removed from cluster members via the process of ram
  pressure stripping. We also find that tidal stripping is an unlikely
  explanation for the nature of spheroids found in the cluster core,
  further suggesting that subcluster mergers are an unlikely source
  for the gas reservoir in \irs. The highly linear radio source
  morphology further indicates that merger activity has ceased for at
  least the last 12 Myr.
%% Again, not long compared to merger timescales
