\documentclass[11pt]{cv}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}
\font\cap=cmcsc10
\topmargin 0pt
\headheight 0pt
\headsep 0pt
\textheight 9in
\pagestyle{empty}
\parindent 0pt
\parskip
\baselineskip
\topmargin 0in
\oddsidemargin -0.25in
\evensidemargin -0.25in
\textwidth 6.9in
\setlength{\topmargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\topskip}{0.4in}
\setlength{\textheight}{9.3in}
\pagestyle{myheadings}
\begin{document}

\markright{K.W. Cavagnolo Resum\'{e}}

\begin{center}
{\large \textbf{\sc Resum\'{e} of Kenneth W. Cavagnolo}}\\
\rule{17.35cm}{1pt}\\
\end{center}
\normalsize

\addresses
{
{\bf Office Address}\\
Michigan State University\\
Department of Physics \& Astronomy\\
3265 Biomedical Physical Sciences Building\\
East Lansing, MI 48824-2320\\
Phone: 1-517-355-9200 ext.2443\\
}
{
{\bf Mailing Address}\\
1111 Kimberly Dr, Apt. \#7, Lansing MI 48912\\
Phone: 1-517-285-9062\\
Fax: 1-517-353-4500\\
E-mail: \href{mailto:cavagnolo@pa.msu.edu}{\tt cavagnolo@pa.msu.edu}\\
Web: \href{http://www.pa.msu.edu/people/cavagnolo/}{\tt www.pa.msu.edu/people/cavagnolo/}\\
}

\begin{llist}

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Education}
\employer{{\bf Michigan State University}}
\location{2005 - Present}
Ph.D. Astrophysics, Expected May-August 2008\\
Thesis Title: ``Feedback, Evolution, and Dynamics in Clusters of Galaxies''\\
Thesis Advisors: Dr. Megan Donahue \& Dr. G. Mark Voit

\employer{{\bf Michigan State University}}
\location{2002 - 2005}
M.S. Astrophysics

\employer{{\bf Georgia Institute of Technology}}
\location{1998 - 2002}
B.S. Physics {\it Cum Laude}

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Research\\Experience}
{\sc \bf{Graduate Research Assistant}}
\location{2003 - Present}
Supervisor: Dr. Megan Donahue, {\textit{Mich. St. Univ.}}\\
Studying clusters of galaxies via their X-ray properties to\\
investigate feedback mechanisms, galaxy evolution, and the process\\
of cluster virialization.

{\sc \bf{Graduate Research Assistant}}
\location{2002 - 2003}
Supervisor: Dr. Jack Baldwin, {\textit{Mich. St. Univ.}}\\
Analyzing echelle spectra for use in studies of {\textit{s}}-process abundances\\
in planetary nebulae.

{\sc \bf{Undergraduate Research Assistant}}
\location{2000 - 2002}
Supervisor: Dr. James Sowell, {\textit{Georgia Tech}}\\
Obtaining orbital solution for the eclipsing Algol binary ET Tau via\\
UBV light curves and spectroscopic radial velocity curves.

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Research\\Interests}
{\sc $\bullet$ Feedback Mechanisms in Galaxy Clusters}\\
{\sc $\bullet$ Galaxy Formation}\\
{\sc $\bullet$ Supermassive Black Holes}\\
{\sc $\bullet$ AGN Accretion Physics}\\
{\sc $\bullet$ Large Scale Structure Formation and Cosmology}
%{\sc $\bullet$ Galaxy Cluster Evolution}\\
%{\sc $\bullet$ High-redshift Cluster Finding}\\

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Teaching\\Experience}
{\sc \bf{Substitute Instructor}}
\location{Fall 2006}
Course: ``Visions of the Universe''\\
Gave lectures covering stellar evolution, supernovae, white dwarves,\\
neutron stars, and black holes.

{\sc \bf{Physics Tutor}}
\location{Summer 2003}
Course: ``Introductory Honors Physics I \& II''\\
Tutored physics students taking introductory physics courses such as\\
classical mechanics, optics, and electromagnetism.

{\sc \bf{Graduate Teaching Assistant}}
\location{2002 - 2003}
Course: ``Visions of the Universe''\\
Directed and supervised laboratories for non-calculus based\\
astronomy course.

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Honors}
- College of Natural Science Dissertation Fellow \hfill 2007 - Present\\
- American Astronomical Society Member\hfill 2002 - Present\\
- American Physical Society Member\hfill 2002 - Present\\
- NASA Center for Astronomy Education Participant\hfill 2007\\
- Sigma Pi Sigma National Honor Society \hfill 2001 - Present\\
- Dean's List, Georgia Tech \hfill 1998-2002

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Scientific\\Skills}
- Profound skills in reducing and analyzing data taken with {\textit{Chandra}} X-ray Telescope.\\
- Extensive experience with {\tt{CIAO}} and {\tt{CALDB}}.\\
- Familiarity with multiwavelength analysis packages: {\tt{AIPS}}, {\tt{IRAF}}, and {\tt{PyRAF}}.\\
- Fluent in Perl, IDL, LaTeX, and HTML.\\
- Working knowledge of Bash, C, CSH, Flash, Fortran, MySQL, and Supermongo.\\
- Mastery of multiple computing architectures: UNIX/Linux, Macintosh, and Windows.\\
- Expert of computer troubleshooting, maintenance, and system construction.

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{First\\Author\\Refereed\\Papers}

{\sc {\textit{"Feedback Mechanisms in Galaxy Clusters and Alteration of ICM Entropy"}}}\\
{\bf Cavagnolo, Kenneth W.}; Donahue, Megan; and Voit, G. Mark\\
2008, in prep.

{\sc {\textit{"Star Formation in BCGs: Resurrecting Conduction''}}}\\
{\bf Cavagnolo, Kenneth W.}; Donahue, Megan; and Voit, G. Mark\\
2008, in prep. for ApJ Letters.

{\sc {\textit{"Athenaeum of Galaxy Cluster Entropy Profiles"}}}\\
{\bf Cavagnolo, Kenneth W.}; Donahue, Megan; Voit, G. Mark; and Sun, Ming\\
2007, near ApJ Supplement submission.

{\sc {\textit{"X-ray Band Dependence of X-ray Temperatures in Galaxy Clusters"}}}\\
{\bf Cavagnolo, Kenneth W.}; Donahue, Megan; Voit, G. Mark; and Sun, Ming\\
2007, near ApJ submission.

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Other\\Refereed\\Papers}

{\sc {\textit{"Star Formation, Radio Sources, Cooling X-Ray Gas and Galaxy Interactions in the Brightest Cluster Galaxy in 2A0335+096"}}}\\
Donahue, Megan; Sun, Ming; O'Dea, Christopher P.; Voit, G. Mark; {\bf Cavagnolo, Kenneth W.}\\
\href{http://adsabs.harvard.edu/abs/2007AJ....134...14D}{2007AJ....134...14D}

{\sc {\textit{"Entropy Profiles in the Cores of Cooling Flow Clusters of Galaxies"}}}\\
Donahue, Megan; Horner, Donald J.; {\bf Cavagnolo, Kenneth W.}; Voit, G. Mark\\
\href{http://adsabs.harvard.edu/abs/2006ApJ...643..730D}{2006ApJ...643..730D}

{\sc {\textit{"s-Process Abundances in Planetary Nebulae"}}}\\
Sharpee, Brian; Zhang, Yong; Williams, Robert; Pellegrini, Eric; {\bf Cavagnolo, Kenneth}; Baldwin, Jack A.; Phillips, Mark; Liu, Xiao-Wei\\
\href{http://adsabs.harvard.edu/abs/2007ApJ...659.1265S}{2007ApJ...659.1265S}

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Presented\\Work\\\& Talks}

{\sc {\textit{"Library of Galaxy Cluster Entropy Profiles: A Study in Feedback"}}}\\
{\bf Cavagnolo, Kenneth W.}; Donahue, Megan; Voit, G. Mark; and Sun, Ming\\
2008 Winter Meeting of the American Astronomical Society, Poster

{\sc {\textit{"The Entropy-Feedback Connection and Quantifying Cluster Virialization"}}}\\
{\bf Cavagnolo, Kenneth W.}; Donahue, Megan; Voit, G. Mark; and Sun, Ming\\
2007 Eight Years of Science with Chandra Symposium, Poster

{\sc {\textit{"Chandra Studies of Dark Matter and Galaxy Formation:
Signatures from the Intracluster Medium"}}}\\
Donahue, Megan; Sun, M.; {\bf Cavagnolo, K.}; Voit, G.\\
\href{http://adsabs.harvard.edu/abs/2006AAS...209.7711D}{2006 Winter
Meeting of the American Astronomical Society, Poster}

{\sc {\textit{"Abundances of s-process elements in planetary nebulae: Br, Kr \& Xe"}}}\\
Zhang, Y.; Williams, R.; Pellegrini, E.; {\bf Cavagnolo, K.}; Baldwin,
J. A.; Sharpee, B.; Phillips, M.; Liu, X.-W.\\
\href{http://adsabs.harvard.edu/abs/2006IAUS..234..549Z}{2006 IAU
Symposium, Proceeding}

{\sc {\textit{"Studies of Entropy Distributions in X-ray Luminous Clusters of Galaxies"}}}\\
{\bf Cavagnolo, K. W.}; Donahue, M. E.; Voit, G. M.; Sun, M.; Evrard, A. E.\\
\href{http://adsabs.harvard.edu/abs/2005AAS...20713903C}{2005 Winter
Meeting of the American Astronomical Society, Poster}

{\sc {\textit{"Entropy Distributions in the Cores of Nearby X-ray Luminous Clusters of Galaxies"}}}\\
{\bf Cavagnolo, K. W.}; Donahue, M. E.; Voit, G. M.; Horner, D. J.; Evrard, A. E.\\
\href{http://adsabs.harvard.edu/abs/2004AAS...20514715C}{2004 Winter
Meeting of the American Astronomical Society, Poster}

{\sc {\textit{"Radio-Free Cluster Cooling Flows"}}}\\
Donahue, M. E.; Voit, G. M.; {\bf Cavagnolo, K.}\\
\href{http://adsabs.harvard.edu/abs/2004AAS...205.6020D}{2004 Winter
Meeting of the American Astronomical Society, Poster}

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{References}

{\sc Dr. Megan Donahue}\\
Department of Physics \& Astronomy\\
Michigan State University\\
East Lansing, MI 48823\\
(517)-355-9500 ext. 2418\\
\href{mailto:donahue@pa.msu.edu}{\tt donahue@pa.msu.edu}

{\sc Dr. G. Mark Voit}\\
Department of Physics \& Astronomy\\
Michigan State University\\
East Lansing, MI 48823\\
(517)-355-9500 ext. 2419\\
\href{mailto:voit@pa.msu.edu}{\tt voit@pa.msu.edu}

{\sc Dr. Jack Baldwin}\\
Department of Physics \& Astronomy\\
Michigan State University\\
East Lansing, MI 48823\\
(517)-355-9500 ext. 2411\\
\href{mailto:baldwin@pa.msu.edu}{\tt baldwin@pa.msu.edu}

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Personal\\Interests}
- Academic: environmental sciences, ``Cradle2Cradle'' design, and urban planning.\\
- Athletics: triathlons, baseball, and everything Georgia Tech.\\
- Hobbies: reading, building model airplanes, and raising bonsai trees.\\

\end{llist}

\end{document}
 



