\documentclass[12pt]{cv}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}
\usepackage[T1]{fontenc}
\usepackage{mathptmx,multicol,common}
\pagestyle{empty}
\parindent 0pt
\parskip
\baselineskip
\setlength{\topmargin}{-0.30in}
\setlength{\oddsidemargin}{-0.30in}
\setlength{\evensidemargin}{-0.30in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0.25in}
\setlength{\topskip}{0.25in}
\setlength{\textwidth}{6.9in}
\setlength{\textheight}{9.25in}
\pagestyle{myheadings}

\begin{document}

\begin{center}
{\huge \textbf{\sc Kenneth W. Cavagnolo\\ \large Resum\'{e}}}\\
\rule{17.35cm}{1pt}\\
\end{center}
\normalsize

\addresses
{
{\bf Office Address}\\
Michigan State University\\
Department of Physics \& Astronomy\\
3265 Biomedical Physical Sciences Building\\
East Lansing, MI 48824-2320\\
}
{
{\bf Contact Information}\\
1111 Kimberly Dr. Apt. \#7\\
Lansing, MI 48912\\
Phone: (517)-285-9062\\
E-mail: \href{mailto:kencavagnolo@gmail.com}{\tt{kencavagnolo@gmail.com}}\\
Web: \href{http://www.pa.msu.edu/people/cavagnolo/}{\tt www.pa.msu.edu/people/cavagnolo/}\\
}

\begin{llist}

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Education}
\employer{{\bf Michigan State University}}
\location{2005 - Present}
Ph.D. Astrophysics, Expected August 2008\\
Thesis Title: ``Virialization, Entropy, \& Feedback in Clusters of Galaxies''\\
Advisors: Dr. Megan Donahue \& Dr. G. Mark Voit

\employer{{\bf Michigan State University}}
\location{2002 - 2005}
M.S. Astrophysics, {\it Magna Cum Laude}\\
Dissertation Title: ``Entropy Profiles of Cooling Flow Clusters''\\
Advisor: Dr. Megan Donahue

\employer{{\bf Georgia Institute of Technology}}
\location{1998 - 2002}
B.S. Physics, {\it Magna Cum Laude}\\
Senior Thesis: ``Analysis of the Eclipsing Binary ET Tau''\\
Advisor: Dr. James Sowell

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Research\\Experience}
{\sc \bf{Graduate Research Assistant}}
\location{2003 - Present}
Supervisor: Dr. Megan Donahue, {\textit{Mich. St. Univ.}}\\
Studying clusters of galaxies via their X-ray properties to\\
investigate feedback mechanisms, galaxy evolution, and the process\\
of cluster virialization.

{\sc \bf{Graduate Research Assistant}}
\location{2002 - 2003}
Supervisor: Dr. Jack Baldwin, {\textit{Mich. St. Univ.}}\\
Analyzing echelle spectra for use in studies of {\textit{s}}-process abundances\\
in planetary nebulae.

{\sc \bf{Undergraduate Research Assistant}}
\location{2000 - 2002}
Supervisor: Dr. James Sowell, {\textit{Georgia Tech}}\\
Obtaining orbital solution for the eclipsing Algol binary ET Tau via\\
UBV light curves and spectroscopic radial velocity curves.

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Research\\Interests}
$\bullet$ Renewable Energy\\
$\bullet$ Sustainable Growth\\
$\bullet$ Closed Loop Manufacturing\\
$\bullet$ Environmental Policy\\
$\bullet$ Global Climate Change

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Teaching\\Experience}
{\sc \bf{Substitute Instructor}}
\location{Fall 2006}
Course: ``Visions of the Universe''\\
Gave lectures covering stellar evolution, supernovae, white dwarves,\\
neutron stars, and black holes.

{\sc \bf{Physics Tutor}}
\location{Summer 2003}
Course: ``Introductory Honors Physics I \& II''\\
Tutored physics students taking introductory physics courses such as\\
classical mechanics, optics, and electromagnetism.

{\sc \bf{Graduate Teaching Assistant}}
\location{2002 - 2003}
Course: ``Visions of the Universe''\\
Directed and supervised laboratories for non-calculus based\\
astronomy course.

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\markright{K.W. Cavagnolo, Resum\'{e}}

\sectiontitle{Honors}
$\bullet$ College of Natural Science Dissertation Fellow \hfill 2007 - Present\\
$\bullet$ American Astronomical Society Member\hfill 2002 - Present\\
$\bullet$ American Physical Society Member\hfill 2002 - Present\\
$\bullet$ Sigma Pi Sigma National Honor Society \hfill 2001 - Present\\
%$\bullet$ NASA Center for Astronomy Education Participant\hfill 2007\\
$\bullet$ Dean's List, Georgia Tech \hfill 1998-2002

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Scientific\\Skills}
$\bullet$ Profound skills in reducing and analyzing data taken with \Chandra\ X-ray Telescope.\\
$\bullet$ Extensive experience with customizing and debugging \Ciao\ and \Caldb.\\
$\bullet$ Familiarity with multiwavelength analysis packages: \aips, \iraf, and \pyraf.\\
$\bullet$ Fluent in \perl, \idl, \LaTeX\, and \html.\\
$\bullet$ Working knowledge of \clang, \flash, \fortran, \mysql, \supmo, and \tcl.\\
$\bullet$ Mastery of multiple computing architectures: DOS, Linux, Macintosh, and Windows.\\
$\bullet$ Expert of computer troubleshooting, maintenance, and system construction.

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{References}

{\sc Dr. Megan Donahue}\\
(517)-355-9200 ext. 2418\\
\href{mailto:donahue@pa.msu.edu}{\tt donahue@pa.msu.edu}\\
Michigan State University\\

{\sc Dr. G. Mark Voit}\\
(517)-355-9200 ext. 2419\\
\href{mailto:voit@pa.msu.edu}{\tt voit@pa.msu.edu}\\
Michigan State University\\

{\sc Dr. Jack Baldwin}\\
(517)-355-9200 ext. 2411\\
\href{mailto:baldwin@pa.msu.edu}{\tt baldwin@pa.msu.edu}\\
Michigan State University\\

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\clearpage
\sectiontitle{First\\Author\\Refereed\\Papers}

{\sc {\textit{``X-ray and Entropy Scaling Relations in Galaxy Clusters''}}}\\
{\bf Cavagnolo, Kenneth W.}; Voit, G. Mark; and Donahue, Megan\\
2008, in prep. for Astrophysical Journal

{\sc {\textit{``Feedback Mechanisms in Galaxy Clusters and Alteration of ICM Entropy''}}}\\
{\bf Cavagnolo, Kenneth W.}; Donahue, Megan; and Voit, G. Mark\\
2008, in prep. for Astrophysical Journal

{\sc {\textit{``Star Formation in BCGs: Resurrecting Conduction''}}}\\
{\bf Cavagnolo, Kenneth W.}; Donahue, Megan; and Voit, G. Mark\\
2008, near Astrophysical Journal Letters submission

{\sc {\textit{``Athenaeum of Galaxy Cluster Entropy Profiles''}}}\\
{\bf Cavagnolo, Kenneth W.}; Donahue, Megan; Voit, G. Mark; and Sun, Ming\\
2007, Astrophysical Journal Supplement submitted

{\sc {\textit{``X-ray Band Dependence of X-ray Temperatures in Galaxy Clusters''}}}\\
{\bf Cavagnolo, Kenneth W.}; Donahue, Megan; Voit, G. Mark; and Sun, Ming\\
2007, Astrophysical Journal submitted

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Other\\Refereed\\Papers}

{\sc {\textit{``Star Formation, Radio Sources, Cooling X-Ray Gas and Galaxy Interactions in the Brightest Cluster Galaxy in 2A0335+096''}}}\\
Donahue, Megan; Sun, Ming; O'Dea, Christopher P.; Voit, G. Mark; {\bf Cavagnolo, Kenneth W.}\\
\href{http://adsabs.harvard.edu/abs/2007AJ....134...14D}{2007AJ....134...14D}

{\sc {\textit{``Entropy Profiles in the Cores of Cooling Flow Clusters of Galaxies''}}}\\
Donahue, Megan; Horner, Donald J.; {\bf Cavagnolo, Kenneth W.}; Voit, G. Mark\\
\href{http://adsabs.harvard.edu/abs/2006ApJ...643..730D}{2006ApJ...643..730D}

{\sc {\textit{``s-Process Abundances in Planetary Nebulae''}}}\\
Sharpee, Brian; Zhang, Yong; Williams, Robert; Pellegrini, Eric; {\bf Cavagnolo, Kenneth}; Baldwin, Jack A.; Phillips, Mark; Liu, Xiao-Wei\\
\href{http://adsabs.harvard.edu/abs/2007ApJ...659.1265S}{2007ApJ...659.1265S}

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Presented\\Work\\\& Talks}

{\sc Invited Talk: {\textit{``The Effect of Cluster Feedback on High-Precision Cosmology''}}}\\
Feb. 2008 -- NASA National Space Science and Technology Center, UAH-Huntsville

{\sc Invited Talk: {\textit{``Understanding Feedback in Galaxy Clusters''}}}\\
Jan. 2008 Center for Study of Cosmic Evolution Seminar, Michigan State University

{\sc Invited Talk: {\textit{``Band Dependence of X-ray Temperatures''}}}\\
\href{http://www.pa.msu.edu/people/cavagnolo/annarbor_07.pdf}{Oct. 2007
University of Michigan Astrophysics Seminar}

{\sc Poster: {\textit{``The Entropy-Feedback Connection and Quantifying Cluster Virialization''}}}\\
{\bf Cavagnolo, Kenneth W.}; Donahue, Megan; Voit, G. Mark; and Sun, Ming\\
\href{http://cxc.harvard.edu/symposium_2007/proceedings/posters//074_Cavagnolo.pdf}{2007
Eight Years of Science with Chandra Symposium}

{\sc Poster: {\textit{``Chandra Studies of Dark Matter and Galaxy Formation:
Signatures from the Intracluster Medium''}}}\\
Donahue, Megan; Sun, M.; {\bf Cavagnolo, K.}; Voit, G.\\
\href{http://adsabs.harvard.edu/abs/2006AAS...209.7711D}{2006 Winter
Meeting of the American Astronomical Society}

{\sc Proceeding: {\textit{``Abundances of s-process elements in planetary nebulae: Br, Kr \& Xe''}}}\\
Zhang, Y.; Williams, R.; Pellegrini, E.; {\bf Cavagnolo, K.}; Baldwin,
J. A.; Sharpee, B.; Phillips, M.; Liu, X.-W.\\
\href{http://adsabs.harvard.edu/abs/2006IAUS..234..549Z}{2006 IAU
Symposium}

{\sc Poster: {\textit{``Studies of Entropy Distributions in X-ray Luminous Clusters of Galaxies''}}}\\
{\bf Cavagnolo, K. W.}; Donahue, M. E.; Voit, G. M.; Sun, M.; Evrard, A. E.\\
\href{http://adsabs.harvard.edu/abs/2005AAS...20713903C}{2005 Winter
Meeting of the American Astronomical Society}

{\sc Poster: {\textit{``Entropy Distributions in the Cores of Nearby X-ray Luminous Clusters of Galaxies''}}}\\
{\bf Cavagnolo, K. W.}; Donahue, M. E.; Voit, G. M.; Horner, D. J.; Evrard, A. E.\\
\href{http://adsabs.harvard.edu/abs/2004AAS...20514715C}{2004 Winter
Meeting of the American Astronomical Society}

{\sc Poster: {\textit{``Radio-Free Cluster Cooling Flows''}}}\\
Donahue, M. E.; Voit, G. M.; {\bf Cavagnolo, K.}\\
\href{http://adsabs.harvard.edu/abs/2004AAS...205.6020D}{2004 Winter
Meeting of the American Astronomical Society}

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Personal\\Interests}
$\bullet$ Academic: environmental sciences, ``Cradle2Cradle'' design, and urban planning.\\
$\bullet$ Athletics: triathlons, baseball, and everything Georgia Tech.\\
$\bullet$ Hobbies: reading, building model airplanes, and raising bonsai trees.\\

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\end{llist}

\end{document}
