\documentclass[11pt]{article}
\usepackage{common}
\setlength{\topmargin}{-.3in}
\setlength{\oddsidemargin}{-0.1in}
\setlength{\evensidemargin}{-0.1in}
\setlength{\textwidth}{6.7in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\topskip}{0.5in}
\setlength{\textheight}{9.25in}
\setlength{\parindent}{0.0in}
\setlength{\parskip}{1em}
\pagestyle{empty}
\begin{document}

In my life, I have been fortunate enough to benefit from the hard-work
of others, such as my mother and two grandfathers. The opportunities
garnered from those benefits have been many and unique. I have not
lived a sheltered life and am well-aware of the educational inequality
which exists in the American public school system. I want to work with
Teach For America because the organization provides a robust
infrastructure which I can utilize to redistribute the fruits of the
many opportunities I've received in life. Teach For America is the
perfect avenue for me to be a member of a school where upward mobility
may be limited or the where the students (and especially gifted
students) would not otherwise have access to teachers with broad
world-views or advanced degrees.

As a member of the Teach For America corp, the gift I personally hope
to give my students is providing each of them with the opportunity to
have their own ``AH HA!''  moment in life. To have a moment where they
think, ``I can do anything,'' or ``I want to dedicate my life to
\_\_\_\_\_\_.'' The lasting effects of those moments in my life have
had a profound and resonating impact on my hopeful, optimistic life
outlook and goal setting. As a measure of my success in this endeavor,
I would hope to leave students that set specific and attainable goals
which lead them into community involvement and academic excellence in
the form of scholarships or grants. Ultimately it would be great to
have those same students achieve their dreams, and then return to the
communities, via their physical or financial influence, and better
those communities.

\end{document}
