%%%%%%%%%%%%%%%%%%%
% Custom commands %
%%%%%%%%%%%%%%%%%%%

\newcommand{\dmb}{\ensuremath{\dot{m_{\rm{B}}}}}
\newcommand{\dme}{\ensuremath{\dot{m_{\rm{E}}}}}
\newcommand{\ldisk}{\ensuremath{L_{\rm{disk}}}}
\newcommand{\ms}{MS 0735.6+7421}
\newcommand{\myi}{\ensuremath{I}}
\newcommand{\myv}{\ensuremath{V}}
\newcommand{\rbs}{RBS 797}
\newcommand{\reff}{\ensuremath{r_{\rm{eff}}}}
\newcommand{\rlos}{\ensuremath{r_{\rm{los}}}}
\newcommand{\mykeywords}{galaxies: active -- galaxies: clusters:
  general -- galaxies: clusters: intracluster medium -- X-rays:
  galaxies: clusters}
\newcommand{\mystitle}{\rbs\ AGN Outburst}
\newcommand{\mytitle}{A Powerful, Possibly Line-of-Sight, AGN Outburst
  in RBS 797}

%%%%%%%%%%
% Header %
%%%%%%%%%%

\documentclass[11pt, preprint]{aastex}
\usepackage{graphicx,common,longtable}
%\documentclass[iop]{emulateapj-rtx4}
%\documentclass[iop]{emulateapj}
%\usepackage{apjfonts,common,graphicx,longtable}
\usepackage[pagebackref,
  pdftitle={\mytitle},
  pdfauthor={K. W. Cavagnolo},
  pdfkeywords={\mykeywords},
  pdfsubject={Astrophysical Journal},
  pdfproducer={ps2pdf},
  pdfcreator={LaTeX with hyperref}
  pdfdisplaydoctitle=true,
  colorlinks=true,
  citecolor=blue,
  linkcolor=blue,
  urlcolor=blue]{hyperref}
\bibliographystyle{apj}
\begin{document}
\title{\mytitle}
\shorttitle{\mystitle}
\author{
  K. W. Cavagnolo\altaffilmark{1,2},
  B. R. McNamara\altaffilmark{1,3,4},
  M. W. Wise\altaffilmark{5}, \\
  P. E. J. Nulsen\altaffilmark{4},
  M. Br\"uggen\altaffilmark{6}, 
  M. Gitti\altaffilmark{4,7}, and
  D. A. Rafferty\altaffilmark{8}
}
\shortauthors{Cavagnolo et al.}

\altaffiltext{1}{Department of Physics \& Astronomy, University of
  Waterloo, Waterloo, ON, Canada.}
\altaffiltext{2}{UNS, CNRS UMR 6202 Cassiop\'{e}e, Observatoire de la
  C\^{o}te d'Azur, Nice, France.}
\altaffiltext{3}{Perimeter Institute for Theoretical Physics,
  Waterloo, ON, Canada.}
\altaffiltext{4}{Harvard-Smithsonian Center for Astrophysics,
  Cambridge, MA, USA.}
\altaffiltext{5}{Astronomical Institute Anton Pannekoek, University
  of Amsterdam, Amsterdam, Netherlands.}
\altaffiltext{6}{Jacobs University Bremen, Bremen, Germany.}
\altaffiltext{7}{Astronomical Observatory of Bologna-INAF, Bologna,
  Italy.}
\altaffiltext{8}{Leiden Observatory, University of Leiden, Leiden,
  Netherlands.}

%%%%%%%%%%%%
% Abstract %
%%%%%%%%%%%%

\begin{abstract}
  Utilizing $\sim 50$ ks of Chandra X-ray Observatory imaging, we
  present analysis of the intracluster medium (ICM) cavities in the
  galaxy cluster RBS 797. In addition to the two extremely deep
  cavities in the cluster core, our new analysis reveals extensive
  substructure in the ICM which may indicate previous episodes of AGN
  activity. Based on surface brightness decrement analysis of the two
  central cavities, we suggest the cavities are elongated along our
  line-of-sight and conservatively estimate a total AGN outburst
  energy of $\approx 6 \times 10^{60}$ erg released at an average rate
  of $\approx 6 \times 10^{45} ~\lum$ which indicate it may be one of
  the most powerful AGN outbursts found to date, energetically similar
  to Cygnus A, Hercules A, and \ms. What appear to be bright rims
  enclosing the cavities may indicate the presence of a weak shock,
  though this cannot be confirmed directly from the existing X-ray
  data. The average mass accretion rate needed power the outburst is
  $\sim 1 ~\msolpy$, and we determine that fueling the AGN through
  accretion of cold or hot gas in the brightest cluster galaxy (BCG)
  requires unrealistic efficiencies and is inconsistent with the BCG
  stellar and ICM properties. With no evidence of on-going nuclear
  accretion, we tentatively discuss black spin as a viable energy
  source for the outburst. We also present evidence of BCG optical
  halo-AGN jet interaction which may be driving star formation.
\end{abstract}

%%%%%%%%%%%%
% Keywords %
%%%%%%%%%%%%

\keywords{\mykeywords}

%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%

Evidence has amassed over the last decade that the growth of galaxies
and supermassive black holes (SMBHs) are coupled, and that energetic
feedback from active galactic nuclei (AGN) strongly influences galaxy
evolution \citep[\eg][]{1995ARA&A..33..581K, 1998A&A...331L...1S,
  2000MNRAS.311..576K, 2002ApJ...574..740T}. The discovery of AGN
induced cavities in the hot halos surrounding many massive galaxies
has strengthened this theory \citep[see][for a review]{mcnamrev},
revealing that AGN mechanical heating is capable of regulating the
radiative cooling responsible for late-time galaxy growth
\citep[\eg][]{birzan04, dunn06, rafferty06}. The discovery of
intracluster medium (ICM) cavities in the galaxy cluster \rbs\ was
first reported by \citet{schindler01} using data from the Chandra
X-ray Observatory (\cxo). Multifrequency radio observations showed
that the cavities are co-spatial with extended radio emission centered
on a strong, jetted radio source coincident with the \rbs\ brightest
cluster galaxy (BCG) \citep{2002astro.ph..1349D, gitti06,
  birzan08}. The observations implicate an AGN in the BCG as the
cavities' progenitor, and \citet[][hereafter B04]{birzan04} estimate
the AGN deposited $\approx 10^{60}$ erg of energy into the ICM at a
rate of $\approx 10^{45} ~\lum$.

The B04 analysis assumed the cavities are roughly spherical, symmetric
about the plane of the sky, and that their centers lie in a plane
passing through the central AGN and perpendicular to our
line-of-sight. However, the abnormally deep surface brightness
decrements of the cavities, and the nebulous correlation between the
radio and X-ray morphologies, suggests the system may be more complex
than B04 could constrain. Using a longer, follow-up \cxo\ observation,
we determine that the cavities are indeed elongated along the
line-of-sight, and go on to provide evidence that additional cavities
may be present at larger radii. We conservatively estimate the total
AGN energy output and power are six times larger than the B04 values,
$\approx 6 \times 10^{60}$ erg and $\approx 6 \times 10^{45} ~\lum$
respectively.

Current models of late-time AGN feedback posit that cooling processes
in a galaxy's halo result in mass accretion onto a central SMBH,
thereby driving AGN activity and ultimately offsetting halo cooling
\citep[\eg][]{croton06, bower06, sijacki07}. While there is direct
evidence that halo cooling and feedback are linked
\citep[\eg][]{haradent, rafferty08}, the observational constraints on
how AGN are fueled and powered remain loose. Mass accretion alone can,
in principle, fuel most AGN \citep[\eg][]{pizzolato05,
  2006MNRAS.372...21A}, and is typically not at odds with the gas
masses and stellar masses of the host galaxy
\citep[\eg][]{rafferty06}. However, for some gas-poor systems hosting
very powerful AGN, for example, Hercules A, Hydra A, and \ms\ where
the AGN energy output is $\sim 10^{61}$ erg with powers of $\sim
10^{45} ~\lum$ \citep{herca, hydraa, ms0735}, pure mass accretion does
not appear to be capable of sustaining the outbursts. The importance
of these systems for understanding AGN feedback is that the fueling
appears to have been very efficient, leading to speculation that some
BCGs may host ultramassive black holes \citep[$> 10^{10} ~\msol$;
  \eg][]{msspin}, or that some AGN outbursts are primarily powered by
the release of energy stored in a rapidly spinning SMBH
\citep[\eg][]{minaspin}. In this paper, we explore these issues and
discuss whether mass accretion alone could have powered the RBS 797
outburst.

Reduction of the X-ray and radio data is discussed in Section
\ref{sec:obs}. Interpretation of observational results are given
throughout Section \ref{sec:results}, and a brief summary concludes
the paper in Section \ref{sec:con}. \LCDM. At a redshift of $z =
0.354$, the look-back time is 3.9 Gyr, $\da = 4.996$ kpc
arcsec$^{-1}$, and $\dl = 1889$ Mpc. All spectral analysis errors are
90\% confidence, while all other errors are 68\% confidence.

%%%%%%%%%%%%%%%%%%%%%%
\section{Observations}
\label{sec:obs}
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%
\subsection{X-ray Data}
\label{sec:xray}
%%%%%%%%%%%%%%%%%%%%%%%

\rbs\ was observed with \cxo\ in October 2000 for 11.4 ks using the
ACIS-I array (\dataset [ADS/Sa.CXO#Obs/02202] {ObsID 2202}) and in
July 2007 for 38.3 ks using the ACIS-S array (\dataset
[ADS/Sa.CXO#Obs/07902] {ObsID 7902}). Datasets were reduced using
\ciao\ and \caldb\ versions 4.2. Events were screened of cosmic rays
using \asca\ grades and {\textsc{vfaint}} filtering. The level-1
events files were reprocessed to apply the most up-to-date corrections
for the time-dependent gain change, charge transfer inefficiency, and
degraded quantum efficiency of the ACIS detector. The afterglow and
dead area corrections were also applied. Time intervals affected by
background flares exceeding 20\% of the mean background count rate
were isolated and removed using light curve filtering. The final,
combined exposure time is 48.8 ks. Point sources were identified and
removed via visual inspection and use of the \ciao\ tool
{\textsc{wavdetect}}. We refer to the \cxo\ data free of point sources
and flares as the ``clean'' data. A mosaiced, fluxed image (see Figure
\ref{fig:img}) was generated by exposure correcting each clean dataset
and reprojecting the normalized images to a common tangent point.

%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Radio Data}
\label{sec:radio}
%%%%%%%%%%%%%%%%%%%%%%%

Very Large Array (\vla) radio images at 325 MHz (A-array), 1.4 GHz (A-
and B-array), 4.8 GHz (A-array), and 8.4 GHz (D-array) are presented
in \citet{gitti06} and \citet{birzan08}. Our re-analysis of the
archival \vla\ radio observations yielded no significant differences
with these prior studies. Using the rms noise ($\sigma_{\rm{rms}}$)
values given in \citet{gitti06} and \citet{birzan08} for each
observation, emission contours between $3\sigma_{\rm{rms}}$ and the
peak image intensity were generated. These are the contours referenced
and shown in all subsequent discussion and figures.

%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{sec:results}
%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cavity Morphologies and ICM Substructure}
\label{sec:morph}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Shown in Figure \ref{fig:img} is the 0.7--2.0 keV \cxo\ mosaiced clean
image. Outside of $\approx 50$ kpc, the global ICM morphology is
regular and elliptical in shape, with the appearance of being skewed
along the northwest-southeast direction. The cavities discovered by
\citet{schindler01} are clearly seen in the cluster core east and west
of the nuclear X-ray source and appear to be enclosed by a thick,
bright, elliptical ridge of emission which we discuss further in
Section \ref{sec:ecav}. The western cavity has more internal
structure, and its boundaries are less well-defined, than the eastern
cavity. The emission from the innermost region of the core is
elongated north-south and has a distinct `S'-shape punctuated by a
hard nuclear X-ray source.

Multifrequency radio images overlaid with ICM X-ray contours are shown
in Figure \ref{fig:composite}. \rbs\ radio properties are discussed in
\citet{gitti06}, and we summarize here. As seen in projection, the
nuclear 4.8 GHz jets are almost orthogonal to the axis connecting the
cavities. Radio imaging at $\approx 5\arcs$ resolution reveals the 325
MHz, 1.4 GHz, and 8.4 GHz radio emission are diffuse and extend
well-beyond the cavities, more similar to the morphology of a radio
mini-halo than relativistic plasma confined to the cavities
\citep[][Doria et al., in preparation]{2008A&A...486L..31C}. Of all
the radio images, the 1.4 GHz emission imaged at $\approx 1 \arcs$
resolution most closely traces the cavity morphologies, yet it is
still diffuse and uniform over the cavities with little structure
outside the radio core. Typically, the connection between a cavity
system, coincident radio emission, and the progenitor AGN is
unambiguous. This is not the case for \rbs, which suggests the cavity
system may be more complex than it appears.

To better reveal the cavity morphologies, residual X-ray images of
\rbs\ were constructed by modeling the ICM emission and subtracting it
off. The X-ray isophotes of two exposure-corrected images -- one
smoothed by a $1\arcs$ Gaussian and another by a $3\arcs$ Gaussian --
were fitted with ellipses using the \iraf\ task \textsc{ellipse}. The
ellipse centers were fixed at the location of the BCG X-ray point
source, and the eccentricities and position angles were free to
vary. A 2D surface brightness model was created from each fit using
the \iraf\ task \textsc{bmodel}, normalized to the parent X-ray image,
and then subtracted off. The residual images are shown in Figure
\ref{fig:subxray}.

In addition to the central east and west cavities (labeled E1 and W1),
depressions north and south of the nucleus (labeled N1 and S1) are
revealed. N1 and S1 lie along the 4.8 GHz jet axis and are coincident
with spurs of significant 1.4 GHz emission. A depression coincident
with the southeastern concentration of 325 MHz emission is also found
(labeled E2), but no counterpart on the opposing side of the cluster
is seen (labeled W2). The N1, S1, and E2 depressions do not show-up in
surface brightness profiles extracted in wedges passing through each
feature, so while coincidence with the radio emission hints at
additional cavities, they may be spurious structures. There is also an
X-ray edge which extends southeast from E2 and sits along a ridge of
325 MHz and 8.4 GHz emission. No substructure associated with the
western-most knot of 325 MHz emission is found, but there is a stellar
object co-spatial with this region.  The X-ray and radio properties of
the object are consistent with those of a galactic RS CVn star
\citep{1993RPPh...56.1145S} -- if the star is less than 1 kpc away,
$\lx \la 10^{31} ~\lum$ and $L_{325} \sim 10^{27} ~\lum$ -- suggesting
the western 325 MHz emission may not be associated with the cluster.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Radial ICM Properties}
\label{sec:icm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In order to analyze the \rbs\ cavity system and AGN outburst
energetics in-detail, the radial ICM density, temperature, and
pressure structure need to be measured. The radial profiles are shown
in Figure \ref{fig:gallery}. A temperature (\tx) profile was created
by extracting spectra from concentric circular annuli (2500 source
counts per annulus) centered on the cluster X-ray peak, binning the
spectra to 25 counts per energy channel, and then fitting each
spectrum in \xspec\ 12.4 \citep{xspec}. Spectra were modeled with an
absorbed, single-component \mekal\ model \citep{mekal1} over the
energy range 0.7--7.0 \keV. For each annulus, weighted responses were
created and a background spectrum was extracted from the ObsID matched
\caldb\ blank-sky dataset normalized using the ratio of 9--12 keV
count rates for an identical off-axis, source-free region of the
blank-sky and target datasets. The absorbing Galactic column density
was fixed to $\nhgal = 2.28 \times 10^{20} ~\pcmsq$ \citep{lab}, and a
spectral model for the Galactic foreground was included as an
additional, fixed background component during spectral fitting (see
\citealt{2005ApJ...628..655V} and \citealt{xrayband} for method). Gas
metal abundance was free to vary and normalized to the \citet{ag89}
solar ratios. Spectral deprojection using the {\textsc{projct}}
\xspec\ model did not produce significantly different results, thus
only projected quantities are discussed.

A 0.7--2.0 keV surface brightness profile was extracted from the
\cxo\ mosaiced clean image using concentric $1\arcs$ wide elliptical
annuli centered on the BCG X-ray point source (central $\approx
1\arcs$ and cavities excluded). A deprojected electron density
(\nelec) profile was derived from the surface brightness profile using
the method of \citet{kriss83} which incorporates the 0.7--2.0 keV
count rates and best-fit normalizations from the spectral analysis
\citep[see][for details]{accept}. Errors for the density profile were
estimated using 5000 Monte Carlo simulations of the original surface
brightness profile. A total gas pressure profile was calculated as $P
= n \tx$ where $n \approx 2.3 \nH$ and $\nH \approx
\nelec/1.2$. Profiles of enclosed X-ray luminosity, entropy ($K = \tx
\nelec^{-2/3}$) and cooling time ($\tcool = 3 n \tx~(2 \nelec \nH
\Lambda)^{-1}$, where $\Lambda$ is the cooling function), were also
generated. Errors for each profile were determined by summing the
individual parameter uncertainties in quadrature.

The radial profiles are consistent with those of a normal cool core
cluster: outwardly increasing temperature profile, centrally peaked
abundance profile, central cooling time of $\approx 400$ Myr within 9
kpc of the cluster center, and a pronounced entropy core. Fitting the
ICM entropy profile with the function $K = \kna +\khun (r/100
~\kpc)^{\alpha}$, where \kna\ [\ent] is core entropy, \khun\ [\ent] is
a normalization at 100 kpc, and $\alpha$ is a dimensionless index,
reveals $\kna = 17.9 \pm 2.2 ~\ent$, $\khun = 92.1 \pm 6.2 ~\ent$, and
$\alpha = 1.65 \pm 0.11$ for \chisq(DOF)$ = 9.3(57)$. Further, the
radial analysis does not indicate any significant temperature,
density, or pressure discontinuities to signal the existence of
large-scale shocks or cold fronts.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{ICM Cavities}
\label{sec:cavities}
%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Energetics}
\label{sec:ecav}
%%%%%%%%%%%%%%%%%%%%%%%%%%

Of all the ICM substructure, the E1 and W1 cavities are unambiguous
detections, and their energetics were determined following standard
methods (see B04). Our fiducial cavity configuration assumes the
cavities are symmetric about the plane of the sky, and the cavity
centers lie in a plane which is perpendicular to our line-of-sight and
passes through the central AGN (configuration-1 in Figure
\ref{fig:config}). Hereafter, we denote the line-of-sight distance of
a cavity's center from this plane as $z$, and the cavity radius along
the line-of-sight as \rlos. The volume of a cavity with $z = 0$ is
thus $V = 4\pi a b \rlos/3$ where $a$ and $b$ are the projected
semi-major and -minor axes, respectively, of the by-eye determined
ellipses in Figure \ref{fig:subxray}. The projected morphologies of E1
and W1 are similar enough that the same regions were used for
both. Initially, the cavities were assumed to be roughly spherical and
\rlos\ was set equal to the projected effective radius, $\reff =
\sqrt{ab}$. For configuration-1, the distance of each cavity from the
central AGN, $D$, is simply the projected distance from the ellipse
centers to the BCG X-ray point source. A systematic error of 10\% is
assigned to the cavity volumes.

Cavity ages were estimated using the \tsonic, \tbuoy, and
\trefill\ timescales discussed in B04. The \tsonic\ age assumes a
cavity reaches its present distance from the central AGN by moving at
the local sound speed, while \tbuoy\ assumes the cavity buoyantly
rises at its terminal velocity, and \trefill\ is simply the time
required to refill the volume displaced by the cavity. The energy in
each cavity, $\ecav = \gamma PV/(\gamma-1)$, was calculated assuming
the contents are a relativistic plasma ($\gamma = 4/3$), and that the
mean internal cavity pressure is equal to the ICM pressure at the
cavity mid-point. We assume the cavities are detached, buoyant
structures and that the time-averaged power needed to create each
cavity is $\pcav = \ecav/\tbuoy$. The individual cavity properties are
given in Table \ref{tab:cavities} and the aggregate properties in
Table \ref{tab:totals}.

For the spherical assumption of configuration-1, we measure a total
cavity energy $\ecav = 3.23 ~(\pm 1.16) \times 10^{60}$ erg and total
power $\pcav = 3.34 ~(\pm 1.41) \times 10^{45} ~\lum$. These values
are larger than those of B04 ($\ecav = 1.52 \times 10^{60}$ erg,
$\pcav = 1.13 \times 10^{44} ~\lum$) by a factor of $\approx 3$ as a
result of our larger E1 and W1 volumes. Using the B04 cavity volumes
in place of our own produces no significant differences between our
energetics calculations and those of B04. The largest uncertainties in
the energetic calculations are the cavity volumes and their
3-dimensional locations in the ICM, issues we consider next.

%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Decrements}
\label{sec:dec}
%%%%%%%%%%%%%%%%%%%%%%%%%%

A cavity's morphology and location in the ICM dictates the X-ray
surface brightness decrement it induces. If the surface brightness of
the undisturbed ICM can be estimated, then the decrement is useful for
constraining the cavity line-of-sight size and its distance from the
launch point \citep[\eg\ \rlos\ and $z$; see][for details]{hydraa}. We
adopt the \citet{hydraa} definition of surface brightness decrement,
$y$, as the ratio of the X-ray surface brightness inside the cavities
to the value of the best-fit ICM surface brightness $\beta$-model at
the same radius. Note the potential for confusion, since small values
of $y$ correspond to large decrements. Consistent with the analysis of
\citet{schindler01}, we find the best-fit $\beta$-model has parameters
$S_0 = 1.65 ~(\pm 0.15) \times 10^{-3}$ \sbr, $\beta = 0.62 \pm 0.04$,
and $r_{\rm{core}} = 7.98\arcs \pm 0.08$ for \chisq(DOF) =
79(97). Using a circular aperture with radius $1\arcs$ centered on the
deepest part of each cavity, we measure mean decrements of
$\bar{y}_{\rm{W1}} = 0.50 \pm 0.18$ and $\bar{y}_{\rm{E1}} = 0.52 \pm
0.23$, with minima of $y^{\rm{min}}_{\rm{W1}} = 0.44$ and
$y^{\rm{min}}_{\rm{E1}} = 0.47$.

To check if the spherical approximation for cavity configuration-1 can
produce the measured decrements, the best-fit $\beta$-model was
integrated over each cavity with a column of gas equal to $2\rlos$
excluded. Integration revealed that decrements $y < 0.67$ cannot be
achieved for the spherical case, indicating our assumption of $\rlos =
\reff$ is poor. If the centers of E1 and W1 lie in the plane of the
sky, the minimum line-of-sight depths needed to reproduce the
decrements of E1 and W1 are $\rlos^{\rm{E1}} = 23.35$ kpc and
$\rlos^{\rm{W1}} = 25.96$ kpc. The energetics for these morphologies
are given as configuration-1a in Tables \ref{tab:cavities} and
\ref{tab:totals}. If the cavities are moving away from the AGN along
an axis perpendicular to our line-of-sight, then it is a bit odd that
the cavities are compressed in the direction orthogonal to their
inflation. But, it may be that the cavities are larger along that axis
than we realize, for example if the bright rims are masking the true
extent of the cavities.

It is also possible that the cavities are inflating close to our
line-of-sight and thus may be large, elongated structures as shown in
configuration-2 of Figure \ref{fig:config}. Presented in Figure
\ref{fig:decs} are curves showing how surface brightness decrement
changes as a function of $z$ for various \rlos. The plots demonstrate
that it is possible to reproduce the measured E1 and W1 decrements
using larger cavities that have centers displaced from the plane of
the sky. Consequently, the limiting case of $z = 0$ is a lower-limit
on the AGN outburst energetics. If the cavity system lies close to our
line-of-sight, and is much larger and more complex than the data
allows us to constrain, it may explain the additional ICM
substructures seen in the residual images and the ambiguous
relationship between the X-ray and radio morphologies.

It should be noted that deep cavities like in \rbs\ are uncommon, with
most other cavity systems having minima $y \ga 0.6$ (B04). The extreme
decrements raise the concern that the $\beta$-model fit has been
influenced by the rim-like structures of E1-W1 and produced
artificially low decrements. The prominent rims can be seen in Figure
\ref{fig:pannorm} which shows the normalized surface brightness
variation in wedges of a $2.5\arcs$ wide annulus centered on the X-ray
peak and passing through the cavity midpoints. In addition to
excluding the cavities, we tried excluding the rims during
$\beta$-model fitting, but this did not provide insight as too much of
the surface brightness profile was removed and the fit did not
converge. Extrapolating the surface brightness profile at larger radii
inward resulted in even lower decrements. The rims, and their possible
connection to gas shocking, are discussed below.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Do the Rims Indicate Shocks?}
\label{sec:shocks}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

It is often assumed that cavity energetics calculations, like those in
Section \ref{sec:ecav}, provide a reasonable estimate of the physical
quantity jet power, \pjet. However, \pcav\ and \pjet\ do not account
for AGN output energy which may be channeled into shocks. Though the
\cxo\ data does not indicate the presence of significant density or
temperature jumps -- which would confirm the presence of a shock --
the cavity/rim morphologies and energetics are strikingly similar to
those of \ms, which hosts a large-scale Mach $\approx 1.4$ shock. If
significant ICM shocking has occurred in \rbs, then the cavity
energetics clearly underestimate the AGN output, which directly
impacts the discussion of AGN fueling in Section \ref{sec:accretion}.

A simplistic model that captures how a bright, shocked rim helps
enhance a cavity decrement is to assume the shocked region is
cylindrical and uniformly compressed. Ignoring emission outside the
shocked cylinder, a compression $\chi$ gives a decrement of $y =
\sqrt{\chi} - \sqrt{\chi - 1}$, hence a decrement of $\ge 0.44$ can be
obtained with $\chi \la 1.84$, \ie\ not dissimilar from the shock Mach
numbers in Hercules A and \ms. This is a rough estimate (arguably
pessimistic since the compressed gas is assumed to be uniform), but it
demonstrates that we may be seeing shocking in \rbs. Assuming axial
symmetry for the unshocked gas, including emission outside the
cylinder adds more to the bright rim than the cavity center,
increasing the surface brightness difference from rim to cavity, but
generally reducing $y$. Because the ICM surface brightness drops
rapidly outside the shocked region, the correction due to emission
from outside the cylinder is modest, and it scales as $\chi^{-3/2}$,
so its effect decreases as the compression increases.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Powering the Outburst}
\label{sec:accretion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

If the AGN was powered by mass accretion alone, then \ecav\ is
representative of the gravitational binding energy released as mass
accreted onto the SMBH. In which case, the total mass accreted can be
approximated as $\macc = \ecav/(\epsilon c^2)$ with an average
accretion rate $\dmacc = \macc/\tbuoy$. Consequently, the black hole's
mass grew by $\ddmbh = (1-\epsilon)\macc$ at an average rate $\dmbh =
\ddmbh/\tbuoy$. Here, $\epsilon$ is a poorly understood mass-energy
conversion factor which may vary from 0.06--0.4, depending on the spin
of the black hole. We adopt the commonly used value $\epsilon = 0.1$
\citep{2002apa..book.....F}. The accretion properties associated with
each cavity configuration are given in Table \ref{tab:totals}, and
\macc\ lies in the range $2 \dash 3 \times 10^7 \msolpy$. Below, we
consider if the accretion of cold or hot gas pervading the BCG could
meet these requirements without being in conflict with observed BCG
and ICM properties.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Cold Accretion}
\label{sec:cold}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Substantial quantities of cold molecular gas and optical nebulae are
found in many cool core clusters \citep{crawford99, edge01}. If
rapidly cooling thermal instabilities form in these structures, it is
possible that they are the source of fuel for AGN activity and star
formation \citep[\eg][]{pizzolato05, 2006NewA...12...38S,
  2010MNRAS.408..961P}. The molecular gas mass (\mmol) of \rbs\ has
not been measured, so it was inferred using the
\mmol-\halpha\ correlation in \citet{edge01}. An optical spectrum
(3200-7600 \AA) of the \rbs\ BCG reveals a strong \hbeta\ emission
line \citep{rbs1, rbs2}, which we used as a surrogate for \halpha\ by
assuming a Balmer decrement of EW$_{\hbeta}$/EW$_{\halpha}$ = 0.29
\citep{2006ApJ...642..775M}, where EW is line equivalent width. Under
these assumptions, we estimate $\mmol \sim 10^{10} ~\msol$,
sufficiently in excess of the $\sim 10^7 ~\msol$ needed to power the
outburst that we can infer there is an ample cold gas reservoir
capable of providing fuel. It must be noted that the
\mmol-\halpha\ relation has substantial scatter \citep{salome03}, and
that the \rbs\ emission line measurements are highly uncertain
(A. Schwope, private communication), so the \mmol\ estimate is simply
a crude estimate.

Accreting gas from the reservoir will cause the central SMBH mass to
grow, but, on average, black hole mass growth is coupled to the star
formation properties of the host galaxy
\citep[\eg][]{1995ARA&A..33..581K, 2000ApJ...539L...9F}. Assuming star
formation accompanied the phase of accretion which powered the AGN
outburst, the Magorrian relation \citep{magorrian} tells us that for
each unit of black hole mass growth, several hundred times as much
goes into bulge stars \citep[\eg][]{2004ApJ...604L..89H}. Thus, the
$\sim 1 ~\msolpy$ mass accretion rate needed to power the
\rbs\ outburst suggests that $\sim 700 ~\msolpy$ of star formation
needed to accompany the AGN fueling event. If we assume the present
BCG star formation rate (SFR), $\sim 1$--10 \msolpy\ (see Section
\ref{sec:bcg}), is of the order the SFR preceding and during the AGN
outburst, we encounter the awkward situation where every mass unit
accreted by the SMBH resulted in a nearly equal amount of star
formation, in conflict with expectations of SMBH-host galaxy
co-evolution. Further, the \rbs\ BCG stellar halo color profile does
not indicate high levels of recent star formation (see Section
\ref{sec:bcg}). This result comes with the caveat that \mbh-SFR
scaling relations calibrated using lower mass galaxies may not hold at
BCG mass scales. Given the limitations of the available data, it
appears if cold gas accretion did power the outburst, it did so with a
efficiency above that of a starburst system.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Hot Accretion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Direct accretion of the hot ICM via the Bondi mechanism provides
another possible AGN fuel source. The accretion flow arising from this
process is characterized by the Bondi equation (Equation
\ref{eqn:bon}) and is often compared with the Eddington limit
describing the maximal accretion rate for a SMBH (Equation
\ref{eqn:edd}):
\begin{eqnarray}
  \dmbon &=& 0.013 ~\kbon^{-3/2} \left(\frac{\mbh}{10^9
    ~\msol}\right)^{2} ~\msolpy \label{eqn:bon}\\
  \dmedd &=& \frac{2.2}{\epsilon} \left(\frac{\mbh}{10^9~\msol}\right)
  ~\msolpy  \label{eqn:edd}
\end{eqnarray}
where $\epsilon$ is a mass-energy conversion factor, \kbon\ is the
mean entropy [\ent] of gas within the Bondi radius, and \mbh\ is black
hole mass [\msol]. We chose the relations of
\citet{2002ApJ...574..740T} and \citet{2007MNRAS.379..711G} to
estimate \mbh, and find a range of $0.6 \dash 7.8 \times 10^9 ~\msol$,
from which we adopted the weighted mean value $1.5^{+6.3}_{-0.9}
\times 10^9 ~\msol$ where the errors span the lowest and highest
$1\sigma$ values of the individual estimates. For $\epsilon = 0.1$ and
$\kbon = \kna$, the relevant accretion rates are $\dmbon \approx 4
\times 10^{-4} ~\msolpy$ and $\dmedd \approx 33 ~\msolpy$. The
Eddington and Bondi accretion ratios are given in Table
\ref{tab:totals}, with $\dme \equiv \dmacc/\dmedd \approx 0.02$ and
$\dmb \equiv \dmacc/\dmbon \approx 2000 \dash 4000$.

The large value of \dmb\ is troubling since it implies all the gas
which reached the Bondi radius ($\approx 10$ pc) was accreted. But,
\dmb\ may be overestimated if $\kbon < \kna$ and \mbh\ is larger than
our adopted value. Using the upper limit of \mbh, $\approx 8 \times
10^9 ~\msol$, and assuming gas near \rbon\ has a mean temperature of
0.5 keV, a \dmb\ of unity requires \kbon\ be less than $1 ~\ent$,
corresponding to $\nelec \approx 0.4 ~\pcc$. This is four times the
measured ICM central density, and a sphere more than 2 kpc in radius
is required for up to $10^7 ~\msol$ to be available for accretion,
\ie\ these are the properties of a galactic corona \citep{coronae}. A
$\sim 2$ kpc, $\tx \sim 1$ keV, $\nelec \sim 0.4 ~\pcc$ corona would
be easily detected in the \cxo\ observations as a bright point source
with a distinct thermal spectrum. However, the spectrum of the
observed nuclear X-ray point source (see Section \ref{sec:nuc}) is
wholly inconsistent with being thermal in origin (\ie\ no $E < 2$ keV
Fe L-shell emission hump and no $E \approx 6.5$ keV Fe K-shell
emission line blend). If the pervading ICM is instead the source of
accretion fuel, these numbers imply the inner-core of the cluster is
fully consumed during the outburst lifetime ($<$ 100 Myr), which is
much shorter than the central cooling time of the ICM ($\approx$ 400
Myr), thereby disconnecting the halo cooling and feedback
processes. While Bondi accretion cannot be definitively ruled out
because the nucleus is unresolved and the cluster is observed
post-outburst when ICM core conditions may have dramatically changed,
a number of observationally unsupported concessions need to be made
for Bondi accretion to be viable.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Black Hole Spin}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In an effort to find lower accretion rates which still produce
powerful jets, we consider below if a rapidly-spinning SMBH could act
as an alternate power source. We consider the spin model with the
caveats that, like cold- and hot-mode accretion, spin is wrought with
its own difficulties, is hard to evaluate for any one system, and how
rapidly spinning black holes are created is unclear (see
\citealt{msspin} and \citealt{minaspin} for discussion on these
points).

In hybrid spin models \citep[\eg][]{1999ApJ...522..753M,
  2001ApJ...548L...9M, 2006ApJ...651.1023R, 2007MNRAS.377.1652N,
  2009MNRAS.397.1302B, gesspin} jets are produced by a combination of
the Blandford-Znajek \citep{bz} and Blandford-Payne \citep{bp}
mechanisms, \ie\ by extracting energy from a spinning black hole and
its accretion disk via the poloidal component of strong magnetic
fields. In these hybrid models, the accretion rate sets an upper limit
to the strength of the magnetic field that can thread the inner disk
and the black hole, which, in turn, determines the emergent jet
power. Of the model parameters, only \pjet\ is truly measured, so a
range of \dme\ and dimensionless spin values ($j$) can produce any
particular \pjet. However, to avoid the need for excessively large
accretion rates, which is the shortcoming of pure mass accretion
mechanisms, $j$ needs to be as near unity as possible, \ie\ the choice
of \dme\ is not completely arbitrary.

In the hybrid spin model of \citet{2007MNRAS.377.1652N}, assuming an
accretion disk viscosity parameter of 0.25
\citep{1999ApJ...520..298Q}, the \rbs\ jet power can be reached for
our fiducial values of $\mbh = 1.5 \times 10^9 ~\msol$ and $\dme =
0.02$ when $j > 0.96$, \ie\ a near maximally spinning SMBH. However,
the high accretion rate suffers from the same problems as cold- and
hot- mode accretion. If \mbh\ has been underestimated and is larger
than $3 \times 10^9 ~\msol$, for $j > 0.96$, accretion rates less than
$0.01 \dmedd \approx 0.3 ~\msolpy$ can achieve the \rbs\ jet
power. This is in good agreement with the argument presented in
\citet{minaspin}, which suggests that for similarly powerful systems,
like \ms\ and Hercules A, \dme\ cannot be much more than $\approx
0.02$. Additional relief can be found in the model of \citet{gesspin}
which has the feature that extremely powerful jets are produced for a
SMBH which is spinning retrograde relative to the direction of the
accreting material. In the \citet{gesspin} model, for $\|j\| \ge 0.9$
and $\mbh \ge 1.5 \times 10^9 ~\msol$, the required mass accretion
rates are $\dme \le 0.005$ or $\la 0.1 ~\msolpy$. So while the true
value of \dme\ is unknown, there are reasonable accretion rates for a
near maximally spinning SMBH which can reproduce the measured
\pjet\ while not being in conflict with the BCG or ICM properties.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Nuclear Emission}
\label{sec:nuc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

There is a bright BCG X-ray point source apparent in the
\cxo\ imaging, and its properties may also provide clues regarding
on-going accretion processes. A source spectrum was extracted from a
region enclosing 90\% of the normalized \cxo\ PSF specific to the
nuclear source median photon energy and off-axis position. The source
region had an effective radius of $0.86\arcs$, and a background
spectrum was taken from an enclosing annulus that had 5 times the
area. The shape and features of the background-subtracted spectrum,
shown in Figure \ref{fig:nucspec}, are inconsistent with thermal
emission. The spectrum was modeled using an absorbed power law with
two Gaussians added to account for emission features around 1.8 keV
and 3.0 keV. Including an absorption edge component to further correct
for the ACIS 2.0 keV iridium feature did not significantly improve any
fit, resulted in optical depths consistent with zero, and did not
negate the need for a Gaussian around 1.8 keV. For the entire bandpass
of both \cxo\ observations, the number of readout frames exposed to
two or more X-ray photons (\ie\ the pile-up percentage) inside an
aperture twice the size of the source region was $< 6\%$, and addition
of a pileup component to the spectral analysis resulted in no
significant improvements to the fits.

A variety of absorption models were fit to the spectrum, and the
best-fit values are given in Table \ref{tab:agn}. The model with a
power-law distribution of $\nhobs \sim 10^{22} ~\pcmsq$ absorbers
yielded the best statistical fit, and the low column densities
indicate the nucleus may not be heavily obscured. If the Gaussian
components represent emission line blends, they would be consistent
with ion species of sulfur, silicon, argon and calcium, possibly
indicating emission or reflection from dense, ionized material in or
near the nucleus \citep[\eg][]{1990ApJ...362...90B,
  1998MNRAS.297.1219I}.

If mass accretion is powering the nuclear emission, the X-ray source
bolometric luminosity, $\lbol = 2.26 \times 10^{44} ~\lum$, implies an
accretion rate of $\dmacc \approx \lbol/(0.1 c^2) \approx 0.04
~\msolpy \approx 0.001 \dme$, well into the regime where accretion
flows are expected to be radiatively inefficient,
\eg\ advection-dominated flows \citep{adaf}. Depending upon the exact
properties of the accretion disk, for $\mbh > 10^9 ~\msol$, the
optical luminosity of a $\dme \sim 0.001$ advection-dominated
accretion disk is roughly $\la 10^{42} ~\lum$
\citep{2002ApJ...570L..13C}, too faint for a point source to be
detected apart from the extended emission of the BCG nucleus (see
Section \ref{sec:bcg}). The low column densities suggested by the
X-ray modeling could not conceal a $> 10^{42} ~\lum$ source, so if
there is a bright, undetected optical point source, the emission must
be beamed away from us.

Extrapolation of the best-fit X-ray spectral model to radio
frequencies reveals good agreement with the measured 1.4 GHz and 4.8
GHz nuclear radio fluxes. Further, the continuous injection
synchrotron model of \citet{1987MNRAS.225..335H} produced an
acceptable fit to the X-ray, 1.4 GHz, and 4.8 GHz nuclear fluxes (see
Figure \ref{fig:sync}). These results suggest the nuclear X-ray source
may be unresolved synchrotron emission from the jets which are obvious
in the high-resolution 4.8 GHz radio image. Regardless, there is no
indication the X-ray source is the remnant of a very dense, hot gas
phase which might be associated with a prior or on-going accretion
event.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{AGN-BCG Interaction and Constraints on Star Formation}
\label{sec:bcg}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The \rbs\ BCG optical halo structure and star formation properties
were investigated using observations from the Hubble Space Telescope
(\hst), \galex, and the \xmm/Optical Monitor (\xom). \hst\ imaged
\rbs\ using the ACS/WFC instrument and the F606W (4500--7500 \AA;
\myv) and F814W (6800--9800 \AA; \myi) filters. Images produced using
the Hubble Legacy Archive pipeline version 1.0 were used for
analysis. The \hst\ \myv+\myi\ image is shown in Figure
\ref{fig:hst}. Comparison of the \hst\ and \cxo\ images reveals the
BCG coincides with the nuclear X-ray source. The BCG has the
appearance of being pinched into two equal brightness halves, and
there is no evidence of an optical point source. There are also
several distinct knots of emission in the halo, and a faint arm of
emission extending south from the BCG. There are two ACS artifacts in
the \myi\ image which begin at $\approx 2.7\arcs$ and $\approx
5.4\arcs$ from the BCG center. Within a $2\arcs$ aperture centered on
the BCG, the measured magnitudes are $m_{\myv} = 19.3 \pm 0.7$ mag and
$m_{\myi} = 18.2 \pm 0.6$ mag, consistent with non-\hst\ measurements
of \citet{rbs1}, indicating the \hst\ photometry in this region is
unaffected.

\rbs\ was imaged in the far-UV (FUV; 1344--1786 \AA) and near-UV (NUV;
1771--2831 \AA) with \galex, and the near-UV with the
\xmm/Optical-Monitor (\xom) using filters UVW1 (2410--3565 \AA) and
UVM2 (1970--2675 \AA). The pipeline reduced observations of
\galex\ Data Release 5 were used for analysis, and the \xom\ data was
processed using \sas\ version 8.0.1. \rbs\ is detected in all but the
UVM2 observation as an unresolved source co-spatial with the optical
and X-ray BCG emission. The individual filter fluxes are $f_{\rm{FUV}}
= 19.2 \pm 4.8 ~\mu$Jy, $f_{\rm{NUV}} = 5.9 \pm 2.1 ~\mu$Jy,
$f_{\rm{UVW1}} = 14.6 \pm 4.6$ $\mu$Jy and $f_{\rm{UVM2}} < 117$
$\mu$Jy, all of which lie above the nuclear power-law emission we
attribute to unresolved jets (see Section \ref{sec:nuc} and Figure
\ref{fig:sync}).

A radial $(\myv-\myi)$ color profile of the central $2\arcs$ ($\approx
10$ kpc) was extracted from the \hst\ images and fitted with the
function $\Delta(\myv-\myi) \log r + b$, where $\Delta(\myv-\myi)$
[mag dex$^{-1}$] is the color gradient, $r$ is radius, and $b$ [mag]
is a normalization. The best-fit parameters are $\Delta(\myv-\myi) =
-0.20 \pm 0.02$ and $b = 1.1 \pm 0.01$ for \chisq(DOF) = 0.009(21),
revealing a flat color profile. In general, BCGs have red centers and
bluer halos, with some showing signs of significant star formation
\citep[\eg][]{rafferty06}. But, because the aperture for analysis is
restricted to the central $\approx 10$ kpc and we do not have
calibrated colors, the flat profile does not clearly indicate if
blue-ing associated with a modest star formation rate is present. In
addition, the high BCG molecular mass estimate ($\sim 10^{10} ~\msol$)
implies a large dust content, which may overwhelm an underlying color
gradient associated with young stars. Star formation rates were
calculated from the UV fluxes using the relations of
\citet{kennicutt2} and \citet{salim2007}, which yield rates in the
range 1--10 ~\msolpy\ (see Table \ref{tab:sfr}), relatively small
values for what should be considered a strong cool core cluster. These
estimates are likely upper limits since the blue \galex\ color signals
some AGN contamination \citep{2005AJ....130.1022A}, and sources of
significant uncertainties have been neglected
\citep[\eg][]{1992ApJ...388..310K, 2004AJ....127.2002K, hicksuv,
  2010MNRAS.tmp..626G}.

Also of interest are the bright halo substructures seen in the
\hst\ images. To better reveal the BCG substructure, residual galaxy
images were constructed by first fitting the \hst\ \myv\ and
\myi\ isophotes with ellipses using the \iraf\ tool
                {\textsc{ellipse}}. Stars and other contaminating
                sources were rejected using a combination of $3\sigma$
                clipping and by-eye masking. The ellipse centers were
                fixed at the galaxy centroid, and ellipticity and
                position angle were fixed at $0.25 \pm 0.02$ and
                $-64\mydeg \pm 2\mydeg$, respectively -- the mean
                values when they were free parameters. Galaxy light
                models were created using {\textsc{bmodel}} in
                \iraf\ and subtracted from the corresponding parent
                image, leaving the residual images shown in Figure
                \ref{fig:subopt}. A color map was also generated by
                subtracting the fluxed \myi\ image from the fluxed
                \myv\ image.

The close alignment of the optical substructure with the nuclear AGN
outflow clearly indicates the jets are interacting with the BCG
halo. There is a spheroid northeast of the nucleus which bares a
morphological resemblance to other galaxies which are falling through
a cluster and have a ram-pressure stripped tail \citep[see][for
  example]{2007ApJ...671..190S}. The numbered regions overlaid on the
residual \myv\ image are the areas of the color map which have the
largest color difference with surrounding galaxy light. Regions 1--5
are relatively the bluest with $\Delta(\myv-\myi) = -0.40, -0.30,
-0.25, -0.22, ~\rm{and} -0.20$, respectively. Regions 6--8 are
relatively the reddest with $\Delta(\myv-\myi) =$ +0.10, +0.15, and
+0.18, respectively. Clusters like \rbs\ with a core entropy less than
$30 ~\ent$ often host a BCG surrounded by extended \halpha\ nebulae
\citep[\eg][]{mcdonald10}. Like these systems, the residual
\myi\ image reveals what appear to be 8--10 kpc long ``whiskers''
surrounding the BCG (regions 9--11). It is interesting that blue
regions 1 and 4 reside at the point where the southern jet appears to
be encountering whiskers 9 and 10.

Without pointed spectroscopy, it is unclear if the blue regions
contain star formation, if the red regions are reddened by dust
extinction, or if both are just strong emission line regions. The
influence of optical emission lines on the photometry was roughly
estimated using the ratio of line EWs taken from \citet{rbs1} to
\hst\ filter widths. The \halpha\ contribution to the \myi\ image is
estimated at $\approx 3\%$ using the scaled \hbeta\ line (see Section
\ref{sec:cold}), and the combined \hbeta, \oii, and
\oiii\ contribution to the \myv\ image is $\approx 7\%$. The low
percentages indicate the stellar continuum may be well-represented,
however, the slit setup of \citet{rbs1} spectrum is unknown, and
because the stellar continuum drops rapidly moving away from the
nucleus, a knot of nebular emission can have an EW comparable to the
10--20\% structures we find.

%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{sec:con}
%%%%%%%%%%%%%%%%%%%%%

We have presented results from a study of the AGN outburst in the
galaxy cluster \rbs. \cxo\ observations have enabled us to constrain
the energetics of the AGN outburst and analyze different powering
mechanisms. We have shown the following:
\begin{enumerate}
\item In addition to the two obvious cavities near the cluster core,
  residual imaging reveals extensive substructure in the ICM (Figure
  \ref{fig:subxray}) which has an unclear correlation with coincident
  radio emission. The extensive ICM substructure and deep decrements
  of the unambiguous cavities lead us to speculate that the cavity
  system may be much larger and more complex than the present data
  allows us to constrain.
\item We find that the two central cavities have surface brightness
  decrements that are inconsistent with the cavities being spheres
  whose centers lie in a plane perpendicular to our line of sight which
  passes through the central AGN. Motivated by the decrement analysis,
  we propose that the cavities are either highly-elongated structures
  in the plane of the sky, or result from the superposition of much
  larger structures lying along our line of sight.
\item Using the cavity decrements as a constraint, we estimate the
  total AGN outburst energy at $3 \dash 6 \times 10^{60}$ erg with a
  total power output of $3 \dash 6 \times 10^{45} ~\lum$. There is the
  possibility that the cavities are larger than we have assumed and
  consider the energetics estimates as lower limits. The thick, bright
  rims surrounding the cavities may also be signaling the presence of
  shocks, which would further boost the AGN energy output.
\item The AGN energetics suggest that pure mass accretion of cold or
  hot gas may not feasible methods for powering the outburst. We
  specifically show that Bondi accretion may not be energetically
  feasible and instead suggest that the outburst may have been powered
  by tapping the energy stored in a maximally spinning SMBH. We show
  that hybrid spin models can achieve the calculated jet powers with
  accretion rates below 0.3 ~\msolpy.
\item Using primarily \hst\ optical images, we present the discover of
  substructure in the BCG stellar halo which clearly indicates the AGN
  is interacting with the host galaxy. While we are unable to
  determine if any regions of interest host star formation or line
  emission, the convergence of what appear to be extended optical
  filaments, bluish knots of emission, and the tip of one jet suggest
  there may be AGN driven star formation.
\end{enumerate}

%%%%%%%%%%%%%%%%%
\acknowledgements
%%%%%%%%%%%%%%%%%

KWC acknowledges financial support from L'Agence Nationale de la
Recherche through grant ANR-09-JCJC-0001-01, and thanks David Gilbank,
Sabine Schindler, Axel Schwope, and Chris Waters for helpful
input. BRM was supported by a generous grant from the Canadian Natural
Science and Engineering Research Council, and thanks support provided
by the National Aeronautics and Space Administration through Chandra
Award Number G07-8122X issued by the Chandra X-ray Observatory Center,
which is operated by the Smithsonian Astrophysical Observatory for and
on behalf of the National Aeronautics Space Administration under
contract NAS8-03060. MG acknowledges support from the grants ASI-INAF
I/088/06/0 and CXO GO0-11003X. Some results are based on observations
made with the NASA/ESA Hubble Space Telescope, and obtained from the
Hubble Legacy Archive, which is a collaboration between the Space
Telescope Science Institute (STScI/NASA), the Space Telescope European
Coordinating Facility (ST-ECF/ESA) and the Canadian Astronomy Data
Centre (CADC/NRC/CSA).

%%%%%%%%%%%%%%%%
% Bibliography %
%%%%%%%%%%%%%%%%

\bibliography{cavagnolo}

%%%%%%%%%%%%%%%%%%%%%%
% Figures and Tables %
%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\input{cavities.tex}
\input{totals.tex}
\input{agn.tex}
\input{sfr.tex}
\input{figs.tex}

%%%%%%%%%%%%%%%%%%%%
% End the document %
%%%%%%%%%%%%%%%%%%%%

\end{document}
