%%%%%%%%%%%%%%%%%%%
% Custom commands %
%%%%%%%%%%%%%%%%%%%

\newcommand{\dmb}{\ensuremath{\dot{m_{\rm{B}}}}}
\newcommand{\dme}{\ensuremath{\dot{m_{\rm{E}}}}}
\newcommand{\ldisk}{\ensuremath{L_{\rm{disk}}}}
\newcommand{\lfir}{\ensuremath{L_{\rm{FIR}}}}
\newcommand{\lfuv}{\ensuremath{L_{\rm{FUV}}}}
\newcommand{\lnuv}{\ensuremath{L_{\rm{NUV}}}}
\newcommand{\ms}{MS 0735.6+7421}
\newcommand{\myi}{\ensuremath{I^{\prime}}}
\newcommand{\myv}{\ensuremath{V^{\prime}}}
\newcommand{\rbs}{R797}
\newcommand{\reff}{\ensuremath{r_{\rm{eff}}}}
\newcommand{\rlos}{\ensuremath{r_{\rm{los}}}}
\newcommand{\mykeywords}{}
\newcommand{\mystitle}{\rbs\ AGN Outburst}
\newcommand{\mytitle}{A Powerful, Line-of-Sight AGN Outburst in RBS
  797}

%%%%%%%%%%
% Header %
%%%%%%%%%%

\documentclass[11pt, preprint]{aastex}
\usepackage{graphicx,common}
%\documentclass[iop]{emulateapj}
%\usepackage{apjfonts,graphicx,here,common,longtable,ifthen,amsmath,amssymb,natbib}
\usepackage[pagebackref,
  pdftitle={\mytitle},
  pdfauthor={Dr. Kenneth W. Cavagnolo},
  pdfsubject={Astrophysical Journal},
  pdfkeywords={galaxies: active -- galaxies: clusters: general --
    X-rays: galaxies -- radio continuum: galaxies},
  pdfproducer={LaTeX with hyperref},
  pdfcreator={LaTeX with hyperref}
  pdfdisplaydoctitle=true,
  colorlinks=true,
  citecolor=blue,
  linkcolor=blue,
  urlcolor=blue]{hyperref}
\bibliographystyle{apj}
\begin{document}
\title{\mytitle}
\shorttitle{\mystitle}
\author{
  K. W. Cavagnolo\altaffilmark{1,2,8},
  B. R. McNamara\altaffilmark{1,3,4},
  M. W. Wise\altaffilmark{5}, \\
  M. Br\"uggen\altaffilmark{6}, 
  P. E. J. Nulsen\altaffilmark{4}, and
  M. Gitti\altaffilmark{4,7},
}
\shortauthors{Cavagnolo et al.}

\altaffiltext{1}{University of Waterloo, 200 University Ave. W.,
  Waterloo, ON, N2L 3G1, Canada.}
\altaffiltext{2}{Observatoire de la C\^ote d'Azur, Boulevard de
  l'Observatoire, B.P. 4229, F-06304, Nice, France.}
\altaffiltext{3}{Perimeter Institute for Theoretical Physics, 31
  Caroline St. N., Waterloo, ON, N2L 2Y5, Canada.}
\altaffiltext{4}{Harvard-Smithsonian Center for Astrophysics, 60
  Garden St., Cambridge, MA, 02138-1516, United States.}
\altaffiltext{5}{Astronomical Institute Anton Pannekoek, P.O. Box
  94249, 1090 GE Amsterdam, The Netherlands.}
\altaffiltext{6}{Jacobs University Bremen, P.O. Box 750561, 28725
  Bremen, Germany.}
\altaffiltext{7}{INAF-Astronomical Observatory of Bologna, Via
  Ranzani 1, I-40127 Bologna, Italy.}
\altaffiltext{8}{cavagnolo@oca.eu}

%%%%%%%%%%%%
% Abstract %
%%%%%%%%%%%%

\begin{abstract}
  Utilizing a $\sim 40$ ks observation from the Chandra X-ray
  Observatory, we present spatially resolved analysis of the
  intracluster medium, cavities, and the nuclear point source of RBS
  797.
\end{abstract}

%%%%%%%%%%%%
% Keywords %
%%%%%%%%%%%%

\keywords{\mykeywords}

%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%

Evidence has amassed over the last decade that the growth of galaxies
and supermassive black holes (SMBHs) are coupled, and that energetic
feedback from active galactic nuclei (AGN) strongly influences galaxy
evolution \citep[\eg][]{1995ARA&A..33..581K, magorrian,
  1998A&A...331L...1S, 2000MNRAS.311..576K, 2000ApJ...539L...9F,
  2000ApJ...539L..13G, 2002ApJ...574..740T}. The discovery of AGN
induced cavities in the hot halos surrounding many massive galaxies
has strengthened this theory \citep[see][for a review]{mcnamrev},
revealing that AGN mechanical heating is capable of regulating the
radiative cooling responsible for late-time galaxy growth
\citep[\eg][]{birzan04, dunn06, rafferty06}. Current models of this
late-time ``feedback loop'' posit that cooling processes in a galaxy's
halo result in mass accretion onto a central SMBH, thereby driving AGN
activity and ultimately heating the cooling halo
\citep[\eg][]{croton06, bower06, sijacki07}. While there is direct
evidence that halo cooling and feedback are linked
\citep[\eg][]{haradent, rafferty08}, the observational constraints on
how AGN are fueled and powered remain loose. For example, what
fraction of the energy released in an AGN outburst is attributable to
the gravitational binding energy of the accreting matter
\citep[see][for a review]{1984RvMP...56..255B} and the SMBH's
rotational energy \citep[see][for a review]{2002NewAR..46..247M} is
still unclear.

Mass accretion alone can, in principle, fuel most AGN
\citep[\eg][]{pizzolato05, 2006MNRAS.372...21A}, and is typically not
at odds with the gas masses and stellar masses of the host galaxy
\citep[\eg][]{rafferty06}. However, there are systems which are
gas-poor and host very powerful AGN where mass accretion alone does
not appear to be capable of sustaining the outburst. In the galaxy
clusters Hercules A, Hydra A, and \ms, for example, an AGN in each
cluster's brightest cluster galaxy (BCG) has deposited more than
$10^{61}$ erg of energy into the surrounding intracluster medium (ICM)
at rates of order $10^{45} ~\lum$ \citep{herca, hydraa, ms0735}. The
importance of these systems in understanding AGN feedback is that
either the AGN fueling has been astoundingly efficient, or the power
has come from an alternate source, such as the release of angular
momentum stored in a rapidly spinning SMBH \citep[\eg][]{msspin,
  minaspin}. SMBH spin is an intriguing energy source because
releasing the energy requires some mass accretion (maintaining the
feedback loop) and a typical BCG SMBH can store more than $10^{62}$
erg of energy if it is rapidly spinning. If more systems can be found
which are best explained as being powered by SMBH spin, then it may be
necessary to incorporate this feedback pathway into galaxy formation
models \citep[\eg][]{2003ApJ...585L.101H, 2007ApJ...658..815S,
  2009MNRAS.397.1302B, gesspin}.

In this paper, we present analysis of the AGN outburst in the galaxy
cluster RBS 797 (\rbs\ hereafter) and, because of the extreme
energetic demands of the outburst, suggest it may have been powered by
black hole spin. The discovery of prominent cavities in the ICM of
\rbs\ was first reported by \citet{schindler01} using data from the
Chandra X-ray Observatory (\cxo). Subsequent multifrequency radio
observations showed that the cavities are co-spatial with extended
radio emission centered on a strong, jetted radio source coincident
with the \rbs\ BCG \citep{2002astro.ph..1349D, gitti06, birzan08}. The
observations implicate an AGN in the BCG as the cavities' progenitor,
and the cavity analysis presented in \citet[][hereafter B04]{birzan04}
shows that the AGN deposited $\sim 10^{60}$ erg of energy into the ICM
at a rate of $\sim 10^{45} ~\lum$, relatively large values for an AGN
outburst. The analysis of B04 assumed that the observed cavities are
distinct, symmetric about the plane of the sky, and that their centers
lie in a plane passing through the central AGN and perpendicular to
our line-of-sight (configuration-1 in Figure
\ref{fig:config}). However, the depth of the cavities and the nebulous
correlation between the radio and X-ray morphologies calls into
question these assumptions.

In this paper, we utilize a longer, follow-up \cxo\ observation of
\rbs\ to suggest that the observed ``cavities'' result from the
superposition of much larger overlapping cavities positioned nearly
along the line-of-sight (configuration-2 in Figure
\ref{fig:config}). Thus, our estimates of the cavity energy, \ecav,
and the jet powers which formed the cavities, \pjet, are 10 times
larger than the B04 values -- of the order $10^{61}$ erg and $10^{46}
~\lum$, respectively. We find that mass accretion alone is an
implausible explanation for how the outburst was powered, and instead
suggest that the outburst resulted from the extraction of rotational
energy stored in a rapidly-spinning SMBH. \rbs\ may be further
observational evidence that some AGN are powered by the release of
SMBH spin energy.

Observations and data reduction are discussed in Section
\ref{sec:obs}, results are given throughout Section \ref{sec:results},
and a brief summary concludes the paper in Section
\ref{sec:con}. \LCDM. At a redshift of $z = 0.354$, the look-back time
is 3.9 Gyr, $\da = 4.996$ kpc arcsec$^{-1}$, and $\dl = 1889$ Mpc. All
errors are 68\% confidence unless stated otherwise.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Observations and Data Reduction}
\label{sec:obs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%
\subsection{X-ray}
%%%%%%%%%%%%%%%%%%

\rbs\ was observed with \cxo\ in October 2000 for 11.4 ks using the
ACIS-I array (\dataset [ADS/Sa.CXO#Obs/02202] {ObsID 2202}; PI
Schindler) and in July 2007 for 38.3 ks using the ACIS-S array
(\dataset [ADS/Sa.CXO#Obs/07902] {ObsID 7902}). Datasets were reduced
using \ciao\ and \caldb\ versions 4.2. Events were screened of cosmic
rays using \asca\ grades and {\textsc{vfaint}} filtering. The level-1
events files were reprocessed to apply the most up-to-date corrections
for the time-dependent gain change, charge transfer inefficiency, and
degraded quantum efficiency of the ACIS detector. The afterglow and
dead area corrections were also applied. Time intervals affected by
background flares exceeding 20\% of the mean background count rate
were isolated and removed using light curve filtering. The final,
combined exposure time is 48.8 ks. Point sources were identified and
removed via visual inspection and use of the \ciao\ tool
{\textsc{wavdetect}}. We refer to the \cxo\ data free of point sources
and flares as the ``clean'' data. A mosaiced, fluxed image (see Figure
\ref{fig:img}) was generated by exposure correcting each clean dataset
and reprojecting the normalized images to a common tangent point.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Ultraviolet}
%%%%%%%%%%%%%%%%%%%%%%%%

The UV measurements below are utilized in Section \ref{sec:bcg} to
constrain the \rbs\ star formation rate. \rbs\ was imaged in the
far-UV (FUV; 1344--1786 \AA; FWHM $\approx 4.5\arcs$) and near-UV
(NUV; 1771--2831 \AA; FWHM $\approx 6.0\arcs$) for 136 s by the Galaxy
Evolution Explorer (\galex) in December 2003. \rbs\ is detected in
both filters but is unresolved. The FUV, NUV, optical, and X-ray
sources are co-spatial, and the next nearest UV source is at a
distance of $19\arcs$, indicating the detection is unlikely to be a
spurious source. The source fluxes are $f_{\rm{FUV}} = 19.2 \pm 4.8
~\mu$Jy and $f_{\rm{NUV}} = 5.9 \pm 2.1 ~\mu$Jy.

The XMM-Newton Optical-Monitor (\xom) imaged \rbs\ in April 2008 for
4.5 ks (DataID 0502940301; PI M. Gitti). Exposures were taken with two
filters: UVW1 (2410--3565 \AA; FWHM $\approx 2.0\arcs$) and UVM2
(1970--2675 \AA; FWHM $\approx 1.8\arcs$). The data was processed
using \sas\ version 8.0.1 and the task {\textsc{omichain}}. Using the
tool {\textsc{omdetect}}, an unresolved source co-spatial with
\rbs\ was detected in the UVW1 image, but no corresponding source was
detected in the UVM2 image. A $3\sigma$ upper limit on the UVM2 flux
was calculated using the UVW1 source as a guide. For each filter, mean
count rates for the source region were measured using the tool
{\textsc{omsource}}, converted to instrumental magnitudes, and then to
fluxes, giving $f_{\rm{UVW1}} = 14.6 \pm 4.6$ $\mu$Jy and
$f_{\rm{UVM2}} < 117$ $\mu$Jy.

%%%%%%%%%%%%%%%%%%%%
\subsection{Optical}
%%%%%%%%%%%%%%%%%%%%

The optical data discussed below are used in Section \ref{sec:bcg} to
investigate interaction of the central AGN with the BCG halo and
constrain BCG star formation properties. \rbs\ was imaged for 1.2 ks
with the Hubble Space Telescope (\hst) ACS/WFC instrument in March and
December 2006 (prop IDs 10491 and 10875; PI H. Ebeling). The F606W
(4500--7500 \AA; \myv) and F814W (6800--9800 \AA; \myi) filters were
used during the observations, and are denoted with primes to
distinguish from the standard Johnson $V$ and $I$ filters. The cosmic
ray cleaned, drizzled images from the Hubble Legacy Archive pipeline
were used for analysis. Two ACS ghosts \citep{acsghost} are present in
the \myi\ image: the northern and western ghosts begin at $\approx
2.7\arcs$ and $\approx 5.4\arcs$, respectively, from the center of the
BCG. Within a $2\arcs$ circular aperture centered on the BCG, the
galaxy magnitudes are $m_{\myv} = 19.3 \pm 0.7$ mag and $m_{\myi} =
18.2 \pm 0.6$ mag, consistent with the non-\hst\ based measurements of
\citet{rbs1} and \citet{rbs2}, indicating the photometry in this
region is not impacted by the ghosts.

A spectrum (3200-7600 \AA) of \rbs\ was obtained with the longslit
spectrograph on the Bolshoi Altazimuth Telescope (BTA) in February
1996 \citep{rbs1, rbs2}. Though positioned on \rbs, the slit setup is
unknown, and flux calibration was applied using the average of
response functions for a set of standard stars, resulting in
wavelength-dependent photometric uncertainties $\ga 50\%$. Because
measurements made from the BTA spectrum are highly uncertain, they are
only discussed for completeness. Wavelength calibration was applied
using a He-Ar-Ne lamp, and sky subtraction was performed pixel-wise
along each CCD column of regions 25 CCD rows wide below and above the
trace of the spectrum. Spectral features were located and fit with
tools in the \iraf\ {\textsc{onedspec}} package.

The BTA spectrum reveals strong emission lines of \hbeta, [O
  \Rmnum{2}], [O \Rmnum{3}], and, presumably, \halpha\ associated with
the region around \rbs. These lines lie within the \hst\ passbands,
and their contribution to the \hst\ images was determined using the
ratio of line equivalent widths (EWs) to passband widths. The
\halpha\ contribution to the \myi\ image was estimated to be $\approx
3\%$ (likely an overestimate since the stellar continuum rises toward
the red) by scaling \hbeta\ using a Balmer decrement of
EW$_{\hbeta}$/EW$_{\halpha}$ = 0.29 \citep{2006ApJ...642..775M}. The
\hbeta, \oii, and \oiii\ contribution to the \myv\ image is $\approx
7\%$. The low line contamination indicates the stellar continuum
should be well-represented in the \hst\ observations.

%%%%%%%%%%%%%%%%%%
\subsection{Radio}
%%%%%%%%%%%%%%%%%%

Very Large Array (\vla) radio images at 325 MHz (A-array), 1.4 GHz (A-
and B-array), 4.8 GHz (A-array), and 8.4 GHz (D-array) were presented
in \citet{gitti06} and \citet{birzan08}. Re-analysis of the archival
\vla\ radio observations yielded no significant differences with the
previous studies. Using rms noise values for each frequency given in
\citet{gitti06} and \citet{birzan08}, emission contours between
$3\sigma_{\rm{rms}}$ and the peak image intensity were
generated. These are the contours referenced and shown in all
subsequent discussion and figures.

%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{sec:results}
%%%%%%%%%%%%%%%%%%%

Shown in Figure \ref{fig:img} are an exposure-corrected 0.7--2.0 keV
\cxo\ X-ray image of the \rbs\ ICM, and an \hst\ optical image of the
\rbs\ BCG. Outside of $\approx 50$ kpc, the global ICM morphology is
regular and elliptical in shape, with the appearance of being skewed
along the NW-SE direction. The cavities discovered by
\citet{schindler01} are clearly seen in the cluster core east and west
of the nuclear X-ray source and appear to be enclosed by a bright,
elliptical ridge of emission. The western cavity has more internal
structure, and its boundaries are less well-defined, than the eastern
cavity. The emission from the innermost region of the core is
elongated N-S and has a distinct `S'-shape puntuated by a hard nuclear
X-ray source. Comparison of the \hst\ optical and \cxo\ X-ray images
reveals the nuclear X-ray source coincides with the BCG, which has the
appearance of being pinched into two equal brightness sources. It is
unclear which, if either, is at the center of the galaxy or might be
associated with an AGN. There is also an emitting structure extending
south from the BCG. The BCG substructure, and its association with the
AGN, is discussed more thoroughly in Section \ref{sec:bcg}.

In Figure \ref{fig:composite} we show multifrequency radio images
overlaid with ICM X-ray contours. The radio structures are discussed
thoroughly in \citet{gitti06}, and we summarize here. As seen in
projection, the nuclear 4.8 GHz jets are almost orthogonal to the axis
connecting the cavities. The 325 MHz, 1.4 GHz, and 8.4 GHz radio
emission are diffuse and extend well-beyond the cavities, more similar
to the morphology of a radio mini-halo than relativistic plasma
confined to the cavities (Doria et al., in preparation). Of all the
radio frequencies, the 1.4 GHz emission most closely traces the cavity
morphologies, yet it is still very diffuse and uniform over the
cavities with little structure outside the radio core. Typically, the
connection between a cavity system, coincident radio emission, and the
progenitor AGN is unambiguous, but this is not the case for \rbs,
which suggests the cavity morphologies may be very complex or that
projection effects are important. The analysis in Sections
\ref{sec:icm} and \ref{sec:cavities} focuses on disentangling the
radio-X-ray relationship to better understand the AGN outburst
energetics.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Radial ICM Properties}
\label{sec:icm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Analysis of the \rbs\ cavity system requires that the ICM density and
temperature structure be known \citep[see][for details]{mcnamrev}. The
ICM temperature (\tx) structure was determined by fitting spectra
extracted from concentric circular annuli containing 2500 source
counts centered on the cluster X-ray peak. For each annulus, weighted
responses were created and background spectra were extracted from the
ObsID matched \caldb\ blank-sky dataset. Background data was
normalized using the ratio of 9--12 keV count rates for identical
off-axis, source-free regions of the blank-sky and target datasets. A
spectral model for the Galactic foreground was included as an
additional, fixed background component during spectral fitting
\citep{2005ApJ...628..655V, xrayband}. Source spectra were binned to
25 counts per energy channel and fitted using \xspec\ 12.4
\citep{xspec} with an absorbed, single-component \mekal\ model
\citep{mekal1} over the energy range 0.7-7.0 \keV. The absorbing
Galactic column density was fixed to $\nhgal = 2.28 \times 10^{20}
~\pcmsq$ \citep{lab}. Gas metal abundance was free to vary and
normalized using the solar ratios of \citet{ag89}. Only projected
spectra are discussed as spectral deprojection using the
{\textsc{proj}} \xspec\ model did not produce significantly different
results. The temperature and abundance profiles are shown in the top
row of Figure \ref{fig:gallery}.

A 0.7-2.0 keV surface brightness profile was extracted from the
mosaiced, clean image using concentric $1\arcs$ wide elliptical annuli
centered on the BCG X-ray point source (central $\approx 1\arcs$ and
cavities excluded). A deprojected electron density (\nelec) profile
was derived from the surface brightness profile using the method of
\citet{kriss83} which incorporates the 0.7-2.0 keV count rates and
best-fit normalizations from the spectral analysis \citep[see][for
  details]{accept}. The spectral quantities were transferred from the
coarser temperature bins to the finer density bins via linear
interpolation. Errors for $\nelec(r)$ were estimated using 5000 Monte
Carlo simulations of the original surface brightness profile. A total
gas pressure ($P$) profile was calculated as $P = n \tx$ where $n
\approx 2.3 \nH$ and $\nH \approx \nelec/1.2$. The surface brightness,
density, and pressure profiles are shown in the second and third rows
of Figure \ref{fig:gallery}.

Profiles of enclosed X-ray luminosity, entropy ($K = \tx
\nelec^{-2/3}$) and cooling time ($\tcool = 3 n \tx~(2 \nelec \nH
\Lambda)^{-1}$, where $\Lambda$ is the cooling function), were also
generated. These profiles are shown in the third and fourth rows of
Figure \ref{fig:gallery}. Errors for each profile were determined by
summing the individual parameter uncertainties in quadrature. The
entropy profile was fitted with the function $K = \kna +\khun (r/100
~\kpc)^{\alpha}$, where \kna\ [\ent] is core entropy, \khun\ [\ent] is
a normalization at 100 kpc, and $\alpha$ is a dimensionless index,
yielding best-fit parameters of $\kna = 17.9 \pm 2.2 ~\ent$, $\khun =
92.1 \pm 6.2 ~\ent$, and $\alpha = 1.65 \pm 0.11$.

The radial analysis does not clearly indicate if any signifcant
discontinuities exist in the ICM to indicate the presence of a shock
or cold front. \rbs\ has a core entropy $< 30 ~\ent$ and ICM cooling
time within 9 kpc of the cluster center of $\sim 400$ Myr. In general,
clusters with these core properties host line emitting BCGs
\citep[\eg][]{crawford99, edge01, haradent}, some of which have
nuclear star formation \citep[\eg][]{rafferty08}. Partially consistent
with this picture, we show in Section \ref{sec:bcg} that wisps of
infrared emission, which may be \halpha\ filaments, radiate from the
\rbs\ BCG, but, that plausible evidence of star formation is
predominately found in areas of the BCG halo directly interacting with
the central AGN.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{ICM Cavities and the AGN Outburst}
\label{sec:cavities}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Cavity Morphologies and ICM Substructure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To better reveal the cavity morphologies, residual X-ray images of
\rbs\ were constructed by modeling the ICM emission and subtracting it
off. The X-ray isophotes of two exposure-corrected images -- one
smoothed by a $1\arcs$ Gaussian and another by a $3\arcs$ Gaussian --
were fitted with ellipses using the \iraf\ task \textsc{ellipse}. The
ellipse centers were fixed at the location of the BCG X-ray point
source, and the eccentricities and position angles were free to
vary. A 2D surface brightness model was created from each fit using
the \iraf\ task \textsc{bmodel}, normalized to the parent X-ray image,
and then subtracted off. The residual images are shown in Figure
\ref{fig:subxray}.

In addition to the central east and west cavities (labeled E1 and W1),
depressions north and south of the nucleus (labeled N1 and S1) are
revealed. N1 and S1 lie along the 4.8 GHz jet axis and are coincident
with spurs of significant 1.4 GHz emission, indicating they may be
related to activity of the central AGN. A depression coincident with
the southeastern concentration of 325 MHz emission is also found
(labeled E2), but no counterpart on the opposing side of the cluster
is seen (labeled W2). There is an X-ray edge which extends southeast
from E2 and sits along a ridge of 325 MHz and 8.4 GHz emission. No
substructure associated with the western-most knot of 325 MHz emission
is found, but there is a stellar object co-spatial with this region.
The X-ray and radio properties of the object are consistent with those
of a galactic RS CVn star \citep{1993RPPh...56.1145S} -- if the star
is less than 1 kpc away, $\lx \la 10^{31} ~\lum$ and $L_{325} \sim
10^{27} ~\lum$ -- suggesting the western 325 MHz emission may not be
associated with the cluster.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Cavity Energetics}
\label{sec:ecav}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The E1-W1 cavities are unambiguously detected, and their energetics
were determined following standard methods \citep[see][for a
  review]{mcnamrev}. Our fiducial cavity configuration assumes the
cavities are symmetric about the plane of the sky, and the cavity
centers lie in a plane which is perpendicular to our line-of-sight and
passes through the central AGN (configuration-1 in Figure
\ref{fig:config}). Hereafter we denote the line-of-sight distance of a
cavity's center from this plane as $z$ and the cavity radius along the
line-of-sight as \rlos. The volume of a cavity is $V = 4\pi a b
\rlos/3$ where $a$ and $b$ are the projected semi-major and -minor
axes, respectively, of the ellipses in Figure \ref{fig:subxray}. For
simplicity, the cavities were assumed to be roughly spherical and
\rlos\ was set equal to the projected effective radius, $\reff =
\sqrt{ab}$. For configuration-1, the distance of each cavity from the
central AGN, $D$, is simply the projected distance from the ellipse
centers to the BCG X-ray point source. A systematic error of 10\% is
assigned to the cavity volumes.

Cavity ages were estimated using the three time scales discussed in
B04: ICM sound speed age (\tsonic), buoyant rise time age (\tbuoy),
and volume refilling age (\trefill). The energy in each cavity, $\ecav
= \gamma PV/(\gamma-1)$, was calculated assuming the contents are a
relativistic plasma ($\gamma = 4/3$), and that the mean internal
cavity pressure is equal to the ICM pressure at the cavity mid-point,
\ie\ cavity pressure equals $P(r = D)$. The time-averaged energy
needed to create each cavity was calculated as $\pcav =
\ecav/\tbuoy$. The cavity properties are listed in Table
\ref{tab:cavities}.

Our analysis indicates the aggregate E1-W1 configuration-1 cavity
energy is at least $\ecav \approx 3 \times 10^{60}$ erg with a total
AGN power output of $\pcav \approx 3 \times 10^{45} ~\lum$. These
values are larger than those of B04 by a factor of $\approx 2$ as a
result of our larger E1 and W1 volumes. Using the B04 cavity volumes
in place of our own produces no significant differences between our
energetics calculations and those of B04. The largest sources of
uncertainty in the energetic calculations are the cavity volumes and
their location in the cluster, issues we consider next.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Plane of the Sky Cavities}
\label{sec:dec}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A cavity's morphology and location in the ICM dictates the X-ray
decrement, $y$, induced by the cavity. If the surface brightness of
the undisturbed ICM can be estimated, then $y$ is useful for
constraining \rlos\ and $z$ \citep[see][for details]{hydraa}. We
define $y$ as the ratio of the X-ray surface brightness inside the
cavities to the value of the best-fit ICM surface brightness
$\beta$-model at the same radius. Consistent with the analysis of
\citet{schindler01}, we find the best-fit $\beta$-model has parameters
$S_0 = 1.65 ~(\pm 0.15) \times 10^{-3}$ \sbr, $\beta = 0.62 \pm 0.04$,
and $r_{\rm{core}} = 7.98\arcs \pm 0.08$ for \chisq(DOF) =
79(97). Using a circular aperture with radius $1\arcs$ centered on the
deepest part of each cavity, we measure mean decrements of
$\bar{y}_{\rm{W1}} = 0.50 \pm 0.18$ and $\bar{y}_{\rm{E1}} = 0.52 \pm
0.23$, with minima of $y^{\rm{min}}_{\rm{W1}} = 0.44$ and
$y^{\rm{min}}_{\rm{E1}} = 0.47$.

Cavities this deep are uncommon, with most other cavity systems having
minima greater than 0.6 (B04). The extreme decrements raise the
concern that the $\beta$-model fit has been influenced by the rim-like
structures surrounding E1-W1 (see Section \ref{sec:icm}) and produced
artificially low decrements. In addition to excluding the cavities, we
tried excluding the rims during $\beta$-model fitting, but this did
not provide insight as too much of the surface brightness profile was
removed and the fit did not converge. Extrapolating the surface
brightness profile at larger radii inward resulted in even lower
decrements. With no suitable alternative, we assume the $\beta$-model
is the best representation of the undisturbed ICM.

Since the $\beta$-model is symmetric about the plane of the sky, a
decrement less than 0.5 requires that gas on both sides of this plane
be displaced. Thus, cavity configuration-3 in Figure \ref{fig:config},
where an elongated radio lobe inflating parallel to the line-of-sight
is viewed along its axis, is unlikely. To see if cavity
configuration-1 could reproduce the measured decrements, the best-fit
$\beta$-model was integrated over each cavity with a column of gas
equal to $2\rlos$ excluded. The integration revealed decrements $<
0.67$ cannot be achieved for configuration-1, indicating $\rlos =
\reff$ is a poor assumption. The measured decrements can be reproduced
when $z = 0$ and $\rlos = 21.1$ kpc for E1 and $\rlos = 25.3$ kpc for
W1. However, these radii suggest that the cavities are two times
larger along the line-of-sight than in the plane of the sky. If the
radio lobes are inflating perpendicular to our line-of-sight, then how
the cavities achieved a highly flattend morphology so close to the
launch point is unclear.

Alternatively, if our sightlines cut through a pair of lobes inflating
along the line-of-sight, as shown in configuration-2 of Figure
\ref{fig:config}, then deep decrements could be achieved. A
line-of-sight cavity configuration may also explain the ambiguous
relationship between the radio and X-ray emission: the superposition
of complex radio-emitting plasma within, and below, the cavities could
wipe-out otherwise clear correlations between X-ray and radio
features. If the cavities lie along the line-of-sight, then the
volumes will be larger, and thus so will the estimated AGN energy
output. Cavity configuration-2 is considered in-detail below.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Line-of-Sight Cavities}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Shown in Figure \ref{fig:proj} is a proposed configuration for a pair
of large cavities (O1 and O2) lying along the line-of-sight whose
projected cross-sections overlap. The elliptical regions were chosen
such that they coincide with most of the X-ray substructure and
enclose most of the radio emission. For this cavity configuration, a
variety of \rlos\ and $z$ can reproduce the measured decrements. Thus,
we selected a simple morphology and again set $\rlos = \reff$. Taking
into consideration that each cavity will account for $\approx 50\%$ of
the total decrement, the $\beta$-model integration indicates
$z_{\rm{E1}} = 66^{+13}_{-9}$ and $z_{\rm{W1}} = 65^{+12}_{-9}$. The
centers of the cavities are then a distance $D \approx \sqrt{d^2+z^2}$
from the central AGN, where $d$ is the projected distance from the
ellipse centers to the BCG X-ray point source. The energetics
calculations of Section \ref{sec:ecav} were repeated for O1 and O2 and
are given in Table \ref{tab:cavities}.

The energetics for the line-of-sight cavity configuration are extreme
-- total cavity energy of $\approx 6 \times 10^{61}$ erg and cavity
power of $\approx 3 \times 10^{46} ~\lum$ -- and are likely upper
limits given the uncertainties in the cavity morphologies and
decrement estimates. But, they do suggest the \rbs\ outburst may be
one of the most powerful found to date. The mechanical power output is
similar to the radiative power output of a typical quasar, and exceeds
the $\approx 3 \times 10^{45} ~\lum$ of energy radiated away by ICM
gas with a cooling time less than the age of the Universe at
$z=0.35$. As we discuss in Section \ref{sec:accretion}, powering an
outburst of this magnitude by mass accretion alone is problematic,
allowing us to consider black hole spin energy as an alternate power
source.

To help visualize the X-ray emission for a cluster with cavities
inflating along the line-of-sight, a hydrodynamical cavity formation
simulation was performed with {\textsc{FLASH}} version 3.0
\citep{flash}. The simulation was tailored to \rbs\ by using the
best-fit $\beta$-model as the cluster atmosphere, and the the O1-O2
parameters listed in Table \ref{tab:cavities}. The mesh refinement
criteria were the standard density and pressure, with a minimum cell
size of 0.66 kpc on a grid of $1024^3$ zones. The simulation was
started by injecting energy into two spheres of radius XX kpc at
distances of XX kpc from the cluster center. The gas in the spheres
was heated and expanded similar to a Sedov explosion to form a pair of
bubbles in a few Myr, a time much shorter than the buoyant rise time
of the bubbles. The simulation ran until the bubbles reached a radius
of XX kpc and a density contrast with the ambient ICM of $\approx
X.XX$ \citep[see][]{2009arXiv0909.1805S}. To aide direct comparison
with the \cxo\ data, the simulation output was processed with the
{\textsc{XIM}}\footnote{http://www.astro.wisc.edu/~heinzs/XIM} X-ray
imaging pipeline \citep{2009arXiv0903.0043H}.

Shown in Figure \ref{fig:sims} are images of the simulated, projected
ICM X-ray emission. The simulated image corresponding to the cavities
lying along the line-of-sight has much in common with the real X-ray
image of \rbs: 1) a bright, azimuthally symmetric rim in the core
region arises from the conjunction of the cavities in projection, 2)
there are faint depressions at the leading edge of each cavity which
may be analogs of E2, and 3) surface brightness analysis of the
cavities reveals decrements of $\la 0.5$ (XX: True?). There are also
some inconsistencies with the real X-ray images: the presence of a
distinct depression at W2, the core resembling a bullseye, and the
much lower core density. However, the simulation represents symmetric
cavities within an idealized cluster atmosphere. Real cavities are
known to entrain denser material and deform they as move away from the
AGN. Also, asymmetries in the large-scale and core ICM gas
distributions have not be considered, and may explain the differences
between the \cxo\ observations and the simulation. Taking these
caveats into consideration, we find a line-of-sight cavity
configuration plausible.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Powering the AGN Outburst}
\label{sec:accretion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Assuming \ecav\ is representative of the gravitational binding energy
released by mass accreted onto the SMBH, then the total mass accreted
and its rate of consumption were $\macc = \ecav/(\epsilon c^2)$ and
$\dmacc = \macc/\tbuoy$, respectively. Here, $\epsilon$ is a poorly
understood mass-energy conversion factor assumed to be 0.1, which
gives $\macc \approx 4 \times 10^8 ~\msol$ and $\dmacc \approx 5
~\msolpy$. Below, we consider if the accretion of cold gas or hot gas
pervading the BCG could meet these requirements.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Cold Accretion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Substantial reservoirs of molecular gas and gaseous filaments are
found in many cool core clusters \citep{crawford99, edge01}, and via
the formation of thermal instabilities in these structures, it is
possible that they provide fuel for AGN activity and star formation
\citep[\eg][]{pizzolato05, 2010arXiv1003.4181P}. The molecular gas
mass (\mmol) of \rbs\ has not been measured, so the
\halpha-\mmol\ correlation presented by \citet{edge01} was used to
estimate \mmol, with the caveat that this correlation has substantial
scatter \citep{salome03}. Using the scaled \hbeta\ line as a surrogate
for \halpha, we estimate $\mmol \sim 10^{10} ~\msol$, sufficiently in
excess of \macc\ that we can infer an ample supply of cold gas exists
to have powered the outburst.

However, SMBHs do not grow independent of the host galaxy, and several
hundred times as much gas should go into stars as is accreted by a
SMBH \citep{1995ARA&A..33..581K, magorrian}. In which case, the
\rbs\ star formation rate (SFR) appears to be suspiciously low, $\psi
\ll 100 ~\msolpy$ (see Section \ref{sec:bcg}), when compared with
\dmacc. Assuming the present SFR is representative of the SFR
preceding and during the AGN outburst, the implication is that for
every mass unit accreted by the SMBH, less than 10 units went into
stars, a ratio well below what is expected from SMBH-host galaxy
co-evolution. Conversely, if the SFR and/or \dmacc\ estimates are
inaccurate, and the SFR during the outburst was commensurate with the
Magorrian relation, \rbs\ should have a strong blue color gradient
indicating newly formed stars \citep{rafferty08}, which it does not
(see Section \ref{sec:bcg}). Lacking better constraints on \mmol\ and
$\psi$, we can only conclude that if cold gas accretion did power the
outburst, it appears the SMBH gas consumption was exceptionally
efficient.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Hot Accretion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Direct accretion of the hot ICM via the Bondi mechanism provides
another possible AGN fuel source. The accretion flow arising from this
process is characterized via the Bondi equation (Equation
\ref{eqn:bon}) and is often compared with the Eddington limit
describing the maximal gas inflow rate (Equation \ref{eqn:edd}):
\begin{eqnarray}
  \dmbon &=& 0.013 ~\kbon^{-3/2} \left(\frac{\mbh}{10^9
    ~\msol}\right)^{2} ~\msolpy \label{eqn:bon}\\
  \dmedd &=& \frac{2.2}{\epsilon} \left(\frac{\mbh}{10^9~\msol}\right)
  ~\msolpy  \label{eqn:edd}
\end{eqnarray}
where $\epsilon$ is a mass-energy conversion factor, \kbon\ is the
mean entropy in \ent\ of gas within the Bondi radius, and \mbh\ is
black hole mass in \msol. We chose the relations of
\citet{2002ApJ...574..740T} and \citet{2007MNRAS.379..711G} to
estimate \mbh, and find a range of $0.6 \dash 7.8 \times 10^9 ~\msol$,
from which we adopted the weighted mean value $1.5^{+6.3}_{-0.9}
\times 10^9 ~\msol$. The errors on \mbh\ were chosen to span the
lowest and highest $1\sigma$ values of the individual estimates. For
$\epsilon = 0.1$ and $\kbon = \kna$, the relevant accretion rates are
$\dmbon \approx 4 \times 10^{-4} ~\msolpy$ and $\dmedd \approx 33
~\msolpy$. The Eddington and Bondi accretion ratios for the outburst
event were thus $\dme \equiv \dmacc/\dmedd \approx 0.15$ and $\dmb
\equiv \dmacc/\dmbon \approx 17000$.

The large value of \dmb\ is troublesome since it implies all the gas
which reached the Bondi radius ($\rbon \approx 10$ pc) was
accreted. But, \dmb\ may be overestimated if $\kbon < \kna$ and
\mbh\ is larger than our adopted value. If $\mbh = 8 \times 10^9
~\msol$ and gas near \rbon\ has a mean temperature of 0.1 keV, for
\dmb\ to approach unity, \kbon\ must be $< 0.3 ~\ent$, corresponding
to $\nelec \sim 0.2 ~\pcc$. This density is twice the observed central
density, and a sphere $\approx 5$ kpc in radius is required for $>
10^8 ~\msol$ to be available for accretion. But this implies the
inner-core of the cluster is fully consumed in less than 100 Myr, much
shorter than the cooling time of gas outside 5 kpc, thereby
short-circuiting the feedback loop. While Bondi accretion cannot be
ruled out because the cluster is observed post-outburst and the core
conditions may have changed dramatically since, a number of
observationally unsupported concessions must be made for Bondi
accretion to be viable.

The nuclear BCG X-ray source may also reveal valuable information
about on-going accretion. A spectrum for this source was extracted
from the region enclosing 90\% of the \cxo\ point-spread function, and
a background spectrum was taken from an annulus immediately outside
this region with 5 times the area. The background-subtracted spectrum
is inconsistent with thermal emission and was instead modeled using an
absorbed power law with two Gaussians to account for features which
may be blends of photoionized lines. The best-fit models are given in
Table \ref{tab:agn} and the spectrum is shown in Figure
\ref{fig:nucspec}. The model with a power-law distribution of $\nhobs
\sim 10^{22} ~\pcmsq$ absorbers is preferred, indicating a lack of
significant obscuration.

If mass accretion is powering the nuclear X-ray emission, the
accretion rate required is $\dmacc \approx \lbol/(0.1 c^2) \approx
0.04 ~\msolpy \approx 0.001 \dme$. The accretion disk model of
\citet{2002NewAR..46..247M} predicts an optical luminosity of $\ldisk
\approx 8 \times 10^{44} ~\lum$ for this \dmacc, but no $L > 10^{44}
~\lum$ sources are found in the \hst\ imaging. Rather, extrapolation
of the best-fit spectral model to radio frequencies showed good
agreement with the measured 1.4 GHz and 4.8 GHz nuclear radio fluxes,
and the continuous injection synchrotron model of
\citet{1987MNRAS.225..335H} produced an acceptable fit to the X-ray,
1.4 GHz, and 4.8 GHz nuclear fluxes. These latter results suggest the
nuclear emission may be from a synchrotron source, \eg\ unresolved
jets, and not the remnants of a very dense, hot gas phase which would
be associated with Bondi accretion.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Black Hole Spin}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Powering the \rbs\ outburst by mass accretion alone appears to be
inconsistent with the properties of the ICM and BCG. However, if the
SMBH in the BCG was rapidly spinning prior to the outburst, the stored
SMBH angular momentum might be sufficient to power the
outburst. Assuming the magnetic field stabilizing the accretion disk,
and connecting it with the SMBH, is sufficiently strong (discussed
below), a modest mass accretion rate, \eg\ $\ll 5 ~\msolpy$, is
capable of applying the necessary torque to extract energy from the
SMBH \citep{1999ApJ...522..753M}. This is in stark contrast to the
high accretion rates needed for mass accretion alone. In the model of
\citet{1999ApJ...522..753M}, the energy of a spinning SMBH is
\begin{equation}
  E_{\rm{spin}} = 1.6 \times 10^{62} ~{\erg} ~j^2
  \left(\frac{\mbh}{10^9 ~\msol}\right)
\end{equation}
where $j$ is a dimensionless spin parameter between -1 and 1. If all
the spin energy of the \rbs\ SMBH was extracted in the outburst, an
outburst energy of $\approx 6.8 \times 10^{61}$ erg requires a $\mbh =
1.5 \times 10^{9} ~\msol$ have at least $\|j\| \approx 0.53$.

In the model of \citet[][GES hereafter]{gesspin}, this spin energy is
paritally released in the form of relativistic jets produced via a
combination of the Blandford-Znajek \citep[BZ;][]{bz} and
Blandford-Payne \citep[BP;][]{1982MNRAS.199..883B} mechanisms. The GES
model predicts energy will be extracted at a rate of
\begin{equation}
  P_{\rm{jet}} = 2 \times 10^{47} ~{\lum} ~\alpha(j) ~\beta^2(j) ~j^2
  B_{d,5}^2 \left(\frac{\mbh}{10^9 ~\msol}\right)^2
  \label{eqn:ges}
\end{equation}
where $j$ has values between -1 and 1, $\alpha(j)$ and $\beta(j)$ are
$j$-dependent functions capturing the BZ and BP powers
\citep[see][]{2009ApJ...699L..52G}, and $B_{d,5}$ is the strength of
the magnetic field threading the accretion disk with units $10^5$
G. The GES model has the appealing feature that the most powerful jets
are produced for a SMBH which is spinning retrograde relative to the
direction of the accreting material, easing the demands on the
magnitude of the highly uncertain $B_{d,5}$ parameter. A constraint on
$B_{d,5}$ was found by plugging $\pm j=0.53$ and $\pjet = 2.7 \times
10^{46} ~\lum$ into Equation \ref{eqn:ges}. We find $B_{d,5}(-j)
\approx 1300$ G and $B_{d,5}(+j) \approx 6400$ G, reasonable values
for a SMBH-accretion disk system
\citep[\eg][]{2002Sci...295.1688K}.

There are clearly uncertainties associated with these estimates, and
the spin power mechanism is wrought with its own difficulties
\citep[see][for thorough discussion]{msspin}. However, no highly
efficient or optimistic scenarios need to play out for SMBH spin to
achieve the extreme energies and jet powers demanded by \rbs. In
addition, the SMBH of \rbs\ does not need to be maximally spinning nor
does the accretion rate need to be excessively large to maintain the
magnetic field strengths which are implied.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{BCG Star Formation and Interaction with the AGN}
\label{sec:bcg}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

An estimate of the \rbs\ SFR is relevant given the general
relationship with the process of SMBH growth via mass accretion. The
SFRs below are likely upper limits since 1) the extremely blue
\galex\ and extremely red 2MASS colors signal the presence of an AGN
\citep[\eg][]{2005AJ....130.1022A}, and 2) sources of significant SFR
uncertainties have been neglected \citep[\eg][]{1992ApJ...388..310K,
  2004AJ....127.2002K, hicksuv, 2010MNRAS.tmp..626G}. Using the
relations of \citet{kennicutt2}, \citet{2006ApJ...642..775M}, and
\citet{salim2007}, the \rbs\ SFR may lie in the range 1--10
~\msolpy\ (see Table \ref{tab:sfr}). Though the shallow 4000
\AA\ break and optical emission line ratios of the BTA spectrum
indicate it arises from a star forming source, the large uncertainties
and unknown slit position mask its strength and location. Further, the
radially-averaged \hst\ $\myv-\myi$ color profile does not have a blue
gradient, suggesting if there is star formation, it may be confined to
compact regions like the optical substructure seen in the
\hst\ images.

To better reveal the BCG substructure, residual galaxy images were
constructed by first fitting the \hst\ \myv\ and \myi\ isophotes with
ellipses using the \iraf\ tool {\textsc{ellipse}}. Stars and other
contaminating sources were rejected using a combination of $3\sigma$
clipping and by-eye masking. The ellipse centers were fixed at the
galaxy centroid, and ellipticity and position angle were fixed at
$0.25 \pm 0.02$ and $-64\mydeg \pm 2\mydeg$, respectively -- the mean
values when they were free parameters. Galaxy light models were
created using {\textsc{bmodel}} in \iraf\ and subtracted from the
corresponding parent image, leaving the residual images shown in
Figure \ref{fig:subopt}. A color map was also generated by subtracting
the fluxed \myi\ image from the fluxed \myv\ image.

The close alignment of the optical substructure with the nuclear AGN
outflow clearly indicates the jets are interacting with the BCG
halo. There also appears to be an in-falling galaxy to the northwest
of the nucleus, possibly with a stripped tail \citep[see][for an
  example]{2007ApJ...671..190S}. The numbered regions overlaid on the
residual \myv\ image are the areas of the color map which have the
largest color difference with surrounding galaxy light. Regions 1--5
are relatively the bluest with $m_{\myv-\myi} = -0.40, -0.30, -0.25,
-0.22, ~\rm{and} -0.20$, respectively. Without spectroscopy, it is
unclear which, if any, of the regions host significant star formation
or strong line emission. Regions 6--8 are relatively the reddest with
$m_{\myv-\myi} =$ +0.10, +0.15, and +0.18, respectively. Again,
without spectroscopy, we can only speculate that these may be emission
line regions (\eg\ \halpha) or regions reddened by dust extinction.

In the residual \myi\ image, regions 9--11 denote what appear to be
8--10 kpc long ``whiskers'' of emission radiating out from the
BCG. The low-entropy state of the cluster core is conducive to the
formation of such structures \citep{conduction}, and the whiskers may
be optical filaments similar to those seen around other BCGs
\citep[\eg][]{2003MNRAS.344L..48F}. It is interesting that regions 1
and 4 reside at the point where the southern jet appears to be
encountering whiskers 9 and 10. It may be that the jet has entrained
and compressed gas in the whiskers to the point of forming stars. If
the AGN is driving star formation, then the estimated SFRs may be
boosted above the putative rate, and thus are not representative of
prior episodes of gas fragmentation in the BCG. If this is the case,
then the discrepancy discussed in Section \ref{sec:accretion} between
the mass accreted by the SMBH and the mass which went into stars,
increases, making cold gas accretion an even less likely scenario for
fueling the AGN.

%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{sec:con}
%%%%%%%%%%%%%%%%%%%%%

We have presented results from a study of the AGN outburst in the
galaxy cluster \rbs. \cxo\ observations have enabled us to constrain
the energetics of the AGN outburst and analyze different mechanisms
which may have powered it. We have shown the following:
\begin{enumerate}
\item \rbs\ is a cool core object with a central cooling time $< 0.5$
  Gyr, core entropy $< 30 ~\ent$, and bolometric cooling luminosity of
  $\sim 10^{45} ~\lum$.
\item The two central cavities have decrements consistent with voids
  that cross the plane of the sky, and residual X-ray images reveal
  additional surface brightness depressions likely associated with AGN
  activity. We have placed constraints on the AGN outburst energetics
  by considering two limiting cases: small cavities with centers in
  the plane of the sky, and large overlapping cavities along the line
  of sight. The total energy in the cavities is $3-70 \times 10^{60}$
  erg, with powers $3-40 \times 10^{45} ~\lum$. If the upper limits
  are accurate, the AGN outburst has released enough energy to
  suppress cooling of the cluster halo.
\item The energetics demand that cold-mode and hot-mode gas accretion
  operate with unrealistic efficiency if mass accretion alone powered
  the outburst. We specifically show that Bondi accretion is an
  unattractive solution, and instead suggest that the outburst was
  powered by tapping the energy stored in a rapidly rotating SMBH. We
  show that the model of \citet{gesspin} can readily achieve our
  \ecav\ and \pcav\ limits.
\item The optical substructure of the BCG clearly indicates
  interaction of the AGN outflow with the galaxy halo. We are unable
  to determine if any regions of interest host star formation or line
  emission. But, the convergence of what appear to be optical
  filaments, bluish knots of emission, and the tip of one jet suggest
  there may be AGN driven star formation.
\end{enumerate}

%%%%%%%%%%%%%%%%%
\acknowledgements
%%%%%%%%%%%%%%%%%

KWC and BRM were supported by CXO grant G07-8122X and a generous grant
from the Natural Science and Engineering Research Council of
Canada. KWC also acknowledges financial support from the Agence
Nationale de la Recherche through grant ANR-09-JCJC-0001-01. KWC
thanks David Gilbanks, Sabine Schindlesr, Axel Schwope, and Chris
Z. Waters for helpful input.

%%%%%%%%%%%%%%
% Facilities %
%%%%%%%%%%%%%%

{\it Facilities:} \facility{CXO (ACIS)} \facility{HST (WFPC2)}
\facility{GALEX} \facility{BTA (SP124)}

%%%%%%%%%%%%%%%%
% Bibliography %
%%%%%%%%%%%%%%%%

\bibliography{cavagnolo}

%%%%%%%%%%%%%%%%%%%%%%
% Figures and Tables %
%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\input{cavities.tex}
\input{agn.tex}
\input{sfr.tex}
\input{figs.tex}

%%%%%%%%%%%%%%%%%%%%
% End the document %
%%%%%%%%%%%%%%%%%%%%

\end{document}

%% Conservation of angular momentum suggests that gas condensing into
%% the very center of a BCG has a preferred direction of rotation,
%% possibly aligned with the semi-major axis of the cluster. The
%% prevalence of systems like \rbs, \ms, and Hercules A is unclear,
%% but their numbers thus far are small, possibly because their BCGs,
%% for whatever reason, formed SMBHs that at some point in the past
%% spun retrograde relative to the preferred rotation direction of the
%% cluster. In which case, if the GES model is assumed, they would
%% undergo a very powerful AGN outburst which releases $\ga 10^{61}$
%% erg of spin energy. If the circumstances which result in retrograde
%% SMBHs are rare, then this naturally explains why not many such
%% systems have been found.
