%%%%%%%%%%%%%%%%%%%
% Custom commands %
%%%%%%%%%%%%%%%%%%%

\newcommand{\dmb}{\ensuremath{\dot{m_{\rm{B}}}}}
\newcommand{\dme}{\ensuremath{\dot{m_{\rm{E}}}}}
\newcommand{\ldisk}{\ensuremath{L_{\rm{disk}}}}
\newcommand{\ms}{MS 0735.6+7421}
%\newcommand{\myi}{\ensuremath{I^{\prime}}}
%\newcommand{\myv}{\ensuremath{V^{\prime}}}
\newcommand{\myi}{\ensuremath{I}}
\newcommand{\myv}{\ensuremath{V}}
\newcommand{\rbs}{RBS 797}
\newcommand{\reff}{\ensuremath{r_{\rm{eff}}}}
\newcommand{\rlos}{\ensuremath{r_{\rm{los}}}}
\newcommand{\mykeywords}{}
\newcommand{\mystitle}{\rbs\ AGN Outburst}
\newcommand{\mytitle}{A Powerful, Line-of-Sight AGN Outburst in RBS
  797}

%%%%%%%%%%
% Header %
%%%%%%%%%%

%\documentclass[11pt, preprint]{aastex}
%\usepackage{graphicx,common}
%\documentclass[iop]{emulateapj-rtx4}
\documentclass[iop]{emulateapj}
\usepackage{apjfonts,common,graphicx,longtable}
\usepackage[pagebackref,
  pdftitle={\mytitle},
  pdfauthor={K. W. Cavagnolo},
  pdfsubject={Astrophysical Journal},
  pdfkeywords={\mykeywords},
  pdfproducer={ps2pdf},
  pdfcreator={LaTeX with hyperref}
  pdfdisplaydoctitle=true,
  colorlinks=true,
  citecolor=blue,
  linkcolor=blue,
  urlcolor=blue]{hyperref}
\bibliographystyle{apj}
\begin{document}
\title{\mytitle}
\shorttitle{\mystitle}
\author{
  K. W. Cavagnolo\altaffilmark{1,2,9},
  B. R. McNamara\altaffilmark{1,3,4},
  M. W. Wise\altaffilmark{5}, \\
  M. Br\"uggen\altaffilmark{6}, 
  P. E. J. Nulsen\altaffilmark{4},
  M. Gitti\altaffilmark{4,7}, and
  D. A. Rafferty\altaffilmark{8}
}
\shortauthors{Cavagnolo et al.}

\altaffiltext{1}{University of Waterloo, 200 University Ave. W.,
  Waterloo, ON, N2L 3G1, Canada.}
\altaffiltext{2}{UNS, CNRS UMR 6202 Cassiop\'{e}e, Observatoire de la
  C\^{o}te d'Azur, Nice, France.}
\altaffiltext{3}{Perimeter Institute for Theoretical Physics, 31
  Caroline St. N., Waterloo, ON, N2L 2Y5, Canada.}
\altaffiltext{4}{Harvard-Smithsonian Center for Astrophysics, 60
  Garden St., Cambridge, MA, 02138-1516, United States.}
\altaffiltext{5}{Astronomical Institute Anton Pannekoek, P.O. Box
  94249, 1090 GE Amsterdam, The Netherlands.}
\altaffiltext{6}{Jacobs University Bremen, P.O. Box 750561, 28725
  Bremen, Germany.}
\altaffiltext{7}{INAF-Astronomical Observatory of Bologna, Via
  Ranzani 1, I-40127 Bologna, Italy.}
\altaffiltext{8}{Leiden Observatory, University of Leiden, P.O. 9513,
  2300 RA Leiden, The Netherlands.}
\altaffiltext{9}{cavagnolo@oca.eu}

%%%%%%%%%%%%
% Abstract %
%%%%%%%%%%%%

\begin{abstract}
  Utilizing a $\sim 40$ ks observation from the Chandra X-ray
  Observatory, we present spatially resolved analysis of the
  intracluster medium, cavities, and the nuclear point source of RBS
  797.
\end{abstract}

%%%%%%%%%%%%
% Keywords %
%%%%%%%%%%%%

\keywords{\mykeywords}

%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%

Evidence has amassed over the last decade that the growth of galaxies
and supermassive black holes (SMBHs) are coupled, and that energetic
feedback from active galactic nuclei (AGN) strongly influences galaxy
evolution \citep[\eg][]{1995ARA&A..33..581K, magorrian,
  1998A&A...331L...1S, 2000MNRAS.311..576K, 2000ApJ...539L...9F,
  2000ApJ...539L..13G, 2002ApJ...574..740T}. The discovery of AGN
induced cavities in the hot halos surrounding many massive galaxies
has strengthened this theory \citep[see][for a review]{mcnamrev},
revealing that AGN mechanical heating is capable of regulating the
radiative cooling responsible for late-time galaxy growth
\citep[\eg][]{birzan04, dunn06, rafferty06}. Current models of this
late-time ``feedback loop'' posit that cooling processes in a galaxy's
halo result in mass accretion onto a central SMBH, thereby driving AGN
activity and ultimately heating the cooling halo
\citep[\eg][]{croton06, bower06, sijacki07}. While there is direct
evidence that halo cooling and feedback are linked
\citep[\eg][]{haradent, rafferty08}, the observational constraints on
how AGN are fueled and powered remain loose. For example, what
fraction of the energy released in an AGN outburst is attributable to
the gravitational binding energy of accreting matter \citep[see][for a
  review]{1984RvMP...56..255B} and a SMBH's rotational energy
\citep[see][for a review]{2002NewAR..46..247M} is still unclear.

Mass accretion alone can, in principle, fuel most AGN
\citep[\eg][]{pizzolato05, 2006MNRAS.372...21A}, and is typically not
at odds with the gas masses and stellar masses of the host galaxy
\citep[\eg][]{rafferty06}. However, there are systems which are
gas-poor and host very powerful AGN where mass accretion alone does
not appear to be capable of sustaining the outburst. In the galaxy
clusters Hercules A, Hydra A, and \ms, for example, an AGN in each
cluster's brightest cluster galaxy (BCG) has deposited more than
$10^{61}$ erg of energy into the surrounding intracluster medium (ICM)
at rates of order $10^{45} ~\lum$ \citep{herca, hydraa, ms0735}. The
importance of these systems in understanding AGN feedback is that
either the AGN fueling has been astoundingly efficient, or the power
has come from an alternate source, such as the release of angular
momentum stored in a rapidly spinning SMBH \citep[\eg][]{msspin,
  minaspin}. SMBH spin is an intriguing energy source because
releasing the energy requires some mass accretion (maintaining the
feedback loop) and a typical BCG SMBH can store more than $10^{62}$
erg of energy if it is rapidly spinning. If more systems can be found
which are best explained as being powered by SMBH spin, then it may be
necessary to incorporate this feedback pathway into galaxy formation
models \citep[\eg][]{2003ApJ...585L.101H, 2007ApJ...658..815S,
  2009MNRAS.397.1302B, gesspin}. In this paper, we present analysis of
the AGN outburst in the galaxy cluster \rbs\ and, because of the
extreme energetic demands of the outburst, suggest it may have been
powered by black hole spin.

The discovery of prominent cavities in the ICM of \rbs\ was first
reported by \citet{schindler01} using data from the Chandra X-ray
Observatory (\cxo). Subsequent multifrequency radio observations
showed that the cavities are co-spatial with extended radio emission
centered on a strong, jetted radio source coincident with the
\rbs\ BCG \citep{2002astro.ph..1349D, gitti06, birzan08}. The
observations implicate an AGN in the BCG as the cavities' progenitor,
and the cavity analysis presented in \citet[][hereafter B04]{birzan04}
shows that the AGN deposited $\sim 10^{60}$ erg of energy into the ICM
at a rate of $\sim 10^{45} ~\lum$, relatively large values for an AGN
outburst. The analysis of B04 assumed that the observed cavities are
distinct, symmetric about the plane of the sky, and that their centers
lie in a plane passing through the central AGN and perpendicular to
our line-of-sight (configuration-1 in Figure
\ref{fig:config}). However, the depth of the cavities and the nebulous
correlation between the radio and X-ray morphologies calls into
question these assumptions.

In this paper, we utilize a longer, follow-up \cxo\ observation of
\rbs\ to suggest that the observed surface brightness decrements
result from the superposition of large, overlapping cavities
positioned nearly along the line-of-sight (configuration-2 in Figure
\ref{fig:config}). Thus, our estimates of the cavity energy, \ecav,
and the jet powers which formed the cavities, \pjet, are 10 times
larger than the B04 values -- of the order $10^{61}$ erg and $10^{46}
~\lum$, respectively. We find that mass accretion alone is an
implausible explanation for how the outburst was powered, and instead
suggest that the outburst resulted from the extraction of rotational
energy stored in a rapidly-spinning SMBH. \rbs\ may be further
observational evidence that some AGN are powered by the release of
SMBH spin energy.

Reduction of X-ray and radio data is discussed in Section
\ref{sec:obs}. Interpretation of observational results are given
throughout Section \ref{sec:results}, and a brief summary concludes
the paper in Section \ref{sec:con}. \LCDM. At a redshift of $z =
0.354$, the look-back time is 3.9 Gyr, $\da = 4.996$ kpc
arcsec$^{-1}$, and $\dl = 1889$ Mpc. All errors are 68\% confidence
unless stated otherwise.

%%%%%%%%%%%%%%%%%%%%%%
\section{Observations}
\label{sec:obs}
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%
\subsection{X-ray Data}
\label{sec:xray}
%%%%%%%%%%%%%%%%%%%%%%%

\rbs\ was observed with \cxo\ in October 2000 for 11.4 ks using the
ACIS-I array (\dataset [ADS/Sa.CXO#Obs/02202] {ObsID 2202}) and in
July 2007 for 38.3 ks using the ACIS-S array (\dataset
[ADS/Sa.CXO#Obs/07902] {ObsID 7902}). Datasets were reduced using
\ciao\ and \caldb\ versions 4.2. Events were screened of cosmic rays
using \asca\ grades and {\textsc{vfaint}} filtering. The level-1
events files were reprocessed to apply the most up-to-date corrections
for the time-dependent gain change, charge transfer inefficiency, and
degraded quantum efficiency of the ACIS detector. The afterglow and
dead area corrections were also applied. Time intervals affected by
background flares exceeding 20\% of the mean background count rate
were isolated and removed using light curve filtering. The final,
combined exposure time is 48.8 ks. Point sources were identified and
removed via visual inspection and use of the \ciao\ tool
{\textsc{wavdetect}}. We refer to the \cxo\ data free of point sources
and flares as the ``clean'' data. A mosaiced, fluxed image (see Figure
\ref{fig:img}) was generated by exposure correcting each clean dataset
and reprojecting the normalized images to a common tangent point.

%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Radio Data}
\label{sec:radio}
%%%%%%%%%%%%%%%%%%%%%%%

Very Large Array (\vla) radio images at 325 MHz (A-array), 1.4 GHz (A-
and B-array), 4.8 GHz (A-array), and 8.4 GHz (D-array) are presented
in \citet{gitti06} and \citet{birzan08}. Our re-analysis of the
archival \vla\ radio observations yielded no significant differences
with these prior studies. Using the rms noise ($\sigma_{\rm{rms}}$)
values given in \citet{gitti06} and \citet{birzan08} for each
observation, emission contours between $3\sigma_{\rm{rms}}$ and the
peak image intensity were generated. These are the contours referenced
and shown in all subsequent discussion and figures.

%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{sec:results}
%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cavity Morphologies and ICM Substructure}
\label{sec:morph}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Shown in Figure \ref{fig:img} is the 0.7--2.0 keV \cxo\ mosaiced clean
image and an \hst\ optical image of the \rbs\ BCG. Outside of $\approx
50$ kpc, the global ICM morphology is regular and elliptical in shape,
with the appearance of being skewed along the NW-SE direction. The
cavities discovered by \citet{schindler01} are clearly seen in the
cluster core east and west of the nuclear X-ray source and appear to
be enclosed by a bright, elliptical ridge of emission. The western
cavity has more internal structure, and its boundaries are less
well-defined, than the eastern cavity. The emission from the innermost
region of the core is elongated N-S and has a distinct `S'-shape
punctuated by a hard nuclear X-ray source. Comparison of the
\hst\ optical and \cxo\ X-ray images reveals the BCG coincides with
the nuclear X-ray source and has the appearance of being pinched into
two equal brightness halves. It is unclear which, if either, is at the
center of the galaxy or might be associated with an AGN. There is
substantial structure to the BCG optical halo, and its association
with the AGN is discussed in Section \ref{sec:bcg}.

Multifrequency radio images overlaid with ICM X-ray contours are shown
in Figure \ref{fig:composite}. \rbs\ radio properties are discussed in
\citet{gitti06}, and we summarize here. As seen in projection, the
nuclear 4.8 GHz jets are almost orthogonal to the axis connecting the
cavities. The 325 MHz, 1.4 GHz, and 8.4 GHz radio emission are diffuse
and extend well-beyond the cavities, more similar to the morphology of
a radio mini-halo than relativistic plasma confined to the cavities
(Doria et al., in preparation). Of all the radio frequencies, the 1.4
GHz emission most closely traces the cavity morphologies, yet it is
still very diffuse and uniform over the cavities with little structure
outside the radio core. Typically, the connection between a cavity
system, coincident radio emission, and the progenitor AGN is
unambiguous. This is not the case for \rbs, which suggests the cavity
morphologies may be complex or that projection effects are
important.

To better reveal the cavity morphologies, residual X-ray images of
\rbs\ were constructed by modeling the ICM emission and subtracting it
off. The X-ray isophotes of two exposure-corrected images -- one
smoothed by a $1\arcs$ Gaussian and another by a $3\arcs$ Gaussian --
were fitted with ellipses using the \iraf\ task \textsc{ellipse}. The
ellipse centers were fixed at the location of the BCG X-ray point
source, and the eccentricities and position angles were free to
vary. A 2D surface brightness model was created from each fit using
the \iraf\ task \textsc{bmodel}, normalized to the parent X-ray image,
and then subtracted off. The residual images are shown in Figure
\ref{fig:subxray}.

In addition to the central east and west cavities (labeled E1 and W1),
depressions north and south of the nucleus (labeled N1 and S1) are
revealed. N1 and S1 lie along the 4.8 GHz jet axis and are coincident
with spurs of significant 1.4 GHz emission, indicating they may be
related to activity of the central AGN. A depression coincident with
the southeastern concentration of 325 MHz emission is also found
(labeled E2), but no counterpart on the opposing side of the cluster
is seen (labeled W2). There is an X-ray edge which extends southeast
from E2 and sits along a ridge of 325 MHz and 8.4 GHz emission. No
substructure associated with the western-most knot of 325 MHz emission
is found, but there is a stellar object co-spatial with this region.
The X-ray and radio properties of the object are consistent with those
of a galactic RS CVn star \citep{1993RPPh...56.1145S} -- if the star
is less than 1 kpc away, $\lx \la 10^{31} ~\lum$ and $L_{325} \sim
10^{27} ~\lum$ -- suggesting the western 325 MHz emission may not be
associated with the cluster. In Section \ref{sec:cavities} we focus on
disentangling the radio-X-ray relationship to better understand the
AGN outburst energetics.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Radial ICM Properties}
\label{sec:icm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In order to analyze the \rbs\ cavity system and AGN outburst
energetics in-detail, the radial ICM density, temperature, and
pressure structure need to be quantified. All of the profiles
discussed below are shown in Figure \ref{fig:gallery}. A temperature
(\tx) profile was created by extracting spectra from concentric
circular annuli (2500 source counts per annulus) centered on the
cluster X-ray peak, binning the spectra to 25 counts per energy
channel, and then fitting each spectrum in \xspec\ 12.4 \citep{xspec}
with an absorbed, single-component \mekal\ model \citep{mekal1} over
the energy range 0.7--7.0 \keV. For each annulus, weighted responses
were created and a background spectrum was extracted from the ObsID
matched \caldb\ blank-sky dataset normalized using the ratio of 9--12
keV count rates for an identical off-axis, source-free region of the
blank-sky and target datasets. A spectral model for the Galactic
foreground was included as an additional, fixed background component
during spectral fitting \citep[see][for method]{2005ApJ...628..655V,
  xrayband}, and the absorbing Galactic column density was fixed to
$\nhgal = 2.28 \times 10^{20} ~\pcmsq$ \citep{lab}. Gas metal
abundance was free to vary and normalized to the \citet{ag89} solar
ratios. Spectral deprojection using the {\textsc{proj}} \xspec\ model
did not produce significantly different results, thus only projected
quantities are discussed.

A 0.7--2.0 keV surface brightness profile was extracted from the
\cxo\ mosaiced clean image using concentric $1\arcs$ wide elliptical
annuli centered on the BCG X-ray point source (central $\approx
1\arcs$ and cavities excluded). A deprojected electron density
(\nelec) profile was derived from the surface brightness profile using
the method of \citet{kriss83} which incorporates the 0.7--2.0 keV
count rates and best-fit normalizations from the spectral analysis
\citep[see][for details]{accept}. Errors for the density profile were
estimated using 5000 Monte Carlo simulations of the original surface
brightness profile. A total gas pressure profile was calculated as $P
= n \tx$ where $n \approx 2.3 \nH$ and $\nH \approx
\nelec/1.2$. Profiles of enclosed X-ray luminosity, entropy ($K = \tx
\nelec^{-2/3}$) and cooling time ($\tcool = 3 n \tx~(2 \nelec \nH
\Lambda)^{-1}$, where $\Lambda$ is the cooling function), were also
generated. Errors for each profile were determined by summing the
individual parameter uncertainties in quadrature.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{ICM Cavities}
\label{sec:cavities}
%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Plane of the Sky Cavities}
\label{sec:ecav}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Of all the ICM substructure, the E1 and W1 cavities are unambiguous
detections, and their energetics were determined following standard
methods (see B04). Our fiducial cavity configuration assumes the
cavities are symmetric about the plane of the sky, and the cavity
centers lie in a plane which is perpendicular to our line-of-sight and
passes through the central AGN (configuration-1 in Figure
\ref{fig:config}). Hereafter, we denote the line-of-sight distance of
a cavity's center from this plane as $z$, and the cavity radius along
the line-of-sight as \rlos. The volume of a cavity is thus $V = 4\pi a
b \rlos/3$ where $a$ and $b$ are the projected semi-major and -minor
axes, respectively, of the by-eye determined ellipses in Figure
\ref{fig:subxray}. For simplicity, the cavities were assumed to be
roughly spherical and \rlos\ was set equal to the projected effective
radius, $\reff = \sqrt{ab}$. For configuration-1, the distance of each
cavity from the central AGN, $D$, is simply the projected distance
from the ellipse centers to the BCG X-ray point source. A systematic
error of 10\% is assigned to the cavity volumes. Cavity ages were
estimated using the three time scales discussed in B04: ICM sound
speed age (\tsonic), buoyant rise time age (\tbuoy), and volume
refilling age (\trefill). The energy in each cavity, $\ecav = \gamma
PV/(\gamma-1)$, was calculated assuming the contents are a
relativistic plasma ($\gamma = 4/3$), and that the mean internal
cavity pressure is equal to the ICM pressure at the cavity
mid-point. We assume the cavities are detached, buoyant structures and
that the time-averaged energy needed to create each cavity is $\pcav =
\ecav/\tbuoy$. The individual cavity properties are listed in Table
\ref{tab:cavities} and the aggregate properties are in Table
\ref{tab:totals}.

For configuration-1, we measure a total cavity energy $\ecav = 2.85
~(\pm 1.02) \times 10^{60}$ erg and total power $\pcav = 2.85 ~(\pm
1.21) \times 10^{45} ~\lum$. These values are larger than those of B04
($\ecav = 1.52 \times 10^{60}$ erg, $\pcav = 1.13 \times 10^{44}
~\lum$) by a factor of $\approx 2$ as a result of our larger E1 and W1
volumes. Using the B04 cavity volumes in place of our own produces no
significant differences between our energetics calculations and those
of B04. The largest uncertainties in the energetic calculations are
the cavity volumes and 3D locations in the ICM, issues we consider
next.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Cavity Decrements}
\label{sec:dec}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A cavity's morphology and location in the ICM dictates the X-ray
surface brightness decrement it induces. If the surface brightness of
the undisturbed ICM can be estimated, then the decrement is useful for
constraining the cavity line-of-sight size and its distance from the
launch point \citep[\ie\ \rlos\ and $z$, respectively; see][for
  details]{hydraa}. We define decrement, $y$, as the ratio of the
X-ray surface brightness inside the cavities to the value of the
best-fit ICM surface brightness $\beta$-model at the same
radius. Consistent with the analysis of \citet{schindler01}, we find
the best-fit $\beta$-model has parameters $S_0 = 1.65 ~(\pm 0.15)
\times 10^{-3}$ \sbr, $\beta = 0.62 \pm 0.04$, and $r_{\rm{core}} =
7.98\arcs \pm 0.08$ for \chisq(DOF) = 79(97). Using a circular
aperture with radius $1\arcs$ centered on the deepest part of each
cavity, we measure mean decrements of $\bar{y}_{\rm{W1}} = 0.50 \pm
0.18$ and $\bar{y}_{\rm{E1}} = 0.52 \pm 0.23$, with minima of
$y^{\rm{min}}_{\rm{W1}} = 0.44$ and $y^{\rm{min}}_{\rm{E1}} = 0.47$.

Cavities this deep are uncommon, with most other cavity systems having
minima greater than 0.6 (B04). The extreme decrements raise the
concern that the $\beta$-model fit has been influenced by the rim-like
structures surrounding E1-W1 (see Section \ref{sec:icm}) and produced
artificially low decrements. In addition to excluding the cavities, we
tried excluding the rims during $\beta$-model fitting, but this did
not provide insight as too much of the surface brightness profile was
removed and the fit did not converge. Extrapolating the surface
brightness profile at larger radii inward resulted in even lower
decrements. With no suitable alternative, we assume the $\beta$-model
is the best representation of the undisturbed ICM.

To check if cavity configuration-1 can produce the measured
decrements, the best-fit $\beta$-model was integrated over each cavity
with a column of gas equal to $2\rlos$ excluded. The integration
revealed decrements $< 0.67$ cannot be achieved for configuration-1,
indicating our initial assumption that $\rlos = \reff$ is poor. The
measured decrements can be reproduced when $z = 0$ and $\rlos = 21.1$
kpc for E1 and $\rlos = 25.3$ kpc for W1 (listed as configuration-1a
in Tables \ref{tab:cavities} and \ref{tab:totals}). These radii
suggest that the cavities are two times larger along the line-of-sight
than in the plane of the sky. If the radio lobes are inflating
perpendicular to our line-of-sight, then how the cavities achieved a
highly flattened morphology so close to the launch point is unclear
since compression and shredding are expected to occur at greater than
one cavity scale-height \citep[$D \ga 2r$;
  \eg][]{2001MNRAS.325..676B}. Since the $\beta$-model is symmetric
about the plane of the sky, a decrement less than 0.5 requires that
gas on both sides of this plane be displaced. Thus, cavity
configuration-3 in Figure \ref{fig:config}, where an elongated radio
lobe inflating parallel to the line-of-sight is viewed along its axis,
is unlikely.

Alternatively, if our sight-lines cut through a pair of lobes inflating
along the line-of-sight, as shown in configuration-2 of Figure
\ref{fig:config}, then deep decrements could be achieved. In addition,
if the cavity cross-sections overlap in the plane of the sky, the
superposition of radio emission from each cavity may wipe-out
otherwise clear correlations between the X-ray and radio morphologies,
yielding an ambiguous relationship like we see in \rbs. The cavity
morphologies are also reminiscent of those seen in simulations where
the launch axis is highly-inclined relative to the plane of the sky
\citep[\eg][]{2009MNRAS.395.2210B}, and the overlapping bubbles found
in some planetary nebulae \citep{1999AJ....118..468S}, for example the
Hourglass Nebula shown in Figure \ref{fig:proj}. The line-of-sight
case is interesting because the cavity volumes may be severely
underestimated, and thus so will the estimated AGN energy
output. Cavity configuration-2 is considered in-detail below.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Line-of-Sight Cavities}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Shown in Figure \ref{fig:proj} is a proposed configuration for a pair
of large cavities (O1 and O2) lying along the line-of-sight whose
projected cross-sections overlap. The elliptical regions were chosen
such that they coincide with most of the X-ray substructure and
enclose most of the radio emission. For this cavity configuration, a
variety of \rlos\ and $z$ can reproduce the measured decrements. Thus,
we selected a simple morphology and again set $\rlos = \reff$. Taking
into consideration that each cavity will account for $\approx 50\%$ of
the total decrement, the $\beta$-model integration indicates
$z_{\rm{E1}} = 66^{+13}_{-9}$ and $z_{\rm{W1}} = 65^{+12}_{-9}$. The
centers of the cavities are then a distance $D \approx \sqrt{d^2+z^2}$
from the central AGN, where $d$ is the projected distance from the
ellipse centers to the BCG X-ray point source. The energetics
calculations of Section \ref{sec:ecav} were repeated for O1 and O2 and
are given in Tables \ref{tab:cavities} and \ref{tab:totals}.

The energetics for the line-of-sight cavity configuration are beyond
extreme -- total cavity energy of $6.77 ~(\pm 2.98) \times 10^{61}$
erg and cavity power of $2.69 ~(\pm 1.33) \times 10^{46} ~\lum$ -- and
are likely upper limits given the uncertainties of the cavity
morphologies and decrement estimates. But, they do indicate the
\rbs\ outburst may be a sibling of other powerful $\sim 10^{46} ~\lum$
outbursts like Cygnus A, Hercules A, and \ms. The mechanical power
output is similar to the radiative power output of a typical quasar,
and exceeds the $\approx 3 \times 10^{45} ~\lum$ of energy radiated
away by ICM gas with a cooling time less than the age of the Universe
at $z=0.35$. As we discuss in Section \ref{sec:accretion}, powering an
outburst of this magnitude by mass accretion alone is problematic,
allowing us to consider alternate power sources like black hole spin.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Powering the AGN Outburst}
\label{sec:accretion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

If the AGN was powered by mass accretion alone, then \ecav\ is
representative of the gravitational binding energy released as mass
accreted onto the SMBH. In this case, the total mass accreted can be
approximated as $\macc = \ecav/(\epsilon c^2)$, and the rate of
consumption was $\dmacc = \macc/\tbuoy$. Consequently, the black hole
mass grew by $\ddmbh = (1-\epsilon)\macc$ at a rate $\dmbh =
\ddmbh/\tbuoy$. Here, $\epsilon$ is a poorly understood mass-energy
conversion factor which may vary from 0.06--0.40, and we adopt the
commonly used 0.1 \citep{2002apa..book.....F}. The accretion
properties needed to reproduce each cavity configuration are given in
Table \ref{tab:totals}, and for the line-of-sight case, two values of
interest are $\macc \approx 3.8 \times 10^8 ~\msol$ and $\dmbh
\approx 4 ~\msolpy$. Below, we consider if the accretion of cold or
hot gas pervading the BCG could meet these requirements without being
in conflict with observed BCG properties.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Cold Accretion}
\label{sec:cold}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Substantial quantities of cold molecular gas and optical nebulae are
found in many cool core clusters \citep{crawford99, edge01}. If
rapidly cooling thermal instabilities form in these structures, it is
possible that they are the source of fuel for AGN activity and star
formation \citep[\eg][]{pizzolato05, 2010arXiv1003.4181P}. The
molecular gas mass (\mmol) of \rbs\ has not been measured, so it was
inferred using the \mmol-\halpha\ correlation in \citet{edge01}. An
optical spectrum (3200-7600 \AA) of the \rbs\ BCG reveals a strong
\hbeta\ emission line \citep{rbs1, rbs2}, which we used as a surrogate
for \halpha\ by assuming a Balmer decrement of
EW$_{\hbeta}$/EW$_{\halpha}$ = 0.29 \citep{2006ApJ...642..775M}, where
EW is line equivalent width. Under these assumptions, we estimate
$\mmol \sim 10^{10} ~\msol$, sufficiently in excess of \macc\ that we
can infer there is a cold gas reservoir capable of providing fuel for
the outburst. It must be noted that the \mmol-\halpha\ relation has
substantial scatter \citep{salome03}, and that the \rbs\ emission line
measurements are highly uncertain (A. Schwope, private communication),
so this \mmol\ estimate is simply informative.

However, an ample gas reservoir is not enough, the gas must be
accreted, and this accretion results in black hole mass growth which
is coupled to the star formation properties of host galaxy bulge
\citep[\eg][]{1995ARA&A..33..581K, 2000ApJ...539L...9F}. The Magorrian
relation \citep{magorrian} tells us that for each unit of black hole
mass growth, several hundred times as much goes into stars
\citep[\eg][]{2004ApJ...604L..89H}. The mass accretion rate needed to
power the \rbs\ outburst ($\dmbh \approx 4 ~\msolpy$) thus requires
that of the order $400 ~\msolpy$ of star formation accompanied the AGN
fueling event. Unfortunately, the current \rbs\ BCG star formation
rate (SFR) is $\sim 1$--10 \msolpy\ and the stellar halo's color
profile is inconsistent with recent star formation (see Section
\ref{sec:bcg}). Assuming the present SFR is representative of the SFR
preceding and during the AGN outburst, the implication is that for
every mass unit accreted by the SMBH, a nearly equal amount went into
stars, in conflict with expectations of SMBH-host galaxy
co-evolution. Considering cavity configuration-1 instead, the black
hole may have grown at a slower pace, $\dmbh \approx 0.5 ~\msolpy$,
but even in this case, a SFR less than 10 \msolpy\ still implies a
very high accretion efficiency of 20-to-1. Given the limitations of
the data available, we conclude that if cold gas accretion did power
the outburst, it appears to have been astoundingly efficient.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Hot Accretion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Direct accretion of the hot ICM via the Bondi mechanism provides
another possible AGN fuel source. The accretion flow arising from this
process is characterized by the Bondi equation (Equation
\ref{eqn:bon}) and is often compared with the Eddington limit
describing the maximal accretion rate for a SMBH (Equation
\ref{eqn:edd}):
\begin{eqnarray}
  \dmbon &=& 0.013 ~\kbon^{-3/2} \left(\frac{\mbh}{10^9
    ~\msol}\right)^{2} ~\msolpy \label{eqn:bon}\\
  \dmedd &=& \frac{2.2}{\epsilon} \left(\frac{\mbh}{10^9~\msol}\right)
  ~\msolpy  \label{eqn:edd}
\end{eqnarray}
where $\epsilon$ is a mass-energy conversion factor, \kbon\ is the
mean entropy [\ent] of gas within the Bondi radius, and \mbh\ is black
hole mass [\msol]. We chose the relations of
\citet{2002ApJ...574..740T} and \citet{2007MNRAS.379..711G} to
estimate \mbh, and find a range of $0.6 \dash 7.8 \times 10^9 ~\msol$,
from which we adopted the weighted mean value $1.5^{+6.3}_{-0.9}
\times 10^9 ~\msol$ where the errors span the lowest and highest
$1\sigma$ values of the individual estimates. Fitting the ICM entropy
profile with the function $K = \kna +\khun (r/100 ~\kpc)^{\alpha}$,
where \kna\ [\ent] is core entropy, \khun\ [\ent] is a normalization
at 100 kpc, and $\alpha$ is a dimensionless index, reveals best-fit
parameters of $\kna = 17.9 \pm 2.2 ~\ent$, $\khun = 92.1 \pm 6.2
~\ent$, and $\alpha = 1.65 \pm 0.11$. For $\epsilon = 0.1$ and $\kbon
= \kna$, the relevant accretion rates are $\dmbon \approx 4 \times
10^{-4} ~\msolpy$ and $\dmedd \approx 33 ~\msolpy$. The Eddington and
Bondi accretion ratios for each cavity configuration are given in Table
\ref{tab:totals}, with the line-of-sight case having $\dme \equiv
\dmacc/\dmedd \approx 0.15$ and $\dmb \equiv \dmacc/\dmbon \approx
17000$.

The large values of \dme\ and \dmb\ are troublesome, particularly the
Bondi ratio which implies all the gas which reached the Bondi radius
($\rbon \approx 10$ pc) was accreted. But, \dmb\ may be overestimated
if $\kbon < \kna$ and \mbh\ is larger than our adopted value. If $\mbh
= 8 \times 10^9 ~\msol$ and gas near \rbon\ has a mean temperature of
0.1 keV, for \dmb\ to approach unity, \kbon\ must be less than $0.3
~\ent$, corresponding to $\nelec \sim 0.2 ~\pcc$. This density is
twice the measured ICM central density, and a sphere more than 2 kpc
in radius is required for up to $10^8 ~\msol$ to be available for
accretion. But this implies the inner-core of the cluster is fully
consumed during the outburst lifetime ($<$ 100 Myr), which is much
shorter than the central cooling time of the ICM (400 Myr), thereby
short-circuiting the feedback loop. Conversely, if the BCG harbors an
ultramassive black hole, $\sim 10^{10}$, the strain on the Bondi
mechanism is eased somewhat \citep[\eg][]{msspin}. While Bondi
accretion cannot be ruled out because the nucleus is unresolved and
the cluster is observed post-outburst when core conditions may have
dramatically changed, a number of observationally unsupported
concessions must be made for Bondi accretion to be viable.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Nucleus Emission}
\label{sec:nuc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A bright BCG X-ray source apparent in the \cxo\ imaging may indicate
on-going accretion processes. A spectrum for the X-ray source was
extracted from a region enclosing 90\% of the normalized \cxo\ PSF
specific to the nuclear source median photon energy and off-axis
position. The source region had an effective radius of $0.86\arcs$,
and a background spectrum was taken from an enclosing annulus that had
5 times the area. The shape and features of the background-subtracted
spectrum, shown in Figure \ref{fig:nucspec}, are inconsistent with
thermal emission, and was instead modeled using an absorbed power law
with two Gaussians added to account for features which may be
photoionized line blends. A variety of absorption models were fit to
the spectrum, and the best-fit values are given in Table
\ref{tab:agn}. The model with a power-law distribution of $\nhobs \sim
10^{22} ~\pcmsq$ absorbers yields the best statistical fit, and the
low column densities (well-below even moderately Compton-thick)
indicate the nucleus is not heavily obscured.

The X-ray source does not appear to have an optical point source
counterpart which may accompany on-going accretion. If mass accretion
is powering the nuclear emission, the X-ray source bolometric
luminosity, $\lbol = 2.21 \times 10^{44} ~\lum$, implies an accretion
rate of $\dmacc \approx \lbol/(0.1 c^2) \approx 0.04 ~\msolpy \approx
0.001 \dme$. For this \dmacc, the accretion disk model of
\citet{2002NewAR..46..247M} predicts an optical disk luminosity of
$\ldisk \approx 8 \times 10^{44} ~\lum$, but no $L_{\rm{opt}} >
10^{44} ~\lum$ sources are found in the \hst\ imaging. The low column
densities found in the X-ray modeling could not conceal such a source,
so either the disk model is inappropriate for the nucleus, the optical
emission is beamed away from us, or it is absent.

Extrapolation of the best-fit X-ray spectral model to radio
frequencies reveals good agreement with the measured 1.4 GHz and 4.8
GHz nuclear radio fluxes. Further, the continuous injection
synchrotron model of \citet{1987MNRAS.225..335H} produced an
acceptable fit to the X-ray, 1.4 GHz, and 4.8 GHz nuclear fluxes (see
Figure \ref{fig:sync}). These results suggest the nuclear X-ray source
may be synchrotron emission from unresolved jets (which are obvious in
the high-resolution 4.8 GHz radio image), and not the remnants of a
very dense, hot gas phase which would be associated with Bondi
accretion.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Black Hole Spin}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Powering the outburst by mass accretion alone appears to be
inconsistent with the properties of the ICM and BCG. In an effort to
find lower accretion rates which still produce powerful jets, we
consider below if a rapidly-spinning SMBH could act as an alternate
power source. We consider the spin model with the caveat that, like
cold- and hot-mode accretion, spin is wrought with its own
difficulties and is hard to evaluate for any one system (see
\citealt{msspin} and \citealt{minaspin} for discussion on these
points).

In the Blandford-Znajek \citep[BZ;][]{bz} and Blandford-Payne
\citep[BP;][]{bp} mechanisms, strong magnetic fields wound around a
black hole extract energy from a rotating accretion disk (BP), or
rotation of the black hole itself (BZ), and funnel the energy into
opposing relativistic jets lying along the SMBH spin axis. Hybrid spin
models \citep[\eg][]{1999ApJ...522..753M, 2001ApJ...548L...9M,
  2006ApJ...651.1023R, 2007MNRAS.377.1652N, 2009MNRAS.397.1302B,
  gesspin} produce jets by pairing the BP and BZ processes with some
variant of an advection-dominated accretion flow \citep{adaf}. In such
models, the normalized mass accretion rate (\dme) dictates the
required magnetic field strength ($B_d$) which determines the overall
jet power, \ie\ $B_d \propto \gamma_1 \dme^{\Gamma_1}$ and $\pjet
\propto \gamma_2 j^{\Gamma_2} B_d^{\Gamma_3}$ where $j$ is a
dimensionless spin parameter and model dependencies like disk
viscosity ($\alpha$), fluid equation of state, and ratio of gas to
magnetic pressure are folded into the $\gamma_i$ and $\Gamma_i$
factors. Of these parameters, only \pjet\ is observationally
constrained, so a range of $j$ and \dme\ combinations can produce any
particular \pjet. However, to avoid the need for excessively large
accretion rates, which is the shortcoming of cold- and hot-mode
accretion, $j$ needs to be as near unity as possible, \ie\ the choice
of \dme\ is not completely arbitrary.

In order to explain the \rbs\ jet power using the hybrid model of
\citet{2007MNRAS.377.1652N}, for $\mbh = 1.5 \times 10^9 ~\msol$,
$\alpha = 0.25$ \citep{1999ApJ...520..298Q}, and $j = 1$, the mass
accretion rate needs to be $\dme \ga 0.13$ or $\dmacc \approx 4
~\msolpy$. This accretion rate is subject to the same problems
discussed for cold- and hot-mode accretion, in which case spin appears
to be no better a solution. Alternatively, adopting the argument
presented in \citet{minaspin}, which suggests $\dme$ for similarly
powerful systems like \ms\ and Hercules A cannot be much more than
$\approx 0.02$, if we have underestimated \mbh\ and the true mass is
$\ge 3 \times 10^9 ~\msol$, then the \citet{2007MNRAS.377.1652N} model
can achieve our \pjet\ limit when $j \approx 1$, which implies
accretion rates $< 1.5 ~\msolpy$. Additional relief can be found in
the model of \citet{gesspin}, which has the feature that extremely
powerful jets are produced for a SMBH which is spinning retrograde
relative to the direction of the accreting material. For the
\citet{gesspin} model, when $\|j\| \ge 0.9$ and $\mbh = 1.5 \times
10^9 ~\msol$, the required mass accretion rate is $\dme \le 0.01$ or
$< 0.3 ~\msolpy$. So while we cannot constrain $j$ or $\dme$, there
are reasonable accretion rates for a maximally spinning SMBH which can
reproduce our \pjet\ upper limit while not being in conflict with the
BCG or ICM properties.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{AGN-BCG Interaction and Star Formation}
\label{sec:bcg}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The \rbs\ BCG star formation properties are directly related to
fueling of the AGN outburst through the Magorrian relation, and these
properties were constrained using optical and UV observations from the
Hubble Space Telescope (\hst), \galex, and \xmm/Optical
Monitor.

\hst\ imaged \rbs\ using the ACS/WFC instrument and the F606W
(4500--7500 \AA; \myv) and F814W (6800--9800 \AA; \myi)
filters. Images produced by the Hubble Legacy Archive pipeline were
used for analysis. There are two ACS artifacts in the \myi\ image
which begin at $\approx 2.7\arcs$ and $\approx 5.4\arcs$ from the BCG
center. Within a $2\arcs$ aperture centered on the BCG, the measured
magnitudes are $m_{\myv} = 19.3 \pm 0.7$ mag and $m_{\myi} = 18.2 \pm
0.6$ mag, consistent with non-\hst\ measurements of \citet{rbs1},
indicating the \hst\ photometry in this region is unaffected. The
influence of optical emission lines on the photometry was estimated
using the ratio of line EWs taken from \citet{rbs1} to \hst\ filter
widths. The \halpha\ contribution to the \myi\ image is estimated at
$\approx 3\%$ using the scaled \hbeta\ line (see Section
\ref{sec:cold}), and the combined \hbeta, \oii, and
\oiii\ contribution to the \myv\ image is $\approx 7\%$. The low
percentages indicate the stellar continuum should be well-represented.

\rbs\ was imaged in the far-UV (FUV; 1344--1786 \AA) and near-UV (NUV;
1771--2831 \AA) with \galex, and the near-UV with the
\xmm/Optical-Monitor (\xom) using filters UVW1 (2410--3565 \AA) and
UVM2 (1970--2675 \AA). The \galex\ pipeline produced images were used
for analysis, and the \xom\ data was processed using \sas\ version
8.0.1. \rbs\ is detected in all but the UVM2 observation as an
unresolved source co-spatial with the optical and X-ray BCG
emission. The individual filter fluxes are $f_{\rm{FUV}} = 19.2 \pm
4.8 ~\mu$Jy, $f_{\rm{NUV}} = 5.9 \pm 2.1 ~\mu$Jy, $f_{\rm{UVW1}} =
14.6 \pm 4.6$ $\mu$Jy and $f_{\rm{UVM2}} < 117$ $\mu$Jy, all of which
lie above the nuclear power-law emission we attribute to unresolved
jets (see Section \ref{sec:nuc} and Figure \ref{fig:sync}).

A radial $(\myv-\myi)$ color profile of the central $2\arcs$ ($\approx
10$ kpc) was extracted from the \hst\ images and fitted with the
function $\Delta(\myv-\myi) \log r + b$, where $\Delta(\myv-\myi)$
[mag dex$^{-1}$] is the color gradient, $r$ is radius, and $b$ [mag]
is a normalization. The best-fit parameters are $\Delta(\myv-\myi) =
-0.20 \pm 0.02$ and $b = 1.1 \pm 0.01$ for \chisq(DOF) = 0.009(21),
revealing a flat, red color profile consistent with other BCGs that do
not have strong nuclear star formation \citep[\eg][]{rafferty06}. Star
formation rates were calculated from the UV fluxes using the relations
of \citet{kennicutt2}, \citet{2006ApJ...642..775M}, and
\citet{salim2007}, which yield rates in the range 1--10 ~\msolpy\ (see
Table \ref{tab:sfr}), relatively small values for what would be
considered a strong cool core cluster. These estimates are likely
upper limits since the blue \galex\ color signals some AGN
contamination \citep{2005AJ....130.1022A}, and sources of significant
uncertainties have been neglected \citep[\eg][]{1992ApJ...388..310K,
  2004AJ....127.2002K, hicksuv, 2010MNRAS.tmp..626G}.

Taken together, the flat color profile and low star formation rate
suggest any star formation may not be smoothly distributed in the halo
but confined to compact regions like the bright substructures seen in
the \hst\ images. To better reveal the BCG substructure, residual
galaxy images were constructed by first fitting the \hst\ \myv\ and
\myi\ isophotes with ellipses using the \iraf\ tool
                {\textsc{ellipse}}. Stars and other contaminating
                sources were rejected using a combination of $3\sigma$
                clipping and by-eye masking. The ellipse centers were
                fixed at the galaxy centroid, and ellipticity and
                position angle were fixed at $0.25 \pm 0.02$ and
                $-64\mydeg \pm 2\mydeg$, respectively -- the mean
                values when they were free parameters. Galaxy light
                models were created using {\textsc{bmodel}} in
                \iraf\ and subtracted from the corresponding parent
                image, leaving the residual images shown in Figure
                \ref{fig:subopt}. A color map was also generated by
                subtracting the fluxed \myi\ image from the fluxed
                \myv\ image.

The close alignment of the optical substructure with the nuclear AGN
outflow clearly indicates the jets are interacting with the BCG
halo. There also appears to be an in-falling galaxy northwest of the
nucleus, possibly with a stripped tail \citep[see][for
  example]{2007ApJ...671..190S}. The numbered regions overlaid on the
residual \myv\ image are the areas of the color map which have the
largest color difference with surrounding galaxy light. Regions 1--5
are relatively the bluest with $m_{\myv-\myi} = -0.40, -0.30, -0.25,
-0.22, ~\rm{and} -0.20$, respectively. Regions 6--8 are relatively the
reddest with $m_{\myv-\myi} =$ +0.10, +0.15, and +0.18,
respectively. Without spectroscopy, we can only speculate that the
blue regions may be star formation sites, the red regions areas of
heavy reddened by dust extinction, or both may be strong emission line
regions.

Clusters like \rbs\ with a core entropy less than $30 ~\ent$ often
host a BCG surrounded by extended \halpha\ nebulae
\citep[\eg][]{mcdonald10}. Like these systems, the residual
\myi\ image reveals what appear to be 8--10 kpc long ``whiskers''
surrounding the BCG (regions 9--11). It is interesting that blue
regions 1 and 4 reside at the point where the southern jet appears to
be encountering whiskers 9 and 10. It may be that the jet is
interacting with gas in the whiskers and possibly driving star
formation. If the AGN outflow is driving star formation, then the
estimated SFRs will be boosted above the putative rate, narrowing the
difference between the AGN mass accretion and star formation rates and
exacerbating the difficulty with cold-mode accretion (see Section
\ref{sec:accretion}).

%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{sec:con}
%%%%%%%%%%%%%%%%%%%%%

We have presented results from a study of the AGN outburst in the
galaxy cluster \rbs. \cxo\ observations have enabled us to constrain
the energetics of the AGN outburst and analyze different mechanisms
which may have powered it. We have shown the following:
\begin{enumerate}
\item Residual imaging reveals extensive substructure in the ICM
  (Figure \ref{fig:subxray}), in addition to the two obvious cavities
  near the cluster core, which has a nebulous correlation with
  coincident radio emission. This leads us to speculate that, in order
  to achieve a proper estimate of the outburst energetics, projection
  effects must be taken into consideration.
\item We find that the two central cavities have surface brightness
  decrements that are inconsistent with the cavities being spheres
  whose centers lie in a plane perpendicular to our line of sight which
  passes through the central AGN. Motivated by the decrement analysis,
  we propose that the cavities are either highly-elongated structures
  in the plane of the sky, or result from the superposition of much
  larger structures lying along our line of sight.
\item For the elongated and line-of-sight cavity configurations, we
  determine that the total AGN outburst energy is likely $5-70 \times
  10^{60}$ erg with a total power output of $5-30 \times 10^{45}
  ~\lum$ (see Tables \ref{tab:cavities} and \ref{tab:totals}). We
  consider the high-end values as definite upper limits because they
  exceed the energetics of every other known AGN outburst and are
  subject to significant uncertainties in the decrement analysis.
\item The AGN energetics demand that accretion of cold or hot gas
  operate with unrealistic efficiency if mass accretion alone powered
  the outburst. We specifically show that Bondi accretion is an
  unattractive solution, and instead suggest that the outburst may
  have been powered by tapping the energy stored in a maximally
  spinning SMBH. We show that in the spin model, accretion rates $\la
  2 ~\msolpy$ are needed to achieve our jet power upper limit, with
  the possibility of accretion rates as low as 0.1 ~\msolpy\ being
  sufficient.
\item Using primarily \hst\ optical images, we present the discover of
  substructure in the BCG stellar halo which clearly indicates the AGN
  is interacting with the host galaxy. While we are unable to
  determine if any regions of interest host star formation or line
  emission, the convergence of what appear to be extended optical
  filaments, bluish knots of emission, and the tip of one jet suggest
  there may be AGN driven star formation. We interpret the paucity of
  star formation indicators as a further sign that cold-mode accretion
  is not a favorable method of powering the AGN outburst.
\end{enumerate}

%%%%%%%%%%%%%%%%%
\acknowledgements
%%%%%%%%%%%%%%%%%

KWC and BRM were supported by CXO grant G07-8122X and a generous grant
from the Canadian Natural Science and Engineering Research Council
(NSERC). KWC also acknowledges financial support from L'Agence
Nationale de la Recherche (ANR) through grant ANR-09-JCJC-0001-01, and
thanks David Gilbanks, Sabine Schindler, Axel Schwope, and Chris
Waters for helpful input.

%%%%%%%%%%%%%%
% Facilities %
%%%%%%%%%%%%%%

{\it Facilities:} \facility{CXO (ACIS)} \facility{HST (WFPC2)}
\facility{GALEX}

%%%%%%%%%%%%%%%%
% Bibliography %
%%%%%%%%%%%%%%%%

\bibliography{cavagnolo}

%%%%%%%%%%%%%%%%%%%%%%
% Figures and Tables %
%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\input{cavities.tex}
\input{totals.tex}
\input{agn.tex}
\input{sfr.tex}
\input{figs.tex}

%%%%%%%%%%%%%%%%%%%%
% End the document %
%%%%%%%%%%%%%%%%%%%%

\end{document}
