\documentclass[12pt]{cv}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}
\usepackage[T1]{fontenc}
\usepackage{mathptmx,multicol,common}
\pagestyle{empty}
\parindent 0pt
\parskip
\baselineskip
\setlength{\topmargin}{-0.30in}
\setlength{\oddsidemargin}{-0.30in}
\setlength{\evensidemargin}{-0.30in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0.25in}
\setlength{\topskip}{0.25in}
\setlength{\textwidth}{6.9in}
\setlength{\textheight}{9.25in}
\pagestyle{myheadings}

\begin{document}

\begin{center}
{\huge \textbf{\sc Kenneth W. Cavagnolo\\ \large Curriculum Vitae}}\\
\rule{17.35cm}{1pt}\\
\end{center}
\normalsize

\addresses
{
{\bf Office Address}\\
Michigan State University\\
Department of Physics \& Astronomy\\
3265 Biomedical Physical Sciences Building\\
East Lansing, MI 48823-2320\\
}
{
{\bf Contact Information}\\
Office: (517)-355-9200 ext.2443\\
Home: (517)-285-9062\\
E-mail: \href{mailto:cavagnolo@pa.msu.edu}{\tt{cavagnolo@pa.msu.edu}}\\
Web: \href{http://www.pa.msu.edu/people/cavagnolo/}{\tt www.pa.msu.edu/people/cavagnolo/}\\
}

\begin{llist}

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Education}
\employer{{\bf Michigan State University}}
\location{2005 - Present}
Ph.D. Astrophysics, Expected August 2008\\
Thesis Title: ``Virialization, Entropy, \& Feedback in Clusters of Galaxies''\\
Advisors: Dr. Megan Donahue \& Dr. G. Mark Voit

\employer{{\bf Michigan State University}}
\location{2002 - 2005}
M.S. Astrophysics, {\it Magna Cum Laude}\\
Dissertation Title: ``Entropy Profiles of Cooling Flow Clusters''\\
Advisor: Dr. Megan Donahue

\employer{{\bf Georgia Institute of Technology}}
\location{1998 - 2002}
B.S. Physics, {\it Magna Cum Laude}\\
Senior Thesis: ``Analysis of the Eclipsing Binary ET Tau''\\
Advisor: Dr. James Sowell

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Research\\Experience}
{\sc \bf{Supermassive Cluster Survey, Member}}
\location{2007 - Present}
Lead: Dr. Rachel Mandelbaum, {\textit{IoA}}\\
Weak lensing collaboration to measure the scatter between\\
X-ray observables and true projected mass.

{\sc \bf{Graduate Research Assistant}}
\location{2003 - Present}
Supervisor: Dr. Megan Donahue, {\textit{Mich. St. Univ.}}\\
Studying clusters of galaxies via their X-ray properties to\\
investigate feedback mechanisms, galaxy evolution, and the process\\
of cluster virialization.

{\sc \bf{Graduate Research Assistant}}
\location{2002 - 2003}
Supervisor: Dr. Jack Baldwin, {\textit{Mich. St. Univ.}}\\
Analyzing echelle spectra for use in studies of {\textit{s}}-process abundances\\
in planetary nebulae.

{\sc \bf{Undergraduate Research Assistant}}
\location{2000 - 2002}
Supervisor: Dr. James Sowell, {\textit{Georgia Tech}}\\
Obtaining orbital solution for the eclipsing Algol binary ET Tau via\\
UBV light curves and spectroscopic radial velocity curves.

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Research\\Interests}
$\bullet$ Large Scale Structure Formation and Cosmology\\
$\bullet$ Galaxy Cluster Evolution\\
$\bullet$ Feedback Mechanisms in Galaxy Clusters\\
$\bullet$ Sunyaev-Zel'dovich Effect\\
$\bullet$ Galaxy Formation

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Teaching\\Experience}
{\sc \bf{Substitute Instructor}}
\location{Fall 2006}
Course: ``Visions of the Universe''\\
Gave lectures covering stellar evolution, supernovae, white dwarves,\\
neutron stars, and black holes.

{\sc \bf{Physics Tutor}}
\location{Summer 2003}
Course: ``Introductory Honors Physics I \& II''\\
Tutored physics students taking introductory physics courses such as\\
classical mechanics, optics, and electromagnetism.

{\sc \bf{Graduate Teaching Assistant}}
\location{2002 - 2003}
Course: ``Visions of the Universe''\\
Directed and supervised laboratories for non-calculus based\\
astronomy course.

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\markright{K.W. Cavagnolo, Curriculum Vitae}

\sectiontitle{Honors}
$\bullet$ MSU College of Natural Science Dissertation Fellow \hfill 2007 - Present\\
$\bullet$ American Astronomical Society Member\hfill 2002 - Present\\
$\bullet$ American Physical Society Member\hfill 2002 - Present\\
$\bullet$ Sigma Pi Sigma National Honor Society \hfill 2001 - Present\\
$\bullet$ Dean's List, Georgia Tech \hfill 1998-2002

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Scientific\\Skills}
$\bullet$ Profound skills in reducing and analyzing data taken with \Chandra\ X-ray Telescope.\\
$\bullet$ Extensive experience with customizing and debugging \Ciao\ and \Caldb.\\
$\bullet$ Familiarity with multiwavelength analysis packages: \aips, \iraf, and \pyraf.\\
$\bullet$ Fluent in \perl, \idl, \LaTeX\, and \html.\\
$\bullet$ Working knowledge of \clang, \flash, \fortran, \mysql, \supmo, and \tcl.\\
$\bullet$ Mastery of multiple computing architectures: DOS, Linux, Macintosh, and Windows.\\
$\bullet$ Expert of computer troubleshooting, maintenance, and system construction.

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{References}

{\sc Dr. Megan Donahue}\\
(517)-355-9200 ext. 2418\\
\href{mailto:donahue@pa.msu.edu}{\tt donahue@pa.msu.edu}\\
Michigan State University

{\sc Dr. G. Mark Voit}\\
(517)-355-9200 ext. 2419\\
\href{mailto:voit@pa.msu.edu}{\tt voit@pa.msu.edu}\\
Michigan State University

{\sc Dr. Jack Baldwin}\\
(517)-355-9200 ext. 2411\\
\href{mailto:baldwin@pa.msu.edu}{\tt baldwin@pa.msu.edu}\\
Michigan State University

%---------------------------------------------------------------%
%---------------------------------------------------------------%

\sectiontitle{Personal\\Interests}
$\bullet$ Academic: environmental sciences, ``Cradle2Cradle'' design, and urban planning.\\
$\bullet$ Athletics: triathlons, baseball, and everything Georgia Tech.\\
$\bullet$ Hobbies: reading, building model airplanes, and raising bonsai trees.\\

\end{llist}

\end{document}
