\documentclass[11pt]{article}
\usepackage{macros_cavag}
\pagestyle{myheadings}
\font\cap=cmcsc10
\setlength{\topmargin}{-0.15in}
\setlength{\oddsidemargin}{-0.15in}
\setlength{\evensidemargin}{-0.15in}
\setlength{\headheight}{0.1in}
\setlength{\headsep}{0.25in}
\setlength{\topskip}{0.1in}
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{9.25in}
\begin{document}
\renewcommand{\labelenumi}{\arabic{enumi}.}
\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}}
\renewcommand{\labelenumiii}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}}
\renewcommand{\labelenumiv}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.\arabic{enumiv}}

Following the email from Megan, there are some tasks I need to undertake:\\

\begin{enumerate}
\item {\bf Focus on ``Are there any...'' type questions!}
\item Do the central entropies pile up into a bi-modal distribution in
the cases where central entropy can be measured?{\bf **DONE**} Use min\_tscal.pro in pf\_fits/
\begin{enumerate}
\item  This is something that can be measured with all sufficient data
in the "collection".{\bf**DONE**}
\item However, a special sub-sample is the one that can answer the
question "What fraction of Log L$_X > 44$ clusters have low central
entropy?"{\bf**DONE**}
\end{enumerate}
\item What central entropy is the mean (and dispersion) for all
clusters known to have $H\alpha$ nebulae?{\bf**DONE**}
\item Are there AGN-dominated nebulae?{\bf**DONE**}
\item Do they exhibit different behavior from the ones that are
largely stellar formation-dominated?{\bf**DONE**}
\item Do clusters with high central L$_{Radio}$ ever exhibit high
K$_0$?{\bf**DONE**}
\item Identify relevant, statistically interesting sub-samples from my
collection, and look for trends in:
\begin{enumerate}
\item Central entropy{\bf**DONE**}
\item Slope of power laws for entropy profiles{\bf**DONE**}
\item Morphology{\bf**DONE**}
\item Presence of BCG{\bf**DONE**}
\item L$_{radio}${\bf**DONE**}
\item L$_{H\alpha}${\bf**DONE**}
\item Separation of BCG and nominal centroid
\item Presence of real BCG
\item Presence of $H\alpha${\bf**DONE**}
\item Optical AGN
\item Which clusters have not been observed by Spitzer?{\bf**DONE**}
\end{enumerate}
\item Of the subsample where I can plot down to the central 10-20 kpc,
is there or is there not bi-modal distribution of central entropy?
This can be done with the entire collection, but toss the things with
poor $\chi^2$.{\bf**DONE**}
\item Do the clusters that exhibit L$_{IR}$ excesses in Chris O'Dea's
sample of 65 show ay difference in their entropy profiles compared to
the ones that do not have an IR excess?{\bf**DONE**}
\item Create a table of clusters and relevant properties.{\bf**DONE**}
\begin{enumerate}
\item Name
\item z
\item K$_0$
\item K$_{100}$
\item K slope
\item T$_{100}$
\item T$_X$
\item L$_X$
\item L$_{Radio}$
\item L$_{H\alpha}$
\item L$_{IR}$
\end{enumerate}
\item Create a table of surface brightness profiles{\bf**DONE**}
\begin{enumerate}
\item Name
\item z
\item SB$_0$
\item $\eta_1$
\item $\beta_1$
\item r$_{core,1}$
\item $\eta_2$
\item $\beta_2$
\item r$_{core,2}$
\item Goodness of fit
\item N$_{bins}$
\end{enumerate}
\item Plot ratio of central beta model luminosity to total beta model
luminosity and compare it to:
\begin{enumerate}
\item Temperature gradient
\item Metallicity gradient
\item Should bear predictable result that clusters with siginificant
compact central beta models tend to have temperature decrements and
iron abundance enhancements.
\item If I think I've done a fantastic job on the metallicity
profiles, I need to check if there is anything new I can say about
them.
\end{enumerate}
\item Are there any low H$\alpha$ clusters with loud radio sources?
\end{enumerate}
\end{document}
