%%%%%%%%%%%%%%%%%%%
% Custom commands %
%%%%%%%%%%%%%%%%%%%

\newcommand{\birzan}{B\^irzan}
\newcommand{\mytitle}{The AGN Jet Power and Radio Power Relationship
  for Giant Elliptical Galaxies}
\newcommand{\samp}{21}
\newcommand{\ecav}{\ensuremath{E_{cav}}}
\newcommand{\pjet}{\ensuremath{P_{jet}}}
\newcommand{\pcav}{\ensuremath{P_{cav}}}
\newcommand{\prad}{\ensuremath{P_{radio}}}
\newcommand{\phigh}{\ensuremath{P_{\mathrm{1.4}}}}
\newcommand{\pthree}{\ensuremath{P_{\mathrm{327}}}}
\newcommand{\plow}{\ensuremath{P_{\mathrm{200-400}}}}
\newcommand{\shigh}{\ensuremath{\sigma_{\mathrm{1.4}}}}
\newcommand{\sthree}{\ensuremath{\sigma_{\mathrm{327}}}}
\newcommand{\slow}{\ensuremath{\sigma_{\mathrm{200-400}}}}
\newcommand{\srad}{\ensuremath{\sigma_{rad}}}
\newcommand{\rhigh}{\ensuremath{r_{\mathrm{1.4}}}}
\newcommand{\rlow}{\ensuremath{r_{\mathrm{200-400}}}}

%%%%%%%%%%
% Header %
%%%%%%%%%%

%\documentclass[12pt, preprint]{aastex}
%\documentclass{aastex}
\documentclass{emulateapj}
\usepackage{apjfonts,graphicx,here,common,longtable,ifthen,amsmath,amssymb,natbib}
%% \usepackage[pagebackref,
%%  pdftitle={\mytitle},
%%  pdfauthor={Kenneth W. Cavagnolo},
%%  pdfsubject={ApJ},
%%  pdfkeywords={},
%%  pdfproducer={LaTeX with hyperref},
%%  pdfcreator={LaTeX}
%%  pdfdisplaydoctitle=true,
%%  colorlinks=true,
%%  citecolor=blue,
%%  linkcolor=blue,
%%  urlcolor=blue]{hyperref}
\bibliographystyle{apj}
\begin{document}
\title{\mytitle}
\shorttitle{AGN Scaling Relations for Giant Ellipticals}
\author{
K. W. Cavagnolo\altaffilmark{1,7},
B. R. McNamara\altaffilmark{1,2,3},
P. E. J. Nulsen\altaffilmark{3},\\
C. L. Carilli\altaffilmark{4},
C. Jones\altaffilmark{3},
W. Forman\altaffilmark{3},\\
L. \birzan\altaffilmark{5,6}, \&
S. Murray\altaffilmark{3}
}
\altaffiltext{1}{Department of Physics and Astronomy, University of
  Waterloo, Waterloo, ON N2L 3G1, Canada.}
\altaffiltext{2}{Perimeter Institute for Theoretical Physics, 31
  Caroline Street N, Waterloo, ON N2L 2Y5, Canada.}
\altaffiltext{3}{Harvard-Smithsonian Center for Astrophysics, 60
  Garden Street, Cambridge, MA 01238, USA.}
\altaffiltext{4}{National Radio Astronomy Observatory, P.O. Box 0,
  Socorro, NM 87801-0387, USA.}
\altaffiltext{5}{Department of Astronomy and Astrophysics,
  Pennsylvania State University, 525 Davey Lab, University Park, PA
  16802, USA.}
\altaffiltext{6}{Astronomical Institute Anton Pannekoek, University of
  Amsterdam, Kruislaan 403, 1098 SJ Amsterdam, Netherlands.}
\altaffiltext{7}{kcavagno@uwaterloo.ca}
\shortauthors{K. W. Cavagnolo et al.}
\journalinfo{}
\slugcomment{For submission to ApJ}

%%%%%%%%%%%%
% Abstract %
%%%%%%%%%%%%

\begin{abstract}
Utilizing X-ray data collected with the \chandra\ X-ray Observatory
and multi-frequency VLA radio data, we present results from an
investigation of the scaling relationship between active galactic
nucleus (AGN) jet power and the radio power associated with the
outflows. Our sample of \samp\ relatively isolated giant elliptical
(gE) galaxies covers a comoving distance range of 0.4-117 Mpc and is
drawn from the 160 gE sample of \citet{jonesge}. This work extends the
studies presented in \citet{birzan04, birzan08}, which focused
primarily on the very upper-end of the galactic mass scale,
\eg\ brightest cluster galaxies (BCGs), to much lower mass scales. The
goal of the study presented here was to better understand if the
power-law scaling relation found by \citet{birzan04} between AGN jet
power and emergant radio power is universal in the sense that the
relation is continuous, both in functional form and intrinsic scatter,
from isolated gEs up to BCGs. Combining the results presented in this
paper with the results from \citet{birzan04, birzan08}, we find a
common scaling relation between jet power and monochromatic radio
powers at 200-400 MHz and 1.4 GHz of $\pjet \propto \prad^{0.6}$ with
considerable scatter of $\approx 1.0$ dex. The utility of this
relation...\\
-- radio observations as a surrogate in studying the total energetic
output of AGN, in addition to yielding information about the growth of
the black holes, for large cosmological volumes covering a broad range
of redshifts\\
--suggest uses\\
--explain implications\\
\end{abstract} 

%%%%%%%%%%%%
% Keywords %
%%%%%%%%%%%%

\keywords{galaxies: active -- galaxies: clusters: general -- X-rays:
  galaxies -- radio continuum: galaxies}

%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%

The process, and broader astrophysical impacts, of energy deposition
into the variety of environments which host supermassive blackholes
(SMBHs), on physical scales varying from pc to Mpc, has been under
intense observational and theoretical study for decades
\citep[\eg][]{1916AbhKP......189S, 1969Natur.223..690L,
  1974MNRAS.166..513S, 1981ApJ...248...55B, 1981ApJ...248...47F,
  1982MNRAS.199..883B, 1984ARA&A..22..471R, 1988Natur.333..829F,
  kaiser91, 1993MNRAS.263..323T, 1997MNRAS.288..355B,
  1998A&A...331L...1S, 2000ApJ...539L..13G, voitbryan,
  2004ApJ...613..811M, best05, benson03, accept}. More specifically,
the role of the energy returned to an environment via relativistic
jets emerging from an active galactic nucleus (AGN; the result of a
SMBH accreting matter) is now understood to be very important in
shaping the galaxy luminosity function \citep{croton06, bower06,
  saro06, sijacki07}. Moreover, better models and observations of the
AGN feedback process are also proving to be important in furthering
our understanding of the formation and evolution of large-scale
structure, such as galaxy clusters and groups \citep[see, for
  example,][]{2008MNRAS.386.1309M, minggroups}. But understanding the
details of coupling AGN feedback energy to an environment via heating
is still hotly debated.

Recent observational advances in studying AGN feedback have came
courtesy of the high-resolution optics of the
\cxo. \chandra\ observations have unambiguously revealed the direct
interaction between AGN jets and the X-ray emitting gas in which many
massive AGN host galaxies reside \citep[\eg][]{2000ApJ...534L.135M,
  perseus1, schindler01}. The presence of cavities (also commonly
refered to as ``bubbles'' in the literature) represented a new channel
for studying the properties of SMBHs and AGN, and thus aided in
furthering the understanding of the influence of AGN feedback on
galaxy and structure formation. When cavities are imaged, and with an
assumption regarding the relativisitc nature of the cavity contents,
one can approximate the jet power required to create the cavities by
calculating enthalpy from measurements of the $pV$ work necessary to
inflate a cavity. Cavities contain a substantial amount of energy,
$10^{54}-10^{61}$ erg, and sometimes the cavity energy is comparable
to or exceeds the energy radiated away by the environment with which
the AGN has interacted \citep{birzan04}, though this is not the case
for all systems \citep{dunn08}. The tremendous energy released by AGN
and transported out by jets represents a very appealing source of the
heat alluded to earlier.

It is worth noting that the energy released by an AGN is not confined
to just the jets, but is also released in shocks, radiation,
photoionization, inverse Compton effects, and powerful winds. In this
sense then, jet powers estimated from X-ray observations are
lower-limits to the total AGN energy output. In addition, bubble
morphology, angle of inclination, and how well-defined the bubbles
boundaries are all affect the bubble volume measurement. As a result,
in the literature it is commonly presumed that the jet powers can be
underestimated by up to an order of magnitude. Thus, it is reasonable
then to question whether jet powers estimated from X-ray observations
are representative of the total AGN energy output. Using mock X-ray
observations generated from 3-D magnetohydrodynamic simulations in
conjunction with the widely accepted methodology of measuring jet
power, \citet{2009arXiv0909.0722M} has demonstrated for the first time
that the jet powers estimated from the mock observations were
{\it{overestimated}} by approximately a factor of two with respect to
the true jet powers measured directly from the simulations. The close
agreement suggests that the observational techniques currently used
are reliable.

The method of measuring jet powers (\ie\ AGN feedback energy which
ultimately goes into heating) using X-ray cavities is presently
comparable to that of a ``cottage industry.'' By moving beyond
analysis of individual systems to analyzing samples of cavities over
large ranges in host system mass, environment, and redshift, we may be
able to develop a better understanding of AGN feedback and its
importance in shaping the present and past of galaxy
formation. However, selecting a representative or statistically
significant sample of cavity-bearing systems is non-trivial, and
arguably not possible. This is primarily because the study of X-ray
cavities is limited by the ability and capacity of the current
generation of X-ray telescopes to obtain data of the quality necessary
to resolve cavities. Cavities come in a large variety of sizes,
morphologies, distances from the AGN host galaxy, and projections on
the sky. These factors, combined with observing constraints, mean that
even in a sample specifically selected to find cavities, a cavity
system may go undetected. Thus, without the leverage of a large
statistical study to draw upon, it behooves observers and theorists
alike to find relationships between simple observables and AGN
energetics. 

In this capacity, X-ray cavities are also well-suited. By quantifying
and calibrating how cavity properties scale with readily available AGN
observables, then it becomes possible to circumvent the need to
undertake deep X-ray observing programs. This can be accomplished if,
for example, there exists a universal scaling relationship between jet
power and the radio emission associated with those jets. A very simple
quantity which has been used in previous investigations is the
monochromatic radio power, \prad. A universal \pjet-\prad\ scaling
relation could then be applied to measurements from all-sky radio
surveys, thereby installing the more readily available radio
observations as a surrogate for jet power \citep{croton06,
  2006MNRAS.366..397S}.

The relationship between the jet power and radio power for galaxy
clusters was discussed extensively in \citet{birzan04, birzan08}. The
most recent of the two papers, \citet{birzan08}, focused on three jet
power surrogate regimes: monochromatic radio power at 327 MHz
(\pthree), monochromatic radio power at 1.4 GHz (\phigh), and total
radio power (\prad). For their sample of galaxy clusters,
\citet{birzan08} found the relations between \pjet\ and these
surrogates took the forms
\begin{eqnarray}
\pjet &\propto& \pthree^{0.62}\\
\pjet &\propto& \phigh^{0.35}\\
\pjet &\propto& \prad^{0.59}
\end{eqnarray}
with scatters of $\sthree = 0.65$ dex, $\shigh = 0.69$ dex, and $\srad
= 0.85$ dex. Several groups have since applied the \birzan\ relation
to study the effects of feedback from elliptical galaxies, most
notably \citet{best07}, \citet{2007MNRAS.379..260M}, and
\citet{2009arXiv0908.3158H}. However, up to now, no observational
evidence has suggested that the \pjet-\prad\ relation which holds for
galaxy clusters is continuous, of comparable scatter, or applicable
for much lower mass systems such as ellipticals.

To address this disparity, the work presented in this paper
investigates the relationships \pjet-\phigh\ and \pjet-\plow\ (see
Section \S\ref{sec:radio} for the explanation of why the specific 327
MHz frequency was not used) for a sample of relatively isolated giant
elliptical galaxies, thus extending the work of \citet{birzan08} to
AGN host system masses orders of magnitude smaller than the BCGs
studied in their work. By combining the results from \citet{birzan08}
and the results in this paper, we find a similar relationship between
jet power and radio power in both high and low frequency radio
domains. The relationships span 6-8 orders of magnitude in \pjet\ and
\prad, and have the general form $\pjet \propto \prad^{0.6}$ with
large (dominately intrinsic) scatter of $\sigma \propto 1.0$ dex. Our
results suggest that a universal relationship between AGN jet power
and radio power exists.

The structure of this paper is as follows: In \S\ref{sec:sample} we
outline initial sample selection criteria and information about the
\chandra\ observations selected under these criteria. X-ray and radio
data reduction is discussed in \S\ref{sec:data}. Results and
discussion are presented in \S\ref{sec:r&d}. Sources of systematics
and possible biases are discussed in \S\ref{sec:sys}. A brief summary
is given in \S\ref{sec:summary}. \LCDM\ All quoted uncertainties are
68\% confidence. Hereafter, the terminology ``cavity power'' and ``jet
power'' are used interchangeably, and are denoted as \pcav\ and \pjet,
respectively.

%%%%%%%%%%%%%%%%%%
\section{Sample}
\label{sec:sample}
%%%%%%%%%%%%%%%%%%

The final sample of \samp\ gEs presented in this paper are taken from
a larger sample of 160 gEs observed with \chandra\ by
\citet{jonesge}. Of those 160 objects, extended X-ray emission was
detected in 109 objects. AGN activity was suspected in 27 objects
based solely on the presence of surface brightness depressions in the
X-ray emitting gas. We have further excluded dwarf galaxies ($M_V <
-19.5$) from the sample since it is not clear that the substructure in
the X-ray gas may be associated with an AGN, leaving
\samp\ objects. The \samp\ gEs in our sample are in relatively low
density environments, meaning these are not the central dominant or
brightest galaxies in clusters or groups. The X-ray emission
associated with the gEs in our sample is dominated by the gas
gravitationally bound to the gE halo and not a diffuse atmosphere of
some larger environment. We defer discussion of possible selection
biases to Section \S\ref{sec:r&d}. The comoving distance range of our
sample is 0.4-117 Mpc, with an X-ray luminosity range of XXX-XXX
\lum. General properties of the sample are listed in Table
\ref{tab:sample}.

\input{sample.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Observations and Data Analysis}
\label{sec:data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%
\subsection{X-ray}
\label{sec:xray}
%%%%%%%%%%%%%%%%%%

The results presented in this paper extend the work presented in
\citet{birzan08} to lower mass AGN host systems. \citet{birzan08}
utilized 1.4 GHz and 327 MHz monochromatic radio powers in their
comparison with X-ray cavity powers to establish the scaling relations
discussed in Section \S\ref{sec:intro}. To ensure a reliable
comparison between the results presented here and those of
\citet{birzan08}, we also focus on monochromatic radio fluxes at 1.4
GHz. However, at lower frequencies, we focus on the frequency range
200-400 MHz since 327 MHz observations were not available for most
systems. Discussed below is our methodology for calculating the cavity
and radio powers for each system.

All data used in measuring the X-ray cavity powers was taken with the
\cxo. All datasets were analyzed using the Chandra Interactive
Analysis of Observations (\ciao) software version XXX with the
calibrations of \caldb\ XXX. The level 1 events files were reprocessed
to apply the most current gain and correct for charge transfer
inefficiency. Additionally, the events lists were filtered for bad
grades, and cosmic rays were further rejected by using VFAINT
filtering when possible. Time periods contaminated by background
flaring were excluded from the data. Point sources were detected and
removed from the observations using the output of the routine
{\textsc{wavdetect}}. For the X-ray spectral analysis a low-energy
cut-off of XXX keV was used in addition to a high-energy cut-off of
XXX keV. Background spectral analysis was performed using the
\caldb\ blank-sky observations included in the CALDB and tailored to
match each targeted observation.

Measurement of cavity powers is performed in the same manner as in
\citet{birzan04, birzan08}. For each observation, azimuthally averaged
deprojected gas density and temperature profiles were used to
calculate the total gas pressure at each radius. Then, using cavity
volumes determined from a by-eye analysis, the total energy contained
in each cavity is estimated as $\ecav = pV[\gamma/(\gamma-1)]$ where
we assume $\gamma = 4/3$. The total cavity energy is then divided by
an estimate of the timescale for the associated AGN outburst yielding
$\pcav = \ecav/t$ (see \citet{mcnamrev} for a thorough discussion of
how the timescales are estimated). Uncertainties for each calculation
were determined by...???

%%%%%%%%%%%%%%%%%%
\subsection{Radio}
\label{sec:radio}
%%%%%%%%%%%%%%%%%%

Measurements of 1.4 GHz continuum radio flux for each source were
taken from the flux-limited NRAO VLA Sky Survey (NVSS,
\citealt{nvss}). In the case of NGC 1553, which is outside the NVSS
survey area, the 843 MHz continuum radio flux from the flux-limited
Sydney University Molonglo Sky Survey (SUMSS, \citealt{sumss1,
  sumss2}) was used. NVSS is complete down to $\approx 2.5$ mJy, while
SUMSS has a declination dependent completeness limit of $\approx 10$
mJy for $\delta > -50\degr$ and $\approx 6$ mJy for $\delta \leq
-50\degr$. The NVSS right ascension and declination positional
uncertainties for sources with flux $>$ 15 mJy are $\la 1''$ and
increases to $\approx 7''$ at the survey flux-limit \citep{nvss}. For
the comoving distances of our sample, the uncertainty in physical
distance on the sky is always $< 5$ kpc. For SUMSS, the positional
uncertainty is slightly larger but always less than 7 kpc. All fluxes
and uncertainties returned from the NVSS and SUMSS are deconvolved. We
calculate the monochromatic radio power for each source using the
relation $\radpow = 4 \pi D_L^2 (1+z)^{-1} S_{\nu} f_0$ where
$S_{\nu}$ is the NVSS or SUMSS flux, $D_L$ is the luminosity distance,
and $f_0$ is the central beam frequency of the radio
observations. Note that the monochromatic radio powers presented in
this paper are an approximation of the bolometric radio luminosity.

The morphologies of the radio sources associated with our sample of
gEs is heterogeneous, some sources are very large and extended, while
some sources are compact and point-like. Hence, to ensure the full
complex of a radio source was found, a fixed angular distance of
$1200\arcsec$ was searched around the X-ray centroid of each
target. The probability of finding a random radio source, for both
NVSS and SUMSS, within this aperture is unity. Thus, for each target
field, the detected radio sources were overlaid on a composite image
made of the X-ray emission as seen with \chandra, optical emission
(using DSS I/II\footnote{http://archive.stsci.edu/dss/}) and infrared
emission (using 2MASS\footnote{http://www.ipac.caltech.edu/2mass/})
within the target field. A visual inspection was then performed to
establish which detected radio sources were associated with the target
gE. The deeper and higher resolution radio data from VLA
FIRST\footnote{http://sundog.stsci.edu} was added to the visual
inspection, when available. After confirming which radio sources
within the search region were associated with the target gE, the
fluxes of the individual sources were then added and the associated
uncertainties summed in quadrature.

As an extension of the NVSS and SUMSS searches, we also reduced and
analyzed all relevant archival VLA data for each source in the
sample. As will be discussed in Section \S\ref{sec:r&d}, the purpose
of this additional step is to establish, albeit subjectively, which
sources can be considered jet dominated and which are not. In the
cases where high-resolution VLA archival data was available, we used
the reduced images as an additional diagnostic for confirming the
connection between what we considered to be the relevant detected NVSS
or SUMSS emission and the host gE. The fluxes measured from the VLA
archival data also served as a check of the fluxes measured taken from
NVSS or SUMSS. We found good agreement for most sources, the
exceptions being IC 4296, N1316, N1600 (which does not have any
archival VLA data), N3608 (which only has FIRST data), N4261, N4374,
and N4782.

\citet{birzan08} found that the \pcav-\pthree\ relation had lower
scatter than the \pcav-\phigh\ relation. For our final sample of
\samp\ gEs, the quality and availability of 327 MHz data was poor, and
thus we resorted to gathering low-frequency (200-400 MHz) radio fluxes
from the CATS Database\footnote{http://www.sao.ru/cats/}
\citep{cats}. The CATS Database is a compilation of over 350 radio
catalogs and serves as a useful clearinghouse for finding radio fluxes
across a broad frequency range without the need to query individual
catalogs. CATS was queried in the frequency range 200-400 MHz using
the list of radio source coordinates found from the NVSS search and a
very small search radius. This approach means that low-frequency radio
emission which does not have a 1.4 GHz counterpart is missed, but this
method also ensures that sources not associated with the radio source
are less likely to be found. Therefore, the 200-400 MHz radio powers
shown in Figure \ref{fig:pcav} may be slightly underestimated, but
given the range of radio powers shown, mobility in the \radpow\ plane
is very limited and our best-fit relations can thus be expected to
vary within the uncertainties of the fit. Of the \samp\ gEs in our
sample, 17 objects were found in the CATS database with fluxes in the
200-400 MHz range.

Both the high- and low-frequency radio data analysis presented in this
paper differs from the work of \citet{birzan08} in that they used
archival VLA data as the source for measuring fluxes for all their
sources. Thus, neither the level of uncertainty nor the flux limit in
\citet{birzan08} are uniform as a result of variation in observing
setups, while our use of NVSS and other catalogs results in more
uniform measurements. Nonetheless, given the large range of radio
powers, it is reasonable to assume that the differences in the
systematic uncertainties are negligible compared to the intrinsic and
statistical scatter.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and Discussion}
\label{sec:r&d}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The results from the X-ray and radio data analysis are shown in the
two plots of \pcav-\phigh\ and \pcav-\plow\ presented in Figure
\ref{fig:pcav}. For each set of cavities analyzed in the X-ray data, a
subjective grade of merit was assigned to each (shown as color coding
in Figure). Currently, there is no standard algorithm for detecting
cavities nor a widely used, rigorous method for determining the
precise morphology of cavities. We have used the subjective merit
grades for the purpose of distinguishing between which cavities are
obvious or dubious. The grading has been assigned as such: grade A
cavities are definitely associated with AGN activity and have
well-defined boundaries; grade B cavities are also definitely
associated with AGN activity, but lack well-defined boundaries; grade
C cavities have poorly-defined boundaries, and their connection to AGN
activity is suspect.

We have also defined a subset of objects which we term jet
dominated. This is also a subjective classification. Using archival
VLA radio data (see Section \S\ref{sec:radio}), if 50\% or more of the
radio flux from a source originates in the jets than the lobes, then
the source is deemed to be jet dominated. The subjective nature of the
classification arises in setting the boundary between what is a lobe
and what is a jet. It is worth noting that the jetted sources have
distinctly different morphologies, and that the cavities in these
jetted systems are more like channels. Most cavity systems are
associated with radio lobes and are found at distances many times the
AGN host galaxy's effective radius. However, for these jetted sources,
the cavities, or channels, are found at the base of the radio jets
where the X-ray gas density is high enough to yield the contrast
needed to detect the influence of the AGN on the galaxy's
environment. One may suspect this means that \pcav\ in these systems
is grossly underestimated, however, it is worth noting that the gas
pressure falls off quickly with radius in these systems, and that this
pressure fall off may be offset by gains in cavity volume. Hence, if
there are classic cavities at larger radii associated with the radio
lobes in these jetted systems, the calculated \pcav\ values would
change by factors of a few and not by orders of magnitude. For this
reason, jetted systems, while are included in the figures, are not
included in any of the fitting.

With the exception of the jet dominated sources, which cluster
together in a region which suggests the cavity power has been
underestimated given the radio power, it is clear from Figure
\ref{fig:pcav} that the power-law relation between cavity power and
monochromatic radio power is continuous over approximately 8 orders of
magnitude in radio power and 6 orders of magnitude in cavity power. To
determine the form of the power-law relation, we performed log-space
linear fits to the data in each frequency regime using the methods
encapsulated in bivariate correlated error and intrinsic scatter
(BCES). The orthogonal BCES regression method developed by
\citet{bces} takes in unequal measurement errors in both variables and
assumes the presence of intrinsic scatter. The uncertaintites are
calculated using 5000 bootstrap resampling trials and a random seed.

The size of the scatter in the data is quite large relative to the
size of the statistical uncertainties of the individual points,
suggesting that the intrinsic scatter in the \pcav-\prad\ relation
dominates (a point discussed further in Section
\S\ref{sec:sys}). Thus, after extensive testing with other methods
(\ie\ mpfit, linfit, fitexy), the BCES fitter was selected over other
methods because it has the advantages of incorporating an intrinsic
scatter term and the method is the least likely to underestimate the
uncertainties on the best-fit parameters. Both jet dominated and grade
C systems were excluded from the fitting.

Using the {\textsc{BCES}} fitting method, the best-fit linear function
in log-space for the \pcav-\phigh\ and \pcav-\plow\ relations are
\begin{eqnarray}
\log~\pcav &=& 0.67 (\pm 0.09)~\log~\phigh + 1.70 (\pm 0.18)\\
\log~\pcav &=& 0.65 (\pm 0.08)~\log~\plow + 1.32 (\pm 0.14).
\end{eqnarray}
The significant factor of two disprecpancy between the slopes of the
\pcav-\phigh\ ($m = 0.62$) and \pcav-\pthree\ ($m = 0.35$) relations
presented in \citet{birzan08} has disappeared and the similarity of
the relations found in this paper strongly suggests a universal
relationship between jet power and radio luminosity exists.

-- what is dominating the fits?\\

Considerable scatter in both relations is also evident in Figure
\ref{fig:pcav}. The scatter for each relation is \shigh\ = 1.05 dex
and \slow\ = 0.89 dex, and the respective correlation coefficients are
\rhigh\ = 0.73 and \rlow\ = 0.80. We have quantified log-space scatter
using the average size of the residuals about the best-fit
relation. As is discussed extensively in \citet{birzan04} and
\citet{birzan08}, the large scatter in the relation between jet power
and radio luminosity likely originates mostly from intrinsic
differences between the properties of the individual
systems. \citet{birzan08} also demonstrated that correcting for the
effect of radio aging reduces the scatter of the relations. Performing
a similar analysis for the sample presented here is beyond the scope
of this paper and we defer discussion to a forthcoming
letter. Additionally, as demonstrated with systems like Hydra A
\citep{hydraa} and MS 0735.6+7421 \citep{ms0735}, the energetics in a
system at any given time can be dominated by larger than average AGN
outbursts and the lingering effects thereof. This may be particularly
true for sysmtems with masses smaller than clusters, like gEs, which
have lower pressure gas halos and are arguably more susceptible to
being disrupted by the effects of an AGN outburst \citep{minggroups}.
The large scatter also highlights that radio luminosity is not an
ideal surrogate for determining the total mechnical energy which has
been, or will be, released via an AGN.

%%%%%%%%%%%%%%%%%%%%%
\section{Systematics}
\label{sec:sys}
%%%%%%%%%%%%%%%%%%%%%

Though the trend in jet power with radio power suggests a continuous,
universal relation exists from isolated giant ellipticals to the
largest brightest cluster galaxies in clusters, the relation has
considerable scatter and the samples presented in this paper and in
\citet{birzan04} were not statistically selected nor
representative. It is therefore useful to consider a few sources of
possible systematics or biases. Below we discuss how underestimating
\pcav\ affects our results and if one should worry about a possible
selection bias in the presented sample. We find that the influence of
systematics on our results are negligible given the large range of
\pcav\ and \prad\ covered.

As mentioned in Section \S\ref{sec:r&d}, the energetics of a system at
any given moment in time can be dominated by an AGN outburst, where
one channel of energy deposition is in cavities. Many other channels
of energy deposition may be important, for example shocks
\citep{ms0735, hydraa, herca, 2005ApJ...635..894F,
  2006MNRAS.371L..65S}, sound waves (\eg\ Perseus \citep{perseus3}),
or overpressured regions (\eg\ large volumes where $V dP$ is
non-negligible). In the limiting circumstance where the energy in
these other channels is of the order the cavity power -- or possibly
greater than the cavity power \citep{2006MNRAS.373..739N} -- then the
jet power will be underestimated. The extent to which these additional
energy channels alter the slope and normalization of the
\pcav-\prad\ relation is not obvious, but, using the well-studied
systems in the citations above as a guide, it is reasonable to assume
the corrections to the total jet power would only be significant in
the very rare cases like MS0735 where the shock energy is XXX times
the cavity energy. In which case the \pcav-\prad\ relation would not
significantly change. A strong scaling of shock energy or sound wave
energy with host system mass would also be another way of altering the
shape and normalization of the \pcav-\prad\ relation. As of now, there
is no observational evidence, nor literature, to suggest such a strong
effect exists.

There is also the issue of drawing the conclusion that a relation
between jet power and radio power is universal based upon samples
which are not statistically selected or representative. The systems
which were used in \citet{birzan04}, citet{birzan08}, and this paper
were obviously chosen because it is possible to measure \pcav,
\eg\ the samples are explicitly biased towards only systems with
cavities in their X-ray atmospheres. This raises the question: does
the scaling relation of $\pjet \propto \prad^{0.6}$ hold for
{\it{all}} systems? More succienctly, is there something special about
how AGN interact with an environment which makes a scaling relation
between mechanical power and radio power a function of the host
galaxy's surroundings? At the moment, we simply raise this question
for consideration, but do not offer an answer of our own.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Conclusions}
\label{sec:summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We have presented a sample of \samp\ giant elliptical galaxies
observed with the \cxo\ and which all have suspected AGN induced
cavity systems in the X-ray halo surrounding the host galaxy. Cavity
powers, \pcav, were calculated for each set of cavities using
adiabatic, isobaric assumptions and which are covered in detail in
\citet{birzan04} and \citet{mcnamrev}. Monochromatic radio powers at
1.4 GHz and between 200-400 MHz were also calculated using
measurements from the NVSS and SUMMS surveys, and the CATS database.
Each set of cavities was graded subjectively with a letter: `A', `B',
or `C,' with `A' being the most reliable cavities and `C' being the
least reliable. For the purposes of isolating those systems which may
not be representative of the true \pcav-\prad\ relation durnig
fitting, we also subjectively determined which of the gE systems were
``jet dominated'' by using jet and lobe fluxes taken from archival,
high-resolution VLA observations. If $\ge 50\%$ of the flux emerges
from the jets than the lobes, then the object was deemed a jet
dominated system.

After incorporating the galaxy cluster \pcav-\prad\ data from
\citep{birzan08}, we found a continuous power-law relation between
\pcav-\prad\ in both frequency regimes covering 6 decades in
\prad\ and 8 decades in \pcav (see Figure \ref{fig:pcav}). Using a
log-space BCES fit, we found similar forms for the
\pcav-\prad\ relations for the 1.4 GHz and 200-400 MHz data and thus
suggest a \birzan-Cavagnolo universal relation between jet power and
radio power with the form $\pcav \propto \prad^{0.6}$. This relation
comes with the caveat of being rife with cosmic scatter, $\approx 1.0$
dex in both parameters, and hence very loosely applicable in
determining the {\it{total}} energy output by an AGN.

Utility and consequences...?

%%%%%%%%%%%%%%%%%
\acknowledgements
%%%%%%%%%%%%%%%%%

KWC and BRM acknowledge generous support from the Canadian National
Science and Engineering Research Council (NSERC) grants
NSERC-**LIST**. The authors were supported in this work through
\chandra\ X-ray Observatory grants CXO-**LIST**. The \chandra\ X-ray
Observatory Center is operated by the Smithsonian Astrophysical
Observatory for and on behalf of NASA under contract NAS8-03060. The
National Radio Astronomy Observatory is a facility of the National
Science Foundation operated under cooperative agreement by Associated
Universities, Inc. This research has made use of software provided by
the Chandra X-ray Center in the application packages \ciao, \chips,
and \sherpa. This research has made use of the NASA/IPAC Extragalactic
Database which is operated by the Jet Propulsion Laboratory,
California Institute of Technology, under contract with NASA. This
research has also made use of NASA's Astrophysics Data System. Some
software was obtained from the High Energy Astrophysics Science
Archive Research Center, provided by NASA's Goddard Space Flight
Center.

%%%%%%%%%%%%%%
% Facilities %
%%%%%%%%%%%%%%

{\it Facilities:} \facility{CXO (ACIS)} \facility{VLA}

%%%%%%%%%%%%%%%%
% Bibliography %
%%%%%%%%%%%%%%%%

\bibliography{cavagnolo}

%%%%%%%%%%%%%%%%%%%%%%
% Figures  and Tables%
%%%%%%%%%%%%%%%%%%%%%%

\input{figs.tex}

%%%%%%%%%%%%%%%%%%%%
% End the document %
%%%%%%%%%%%%%%%%%%%%
\end{document}
