%%%%%%%%%%%%%%%%%%%
% Custom commands %
%%%%%%%%%%%%%%%%%%%

\newcommand{\birzan}{B\^irzan}
\newcommand{\samp}{21}
\newcommand{\phigh}{\ensuremath{P_{\mathrm{1.4}}}}
\newcommand{\pthree}{\ensuremath{P_{\mathrm{327}}}}
\newcommand{\plow}{\ensuremath{P_{\mathrm{200-400}}}}
\newcommand{\shigh}{\ensuremath{\sigma_{\mathrm{1.4}}}}
\newcommand{\sthree}{\ensuremath{\sigma_{\mathrm{327}}}}
\newcommand{\slow}{\ensuremath{\sigma_{\mathrm{200-400}}}}
\newcommand{\rhigh}{\ensuremath{r_{\mathrm{1.4}}}}
\newcommand{\rlow}{\ensuremath{r_{\mathrm{200-400}}}}
\newcommand{\mytitle}{A RELATIONSHIP BETWEEN AGN JET POWER AND RADIO POWER}
\newcommand{\mystitle}{AGN \pjet-\prad\ Relation}

%%%%%%%%%%
% Header %
%%%%%%%%%%

%\documentclass[12pt, preprint]{aastex}
%\documentclass{aastex}
\documentclass{emulateapj}
\usepackage{apjfonts,graphicx,here,common,longtable,ifthen,amsmath,amssymb,natbib}
\usepackage[pagebackref,
  pdftitle={\mytitle},
  pdfauthor={Dr. Kenneth W. Cavagnolo},
  pdfsubject={Astrophysical Journal},
  pdfkeywords={galaxies: active -- galaxies: clusters: general --
    X-rays: galaxies -- radio continuum: galaxies},
  pdfproducer={LaTeX with hyperref},
  pdfcreator={LaTeX with hyperref}
  pdfdisplaydoctitle=true,
  colorlinks=true,
  citecolor=blue,
  linkcolor=blue,
  urlcolor=blue]{hyperref}
\bibliographystyle{apj}
\begin{document}
\title{\mytitle}
\shorttitle{\mystitle}
\author{
K. Cavagnolo\altaffilmark{1,6},
B. McNamara\altaffilmark{1,2,3},
P. Nulsen\altaffilmark{3},\\
C. Carilli\altaffilmark{4},
C. Jones\altaffilmark{3},
\& L. \birzan\altaffilmark{5},
}
\altaffiltext{1}{Department of Physics and Astronomy, University of
  Waterloo, Waterloo, ON N2L 3G1, Canada.}
\altaffiltext{2}{Perimeter Institute for Theoretical Physics, 31
  Caroline Street N, Waterloo, ON N2L 2Y5, Canada.}
\altaffiltext{3}{Harvard-Smithsonian Center for Astrophysics, 60
  Garden Street, Cambridge, MA 01238, USA.}
\altaffiltext{4}{National Radio Astronomy Observatory, P.O. Box 0,
  Socorro, NM 87801-0387, USA.}
\altaffiltext{5}{Leiden Observatory, University of Leiden, P.O. 9513,
  2300 RA Leiden, The Netherlands}
\altaffiltext{6}{kcavagno@uwaterloo.ca}
\shortauthors{K. W. Cavagnolo et al.}
\journalinfo{}
\slugcomment{For submission to ApJ}

%%%%%%%%%%%%
% Abstract %
%%%%%%%%%%%%

\begin{abstract}
  Using X-ray data collected with the \cxo\ and multi-frequency VLA
  radio data, we investigate the scaling relationship between active
  galactic nucleus jet power, \pjet, and observed radio power,
  \prad. We sought to determine if the \pjet-\prad\ scaling relations
  presented in \citet{birzan08} for, primarily, brightest cluster
  galaxies (BCGs) are continuous in form and scatter from giant
  elliptical galaxies (gEs) up to BCGs. We expand the sample used in
  \citet{birzan08} to lower radio power by incorporating measurements
  for \samp\ gEs. Combining our results with those presented in
  \citet{birzan08}, we find a mean scaling relation of $\pjet \approx
  5.8 \times 10^{43} (\prad/10^{40})^{0.70} ~\lum$ with a scatter of
  $\approx 0.7$ dex. We briefly comment on the consistency of our
  results with theoretical models, specifically those of
  \citet{1979ApJ...232...34B} and \citet{1999MNRAS.309.1017W}. Our
  results are consistent with models for confined radio sources that
  are close to minimum energy density, with the ratio of lobe energy
  in neutralizing species to that in relativistic electrons of $\ga
  100$. Focusing on a sub-set of gEs with what we suspect are poorly
  confined radio sources, we discuss the importance of environment
  when measuring a \pjet-\prad\ relation, and a possible connection to
  the process of entrainment. A brief discussion of the implications
  and utility of our results for large-scale structure formation
  models is also included.
\end{abstract} 

%%%%%%%%%%%%
% Keywords %
%%%%%%%%%%%%

\keywords{galaxies: active -- galaxies: clusters: general -- X-rays:
  galaxies -- radio continuum: galaxies}

%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%

Observational evidence accumulated over the last decade indicates that
most galaxy bulges harbor a central supermassive black hole (SMBH).
It has been suggested that SMBHs co-evolved with the host galaxy,
giving rise to the well-known correlations between bulge luminosity,
stellar velocity dispersion, and central black hole mass
\citep{1995ARA&A..33..581K, magorrian, 2000ApJ...539L...9F,
  2000ApJ...539L..13G, marconihunt03, 2005MNRAS.362...25B}. Models
also suggest that these correlations were imprinted by co-evolution
through galaxy mergers and by the influence of feedback from active
galactic nuclei (AGN) \citep[\eg][]{1998A&A...331L...1S,
  2000MNRAS.311..576K}. Around the same time as these discoveries, the
\cxo\ \citep{chandra} found direct evidence for AGN feedback when
observations unambiguously revealed AGN induced cavities and shock
fronts in the X-ray emitting gas surrounding many massive galaxies
\citep[\eg][]{2000ApJ...534L.135M, perseus1, schindler01,
  2007ApJ...665.1057F, 2009ApJ...707.1034B}. Prior to \chandra, cavity
detections were difficult, and few cavity systems had been discovered
\citep{1981ApJ...248...47F, 1981ApJ...248...55B, perseus0,
  1994MNRAS.270..173C, 1998ApJ...493...73O, 1998ApJ...496..728H}.

It was recognized that X-ray cavities provide an unambiguous gauge of
the total mechanical energy and mean jet power produced by SMBHs
\citep{2000ApJ...534L.135M}. Jet powers, \pjet, are approximated using
estimates of cavity age and measurement of the $pV$ work done by an
AGN in excavating a cavity \citep[see][for reviews]{cfreview,
  mcnamrev}. It is important to note that cavity power, \pcav, is the
measured quantity and it is assumed to be a good estimate of the
physical quantity \pjet. Further, \pcav\ does not include the energy
which may go into shocks, which at times may exceed the energy in
cavities. Several detailed studies of cavities have shown that AGN
feedback supplies enough energy to regulate star formation and
suppress cooling of the hot halos of galaxies and clusters
\citep{birzan04, 2005MNRAS.364.1343D, rafferty06, dunn08, birzan08,
  2008ApJ...680..897D}. Likewise, the existence of correlations
between low core entropy, short central cooling time, cooling
luminosity, and \pjet\ indicate the presence of a finely-tuned
environmental feedback loop \citep[\ie][]{haradent,
  2008ApJ...687..899R, accept, 2009A&A...501..835M,
  2009MNRAS.395..764S}

The mounting observational evidence has changed our view of galaxy
formation. A consensus has emerged that AGN feedback plays an
important role in suppressing star formation in bulges at late
times. Including energetic feedback from AGN in numerical simulations
has been shown to bring the shape and normalization of the galaxy
luminosity function into better agreement with observations
\citep{croton06, bower06, saro06, sijacki07}. However, the details of
how AGN couple to their ambient environments remain poorly understood
\citep{2008ASPC..386..343D, 2009arXiv0910.3691M}. A long-standing
problem with extragalactic radio sources has been finding a method to
reliably measure their total mechanical output, which is central to
understanding AGN feedback \citep[\eg][]{1991Natur.349..138R,
  1996AJ....112....9L}.

Individual studies of X-ray cavities have yielded reliable constraints
on AGN energetics, ages, and radio lobe composition. But, the
systematic study of large samples of cavities has been restricted by
observational limitations such as the need for long exposure times and
high spatial resolution \citep{2009arXiv0909.0397B}. Therefore,
measuring and calibrating correlations between simple observables,
like AGN radio power (\prad), and jet power (\eg\ \pjet) in bright,
relatively nearby objects will enable more statistical studies of
feedback in galaxies, groups, and clusters that are beyond the grasp
of current X-ray instrumentation. A robust \pjet-\prad\ scaling
relation could then be applied to measurements from current and future
all-sky radio surveys (\eg\ NVSS, SUMSS, LOFAR, SKA) to study SMBH
formation history and subsequent AGN mechanical heating of the
Universe \citep{croton06, 2006MNRAS.366..397S}.

Observational relationships between \pjet\ and \prad\ for samples of,
primarily, BCGs were presented in \citet[][hereafter B04]{birzan04}
and \citet[][hereafter B08]{birzan08}. In B08, scaling relations
between \pjet\ and 327 MHz, 1.4 GHz, and bolometric radio luminosities
were presented. B08 showed that $\pjet \propto \prad^{0.5-0.7}$
depending on the choice of frequency. However, there are few objects
in the B08 study with $\prad \lesssim 10^{38} ~\lum$ and $\pjet
\lesssim 10^{43} ~\lum$, \ie\ the region generally populated by
low-power radio galaxies.

In this paper we extend the study of B08 with the inclusion of
\samp\ gEs from systems with lower X-ray luminosities than rich
clusters. Combining the B08 results and the results in this paper, we
find a relationship between jet power and radio power which is similar
at high and low radio frequencies. The relationships span 6-8 orders
of magnitude in \pjet\ and \prad, and have the general form $\pjet
\sim 10^{43} (\prad/10^{40})^{0.7} ~\lum$ with dominantly intrinsic
scatter of $\sim 0.7$ dex. We also find encouraging similarity between
our best-fit relations, previous studies, and theoretical AGN models.

This paper is structured as follows: \S\ref{sec:sample} outlines the
sample of selected gEs. X-ray and radio data reduction is discussed in
\S\ref{sec:data}. Results and discussion are presented in
\S\ref{sec:r&d}. The summary and concluding remarks are given in
\S\ref{sec:summary}. \LCDM\ All quoted uncertainties are 68\%
confidence.

%%%%%%%%%%%%%%%%%%
\section{Sample}
\label{sec:sample}
%%%%%%%%%%%%%%%%%%

Our sample of \samp\ gEs is taken from the sample of 160 gEs compiled
by Jones et al. \citetext{in preparation}. The B08 sample is taken
from \citet[][hereafter R06]{rafferty06}. Information regarding our gE
sample is listed in Table \ref{tab:sample}. The Jones et
al. compilation is drawn from the samples of
\citet{1999MNRAS.302..209B} and \citet{2003MNRAS.340.1375O} using the
criteria that the $K$-band luminosity is $> 10^{10}~\Lsol$ and the
object has been observed with \chandra. Of the 160 gEs, extended X-ray
emission was detected in 109 objects. AGN activity was suspected in 27
objects based solely on the presence of surface brightness depressions
in the X-ray emitting gas. We have further excluded dwarf galaxies
($M_V < -19.5$) from the sample since it is not clear that the
substructure in the X-ray gas is associated with an AGN, leaving
\samp\ objects. Most of the gEs studied here have X-ray halos and
radio sources with luminosities lower than are typically found for cDs
and BCGs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Observations and Data Analysis}
\label{sec:data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%
\subsection{X-ray}
\label{sec:xray}
%%%%%%%%%%%%%%%%%%

Outburst powers were determined in the usual manner from the X-ray
data (see B04 and R06). Gas properties used here are taken from the
analysis by Jones et al. (in preparation). Cavity locations and sizes
are from Nulsen et al. (in preparation), with cavity volumes and their
errors calculated by the method of B04. The enthalpy of each cavity
was determined as $H_{\mathrm{cav}} = [\gamma/(\gamma-1)] p V$, where
$p$ is the gas pressure at the radius of the projected center of the
cavity, $V$ is cavity volume, and $\gamma = 4/3$ is assumed for the
ratio of specific heat capacities within the cavities. To estimate the
average power of an outburst, the enthalpy of each cavity was divided
by an estimate of its age. For compatibility with B08, we give results
derived assuming the age of the cavities is approximated by the
buoyant rise time, $t_{\mathrm{buoy}}$. Models have suggested cavities
are well-described as buoyant bubbles \citep{2001ApJ...554..261C,
  2003ApJ...592..839B, 2009ApJ...694.1317O}. The cavity power
estimates were summed for all the cavities in each system to obtain an
estimate of the average outburst power of its AGN. Because the
uncertainties are large (chiefly due to the uncertain volume
estimates), errors are propagated in log space assuming that the
errors in the observable inputs $p$, $V$, and age are independent of
one another.

%%%%%%%%%%%%%%%%%%
\subsection{Radio}
\label{sec:radio}
%%%%%%%%%%%%%%%%%%

Radio powers were estimated using the relation $\nu_0 L_{\nu_0} = 4
\pi D_L^2 (1+z)^{\alpha-1} S_{\nu_0} \nu_0$, where $S_{\nu_0}$ is the
flux density at the observed frequency, $\nu_0$, over the integrated
area of the source, $z$ is redshift, $D_L$ is luminosity distance, and
$\alpha$ is radio spectral index. The radio powers estimated using
200-400 MHz and 1.4 GHz fluxes are denoted as \plow\ and \phigh,
respectively. The redshift dependent $\alpha$ correction in $\nu_0
L_{\nu_0}$ is small for our sample since the objects are nearby. We
have assumed the radio spectra behave as $S_{\nu} \propto
\nu^{-\alpha}$ with a spectral index of $\alpha = 0.8$, typical for
extragalactic radio galaxies \citep{1992ARA&A..30..575C}.

The 1.4 GHz continuum radio flux for each source was taken from the
flux-limited NRAO VLA Sky Survey (NVSS, \citealt{nvss}). For NGC 1553,
which lies outside the NVSS survey area, the 843 MHz continuum radio
flux was taken from the Sydney University Molonglo Sky Survey (SUMSS,
\citealt{sumss1, sumss2}). The 1.4 GHz flux for N1553 was estimated
using $\alpha = 0.89$, which was calculated from the 843 MHz SUMSS
flux and 5 GHz Parkes flux \citep{1970ApL.....5...29W}.

The radio morphologies for our sample are heterogeneous: some sources
are large and extended, while others are compact. To ensure the entire
radio source was measured, a fixed physical aperture of 1 Mpc was
searched around the X-ray centroid of each target. For each target
field, all detected radio sources were overlaid on a composite image
of X-ray, optical (DSS I/II\footnote{http://archive.stsci.edu/dss/}),
and infrared emission
(2MASS\footnote{http://www.ipac.caltech.edu/2mass/}). When available,
the deeper and higher resolution radio data from VLA
FIRST\footnote{http://sundog.stsci.edu} was included. A visual
inspection was then performed to establish which radio sources were
associated with the target gE. After confirming which radio sources
within the search region were associated with the target gE, the
fluxes of the individual sources were added and the associated
uncertainties summed in quadrature.

Archival VLA data for each source in the sample was also reduced and
analyzed. The continuum VLA data was reduced using a customized
version of the NRAO VLA Archive
Survey\footnote{http://www.aoc.nrao.edu/$\sim$vlbacald} reduction
pipeline. In the cases where high-resolution VLA archival data is
available, multifrequency images were used to confirm the connection
between NVSS detected radio sources and the host gE. Images at 1.4 GHz
were further used to check NVSS fluxes. We found flux agreement for
most sources, the exceptions being IC 4296 and NGC 4782, where the
NVSS flux is approximately a factor of 2 lower. These sources are
unique because the radio lobes contain significant power in diffuse,
extended emission which is not detected in NVSS. For these sources,
the fluxes measured from the archival VLA data are used in our
analysis. The additional data analysis step was also used to
investigate the poorly confined sources discussed in Section
\S\ref{sec:r&d}. For the systems where nuclear radio emission was
resolved, we found, on average $S_{\nu_0,\mathrm{nucleus}} /
S_{\nu_0,\mathrm{total}} \la 0.1$, suggesting the nuclear contribution
to the low-resolution NVSS measurements has a negligible impact on our
results.

B08 found that using lower frequency radio data, \ie\ 327 MHz versus
1400 MHz, resulted in a lower scatter \pjet-\prad\ relation. For our
sample of gEs, the quality and availability of 327 MHz data were not
ideal, and thus we gathered low-frequency radio fluxes from the CATS
Database\footnote{http://www.sao.ru/cats/} \citep{cats}. The CATS
Database is a compilation of more than 350 various radio catalogs
(\eg\ WENSS, WISH, TXS, B3). CATS was queried for low frequency
counterparts to the the NVSS and SUMMS sources. Fluxes in the
frequency range 200-400 MHz were then retrieved from the returned
lists. Of the \samp\ gEs in our sample, 17 of them were found to have
radio sources in the CATS database with measured fluxes in the 200-400
MHz range.

Our approach for searching CATS implies that objects with
low-frequency radio emission but without a higher frequency
counterpart will not be included in our sample. However, because CATS
does not provide images for visual inspection, and is composed of
catalogs having a wide variety of spatial resolutions and flux limits,
our method of using highly-restricted search areas was intended to
mitigate the inclusion of spurious sources. Therefore, the radio
powers shown in Figure \ref{fig:pcav} may not accurately estimate the
200-400 MHz fluxes for these gEs. However, because of the large range
of cavity and radio powers, a systematic shift by a factor of a few
along the \prad\ axis for all the gE points should not alter the
best-fit slope significantly, and would not change our overall
conclusions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and Discussion}
\label{sec:r&d}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\pjet-\prad\ Scaling Relation}
\label{sec:relation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The results from the X-ray and radio data analysis are shown in the
plots of \pcav-\phigh\ and \pcav-\plow\ presented in Figure
\ref{fig:pcav}. A subjective figure of merit (FM) was assigned to each
set of cavities -- shown as color coding in Figure \ref{fig:pcav} and
listed in Table \ref{tab:sample}. We assigned FMs because no automated
algorithm exists for detecting cavities and determining their
volumes. The FMs represent our qualitative visual assessment. FM-A
cavities are associated with AGN radio activity and have well-defined
boundaries; FM-B cavities are associated with AGN radio activity, but
lack well-defined boundaries; FM-C cavities have poorly-defined
boundaries, and their connection to AGN radio activity is
unclear. FM-C cavities are excluded from all fitting, as are a subset
of objects we have defined as being poorly confined and which are
discussed in Section \ref{sec:jet}.

Figure \ref{fig:pcav} shows a continuous power law relationship
between cavity power and radio power over approximately 8 orders of
magnitude in radio power and 6 orders of magnitude in cavity power. To
determine the form of the power-law relation, we performed linear fits
in log-space for each frequency regime using the bivariate correlated
error and intrinsic scatter (\bces) algorithm \citep{bces}. The
orthogonal \bces\ algorithm takes in asymmetric uncertainties for both
variables, assumes the presence of intrinsic scatter, and performs a
linear least-squares regression which minimizes the squared orthogonal
distance to the best-fit relation. This differs from the fitting
approach in B08 which minimized the distance in the
\pcav\ coordinate. The best-fit parameter uncertainties were
calculated using $10,000$ Monte Carlo bootstrap resampling trials.

The best-fit orthogonal \bces\ determined linear function in log-space
for the \pcav-\phigh\ and \pcav-\plow\ relations are:
\begin{eqnarray}
  \log~\pcav &=& 0.75~(\pm 0.14)~\log~\phigh + 1.91~(\pm 0.18) \label{eqn:high}\\
  \log~\pcav &=& 0.64~(\pm 0.09)~\log~\plow + 1.54~(\pm 0.12) \label{eqn:low}
\end{eqnarray}
where \pcav\ is in units $10^{42} ~\lum$, and \phigh\ and \plow\ are
in units $10^{40} ~\lum$. The scatter for each relation is $\shigh =
0.78$ dex and $\slow = 0.61$ dex, and the respective correlation
coefficients are \rhigh\ = 0.72 and \rlow\ = 0.81. We have quantified
the total scatter about the best-fit relation using a weighted
estimate of the orthogonal distances to the best-fit line
\citep[see][]{2009A&A...498..361P}. For comparison, the B08 scaling
relations are
\begin{eqnarray}
  \log~\pcav &=& 0.35~(\pm 0.07)~\log~\phigh + 1.85~(\pm 0.10) \\
  \log~\pcav &=& 0.51~(\pm 0.07)~\log~\pthree + 1.51~(\pm 0.12) \label{eqn:err}
\end{eqnarray}
where \pcav\ is in units $10^{42} ~\lum$, and \phigh\ and \pthree\ are
in units $10^{24}$ W Hz$^{-1}$ (or $\approx 10^{40} ~\lum$). The B08
relations have scatters of $\shigh = 0.85$ dex and $\sthree = 0.81$
dex. Equation 15 of B08 contains an error \citep{birzan08err} which is
corrected in Equation \ref{eqn:err} above.

In contrast to B08, the slopes of the relations in this work now agree
to within their uncertainties. Note that we find a steeper
relationship at 1.4 GHz than B08. This difference in slope at 1.4 GHz
between our work and B08 is due to the additional data points at lower
\pjet\ and the different fitting method. The B08 points tend to be
clumped in a fairly narrow power range, which gave the few points at
the upper and lower power extremes excessive leverage over the
slope. The new data extends to lower jet powers, giving a more uniform
sampling and a more robust measurement of the slope and zero point.

As a simple check, we point out two systems with accurate estimates of
AGN jet power: Cygnus A and Hercules A. For Cygnus A (point with
largest \phigh\ in Figure \ref{fig:pcav}), where our
\pjet-\prad\ relations appear to overestimate the jet power by a
factor of $\approx 40$, the total kinetic luminosity of $\sim 2 \times
10^{46} ~\lum$ calculated by \citet{2006ApJ...644L...9W} using the
shock is consistent with the \pjet\ value of $\sim 5 \times 10^{46}
~\lum$ predicted by our relations. Hercules A (which is not in the B08
sample) is a similar case to Cygnus A. With $\pcav = 310 \times
10^{42} ~\lum$ and $\phigh = 4100 \times 10^{40} ~\lum$, Hercules A
falls in the same region of Figure \ref{fig:pcav} as Cygnus A. But,
the total kinetic luminosity of $\sim 1.6 \times 10^{46} ~\lum$
calculated by \citet{herca} using the shock agrees with the prediction
from our relations, $\sim 3 \times 10^{46} ~\lum$.

The substantial scatter in the \pjet-\prad\ relations highlights that
radio power is an inaccurate surrogate for determining AGN power in
individual systems. As seen in systems like Hydra A \citep{hydraa} or
MS 0735.6+7421 \citep{ms0735}, the energetics can be dominated by the
effects of an AGN outburst which is more powerful than average. This
may be particularly true for gEs, which have lower pressure halos and
are more susceptible to disruption by AGN outbursts
\citep{2006MNRAS.372.1161W, 2008ApJ...687L..53P}. B08 showed that
correcting for the effect of radio aging by including a scaling with
break frequency does reduce the scatter within the relations, but by
only $\approx 50\%$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with Models and Observational Studies}
\label{sec:models}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A multitude of jet models can be found in the literature
\citep[\ie][]{1973MNRAS.164..243L, 1974MNRAS.166..513S,
  1974MNRAS.169..395B, 1987MNRAS.226..531G, 1989ApJ...345L..21B,
  2002ApJS..141..337C, 2002ApJS..141..371C}, and it is beyond the
scope of this paper to evaluate all of them. Therefore, we restrict
our focus to models which explicitly deal with correlations between
jet power and radio emission. We also examine earlier observational
studies of \pjet-\prad\ other than B08. In this section we use the
parameterization $\pjet = \eta \prad^{\Gamma}$, where \pjet\ is total
kinetic jet power, $\eta$ is some normalization, $\Gamma$ is a scaling
index, and \prad\ is emergent synchrotron power.

For flat-spectrum compact radio cores (\eg\ small scale jets and not
radio lobes), the jet model by \citet{1979ApJ...232...34B} predicts
$\Gamma = 12/17 ~(\approx 0.71)$. Starting with the
\citet{1979ApJ...232...34B} model, \citet{1995A&A...293..665F} found a
similar slope when assuming emergent jet power scales with accretion
power in a jet-disk system. The more general model for scale-invariant
jets by \citet{2003MNRAS.343L..59H} also predicts $\Gamma =
12/17$. \citet{2005ApJ...633..384H} undertook an observational study
using 5 GHz core powers and an estimate of $\pjet$ from the Galactic
X-ray binary mass-radio-X-ray fundamental plane relation
\citep{2003MNRAS.344...60G, 2003MNRAS.345.1057M}. Fixing $\Gamma =
12/17$, \citet{2005ApJ...633..384H} found $\eta \approx 6 \times
10^{44} ~\lum$ with \prad\ in units of $10^{40} ~\lum$.  Utilizing a
collection of objects from the R06 sample and 5 GHz core powers
corrected for relativistic Doppler boosting,
\citet{2007MNRAS.381..589M} found that $\Gamma = 0.81$ with $\eta
\approx 2 \times 10^{44} ~\lum$ with \prad\ in units of $10^{40}
~\lum$. The similarity of our relations with these models and studies
may be coincidental given that our measurements are for integrated
radio emission and not just nuclear radio emission.

\citet[][hereafter W99]{1999MNRAS.309.1017W} derive $\Gamma$ and
$\eta$ using the hypersonic jet model of \citet{1991MNRAS.250..581F}
and assuming the radio lobes are at minimum energy density
\citep[see][for details]{1980ARA&A..18..165M}. W99 derived $\Gamma =
6/7 ~(\approx 0.86)$ with $\eta \approx f^{3/2}~4.61 \times 10^{41}
~\lum$ when \prad\ is in units of $10^{40} ~\lum$. We have adjusted
the fiducial W99 normalization from 151 MHz to 1.4 GHz assuming
$S_{\nu} \propto \nu^{-0.8}$. The factor $f$ consolidates a variety of
unknowns (see W99 for details). The fiducial W99 model ($f=1$) yields
$\eta$ two orders of magnitude lower than our best-fit
normalizations. Because the W99 model has been widely used for
estimating jet power, the difference in $\eta$'s needs to be explored.

The W99 normalization has a weak dependence on ambient gas density.
Using observationally consistent shallower and lower density gas
profiles than those used to derive the fiducial W99 model results in
faster jet outflow velocities, which in turn increases $\eta$ by
factors of $\sim 2-5$. In addition, the W99 model has a critical
dependence on the fractional deviation from the minimum-energy
condition and $k$, which is the ratio of energy in neutralizing
species to relativistic electrons. We find that for $k$ lying in the
range of tens to hundreds, values consistent with observational
findings \citep{2005MNRAS.364.1343D, 2006MNRAS.372.1741D,
  2006ApJ...648..200D, birzan08}, the W99 normalization is brought
into agreement with our work. Figure \ref{fig:radeff} shows that the
W99 zero-point lies significantly below our best-fit
\pjet-\prad\ relations, but the slopes formally agree. W99 find that
to fit their model to narrow-line region luminosities (assuming
$L_{\mathrm{NLR}} \propto \pjet$) for sources in the 7C and 3CRR
surveys, $f$ must equal 20, which is the upper-limit of $f$ in their
model and implies $k \approx 20$. The apparent dependence on $k$ in
describing our results suggests environment, via processes like
entrainment, may be vital for understanding the properties of
large-scale radio sources. There is a sub-set of peculiar objects in
our sample which may be explained with this picture.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Poorly Confined Sources}
\label{sec:jet}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

It appears the X-ray data are not deep enough to define the extent of
the cavities for several objects in our sample: IC 4296
\citep{1988ApJ...324..198K, 2003ApJ...585..677P}, NGC 315
\citep{1979ApJ...228L...9B, 1981A&A....95..250W}, NGC 4261
\citep{1997ApJ...484..186J, 2000ApJ...534..165J}, NGC 4782
\citep{2007ApJ...664..804M}, and NGC 7626 \citep{1985ApJ...291...32B}.
For these objects, the X-ray surface brightness decrements are
reminiscent of tunnels rather than bubbles, and the radio morphologies
are distinctly different from the rest of the gE and B08
objects. X-ray cavities typically enclose the jet+lobe radio emission,
for example in M84 \citep{2001ApJ...547L.107F, 2008ApJ...686..911F}
where the interaction takes on some complexity (see Figure
\ref{fig:pics}). However, for this set of sources, the only indication
of gas excavation in the X-ray halo is found near the base of the
jets, seemingly at the ``edge'' of the X-ray halo (see Figure
\ref{fig:pics} for an example in NGC 4261). The appearance of
breaking-out from the X-ray halo is our reason for suggesting these
sources are poorly confined (PC). Because we do not have a robust
measurement of \pcav\ for the PC systems, they were excluded from the
preceding analysis of the \pjet-\prad\ relations.

The observed tunnels do not capture the total $p~dV$ work being done
by the jets. There may well be cavities which are not imaged extending
to larger radii and enclosing the radio lobes. But, for PC systems,
the ambient medium at those radii is too faint to yield a cavity
detection. To compare the properties of PC sources with the rest of
our sample, we calculated \pcav\ values for the PC systems assuming
radio lobe morphology approximates the volume of cavities potentially
at larger radii. Pressure profiles were extrapolated to large radii
using the best-fit parameters of a $\beta$-model \citep{betamodel} fit
to the surface brightness profile, assuming the ambient atmosphere is
isothermal, and adding a background gas pressure of $10^{-13}$ dyne
\pcmsq. The assumed background gas pressure is based on the mean value
observed in the outskirts of clusters and groups (see the
\accept\ database\footnote{http://www.pa.msu.edu/astro/MC2/accept} for
a catalog of such pressure profiles). For simplicity, cavity buoyancy
ages were calculated using a scaled version of the gas sound speed,
$t_{\mathrm{cs}} = 0.65 t_{\mathrm{buoy}}$, where 0.65 is the mean
value of the ratio $t_{\mathrm{cs}}/t_{\mathrm{buoy}}$ for the B04
sample. As a result of the radio lobes extending into regions where
the pressure profiles are very steep and approaching the background
pressure, the large volumes are offset by much lower pressures and
longer ages, resulting in modest values of \pcav.

Two of the PC sources, NGC 315 and NGC 4261, are part of a sample of
nine FR-I objects analyzed in detail by \citet[][hereafter
  C08]{2008MNRAS.386.1709C} using \xmm\ X-ray observations. Provided
in C08 are the $4pV$ enthalpies for each FR-I source (calculated using
the radio lobe volumes and the external thermal pressure at the lobe
mid-point), and the mean temperature of the group environments into
which the lobes are expanding. Assuming lobe inflation occurs at the
ambient gas sound speed, we calculated \pcav\ values for each of the
C08 FR-I sources again using scaled sound speed. For N315 and N4261 we
find no significant difference between the \pcav\ values calculated
using the \chandra\ data and the \xmm\ data from C08. Using the NVSS
search method outlined in Section \ref{sec:radio} we calculated
\phigh\ for each C08 FR-I source. Our PC objects and the C08 FR-I
objects are plotted in Figure \ref{fig:radeff}.

In Figure \ref{fig:radeff} we highlight the location of the PC sources
relative to our best-fit 1.4 GHz relation and the W99 relation. Figure
\ref{fig:radeff} shows that the PC and C08 FR-I sources reside well
below our best-fit relation. This discrepancy implies that these
sources have the lowest jet power per unit radio power of all objects
in the sample. One explanation is that these sources may have lower
$k$ values, possibly because there are intrinsic differences in radio
sources (light and heavy jets), or because confined jets are born
light and become heavy on large scales due to entrainment. Another
explanation is that that PC sources are systematically more powerful
than our measurements indicate due to energy being imparted to
shocks. On average, shock energy is a small correction to \pcav,
factor of a few in clusters \citep{mcnamrev}, but the frequency and
variety of AGN driven shocks is broad, ranging from strong (Mach $\ga
2$) -- Centaurus A, NGC 3801 \citep{2003ApJ...592..129K,
  2009MNRAS.395.1999C, 2007ApJ...660..191C} -- to weak (Mach $\la 2$)
-- 3C31, Cygnus A, Hydra A, Hercules A, M87, MS 0735.6+7421, NGC 4552,
NGC 4636, NGC 4782 \citep{2002MNRAS.336.1161L, 2006ApJ...644L...9W,
  hydraa, herca, 2007ApJ...665.1057F, ms0735, 2006ApJ...648..947M,
  2009ApJ...707.1034B, 2007ApJ...664..804M} -- to undetected -- 3C
186, 3C 388, NGC 6764 \citep{2008ApJ...684..811S, 2006ApJ...639..753K,
  2008ApJ...688..190C}. However, this explanation would require that
the fraction of jet power going into shocks is preferentially higher
for systems with relatively high implied radiative efficiencies
(\ie\ $\pjet/\prad < \eta$).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Conclusions}
\label{sec:summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We have presented analysis of the jet power versus radio power scaling
relation for the B08 sample and a sample of \samp\ giant elliptical
galaxies observed with the \cxo. Cavity powers were calculated for
each set of cavities using similar methods to those outlined in
R06. Radio powers for our sample were estimated using 1.4 GHz and
200-400 MHz fluxes taken from the NVSS/SUMSS surveys and the CATS
database, respectively.

We find a continuous power-law relation between \pjet-\prad\ covering
6 decades in \prad\ and 8 decades in \pjet\ (Figure
\ref{fig:pcav}). We find similar forms for the power laws describing
the \pjet-\prad\ trend with the mean form $\pjet \approx 5.8 \times
10^{43} (\prad/10^{40})^{0.70} ~\lum$, and a scatter about the fit of
$\approx 0.7$ dex. Our relations agree reasonably well with previous
observational studies and predictions from theoretical jet models.

Several groups have applied the \birzan\ scaling relations to study
the effects of AGN feedback on structure formation,
\eg\ \citet{best07} and \citet{2007MNRAS.379..260M}, with some groups
now suggesting that distributed low-power radio galaxies may dominate
heating of the intracluster medium,
\eg\ \citet{2009ApJ...705..854H}. Up to now, the available
observational results, which were primarily calibrated to high-power
radio sources, did not clearly indicate if a \pjet-\prad\ relation
would be continuous, or of comparable scatter, for lower power radio
sources. Assuming there is no redshift evolution of \pjet-\prad, our
relations suggest higher mass galaxies dominate over lower mass
galaxies in the process of mechanical heating within clusters. The
next step is to study the process of mechanical heating in a
cosmological context, \eg\ evaluating the contribution of mechanically
dominated AGN on the bolometric AGN luminosity function over cosmic
time \citep[\ie][]{2009MNRAS.395..518C}.

We discussed a subset of objects that we classified as being poorly
confined (PC) by their environments (Figure \ref{fig:radeff}). These
objects have \pjet/\prad\ ratios which are large relative to the rest
of our sample. In addition, PC sources reside in the same region of
the \pjet-\prad\ plane as the FR-I sources taken from C08. Possible
explanations for the nature of these sources may lie in the
long-standing effort to understand the connection between properties
of radio galaxies and their environment. Radio emission from lobes
depends on their composition, so that the large scatter in the
\pjet-\prad\ relationship may result from processes such as gas
entrainment and shocks. It seems likely that some of the scatter
arises as radio sources age, but it remains unclear what other factors
are important.

With tighter, self-consistent observational constraints on the
\pjet-\prad\ relation across several decades in both parameters, and
host system mass, the need to rely on theoretical models to relate jet
power to observed radio properties has weakened. With the aide of
\pjet-\prad\ and statistical populations of radio galaxies found from
monochromatic all-sky radio surveys, constraints on the kinetic
heating of the Universe over vast swathes of cosmic time can be made.
As a consequence, inferences can be drawn about AGN duty cycles, the
total accretion history of SMBHs, and the growth of SMBHs as a
function of redshift. Moreover, future AGN feedback models, when used
in simulations, must replicate the observed relations studied in this
work, possibly yielding a better understanding of the power plants
which underlie AGN activity.

%%%%%%%%%%%%%%%%%
\acknowledgements
%%%%%%%%%%%%%%%%%

KWC and BRM acknowledge generous support from the Natural Sciences and
Engineering Research Council of Canada and grants from the \cxo. CJ
thanks the Smithsonian Institution for generous support. PN thanks the
\cxo\ Center for supporting this work. KWC sincerely thanks Judith
Croston, David Rafferty, and Chris Willott for helpful insight. The
\cxo\ Center is operated by the Smithsonian Astrophysical Observatory
for and on behalf of NASA under contract NAS8-03060. The National
Radio Astronomy Observatory is a facility of the National Science
Foundation operated under cooperative agreement by Associated
Universities, Inc. This research has made use of software provided by
the \chandra\ X-ray Center, the NASA/IPAC Extragalactic Database
operated by the California Institute of Technology Jet Propulsion
Laboratory, and NASA's Astrophysics Data System. Some software was
obtained from the High Energy Astrophysics Science Archive Research
Center, provided by NASA's Goddard Space Flight Center.

%%%%%%%%%%%%%%
% Facilities %
%%%%%%%%%%%%%%

{\it Facilities:} \facility{CXO (ACIS)} \facility{VLA}

%%%%%%%%%%%%%%%%
% Bibliography %
%%%%%%%%%%%%%%%%

\bibliography{cavagnolo}

%%%%%%%%%%%%%%%%%%%%%%
% Figures  and Tables%
%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\input{sample.tex}
\input{figs.tex}

%%%%%%%%%%%%%%%%%%%%
% End the document %
%%%%%%%%%%%%%%%%%%%%
\end{document}

% LocalWords:  PN
