%%%%%%%%%%%%%%%%%%%
% Custom commands %
%%%%%%%%%%%%%%%%%%%

\newcommand{\birzan}{B\^irzan}
\newcommand{\mytitle}{A Relationship Between AGN Jet Power and Radio Luminosity}
\newcommand{\samp}{21}
\newcommand{\ecav}{\ensuremath{E_{cav}}}
\newcommand{\pjet}{\ensuremath{P_{jet}}}
\newcommand{\pcav}{\ensuremath{P_{cav}}}
\newcommand{\prad}{\ensuremath{P_{radio}}}
\newcommand{\phigh}{\ensuremath{P_{\mathrm{1.4}}}}
\newcommand{\pthree}{\ensuremath{P_{\mathrm{327}}}}
\newcommand{\plow}{\ensuremath{P_{\mathrm{200-400}}}}
\newcommand{\shigh}{\ensuremath{\sigma_{\mathrm{1.4}}}}
\newcommand{\sthree}{\ensuremath{\sigma_{\mathrm{327}}}}
\newcommand{\slow}{\ensuremath{\sigma_{\mathrm{200-400}}}}
\newcommand{\srad}{\ensuremath{\sigma_{rad}}}
\newcommand{\rhigh}{\ensuremath{r_{\mathrm{1.4}}}}
\newcommand{\rlow}{\ensuremath{r_{\mathrm{200-400}}}}

%%%%%%%%%%
% Header %
%%%%%%%%%%

%\documentclass[12pt, preprint]{aastex}
%\documentclass{aastex}
\documentclass{emulateapj}
\usepackage{apjfonts,graphicx,here,common,longtable,ifthen,amsmath,amssymb,natbib}
\usepackage[pagebackref,
 pdftitle={\mytitle},
 pdfauthor={Kenneth W. Cavagnolo},
 pdfsubject={ApJ},
 pdfkeywords={},
 pdfproducer={LaTeX with hyperref},
 pdfcreator={LaTeX}
 pdfdisplaydoctitle=true,
 colorlinks=true,
 citecolor=blue,
 linkcolor=blue,
 urlcolor=blue]{hyperref}
\bibliographystyle{apj}
\begin{document}
\title{\mytitle}
\shorttitle{AGN Scaling Relations for Giant Ellipticals}
\author{
K. W. Cavagnolo\altaffilmark{1,7},
B. R. McNamara\altaffilmark{1,2,3},
P. E. J. Nulsen\altaffilmark{3},\\
C. L. Carilli\altaffilmark{4},
C. Jones\altaffilmark{3},
W. Forman\altaffilmark{3},\\
L. \birzan\altaffilmark{5,6}, \&
S. Murray\altaffilmark{3}
}
\altaffiltext{1}{Department of Physics and Astronomy, University of
  Waterloo, Waterloo, ON N2L 3G1, Canada.}
\altaffiltext{2}{Perimeter Institute for Theoretical Physics, 31
  Caroline Street N, Waterloo, ON N2L 2Y5, Canada.}
\altaffiltext{3}{Harvard-Smithsonian Center for Astrophysics, 60
  Garden Street, Cambridge, MA 01238, USA.}
\altaffiltext{4}{National Radio Astronomy Observatory, P.O. Box 0,
  Socorro, NM 87801-0387, USA.}
\altaffiltext{5}{Department of Astronomy and Astrophysics,
  Pennsylvania State University, 525 Davey Lab, University Park, PA
  16802, USA.}
\altaffiltext{6}{Astronomical Institute Anton Pannekoek, University of
  Amsterdam, Kruislaan 403, 1098 SJ Amsterdam, Netherlands.}
\altaffiltext{7}{kcavagno@uwaterloo.ca}
\shortauthors{K. W. Cavagnolo et al.}
\journalinfo{}
\slugcomment{For submission to ApJ}

%%%%%%%%%%%%
% Abstract %
%%%%%%%%%%%%

\begin{abstract}
Using X-ray data collected with the \chandra\ X-ray Observatory and
multi-frequency VLA radio data, we investigate the scaling
relationship between active galactic nuclei (AGN) jet power (\pjet)
and radio power (\prad). The goal of our study is to determine if the
\pjet-\prad\ scaling relation found by \citet{birzan04} for brightest
cluster galaxies (BCGs) is continuous, both in functional form and
intrinsic scatter, from isolated giant elliptical (gE) galaxies up to
BCGs. We expand the sample presented in \citet{birzan04} to much lower
mass scales by incorporating measurements for \samp\ relatively
isolated gEs. Combining the results presented in this paper with the
results from \citet{birzan04, birzan08}, we find a common scaling
relation of $\pjet \propto \prad^{0.6}$ with a scatter of $\approx
1.0$ dex using monochromatic radio powers at 200-400 MHz and 1.4
GHz. We discuss the utility and broader consequences of a universal
relation between jet power and radio luminosity as it pertains to AGN
feedback and the growth of black holes.
\end{abstract} 

%%%%%%%%%%%%
% Keywords %
%%%%%%%%%%%%

\keywords{galaxies: active -- galaxies: clusters: general -- X-rays:
  galaxies -- radio continuum: galaxies}

%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%

--Add \citet{2008ApJ...680..897D} as ref for connection between x-ray
lum and radio lum.\\

The astrophysical influence of energy deposition into an environment
hosting a supermassive black hole (SMBH), on physical scales varying
from sub-pc to Mpc, has been under intense observational and
theoretical study for decades \citep[\eg][]{1969Natur.223..690L,
  1974MNRAS.166..513S, cowie77, 1981ApJ...248...55B,
  1982MNRAS.199..883B, 1982MNRAS.200..115S, 1984ARA&A..22..471R,
  burns90, kaiser91, 1993MNRAS.263..323T, 1995MNRAS.276..663B,
  1997MNRAS.288..355B, magorrian, 1998A&A...331L...1S,
  2000ApJ...534L.135M, voitbryan, best05, haradent}. More
specifically, the role of the energy returned to an environment via
relativistic jets emerging from an AGN (the result of a SMBH accreting
matter) is now understood to be a very important mode of feedback
which aides in shaping the galaxy luminosity function \citep{croton06,
  bower06, saro06, sijacki07}. Moreover, better models and
observations of the AGN feedback process are proving to be important
in furthering our understanding of the formation and evolution of
large-scale structure, such as galaxy clusters and groups \citep[see,
  for example,][]{2008MNRAS.386.1309M, minggroups}. But understanding
the details of how AGN feedback is coupled to heating an environment
are still hotly debated.

Recent observational advances in studying AGN feedback have come
courtesy of the high-resolution optics of the
\cxo. \chandra\ observations have unambiguously revealed the direct
interaction between AGN jets and the X-ray emitting gas in which many
massive AGN host galaxies reside \citep[\eg][]{2000ApJ...534L.135M,
  perseus1, schindler01}. The presence of cavities (or ``bubbles'')
presented a new pathway to study the properties of SMBHs and AGN, and
have aided in furthering the understanding of the influence of AGN
feedback on galaxy and structure formation. X-ray images of cavities
are used to approximate the jet power required to create the cavities
by calculating enthalpy from measurements of the $pV$ work necessary
to inflate a cavity. Cavities contain a substantial amount of energy,
$10^{54}-10^{62}$ erg, and usually the cavity energy is comparable to,
or exceeds, the energy radiated away by the environment with which the
AGN has interacted \citep{birzan04, rafferty06}, though this is not
the case for all systems \citep{dunn08}. The energy transported out by
AGN jets is a viable source for the heat necessary to impact galaxy
and structure formation.

Energy released in an AGN is not confined to just jets, but is also
released in shocks, radiation, and powerful winds. In this sense then,
jet powers estimated from X-ray observations are lower-limits to the
total AGN energy output. In addition, bubble morphology, projection
effects, and the definition of the bubbles boundaries all affect the
enthalpy measurement. Thus, it is reasonable to ask if jet powers
estimated from X-ray observations are representative of the total AGN
energy output. Using mock X-ray observations generated from 3-D
magnetohydrodynamic simulations in conjunction with the widely
accepted methodology of measuring jet power,
\citet{2009arXiv0909.0722M} have demonstrated that the jet powers
estimated from the mock observations were overestimated by
approximately a factor of two with respect to the true jet powers
measured directly from the simulations. The close agreement suggests
that the observational techniques currently used are reliable.

The method of measuring jet powers using X-ray cavities is presently
comparable to that of a ``cottage industry.'' By moving beyond
analysis of individual systems to analyzing samples of cavities over
large ranges in host system mass, environment, and redshift, we may be
able to develop a better understanding of AGN feedback and its
importance in shaping the present and past of galaxy
formation. However, selecting a representative or statistically
significant sample of cavity-bearing systems is non-trivial, and
arguably not possible. This is primarily because the study of X-ray
cavities is limited by the ability and capacity of the current
generation of X-ray telescopes to obtain data of the quality necessary
to resolve cavities. Cavities come in a wide variety of sizes,
morphologies, distances from the AGN host galaxy, and projections on
the sky. These factors, combined with observing constraints, mean that
even in a sample specifically selected to find cavities, a cavity
system may go undetected. Thus, without the leverage of a large
statistical study to draw upon, it behooves observers and theorists
alike to find relationships between simple observables and AGN
energetics.

By quantifying and calibrating how cavity properties scale with
readily available AGN observables, then it becomes possible to
circumvent the need to undertake deep X-ray observing programs. This
can be accomplished if, for example, there exists a universal scaling
relationship between jet power and the radio emission associated with
those jets. A very simple quantity which has been used in previous
investigations is the monochromatic radio power, \prad. A universal
\pjet-\prad\ scaling relation could then be applied to measurements
from all-sky radio surveys, thereby installing the more readily
available radio observations as a surrogate for jet power
\citep{croton06, 2006MNRAS.366..397S}.

An observationally established relationship between jet power and
radio power was first determined by \citet{birzan04, birzan08} using a
sample of galaxy clusters. \citet{birzan08}, focused on three radio
frequency regimes, 327 MHz (\pthree), 1.4 GHz (\phigh), and bolometric
radio luminosity (\prad), and found functional forms of
\begin{eqnarray}
\pjet &\propto& \pthree^{0.62 \pm 0.08}\\
\pjet &\propto& \phigh^{0.35 \pm 0.07}\\
\pjet &\propto& \prad^{0.48 \pm 0.07}
\end{eqnarray}
with scatters of $\sthree = 0.65$ dex, $\shigh = 0.69$ dex, and $\srad
= 0.85$ dex. Several groups have since applied the \birzan\ relation
to study the effects of feedback from elliptical galaxies, most
notably \citet{best07}, \citet{2007MNRAS.379..260M}, and
\citet{2009arXiv0908.3158H}. However, up to now, no observational
evidence has suggested that the \pjet-\prad\ relation which holds for
galaxy clusters is continuous, of comparable scatter, or applicable
for much lower mass systems such as ellipticals.

To address this disparity, the work presented in this paper
investigates the relationships \pjet-\phigh\ and \pjet-\plow\ (see
Section \S\ref{sec:radio}) for a sample of relatively isolated giant
elliptical galaxies, thus extending the work of \citet{birzan08} to
AGN host system masses orders of magnitude smaller than the BCGs
studied in their work. By combining the results from \citet{birzan08}
and the results in this paper, we show a similar relationship between
jet power and radio power in both high and low frequency radio
domains. The relationships span 6-8 orders of magnitude in \pjet\ and
\prad, and have the general form $\pjet \propto \prad^{0.6}$ with
large, dominantly intrinsic scatter of $\sigma \propto 1.0$ dex. Our
results suggest that a universal relationship between AGN jet power
and radio power exists.

The structure of this paper is as follows: In \S\ref{sec:sample} we
outline initial sample selection criteria and information about the
\chandra\ observations selected under these criteria. X-ray and radio
data reduction is discussed in \S\ref{sec:data}. Results and
discussion are presented in \S\ref{sec:r&d}. A brief summary is given
in \S\ref{sec:summary}. \LCDM\ All quoted uncertainties are 68\%
confidence. Hereafter, the terminology ``cavity power'' and ``jet
power'' are used interchangeably, and are denoted as \pcav\ and \pjet,
respectively.

%%%%%%%%%%%%%%%%%%
\section{Sample}
\label{sec:sample}
%%%%%%%%%%%%%%%%%%

Our sample of \samp\ gEs are taken from the larger sample of 160 gEs
compiled by \citet{jonesge}. The \citet{jonesge} compilation is drawn
from the samples of \citet{1999MNRAS.302..209B} and
\citet{2003MNRAS.340.1375O} using the criteria that $L_K >
10^{10}~\Lsol$ and the object has been observed with \chandra. Of the
160 gEs, extended X-ray emission was detected in 109 objects. AGN
activity was suspected in 27 objects based solely on the presence of
surface brightness depressions in the X-ray emitting gas. We have
further excluded dwarf galaxies ($M_V < -19.5$) from the sample since
it is not clear that the substructure in the X-ray gas is associated
with an AGN, leaving \samp\ objects. The \samp\ gEs in our sample are
in relatively low density environments, meaning these are not the
central dominant or brightest galaxies in clusters or groups. The
X-ray emission associated with the gEs in our sample is dominated by
the gas gravitationally bound to the gE halo and not a diffuse
atmosphere of some larger environment. The sample we present here is
clearly incomplete, and we defer discussion of possible selection
biases to Section \S\ref{sec:r&d}. The comoving distance range of our
sample is 0.4-117 Mpc, with an X-ray luminosity range of $\sim
10^{31}-10^{36} \lum$. General properties of the sample are listed in
Table \ref{tab:sample}.

\input{sample.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Observations and Data Analysis}
\label{sec:data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\citet{birzan08} used 1.4 GHz and 327 MHz monochromatic radio powers
in their comparison with X-ray cavity powers to establish the scaling
relations discussed in Section \S\ref{sec:intro}. To ensure a reliable
comparison between the results presented here and those of
\citet{birzan08}, we also focus on monochromatic radio fluxes at 1.4
GHz. At lower frequencies, we use the frequency range 200-400 MHz
since 327 MHz observations were not available for most systems. Our
methodologies for calculating the cavity and radio powers for each
system are presented below.

%%%%%%%%%%%%%%%%%%
\subsection{X-ray}
\label{sec:xray}
%%%%%%%%%%%%%%%%%%

More extensive details of the X-ray data reduction and analysis will
be presented in \citet{nulsen09}. All data used in measuring the X-ray
cavity powers was taken with the \cxo. All datasets were analyzed
using the Chandra Interactive Analysis of Observations (\ciao)
software version XXX with the calibrations of \caldb\ XXX. The level 1
events files were reprocessed to apply the most current gain and
correct for charge transfer inefficiency. Additionally, the events
lists were filtered for bad grades, and cosmic rays were further
rejected by using VFAINT filtering when possible. Time periods
contaminated by background flaring were excluded from the data. Point
sources were detected and removed from the observations using the
output of the routine {\textsc{wavdetect}}. For the X-ray spectral
analysis a low-energy cut-off of 0.7 keV was used in addition to a
high-energy cut-off of 7.0 keV. Background spectral analysis was
performed using the \caldb\ blank-sky observations included in the
CALDB and tailored to match each targeted observation.

Measurement of cavity powers is performed identically to
\citet{rafferty06}. For each observation, azimuthally averaged
deprojected gas density and temperature profiles were used to
calculate the total gas pressure at each radius. Then, using cavity
volumes determined by-eye, the total energy contained in each cavity
is estimated as $\ecav = pV[\gamma/(\gamma-1)]$ where we assume
$\gamma = 4/3$. The total cavity energy is then divided by an estimate
of the sound crossing timescale for the associated AGN outburst,
yielding $\pcav = \ecav/t_{sonic}$ (see \citet{mcnamrev} for a
thorough discussion of how timescales are estimated). Uncertainties
for each calculation were determined by propogating errors and summing
in quadrature.

%%%%%%%%%%%%%%%%%%
\subsection{Radio}
\label{sec:radio}
%%%%%%%%%%%%%%%%%%

%% NVSS is complete down to $\approx 2.5$ mJy, while SUMSS has a
%% declination dependent completeness limit of $\approx 10$ mJy for
%% $\delta > -50\degr$ and $\approx 6$ mJy for $\delta \leq
%% -50\degr$. The NVSS right ascension and declination positional
%% uncertainties for sources with flux $>$ 15 mJy are $\la 1''$ and
%% increases to $\approx 7''$ at the survey flux-limit \citep{nvss}.

The 1.4 GHz continuum radio flux for each source was taken from the
flux-limited NRAO VLA Sky Survey (NVSS, \citealt{nvss}). For NGC 1553,
which is outside the NVSS survey area, the 843 MHz continuum radio
flux was taken from the flux-limited Sydney University Molonglo Sky
Survey (SUMSS, \citealt{sumss1, sumss2}). For the comoving distances
of our sample, the uncertainty in physical distance on the sky is
always $< 5$ kpc. For SUMSS, the positional uncertainty is slightly
larger but always less than 7 kpc. All fluxes and uncertainties
returned from the NVSS and SUMSS are deconvolved. We calculate the
monochromatic radio power for each source using the relation $\radpow
= 4 \pi D_L^2 (1+z)^{-1} S_{\nu} f_0$ where $S_{\nu}$ is the NVSS or
SUMSS flux, $D_L$ is the luminosity distance, and $f_0$ is the central
beam frequency of the radio observations.

The morphologies of the radio sources associated with our sample of
gEs is heterogeneous, some sources are very large and extended, while
some sources are compact and point-like. To ensure the entire radio
source was measured, a fixed angular distance of $1200\arcsec$ was
searched around the X-ray centroid of each target. The probability of
finding a background source, for both NVSS and SUMSS, within this
aperture is unity. Thus, for each target field, the detected radio
sources were overlaid on a composite image made of the X-ray emission
as seen with \chandra, optical emission (using DSS
I/II\footnote{http://archive.stsci.edu/dss/}) and infrared emission
(using 2MASS\footnote{http://www.ipac.caltech.edu/2mass/}). A visual
inspection was then performed to establish which detected radio
sources were associated with the target gE. When available, the deeper
and higher resolution radio data from VLA
FIRST\footnote{http://sundog.stsci.edu} was added to the visual
inspection. After confirming which radio sources within the search
region were associated with the target gE, the fluxes of the
individual sources were added and the associated uncertainties summed
in quadrature.

As an extension of the NVSS and SUMSS searches, we also reduced and
analyzed archival VLA data for each source in the sample. As will be
discussed in Section \S\ref{sec:r&d}, the purpose of this additional
step is to establish which sources are jet dominated and which are
not. In the cases where high-resolution VLA archival data is
available, we used the reduced images as an additional diagnostic for
confirming the connection between what we considered to be the
relevant detected NVSS or SUMSS emission and the host gE. The fluxes
measured from the VLA archival data also served as a check of the
fluxes measured taken from NVSS or SUMSS. We found good agreement for
most sources, the exceptions being IC 4296 and NGC 4782. These sources
are unique because the radio lobes contain non-negligible power in
diffuse, extended emission which is not detected in NVSS. For these
sources, the fluxes measured from the archival VLA data are used.

\citet{birzan08} found that the \pcav-\pthree\ relation had lower
scatter than the \pcav-\phigh\ relation. For our sample of gEs, the
quality and availability of 327 MHz data were poor, and thus we
resorted to gathering low-frequency (200-400 MHz) radio fluxes from
the CATS Database\footnote{http://www.sao.ru/cats/} \citep{cats}. The
CATS Database is a compilation of over 350 radio catalogs and was
queried in the frequency range 200-400 MHz using the list of radio
source coordinates found from the NVSS and SUMSS searches. This
approach means that low-frequency radio emission which does not have a
1.4 GHz counterpart is missed, but this method also ensures that
background sources are less likely to be found. Therefore, the 200-400
MHz radio powers shown in Figure \ref{fig:pcav} may be slightly
underestimated, but given the range of radio powers shown, mobility in
the \radpow\ plane is very limited, and our best-fit relations can
thus be expected to vary within the uncertainties of the fit. Of the
\samp\ gEs in our sample, 17 objects were found in the CATS database
with fluxes in the 200-400 MHz range.

%% Both the high- and low-frequency radio data analysis presented in this
%% paper differs from the work of \citet{birzan08} in that they used
%% archival VLA data as the source for measuring fluxes for all their
%% sources. Thus, neither the level of uncertainty nor the flux limit in
%% \citet{birzan08} are uniform as a result of variation in observing
%% setups, while our use of NVSS and other catalogs results in more
%% uniform measurements. Nonetheless, given the large range of radio
%% powers, it is reasonable to assume that the differences in the
%% systematic uncertainties are negligible compared to the intrinsic and
%% statistical scatter.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and Discussion}
\label{sec:r&d}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\pjet-\prad\ Scaling Relation}
\label{sec:relation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The results from the X-ray and radio data analysis are shown in the
two plots of \pcav-\phigh\ and \pcav-\plow\ presented in Figure
\ref{fig:pcav}. For each set of cavities, a subjective grade of merit
was assigned to each (shown as color coding in Figure
\ref{fig:pcav}). We assigned merit grades because, currently, no
standard algorithm for detecting cavities and determining cavity
morphology exists, and the grades quantify our by-eye
assessment. Grade A cavities are decidedly associated with AGN radio
activity and have well-defined boundaries; grade B cavities are also
decidedly associated with AGN radio activity, but lack well-defined
boundaries; grade C cavities have poorly-defined boundaries, and their
connection to AGN radio activity is questionable. Grade C cavities are
excluded from all fitting.

With the exception of the jet dominated sources (which are not
included in the fitting, see Section \ref{sec:jet}), it is clear from
Figure \ref{fig:pcav} that the relationship between cavity power and
monochromatic radio power is continuous over approximately 8 orders of
magnitude in radio power and 6 orders of magnitude in cavity power. To
determine the form of the power-law relation, we performed log-space
linear fits to the data in each frequency regime using the methods
encapsulated in bivariate correlated error and intrinsic scatter
\citet[BCES][]{bces}. The orthogonal BCES regression method takes in
asymmetric uncertainties for both variables and assumes the presence
of intrinsic scatter and performs a linear least-squares
regression. The best-fit parameter uncertainties are calculated using
5000 Monte Carlo bootstrap resampling trials.

The magnitude of the scatter in the data is large relative to the size
of the statistical uncertainties for the individual points, suggesting
that the intrinsic scatter in the \pcav-\prad\ relation dominates (a
point discussed further in Section \S\ref{sec:sys}). So while we
assumed BCES was the best fitting method, extensive testing with other
fitting methods (\ie\ Craig Markwardt's mpfit, IDL's linfit and
fitexy) was performed using synthetic idealized data. The BCES fitter
proved to be the best fitting method for our data because the addition
of an intrinsic scatter term into the fitting produces uncertainties
which are least likely to underestimate the 90\% confidence intervals
of the true underlying relationship.

The best-fit linear function in log-space output by the
{\textsc{BCES}} fitting method for the \pcav-\phigh\ and
\pcav-\plow\ relations are:
\begin{eqnarray}
\log~\pcav &=& 0.70~(\pm 0.10)~\log~\phigh + 1.69~(\pm 0.18)\\
\log~\pcav &=& 0.67~(\pm 0.08)~\log~\plow + 1.30~(\pm 0.14).
\end{eqnarray}
The analogous relations presented in \citet{birzan08} have power-law
indices which significantly differ from each other by a factor of two:
$m = 0.62 \pm 0.08$ for \pcav-\pthree\ and $m = 0.35 \pm 0.07$ for
\pcav-\phigh. With the inclusion of the new gE dataset, it is clear
that the discrepancy arose from undersampling. The similarity of the
power-laws for both frequency regimes is encouraging, it strongly
suggests an underlying universal relationship between jet power and
radio luminosity.

The scatter for each relation is \shigh\ = 1.07 dex and \slow\ = 0.88
dex, and the respective correlation coefficients are \rhigh\ = 0.74
and \rlow\ = 0.81. We have quantified log-space scatter using the
average size of the residuals about the best-fit relation. As is
discussed extensively in \citet{birzan04} and \citet{birzan08}, the
large scatter in the relation between jet power and radio luminosity
likely originates mostly from intrinsic differences between the
properties of the individual systems. \citet{birzan08} also
demonstrated that correcting for the effect of radio aging reduces the
scatter of the relations. Additionally, as demonstrated with systems
like Hydra A \citep{hydraa} and MS 0735.6+7421 \citep{ms0735,
  2009ApJ...698..594M}, the energetics in a system at any given time
can be dominated by larger than average AGN outbursts. This may be
particularly true for gEs, which have lower pressure halos and are
more susceptible to disruption by AGN outbursts \citep{minggroups}.
The large scatter also highlights that radio luminosity is a poor
surrogate for determining the total energy released via an AGN.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Jet Dominated Sources}
\label{sec:jet}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In Figure \ref{fig:pcav} some points are enclosed in an open circle,
these are a subset of systems we have defined as jet dominated. Using
archival VLA radio data (see Section \S\ref{sec:radio}), if 50\% or
more of the radio flux from a source originates in the jets than the
lobes, then the source is deemed jet dominated. The subjective nature
of the classification arises in setting the boundary between what is
the lobe and what is the jet. The objects we have identified as jetted
are: IC 4296 \citep{2003ApJ...585..677P}, NGC 315
\citep{1979ApJ...228L...9B, 1981A&A....95..250W}, NGC 4261
\citep{1997ApJ...484..186J, 2000ApJ...534..165J}, NGC 4782
\citep{2007ApJ...664..804M}, and NGC 7626
\citep{1985ApJ...291...32B}. Interestingly, as can be seen in Figure
\ref{fig:pcav}, jetted sources cluster in a particular region of the
\pjet-\prad\ plane. The jetted sources also have radio morphologies
which are distinctly different from the rest of the gEs, but are
similar to other jetted sources. In addition, for these jetted
sources, the morphologies of the X-ray halo surface brightness
decrements are reminiscent of ``tunnels'' rather than bubbles.

Typically, cavity systems are coincident with the general region of
the radio outflow's termination point, \ie\ the location where a
bubble is being inflated {\it{in situ}}, see Figure \ref{fig:m84} for
an example in M84. However, for these jetted sources, the X-ray
tunnels are found at the base of the radio outflows, approximately
along the jets, see Figure \ref{fig:n4261} for an example in NGC
4261. It may be that jetted sources also have classical cavities
associated with the radio lobes, but for these systems the X-ray gas
at those radii is too faint to yield the contrast needed to detect the
cavities. Because the \pcav\ values reported for these systems are for
tunnels and not cavities, one may suspect means that \pcav\ has been
grossly underestimated. However, gas pressure falls off quickly as a
function of radius in these systems, while expected cavity volume will
quickly increase. If there are classic cavities at larger radii
associated with the radio lobes in these jetted systems, the
calculated \pcav\ values would change by factors of a few and not by
orders of magnitude. For this reason, jetted systems, which are
included in the figures for completeness, are not included in any of
the fitting because it appears they are systems dominated by
environmental effects and are not indicative of the
\pjet-\prad\ relation under study.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Systematics}
\label{sec:sys}
%%%%%%%%%%%%%%%%%%%%%%%%

The \pjet-\prad\ trend has considerable scatter, and the samples
presented in this paper and in \citet{birzan04} were not statistically
selected nor representative. It is therefore useful to consider a few
sources of possible systematics or biases. Below we discuss how
underestimating \pcav\ affects our results and if one should worry
about a possible selection bias in the presented sample. We find that
the influence of systematics on our results are negligible given the
large range of \pcav\ and \prad\ covered.

On short timescales, the energetics of a system can be dominated by an
AGN outburst, where one mode of energy deposition is via
cavities. Many other channels of energy deposition may be important,
for example shocks \citep{ms0735, hydraa, herca, 2005ApJ...635..894F,
  2006MNRAS.371L..65S} or sound waves (\eg\ Perseus
\citep{perseus3}). In the limiting circumstance where the energy in
these other channels is of the order the cavity power -- or possibly
greater than the cavity power \citep{2006MNRAS.373..739N} -- then the
jet power is a poor representation of the total energy output. The
extent to which these additional energy channels alter the slope and
normalization of the \pcav-\prad\ relation is not obvious, but, it is
reasonable to assume the corrections to the total jet power would only
be significant in the very rare cases like MS0735 where the shock
energy is a few times the cavity energy. In which case the
\pcav-\prad\ relation would not significantly change. A strong scaling
of shock energy or sound wave energy with host system mass would also
be another way of altering the shape and normalization of the
\pcav-\prad\ relation. As of now, there is no observational evidence,
nor literature, to suggest such a strong effect exists.

There is also the issue of drawing the conclusion that a relation
between jet power and radio power is universal based upon samples
which are not statistically selected or representative. The systems
which were used in \citet{birzan04, birzan08}, and this paper were
obviously chosen because it is possible to measure \pcav, \eg\ the
samples are explicitly biased towards only systems with cavities in
their X-ray atmospheres. This raises the question: does the scaling
relation of $\pjet \propto \prad^{0.6}$ hold for {\it{all}} systems?
More succinctly, is there something special about how AGN interact
with an environment which makes a scaling relation between mechanical
power and radio power a function of the host galaxy's surroundings?
And...???

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Conclusions}
\label{sec:summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We have presented a sample of \samp\ giant elliptical galaxies
observed with the \cxo\ and which all have suspected AGN induced
cavity systems in the X-ray halo surrounding the host galaxy. Cavity
powers, \pcav, were calculated for each set of cavities using the
methods outline in \citet{rafferty06}. Monochromatic radio powers at
1.4 GHz and between 200-400 MHz were also calculated using
measurements from the NVSS and SUMMS surveys, and the CATS database.
Each set of cavities was graded subjectively with a letter: `A', `B',
or `C,' with `A' being the most reliable cavities and `C' being the
least reliable. For the purposes of isolating those systems which may
not be representative of the true \pcav-\prad\ relation durnig
fitting, we also subjectively determined which of the gE systems were
``jet dominated'' by using jet and lobe fluxes taken from archival,
high-resolution VLA observations. If $\ge 50\%$ of the flux emerges
from the jets than the lobes, then the object was deemed a jet
dominated system.

After incorporating the galaxy cluster \pcav-\prad\ data from
\citep{birzan08}, we found a continuous power-law relation between
\pcav-\prad\ in both frequency regimes covering 6 decades in
\prad\ and 8 decades in \pcav (see Figure \ref{fig:pcav}). Using a
log-space BCES fit, we found similar forms for the
\pcav-\prad\ relations for the 1.4 GHz and 200-400 MHz data and thus
suggest a \birzan-Cavagnolo universal relation between jet power and
radio power with the form $\pcav \propto \prad^{0.6}$. This relation
comes with the caveat of being rife with cosmic scatter, $\approx 1.0$
dex in both parameters, and hence very loosely applicable in
determining the {\it{total}} energy output by an AGN.

Utility and consequences...?

%%%%%%%%%%%%%%%%%
\acknowledgements
%%%%%%%%%%%%%%%%%

KWC and BRM acknowledge generous support from the Canadian National
Science and Engineering Research Council (NSERC) grants
NSERC-**LIST**. The authors were supported in this work through
\chandra\ X-ray Observatory grants CXO-**LIST**. The \chandra\ X-ray
Observatory Center is operated by the Smithsonian Astrophysical
Observatory for and on behalf of NASA under contract NAS8-03060. The
National Radio Astronomy Observatory is a facility of the National
Science Foundation operated under cooperative agreement by Associated
Universities, Inc. This research has made use of software provided by
the Chandra X-ray Center in the application packages \ciao, \chips,
and \sherpa. This research has made use of the NASA/IPAC Extragalactic
Database which is operated by the Jet Propulsion Laboratory,
California Institute of Technology, under contract with NASA. This
research has also made use of NASA's Astrophysics Data System. Some
software was obtained from the High Energy Astrophysics Science
Archive Research Center, provided by NASA's Goddard Space Flight
Center.

%%%%%%%%%%%%%%
% Facilities %
%%%%%%%%%%%%%%

{\it Facilities:} \facility{CXO (ACIS)} \facility{VLA}

%%%%%%%%%%%%%%%%
% Bibliography %
%%%%%%%%%%%%%%%%

\bibliography{cavagnolo}

%%%%%%%%%%%%%%%%%%%%%%
% Figures  and Tables%
%%%%%%%%%%%%%%%%%%%%%%

\input{figs.tex}

%%%%%%%%%%%%%%%%%%%%
% End the document %
%%%%%%%%%%%%%%%%%%%%
\end{document}

% LocalWords:  dominately
