%%%%%%%%%%%%%%%%%%%
% Custom commands %
%%%%%%%%%%%%%%%%%%%

\newcommand{\bces}{{\textsc{BCES}}}
\newcommand{\birzan}{B\^irzan}
\newcommand{\mytitle}{A Relationship Between AGN Jet Power and Radio Luminosity}
\newcommand{\samp}{21}
\newcommand{\ecav}{\ensuremath{E_{cav}}}
\newcommand{\pjet}{\ensuremath{P_{jet}}}
\newcommand{\pcav}{\ensuremath{P_{cav}}}
\newcommand{\prad}{\ensuremath{P_{radio}}}
\newcommand{\pbolo}{\ensuremath{P_{bolo.}}}
\newcommand{\phigh}{\ensuremath{P_{\mathrm{1.4}}}}
\newcommand{\pthree}{\ensuremath{P_{\mathrm{327}}}}
\newcommand{\plow}{\ensuremath{P_{\mathrm{200-400}}}}
\newcommand{\shigh}{\ensuremath{\sigma_{\mathrm{1.4}}}}
\newcommand{\sthree}{\ensuremath{\sigma_{\mathrm{327}}}}
\newcommand{\slow}{\ensuremath{\sigma_{\mathrm{200-400}}}}
\newcommand{\sbolo}{\ensuremath{\sigma_{bolo.}}}
\newcommand{\rhigh}{\ensuremath{r_{\mathrm{1.4}}}}
\newcommand{\rlow}{\ensuremath{r_{\mathrm{200-400}}}}

%%%%%%%%%%
% Header %
%%%%%%%%%%

%\documentclass[12pt, preprint]{aastex}
%\documentclass{aastex}
\documentclass{emulateapj}
\usepackage{apjfonts,graphicx,here,common,longtable,ifthen,amsmath,amssymb,natbib}
\usepackage[pagebackref,
  pdftitle={\mytitle},
  pdfauthor={Kenneth W. Cavagnolo},
  pdfsubject={ApJ},
  pdfkeywords={},
  pdfproducer={LaTeX with hyperref},
  pdfcreator={LaTeX}
  pdfdisplaydoctitle=true,
  colorlinks=true,
  citecolor=blue,
  linkcolor=blue,
  urlcolor=blue]{hyperref}
\bibliographystyle{apj}
\begin{document}
\title{\mytitle}
\shorttitle{AGN Scaling Relations for Giant Ellipticals}
\author{
K. W. Cavagnolo\altaffilmark{1,7},
B. R. McNamara\altaffilmark{1,2,3},
P. E. J. Nulsen\altaffilmark{3},\\
C. L. Carilli\altaffilmark{4},
C. Jones\altaffilmark{3},
W. Forman\altaffilmark{3},\\
L. \birzan\altaffilmark{5,6},
S. Murray\altaffilmark{3}, \&
M. W. Wise\altaffilmark{6}
}
\altaffiltext{1}{Department of Physics and Astronomy, University of
  Waterloo, Waterloo, ON N2L 3G1, Canada.}
\altaffiltext{2}{Perimeter Institute for Theoretical Physics, 31
  Caroline Street N, Waterloo, ON N2L 2Y5, Canada.}
\altaffiltext{3}{Harvard-Smithsonian Center for Astrophysics, 60
  Garden Street, Cambridge, MA 01238, USA.}
\altaffiltext{4}{National Radio Astronomy Observatory, P.O. Box 0,
  Socorro, NM 87801-0387, USA.}
\altaffiltext{5}{Department of Astronomy and Astrophysics,
  Pennsylvania State University, 525 Davey Lab, University Park, PA
  16802, USA.}
\altaffiltext{6}{Astronomical Institute Anton Pannekoek, University of
  Amsterdam, Kruislaan 403, 1098 SJ Amsterdam, Netherlands.}
\altaffiltext{7}{kcavagno@uwaterloo.ca}
\shortauthors{K. W. Cavagnolo et al.}
\journalinfo{}
\slugcomment{For submission to ApJ}

%%%%%%%%%%%%
% Abstract %
%%%%%%%%%%%%

\begin{abstract}
Using X-ray data collected with the \cxo\ and multi-frequency VLA
radio data, we investigate the scaling relationship between active
galactic nuclei (AGN) jet power (\pjet) and radio power (\prad). The
goal of our study is to determine if the \pjet-\prad\ scaling relation
found by \citet{birzan04, birzan08} for brightest cluster galaxies
(BCGs) is continuous in form and scatter from isolated giant
elliptical galaxies (gEs) up to BCGs. We expand the sample presented
in \citet{birzan04, birzan08} to much lower radio power by
incorporating measurements for \samp\ relatively isolated
gEs. Combining the results presented in this paper with the results
from \citet{birzan04, birzan08}, we find a common scaling relation of
$\pjet \propto \prad^{0.7}$ with a scatter of $\approx 1.0$ dex using
monochromatic radio powers at 200-400 MHz and 1.4 GHz. We discuss the
utility and broader consequences of a universal relation between jet
power and radio luminosity as it pertains to AGN feedback and the
growth of black holes.
\end{abstract} 

%%%%%%%%%%%%
% Keywords %
%%%%%%%%%%%%

\keywords{galaxies: active -- galaxies: clusters: general -- X-rays:
  galaxies -- radio continuum: galaxies}

%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%

The astrophysical influence of energy deposition into an environment
hosting a supermassive black hole (SMBH), on physical scales varying
from sub-pc to Mpc, has been under intense observational and
theoretical study for decades \citep[\eg][]{1969Natur.223..690L,
  1974MNRAS.166..513S, cowie77, 1981ApJ...248...55B,
  1982MNRAS.200..115S, 1984ARA&A..22..471R, burns90,
  1993MNRAS.263..323T, 1997MNRAS.288..355B, magorrian,
  1999MNRAS.303..188K, 2000ApJ...534L.135M, best05, haradent}. More
specifically, the energy returned to an environment via AGN feedback
(the result of a SMBH accreting matter) is now understood to be a very
important mode of feedback which impacts the shape and normalization
of the galaxy luminosity function \citep{croton06, bower06, saro06,
  sijacki07}. Moreover, better models and observations of the AGN
feedback process have also proved important in furthering our
understanding of the formation and evolution of large-scale structure,
such as galaxy clusters and groups \citep[see, for
  example,][]{2008MNRAS.386.1309M, minggroups}. But understanding the
details of how AGN feedback is coupled to heating an environment are
still hotly debated \citep[\eg][]{2008ASPC..386..343D}.

The launch of \chandra\ enabled observational advances in studying AGN
feedback. \chandra\ observations unambiguously revealed cavities
excavated in the X-ray emitting gas which surrounds many massive
galaxies \citep[\eg][]{2000ApJ...534L.135M, perseus1,
  schindler01}. These cavities result from the interaction of AGN jets
with a hot halo, and the cavity properties (\ie\ morphology and
location) act as an energetics record. From X-ray images of cavities,
measurements of the $pV$ work necessary to inflate a cavity are used
to calculate enthalpy, which in turn is an approximation of total jet
power. Observations have shown that cavities contain a substantial
amount of energy, $10^{54}-10^{62}$ erg, and on average cavity energy
is comparable to, or exceeds, the cooling luminosity of the
environment with which the AGN has interacted \citep{birzan04,
  rafferty06}, though this is not the case for all systems
\citep{dunn08}. In addition to confirming that AGN are a viable source
for the heat necessary to impact galaxy and structure formation, the
use of cavities as calorimeters opened a new pathway to study the AGN
feedback process and properties of SMBHs \citep{2009ApJ...698..594M}.

Development of a more fundamental understanding of AGN feedback as it
relates to structure formation has been attained by using samples of
systems with cavities covering interesting ranges of host system mass,
environment, and redshift. However, selecting representative or
statistically significant samples of cavity-bearing systems is
non-trivial, and arguably not possible. This is primarily because the
study of X-ray cavities is limited by the ability and capacity of the
current generation of X-ray telescopes to obtain data of the quality
necessary to resolve cavities \citep{2009arXiv0909.0397B}. Factors
such as morphology, distance from the AGN host galaxy, and projection,
combined with observing constraints, mean that even in a sample
specifically selected to find cavities, they may go
undetected. Lacking the leverage of a large statistical study, it
behooves observers and theorists alike to find relationships between
simple observables and AGN energetics if we wish to study feedback in
broader terms.

It may be possible to circumvent the need for deep X-ray observing
programs by quantifying and calibrating how cavity properties scale
with readily available AGN observables, a strategy similar to that
used for studying dark matter halo masses \citep[\eg][]{kravtsov06,
2007ApJ...668..772M, 2009A&A...498..361P}. This can be accomplished
if, for example, there exists a universal scaling relationship between
jet power and the radio emission associated with those jets. A very
simple quantity which has been used in previous investigations is the
monochromatic radio power. A universal \pjet-\prad\ scaling relation
could then be applied to measurements from all-sky radio surveys,
thereby installing the more readily available radio observations as a
surrogate for jet power \citep{croton06, 2006MNRAS.366..397S}.

An observational relationship between jet power and radio power was
first determined by \citet{birzan04, birzan08} using a sample of
BCGs. \citet{birzan04, birzan08} presented scaling relations between
\pjet\ and \prad\ for the 327 MHz and 1.4 GHz radio frequencies, in
addition to the bolometric radio
luminosity. \citet{2008ApJ...680..897D} also found a similar
connection between gE X-ray luminosity and radio luminosity, but no
study has been undertaken of the \pjet-\prad\ relation for gEs. To
address this deficiency, we investigate the relationships
\pjet-\phigh\ and \pjet-\plow\ (see Section \S\ref{sec:radio}) for a
sample of relatively isolated gEs. Combining the \citet{birzan08}
results and the results in this paper, we find a relationship between
jet power and radio power which is similar at high and low radio
frequencies. The relationships span 6-8 orders of magnitude in
\pjet\ and \prad, and have the general form $\pjet \propto
\prad^{0.7}$ with dominantly intrinsic scatter of $\sigma \sim 1.0$
dex.

The paper is structured as follows: \S\ref{sec:sample} outlines the
sample selected. X-ray and radio data reduction is discussed in
\S\ref{sec:data}. Results and discussion are presented in
\S\ref{sec:r&d}. A brief summary is given in
\S\ref{sec:summary}. \LCDM\ All quoted uncertainties are 68\%
confidence. Hereafter, the terminology cavity power and jet power are
used interchangeably, and are denoted as \pcav\ and \pjet,
respectively.

%%%%%%%%%%%%%%%%%%
\section{Sample}
\label{sec:sample}
%%%%%%%%%%%%%%%%%%

Our sample of \samp\ gEs is taken from the sample of 160 gEs compiled
by Jones et al. (in preparation). The Jones et al. compilation is
drawn from the samples of \citet{1999MNRAS.302..209B} and
\citet{2003MNRAS.340.1375O} using the criteria that $L_K >
10^{10}~\Lsol$ and the object has been observed with \chandra. Of the
160 gEs, extended X-ray emission was detected in 109 objects. AGN
activity was suspected in 27 objects based solely on the presence of
surface brightness depressions in the X-ray emitting gas. We have
further excluded dwarf galaxies ($M_V < -19.5$) from the sample since
it is not clear that the substructure in the X-ray gas is associated
with an AGN, leaving \samp\ objects. The \samp\ gEs in our sample are
in relatively low density environments, meaning these are not the
central dominant or brightest galaxies in clusters or groups. The
X-ray emission associated with the gEs in our sample is dominated by
the gas gravitationally bound to the gE halo and not a diffuse
atmosphere of some larger environment. The comoving distance range of
our sample is 0.4-117 Mpc, with an X-ray luminosity range of $\sim
10^{31}-10^{36} \lum$. General properties of the sample are listed in
Table \ref{tab:sample}.

\input{sample.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Observations and Data Analysis}
\label{sec:data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%
\subsection{X-ray}
\label{sec:xray}
%%%%%%%%%%%%%%%%%%

Details of the X-ray data analysis will be presented in Nulsen et
al. (in preparation). \chandra\ data was reduced following standard
procedures: gain correction, CTI correction, bad grade filtering,
flare filtering, and point source exclusion. Background spectral
analysis was performed using the \caldb\ blank-sky observations
included in the CALDB and tailored to match each targeted observation.
Measurement of cavity power is performed identically to
\citet{rafferty06}. For each observation, an azimuthally averaged
deprojected gas density and temperature profile were used to calculate
the total gas pressure at each radius. Then, using cavity volumes
calculated from a visual measurement of a cavity's projected
cross-section, the total energy contained in each cavity is estimated
as $\ecav = pV[\gamma/(\gamma-1)]$ where $p$ is pressure, $V$ is
volume, and we assume $\gamma = 4/3$ for the ratio of specific heat
capacities. The total cavity energy is then divided by an age estimate
for the AGN outburst, yielding $\pcav = \ecav/t$ (see \citet{mcnamrev}
for discussion of how timescales are estimated). Uncertainties for
each calculation were determined by propagating errors and summing in
quadrature.

%%%%%%%%%%%%%%%%%%
\subsection{Radio}
\label{sec:radio}
%%%%%%%%%%%%%%%%%%

The 1.4 GHz continuum radio flux for each source was taken from the
flux-limited NRAO VLA Sky Survey (NVSS, \citealt{nvss}). For NGC 1553,
which is outside the NVSS survey area, the 843 MHz continuum radio
flux was taken from the flux-limited Sydney University Molonglo Sky
Survey (SUMSS, \citealt{sumss1, sumss2}). We calculate the
monochromatic radio power for each source using the relation $\radpow
= 4 \pi D_L^2 (1+z)^{-1} S_{\nu} f_0$ where $S_{\nu}$ is the NVSS or
SUMSS flux, $D_L$ is the luminosity distance, and $f_0$ is the central
beam frequency of the observations.

The radio morphologies are heterogeneous, some sources are large and
extended, while some sources are compact. To ensure the entire radio
source was measured, a fixed angular distance of $1200\arcsec$ was
searched around the X-ray centroid of each target. For each target
field, all detected radio sources were overlaid on a composite image
of X-ray, optical (using DSS
I/II\footnote{http://archive.stsci.edu/dss/}), and infrared emission
(using 2MASS\footnote{http://www.ipac.caltech.edu/2mass/}) image, and
when available, the deeper and higher resolution radio data from VLA
FIRST\footnote{http://sundog.stsci.edu} was included. A visual
inspection was then performed to establish which detected radio
sources were associated with the target gE. After confirming which
radio sources within the search region were associated with the target
gE, the fluxes of the individual sources were added and the associated
uncertainties summed in quadrature.

As an extension of the NVSS search, we also reduced and analyzed
archival VLA data for each source in the sample. The purpose of this
additional step was to establish which sources are jet dominated and
which are not (see Section \S\ref{sec:r&d}). In the cases where
high-resolution VLA archival data is available, we used the reduced
images to confirm the connection between the NVSS emission and the
host gE. The fluxes measured from the VLA archival data also served as
a check of the fluxes taken from NVSS. We found agreement for most
sources, the exceptions being IC 4296 and NGC 4782 where the NVSS flux
is approximately a factor of 2 lower. These sources are unique because
the radio lobes contain significant power in diffuse, extended
emission which is not detected in NVSS. For these sources, the fluxes
measured from the archival VLA data are used.

\citet{birzan08} found that the \pcav-\pthree\ relation had lower
scatter than the \pcav-\phigh\ relation. For our sample of gEs, the
quality and availability of 327 MHz data were poor, and thus we
gathered low-frequency radio fluxes from the CATS
Database\footnote{http://www.sao.ru/cats/} \citep{cats}. The CATS was
queried in the frequency range 200-400 MHz using the list of radio
source coordinates found from the NVSS and SUMSS searches. Of the
\samp\ gEs in our sample, 17 objects were found in the CATS database
with fluxes in the 200-400 MHz range. The search approach used means
that low-frequency radio emission which does not have a 1.4 GHz
counterpart (or vice versa) is missed. Because CATS does not provide
source images for visual inspection, this method also ensures that
non-relevant detections are less likely to be included. Therefore, the
200-400 MHz radio powers shown in Figure \ref{fig:pcav} likely
underestimate the 200-400 MHz fluxes for these gEs. However, because
of the large range of radio powers, a systematic shift by a factor of
a few along the \radpow\ axis for all the gE points alters the
best-fit relations within the uncertainties.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and Discussion}
\label{sec:r&d}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\pjet-\prad\ Scaling Relation}
\label{sec:relation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The results from the X-ray and radio data analysis are shown in the
plots of \pcav-\phigh\ and \pcav-\plow\ presented in Figure
\ref{fig:pcav}. A subjective grade of quality was assigned for each
set of cavities -- shown as color coding in Figure \ref{fig:pcav} and
listed in Table \ref{tab:sample}. We assigned grades because,
currently, no standard algorithm for detecting cavities and
determining cavity morphology exists, and the grades quantify our
visual assessment. Grade A cavities are associated with AGN radio
activity and have well-defined boundaries; grade B cavities are
associated with AGN radio activity, but lack well-defined boundaries;
grade C cavities have poorly-defined boundaries, and their connection
to AGN radio activity is uncertain. Grade C cavities are excluded from
all fitting, as are jet dominated sources (see Section \ref{sec:jet}).

Figure \ref{fig:pcav} shows that a power law relationship between
cavity power and monochromatic radio power is continuous over
approximately 8 orders of magnitude in radio power and 6 orders of
magnitude in cavity power. To determine the form of the power-law
relation, we performed linear fits in log space to the data for each
frequency regime using the bivariate correlated error and intrinsic
scatter (\bces) algorithm \citep{bces}. The orthogonal
\bces\ algorithm takes in asymmetric uncertainties for both variables,
assumes the presence of intrinsic scatter, and performs a linear
least-squares regression. The best-fit parameter uncertainties are
calculated using 5000 Monte Carlo bootstrap resampling trials.

The intrinsic scatter in the data is large relative to the size of the
statistical uncertainties for the individual points. So while we
assumed \bces\ was the best fitting method, extensive testing with
other fitting methods (\ie\ C. Markwardt's {\textsc{mpfit}}, IDL's
{\textsc{linfit}} and {\textsc{fitexy}}) was performed using synthetic
data. The \bces\ algorithm proved to be the best fitting method for
our data because the addition of an intrinsic scatter term into the
fitting produces uncertainties which are least likely to underestimate
the 90\% confidence intervals of an underlying relationship.

The best-fit BCES determined linear function in log-space for the
\pcav-\phigh\ and \pcav-\plow\ relations are:
\begin{eqnarray}
\log~\pcav &=& 0.70~(\pm 0.10)~\log~\phigh + 1.69~(\pm 0.18)\\
\log~\pcav &=& 0.67~(\pm 0.08)~\log~\plow + 1.30~(\pm 0.14)
\end{eqnarray}
where \pcav\ has units of $10^{42} \lum$ and \phigh\ and \plow\ have
units $10^{40} \lum$.  The scatter for each relation is \shigh\ = 1.07
dex and \slow\ = 0.88 dex, and the respective correlation coefficients
are \rhigh\ = 0.74 and \rlow\ = 0.81. We have quantified log-space
scatter using the average size of the residuals about the best-fit
relation. For comparison, the scaling relations found by
\citet{birzan08} are
\begin{eqnarray}
\pjet &\propto& \pthree^{0.62 \pm 0.08}\\
\pjet &\propto& \phigh^{0.35 \pm 0.07}\\
\pjet &\propto& \pbolo^{0.48 \pm 0.07}
\end{eqnarray}
with scatters of $\sthree = 0.65$ dex, $\shigh = 0.69$ dex, and
$\sbolo = 0.85$ dex. Note that high and low frequency relations
presented in \citet{birzan08} have power-law indices which
significantly differ from each other by a factor of two. Inclusion of
the new gE dataset shows that the difference arose from under-sampling,
\ie\ the 1.4 GHz relationship simply had too few data points covering
too small a range in \pcav\ and \prad\ to reveal a steeper
relationship. The similarity of the power-laws for both frequency
regimes is encouraging, it strongly suggests an underlying universal
relationship between jet power and radio luminosity.

\citet{birzan08} demonstrated that correcting for the effect of radio
aging reduces the scatter of the relations. Additionally, as
demonstrated with systems like Hydra A \citep{hydraa} and MS
0735.6+7421 \citep{ms0735}, the energetics in a system at any given
time can be dominated by AGN outbursts which are more powerful than
average. This may be particularly true for gEs, which have lower
pressure halos and are more susceptible to disruption by AGN outbursts
\citep{minggroups}. The substantial scatter also highlights that radio
luminosity is a poor surrogate for accurately determining the total
energy released via an AGN.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Jet Dominated Sources}
\label{sec:jet}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


In Figure \ref{fig:pcav} we have enclosed a subset of points in open
circles to highlight the systems which are jet dominated. Using
archival VLA radio data (see Section \S\ref{sec:radio}), if 50\% or
more of the radio flux from a source originates in the jets than the
lobes, then the source is deemed to be jet dominated. The objects we
have identified as jetted are: IC 4296 \citep{2003ApJ...585..677P},
NGC 315 \citep{1979ApJ...228L...9B, 1981A&A....95..250W}, NGC 4261
\citep{1997ApJ...484..186J, 2000ApJ...534..165J}, NGC 4782
\citep{2007ApJ...664..804M}, and NGC 7626
\citep{1985ApJ...291...32B}. Interestingly, Figure \ref{fig:pcav}
shows the jetted sources clustered in the region where $\pcav <
10^{42} \lum$ and $\pcav \le \prad$. The jetted sources also have
radio morphologies which are distinct from the rest of the gEs, but
are similar to other jetted sources. In addition, for these jetted
sources, the morphologies of the X-ray halo surface brightness
decrements are reminiscent of tunnels rather than bubbles.

Typically, cavity systems are coincident with the general region of a
radio outflow termination point, \ie\ the location where a bubble is
being inflated {\it{in situ}}, see Figure \ref{fig:pics} for an
example in M84. However, for these jetted sources, the X-ray tunnels
are found at the base of the radio outflows, approximately along the
jets, see Figure \ref{fig:pics} for an example in NGC 4261. It may be
that jetted sources also have classical cavities associated with the
radio lobes, but for these systems the X-ray halo at those radii is
too faint to yield a cavity detection. To investigate this
possibility, we asked the question: what ambient pressure, cavity
volume, or outburst age is required to yield a \pcav\ which places
each jetted system within $1\sigma$ of the best-fit
\pcav-\prad\ relations?

{\bfseries{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}}\\
{\bfseries{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}}

(1) Fixed cavity volume: We measured cavity volumes assuming cavity
shape traces radio lobe morphology. Outburst ages were calculated
using the distance to the leading edge of the radio lobes and assuming
cavity excavation proceeded at the gas sound speed. The pressure
necessary to yield a \pcav\ within $1\sigma$ of each best-fit relation
was then calculated. The results are... pressures which are greater
than or equal to the central pressures of the host gE, implying radial
pressure profiles which are shallower than have ever been observed.

(2) Fixed pressure: Using the central density, $\rho_0$, in each
system, we generated a $beta$-model gas density profile
\citep{betamodel}, $\rho(r) = \rho_0 [1+(r/r_c)^2]^{-3\beta/2}$, where
$\beta = 2/3$ \citep{1984ApJ...276...38J}, and $r_c = 2$ kpc for the
core radius. Radial gas pressures were then calculated using a
temperature profile which starts at X.XX keV and asymptotically
approaches X.XX keV within XX kpc. The same outburst ages were assumed
as in calculation (1). Finally, the cavity volumes necessary to yield
\pcav\ within $1\sigma$ of each best-fit relation were calculated. The
results are... volumes are larger than anything which has been
observed, with radii in the range XX-XX kpc.

(3) Variable outburst ages: Combining the fixed volumes from (1) and
fixed pressures from (2), outburst ages were calculated that satisfied
the $1\sigma$ \pcav-\prad\ criterion. The results are... timescales
shorter than a XX Myr, which implies supersonic inflation speeds out
to many kpcs.

We conclude that to place these systems along the best-fit
\pcav-\prad\ relations requires physical scenarios which have no
observational support. Thus, it is unlikely for jetted systems that
larger bubbles at greater radii would move the points up to a location
where they are consistent with the \pcav-\prad\ trend. For this
reason, jetted systems, which are included in the figures for
completeness, are not included in any of the fitting because it
appears they are not representative of the \pjet-\prad\ relation under
study.

{\bfseries{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}}\\
{\bfseries{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}}\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Conclusions}
\label{sec:summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We have presented a sample of \samp\ giant elliptical galaxies
observed with the \cxo\ and which all have suspected AGN induced
cavity systems in the X-ray halo surrounding the host galaxy. Cavity
powers, \pcav, were calculated for each set of cavities using the
methods outlined in \citet{rafferty06}. Monochromatic radio powers at
1.4 GHz and between 200-400 MHz were also calculated using
measurements from the NVSS and SUMSS surveys, and the CATS database.
Each set of cavities was graded subjectively with a letter: `A', `B',
or `C,' with `A' being the most reliable cavities and `C' being the
least reliable. For the purposes of isolating those systems which may
not be representative of the true \pcav-\prad\ relation during
fitting, we also subjectively determined which of the gE systems were
jet dominated by using jet and lobe fluxes taken from archival,
high-resolution VLA observations. If $\ge 50\%$ of the flux emerges
from the jets than the lobes, then the object was deemed a jet
dominated system.

After incorporating the galaxy cluster \pcav-\prad\ data from
\citep{birzan08}, we found a continuous power-law relation between
\pcav-\prad\ in both frequency regimes covering 6 decades in
\prad\ and 8 decades in \pcav (see Figure \ref{fig:pcav}). Using a
log-space \bces\ fit, we found similar power laws for the
\pcav-\prad\ relations for the 1.4 GHz and 200-400 MHz data with the
form $\pcav \propto \prad^{0.7}$. This relation comes with the caveat
of $\approx 1.0$ dex cosmic scatter in both parameters, and hence the
relation is weakly applicable in determining the {\it{total}} energy
output by an AGN.

{\bfseries{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}}\\
{\bfseries{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}}\\

Utility and consequences...?

Several groups have applied the \birzan\ scaling relations to study
the effects of feedback from elliptical galaxies, most notably
\citet{best07}, \citet{2007MNRAS.379..260M}, and
\citet{2009arXiv0908.3158H}. However, up to now, no observational
evidence suggested that the \pjet-\prad\ relations for galaxy clusters
are continuous, of comparable scatter, or applicable for lower power
radio sources like ellipticals. And...?

What is Q? How is it theoretically determined? Parameterized in the
form $Q \sim L^{\alpha}$, \citet{1979ApJ...232...34B} derive a
theoretical value of $\alpha = 12/17$ using a jet model...? Using the
self-similar jet model of \citet{1991MNRAS.250..581F} to estimate $Q$
and radio power at 151 MHz, \citet{1999MNRAS.309.1017W} found $\alpha
= 6/7$. Our $\alpha$ of $\approx 0.7$ agrees with the result by
\citet{1979ApJ...232...34B}, and significantly differs from the result
by \citet{1999MNRAS.309.1017W}. However, \citet{1999MNRAS.309.1017W}
used lower frequency radio data, and as shown in \citet{birzan08}, the
effect of radio aging may contribute to a steeper
\pjet-\prad\ relation at much lower frequencies.

{\bfseries{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}}\\
{\bfseries{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}}\\

%%%%%%%%%%%%%%%%%
\acknowledgements
%%%%%%%%%%%%%%%%%

KWC and BRM acknowledge generous support from Canadian National
Science and Engineering Research Council grants NSERC-XXX and
\cxo\ grants CXO-XXX. The \chandra\ X-ray Observatory Center is
operated by the Smithsonian Astrophysical Observatory for and on
behalf of NASA under contract NAS8-03060. The National Radio Astronomy
Observatory is a facility of the National Science Foundation operated
under cooperative agreement by Associated Universities, Inc.

%%%%%%%%%%%%%%
% Facilities %
%%%%%%%%%%%%%%

{\it Facilities:} \facility{CXO (ACIS)} \facility{VLA}

%%%%%%%%%%%%%%%%
% Bibliography %
%%%%%%%%%%%%%%%%

\bibliography{cavagnolo}

%%%%%%%%%%%%%%%%%%%%%%
% Figures  and Tables%
%%%%%%%%%%%%%%%%%%%%%%

\input{figs.tex}

%%%%%%%%%%%%%%%%%%%%
% End the document %
%%%%%%%%%%%%%%%%%%%%
\end{document}
