%%%%%%%%%%%%%%%%%%%
% Custom commands %
%%%%%%%%%%%%%%%%%%%

\newcommand{\bces}{{\textsc{BCES}}}
\newcommand{\birzan}{B\^irzan}
\newcommand{\mytitle}{A Relationship Between AGN Jet Power and Radio Luminosity}
\newcommand{\samp}{21}
\newcommand{\ecav}{\ensuremath{E_{cav}}}
\newcommand{\pjet}{\ensuremath{P_{jet}}}
\newcommand{\pcav}{\ensuremath{P_{cav}}}
\newcommand{\prad}{\ensuremath{P_{radio}}}
\newcommand{\pnu}{\ensuremath{P_{\nu}}}
\newcommand{\pbolo}{\ensuremath{P_{bolo.}}}
\newcommand{\phigh}{\ensuremath{P_{\mathrm{1.4}}}}
\newcommand{\pthree}{\ensuremath{P_{\mathrm{327}}}}
\newcommand{\plow}{\ensuremath{P_{\mathrm{200-400}}}}
\newcommand{\shigh}{\ensuremath{\sigma_{\mathrm{1.4}}}}
\newcommand{\sthree}{\ensuremath{\sigma_{\mathrm{327}}}}
\newcommand{\slow}{\ensuremath{\sigma_{\mathrm{200-400}}}}
\newcommand{\sbolo}{\ensuremath{\sigma_{bolo.}}}
\newcommand{\rhigh}{\ensuremath{r_{\mathrm{1.4}}}}
\newcommand{\rlow}{\ensuremath{r_{\mathrm{200-400}}}}

%%%%%%%%%%
% Header %
%%%%%%%%%%

%\documentclass[12pt, preprint]{aastex}
%\documentclass{aastex}
\documentclass{emulateapj}
\usepackage{apjfonts,graphicx,here,common,longtable,ifthen,amsmath,amssymb,natbib}
\usepackage[pagebackref,
  pdftitle={\mytitle},
  pdfauthor={Kenneth W. Cavagnolo},
  pdfsubject={ApJ},
  pdfkeywords={},
  pdfproducer={LaTeX with hyperref},
  pdfcreator={LaTeX}
  pdfdisplaydoctitle=true,
  colorlinks=true,
  citecolor=blue,
  linkcolor=blue,
  urlcolor=blue]{hyperref}
\bibliographystyle{apj}
\begin{document}
\title{\mytitle}
\shorttitle{AGN Scaling Relations for Giant Ellipticals}
\author{
K. W. Cavagnolo\altaffilmark{1,7},
B. R. McNamara\altaffilmark{1,2,3},
P. E. J. Nulsen\altaffilmark{3},\\
C. L. Carilli\altaffilmark{4},
C. Jones\altaffilmark{3},
W. Forman\altaffilmark{3},\\
L. \birzan\altaffilmark{5,6},
S. Murray\altaffilmark{3}, \&
M. W. Wise\altaffilmark{6}
}
\altaffiltext{1}{Department of Physics and Astronomy, University of
  Waterloo, Waterloo, ON N2L 3G1, Canada.}
\altaffiltext{2}{Perimeter Institute for Theoretical Physics, 31
  Caroline Street N, Waterloo, ON N2L 2Y5, Canada.}
\altaffiltext{3}{Harvard-Smithsonian Center for Astrophysics, 60
  Garden Street, Cambridge, MA 01238, USA.}
\altaffiltext{4}{National Radio Astronomy Observatory, P.O. Box 0,
  Socorro, NM 87801-0387, USA.}
\altaffiltext{5}{Department of Astronomy and Astrophysics,
  Pennsylvania State University, 525 Davey Lab, University Park, PA
  16802, USA.}
\altaffiltext{6}{Astronomical Institute Anton Pannekoek, University of
  Amsterdam, Kruislaan 403, 1098 SJ Amsterdam, Netherlands.}
\altaffiltext{7}{kcavagno@uwaterloo.ca}
\shortauthors{K. W. Cavagnolo et al.}
\journalinfo{}
\slugcomment{For submission to ApJ}

%%%%%%%%%%%%
% Abstract %
%%%%%%%%%%%%

\begin{abstract}
  Using X-ray data collected with the \cxo\ and multi-frequency VLA
  radio data, we investigate the scaling relationship between active
  galactic nucleus (AGN) jet power (\pjet) and observed radio power
  (\prad). The goal of our study was to determine if the
  \pjet-\prad\ scaling relation found by \citet{birzan04, birzan08}
  for brightest cluster galaxies (BCGs) is continuous in form and
  scatter from isolated giant elliptical galaxies (gEs) up to BCGs. We
  expand the sample presented in \citet{birzan04, birzan08} to lower
  radio power by incorporating measurements for \samp\ relatively
  isolated gEs. Combining our results with those of \citet{birzan04,
    birzan08}, for monochromatic radio powers at $\nu = 200-400$ MHz
  or $\nu = 1.4$ GHz we find scaling relations of $\pjet \propto
  \pnu^{0.7\pm0.1}$ with a scatter of $\sim 1.0$ dex. We briefly
  comment on the consistency of an $\approx 7/10$ slope with
  theoretical predictions, specifically those of
  \citet{1979ApJ...232...34B} and \citet{1995A&A...293..665F}. We also
  discuss the utility and broader consequences of a universal relation
  between jet power and radio luminosity as it pertains to studying
  AGN feedback and the growth of black holes.
\end{abstract} 

%%%%%%%%%%%%
% Keywords %
%%%%%%%%%%%%

\keywords{galaxies: active -- galaxies: clusters: general -- X-rays:
  galaxies -- radio continuum: galaxies}

%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%

Energetic feedback via AGN, the result of matter accreting onto a
supermassive black hole (SMBH), has been shown to have a significant
impact on the shape and normalization of $\Lambda$CDM galaxy
luminosity functions \citep{croton06, bower06, saro06,
  sijacki07}. Combined with better observations of the AGN feedback
process, these improved models have proven important in furthering our
understanding of the formation and evolution of large-scale structure
(\eg\ \citealt{2008MNRAS.386.1309M}, \citealt{minggroups}, or
\citealt{2009arXiv0906.4370B} for a review). But, the details of how
AGN feedback is coupled to the cooling and heating of an environment
are still hotly debated \citep{2008ASPC..386..343D}. Observational
studies, such as the one presented in this paper, have aided in
illuminating those details by studying the relationship between
observables and AGN energetics \citep{birzan04, 2005MNRAS.364.1343D,
  rafferty06, dunn08, haradent, birzan08}.

Observational advances in studying AGN feedback occurred when
\chandra\ unambiguously revealed cavities excavated by AGN in the
X-ray emitting gas surrounding many massive galaxies
\citep[\eg][]{2000ApJ...534L.135M, perseus1, schindler01}. The
morphology and location of cavities are useful for estimating the $pV$
work necessary to inflate a cavity. This in turn yields an estimate of
total jet power \citep[see][for a review]{mcnamrev}. Observations have
shown that cavities contain a substantial amount of energy,
$10^{54}-10^{62}$ erg, and, on average, cavity power is comparable to,
or exceeds, the cooling luminosity of the environment with which the
AGN has interacted, though this is not the case for all systems
\citep{birzan04, rafferty06, dunn08}. In addition to confirming that
AGN are a viable source for the energy necessary to impact galaxy and
structure formation, the use of cavities as calorimeters opened a new
pathway to study properties of SMBHs \citep{2009ApJ...698..594M}.

Development of a more fundamental understanding of AGN feedback as it
relates to structure formation has been attained by using samples of
systems with cavities covering interesting ranges of host system mass,
environment, and redshift. However, selecting representative or
statistically significant samples of cavity-bearing systems is
non-trivial, and arguably not possible. This is primarily because the
study of X-ray cavities is limited by the capabilities of the current
generation of X-ray telescopes \citep{2009arXiv0909.0397B}. Combined
with observing constraints, factors such as morphology, distance from
the AGN host galaxy, and projection mean that even in a sample
specifically selected to host cavities, they may go
undetected. Lacking the leverage of a large statistical study, it
behooves observers and theorists alike to find relationships between
simple observables and AGN energetics if we wish to study feedback,
in broader terms.

It may be possible to circumvent the need for deep X-ray observing
programs by quantifying and calibrating how cavity properties scale
with readily available AGN observables, a strategy similar to that
used for studying dark matter halo masses \citep[\eg][]{kravtsov06,
  2007ApJ...668..772M, 2009A&A...498..361P}. This can be accomplished
if, for example, there exists a universal scaling relationship between
jet power and emergent radio emission. A universal scaling relation
could then be applied to measurements from all-sky radio surveys,
thereby installing the more readily available radio observations as a
surrogate for jet power \citep{croton06, 2006MNRAS.366..397S}. A very
simple quantity which has been used in previous investigations is
radio power, \prad.

An observational relationship between jet power and radio power was
first determined by \citet{birzan04, birzan08} using a sample of
BCGs. \citet{birzan04, birzan08} presented scaling relations between
\pjet\ and \prad\ for the 327 MHz and 1.4 GHz radio frequencies, in
addition to the bolometric radio
luminosity. \citet{2008ApJ...680..897D} also found a similar
connection between gE X-ray luminosity and radio luminosity, but no
study has been undertaken of the \pjet-\prad\ relation for gEs. To
address this deficiency, we investigate the relationships
\pjet-\phigh\ and \pjet-\plow\ for a sample of relatively isolated
gEs. Combining the \citet{birzan08} results and the results in this
paper, we find a relationship between jet power and radio power which
is similar at high and low radio frequencies. The relationships span
6-8 orders of magnitude in \pjet\ and \prad, and have the general form
$\pjet \propto \prad^{0.7}$ with dominantly intrinsic scatter of
$\sigma \sim 1.0$ dex.

This paper is structured as follows: \S\ref{sec:sample} outlines the
sample of selected gEs. X-ray and radio data reduction is discussed in
\S\ref{sec:data}. Results and discussion are presented in
\S\ref{sec:r&d}. A brief summary and concluding remarks are given in
\S\ref{sec:summary}. \LCDM\ All quoted uncertainties are 68\%
confidence. Hereafter, the terminology cavity power and jet power are
used interchangeably, and are denoted as \pcav\ and \pjet,
respectively.

%%%%%%%%%%%%%%%%%%
\section{Sample}
\label{sec:sample}
%%%%%%%%%%%%%%%%%%

Our sample of \samp\ gEs is taken from the sample of 160 gEs compiled
by Jones et al. \citetext{in prep.}. General properties of the sample
are listed in Table \ref{tab:sample}. The Jones et al. compilation is
drawn from the samples of \citet{1999MNRAS.302..209B} and
\citet{2003MNRAS.340.1375O} using the criteria that $L_K >
10^{10}~\Lsol$ and the object has been observed with \chandra. Of the
160 gEs, extended X-ray emission was detected in 109 objects. AGN
activity was suspected in 27 objects based solely on the presence of
surface brightness depressions in the X-ray emitting gas. We have
further excluded dwarf galaxies ($M_V < -19.5$) from the sample since
it is not clear that the substructure in the X-ray gas is associated
with an AGN, leaving \samp\ objects. The \samp\ gEs in our sample are
in relatively low density environments -- these are not the central
dominant or brightest galaxies in clusters or groups -- \ie\ regions
of low projected local galaxy density. The X-ray emission associated
with the gEs in our sample is dominated by the gas gravitationally
bound to the gE halo and not a diffuse atmosphere of some larger
environment. \input{sample.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Observations and Data Analysis}
\label{sec:data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%
\subsection{X-ray}
\label{sec:xray}
%%%%%%%%%%%%%%%%%%

Details of the X-ray data analysis will be presented in Nulsen et
al. \citetext{in prep.}. \chandra\ data was reduced following standard
procedures: gain correction, CTI correction, bad grade filtering,
flare filtering, and point source exclusion. Background spectral
analysis was performed using the \caldb\ blank-sky observations
included in the CALDB and tailored to match each targeted
observation. Measurement of cavity power is performed identically to
\citet{rafferty06}. For each observation, an azimuthally averaged
deprojected gas density and temperature profile were used to calculate
the total gas pressure at each radius. Then, using cavity volumes
calculated from a visual measurement of a cavity's projected
cross-section, the total energy contained in each cavity is estimated
as $\ecav = pV[\gamma/(\gamma-1)]$ where $p$ is pressure, $V$ is
volume, and we assume $\gamma = 4/3$ for the ratio of specific heat
capacities. The total cavity energy is then divided by an age estimate
for the AGN outburst, yielding $\pcav = \ecav/t_{sonic}$ (see
\citet{birzan04} for discussion of how timescales are
estimated). Uncertainties for each calculation were determined by
propagating errors and summing in quadrature.

%%%%%%%%%%%%%%%%%%
\subsection{Radio}
\label{sec:radio}
%%%%%%%%%%%%%%%%%%

The 1.4 GHz continuum radio flux for each source was taken from the
flux-limited NRAO VLA Sky Survey (NVSS, \citealt{nvss}). For NGC 1553,
which is outside the NVSS survey area, the 843 MHz continuum radio
flux was taken from the flux-limited Sydney University Molonglo Sky
Survey (SUMSS, \citealt{sumss1, sumss2}). We approximate the
bolometric radio luminosity for each source using the relation $\nu
L_{\nu} = 4 \pi D_L^2 (1+z)^{\alpha-1} S_{\nu} \nu_0$ where $S_{\nu}$
is the NVSS or SUMSS flux, $z$ is redshift, $D_L$ is the luminosity
distance, $\nu_0$ is the central beam frequency of the observations,
and $\alpha$ is the radio spectral index, \eg\ $S_{\nu} \propto
\nu^{-\alpha}$. We have assumed a typical non-thermal spectral index
of $\alpha = 0.8$ \citep{1992ARA&A..30..575C}.

The radio morphologies for our sample are heterogeneous, some sources
are large and extended, while some sources are compact. To ensure the
entire radio source was measured, a fixed physical aperture of 1 Mpc
was searched around the X-ray centroid of each target. For each target
field, all detected radio sources were overlaid on a composite image
of X-ray, optical (using DSS
I/II\footnote{http://archive.stsci.edu/dss/}), and infrared emission
(using 2MASS\footnote{http://www.ipac.caltech.edu/2mass/}). When
available, the deeper and higher resolution radio data from VLA
FIRST\footnote{http://sundog.stsci.edu} was included. A visual
inspection was then performed to establish which detected radio
sources were associated with the target gE. After confirming which
radio sources within the search region were associated with the target
gE, the fluxes of the individual sources were added and the associated
uncertainties summed in quadrature.

As an extension of the NVSS search, we also reduced and analyzed
archival VLA data for each source in the sample. This additional step
was used to establish which sources are jet dominated and which are
not (see Section \S\ref{sec:r&d}). In the cases where high-resolution
VLA archival data is available, we also used the reduced images to
check the fluxes taken from NVSS, and confirm the connection between
the NVSS emission and the target gE. We found flux agreement for most
sources, the exceptions being IC 4296 and NGC 4782 where the NVSS flux
is approximately a factor of 2 lower. These sources are unique because
the radio lobes contain significant power in diffuse, extended
emission which is not detected in NVSS. For these sources, the fluxes
measured from the archival VLA data are used.

\citet{birzan08} found that the \pcav-\pthree\ relation had lower
scatter than the \pcav-\phigh\ relation. For our sample of gEs, the
quality and availability of 327 MHz data were poor, and thus we
gathered low-frequency radio fluxes from the CATS
Database\footnote{http://www.sao.ru/cats/} \citep{cats}. CATS was
queried in the frequency range 200-400 MHz using the list of radio
source coordinates found from the NVSS and SUMSS searches. Of the
\samp\ gEs in our sample, 17 objects were found in the CATS database
with fluxes in the 200-400 MHz range. The approach used for the
database search means that low-frequency radio emission which does not
have a 1.4 GHz counterpart is missed. Because CATS does not provide
source images for visual inspection, this method also ensures that
non-relevant detections are less likely to be included. Therefore, the
200-400 MHz radio powers shown in Figure \ref{fig:pcav} likely
underestimate the 200-400 MHz fluxes for these gEs. However, because
of the large range of radio powers, a systematic shift by a factor of
a few along the $P_{\nu}$ axis for all the gE points alters the
best-fit relations within the uncertainties.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and Discussion}
\label{sec:r&d}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\pjet-\prad\ Scaling Relation}
\label{sec:relation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The results from the X-ray and radio data analysis are shown in the
plots of \pcav-\phigh\ and \pcav-\plow\ presented in Figure
\ref{fig:pcav}. A subjective grade of quality was assigned for each
set of cavities -- shown as color coding in Figure \ref{fig:pcav} and
listed in Table \ref{tab:sample}. We assigned grades because,
currently, no standard algorithm for detecting cavities and
determining cavity morphology exists, and the grades quantify our
visual assessment. Grade A cavities are associated with AGN radio
activity and have well-defined boundaries; grade B cavities are
associated with AGN radio activity, but lack well-defined boundaries;
grade C cavities have poorly-defined boundaries, and their connection
to AGN radio activity is uncertain. Grade C cavities are excluded from
all fitting, as are jet dominated sources (see Section \ref{sec:jet}).

Figure \ref{fig:pcav} shows that a power law relationship between
cavity power and monochromatic radio power is continuous over
approximately 8 orders of magnitude in radio power and 6 orders of
magnitude in cavity power. To determine the form of the power-law
relation, we performed linear fits in log-space for each frequency
regime using the bivariate correlated error and intrinsic scatter
(\bces) algorithm \citep{bces}. The orthogonal \bces\ algorithm takes
in asymmetric uncertainties for both variables, assumes the presence
of intrinsic scatter, and performs a linear least-squares
regression. The best-fit parameter uncertainties are calculated using
5000 Monte Carlo bootstrap resampling trials.

The best-fit BCES determined linear function in log-space for the
\pcav-\phigh\ and \pcav-\plow\ relations are:
\begin{eqnarray}
  \log~\pcav &=& 0.70~(\pm 0.10)~\log~\phigh + 1.69~(\pm 0.18)\\
  \log~\pcav &=& 0.69~(\pm 0.08)~\log~\plow + 1.33~(\pm 0.13)
\end{eqnarray}
where \pcav\ has units $10^{42} \lum$, and \phigh\ and \plow\ have
units $10^{40} \lum$. The scatter for each relation is $\shigh = 1.07$
dex and $\slow = 0.84$ dex, and the respective correlation
coefficients are \rhigh\ = 0.74 and \rlow\ = 0.84. We have quantified
log-space scatter using the average size of the residuals about the
best-fit relation. For comparison, the scaling relations found by
\citet{birzan08} are
\begin{eqnarray}
  \log~\pcav &=& 0.35~(\pm 0.07)~\log~\phigh + 1.85~(\pm 0.10)\\
  \log~\pcav &=& 0.62~(\pm 0.08)~\log~\pthree + 1.11~(\pm 0.17)
\end{eqnarray}
where \pcav\ has units $10^{42} \lum$, and \phigh\ and \pthree\ have
units $10^{24}$ W Hz$^{-1}$ (or $\approx 10^{40} \lum$). The relations
have scatters of $\shigh = 0.85$ dex and $\sthree = 0.69$ dex. Note
that the \citet{birzan08} relations have power-law indices which
significantly differ from each other by a factor of $\approx 2$, and
that the only significant difference between the \citet{birzan08}
relations and our best-fit relations is the 1.4 GHz slope. Inclusion
of the new gE dataset shows that the \citet{birzan08} 1.4 GHz data
covered too small a range in \pcav\ to reveal a steeper relationship.

The substantial scatter highlights that radio luminosity is a poor
surrogate for accurately determining the total energy released via an
AGN in any given system because, as demonstrated with systems like
Hydra A \citep{hydraa} or MS 0735.6+7421 \citep{ms0735}, the
energetics for a system can be dominated by AGN outbursts which are
more powerful than average. This may be particularly true for gEs,
which have lower pressure halos and are more susceptible to disruption
by AGN outbursts \citep{2006MNRAS.372.1161W, 2008ApJ...687L..53P}.
However, \citet{birzan08} showed that correcting for the effect of
radio aging does reduce the scatter within the relations by 20\%. We
also point out that for the gEs, the scatter in \prad\ is larger than
the scatter in \pcav, while the opposite is true for the BCGs. This
may result from the influence of an environment on the properties of a
radio source.

We now compare our results with theoretical predictions for power
emerging from confined radio sources. Using the favored
parameterization $Q \sim L_{radio}^{\alpha}$, where $Q$ is total
kinetic jet power (\eg\ particles plus fields) and $L_{radio}$ is
observed synchrotron power, \citet{1979ApJ...232...34B} and
\citet{1995A&A...293..665F} derive a theoretical scaling relation with
slope $\alpha = 12/17~(\approx 0.71)$. Using 7C Redshift Survey 151
MHz radio powers and an estimate of $Q$ based on the hypersonic
expansion jet model of \citet{1991MNRAS.250..581F},
\citet{1999MNRAS.309.1017W} found $\alpha = 6/7~(\approx 0.86)$. These
scaling relations are plotted in Figure \ref{fig:pcav} using our
best-fit normalizations. While the $6/7$ slope of
\citet{1999MNRAS.309.1017W} significantly differs from our best-fit
relations, the agreement between these theoretical models and our data
is encouraging. With these models in mind, we now discuss jetted
sources which may not be confined and thus do not represent the
scaling relation under investigation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Jet Dominated Sources}
\label{sec:jet}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In Figure \ref{fig:pcav} we have encircled a subset of points to
highlight the systems which are jet dominated. Using high-resolution
archival VLA radio data, if $\ge 50\%$ of the radio flux from a source
originates in the jets than the lobes, then the source is deemed to be
jet dominated. The objects we have identified as jetted are: IC 4296
\citep{2003ApJ...585..677P}, NGC 315 \citep{1979ApJ...228L...9B,
  1981A&A....95..250W}, NGC 4261 \citep{1997ApJ...484..186J,
  2000ApJ...534..165J}, NGC 4782 \citep{2007ApJ...664..804M}, and NGC
7626 \citep{1985ApJ...291...32B}. Figure \ref{fig:pcav} shows the
jetted sources clustered in the region where $\pcav < 10^{42} \lum$
and $\pcav/\prad \la 70$. The jetted sources also have radio
morphologies which are distinct from the rest of the gEs, but are
similar to other jetted sources. In addition, the morphologies of the
X-ray halo surface brightness decrements are reminiscent of tunnels
rather than bubbles.

Cavity systems are typically coincident with the region of a radio
lobe, see Figure \ref{fig:pics} for an example in M84. However, for
our jetted sources, the X-ray tunnels are found at the base of the
radio outflows, approximately along the jets, see Figure
\ref{fig:pics} for an example in NGC 4261. It may be that jetted
sources do have cavities at larger radii associated with the radio
lobes, but for these systems the X-ray halo at those radii is too
faint to yield a cavity detection. If this is the case, then the
\pcav\ values might be severe underestimates, and the jetted systems
should lie closer to the best-fit \pcav-\prad\ relations. To
investigate this possibility, we calculated new \pcav\ values for the
jetted systems assuming the distances and morphologies of the radio
lobes approximately trace any potential cavities at larger radii. We
found that the change in \pcav\ was at most a factor of 5, and none of
the jetted sources moved above the $\pcav = 100\prad$ line.

Next, we calculated what cavity volumes would be required to yield a
\pcav\ which places each jetted system within $1\sigma$ of the
best-fit \pcav-\prad\ relations. Assuming spherical symmetry, the
required volumes implied cavity radii $\ga 100$ kpc, which is $10-100$
times the measured size of the radio lobes. Presently, MS 0735.6+7421
is the only known system with cavities this large \citep{ms0735}, and
no known system has a difference between the radio lobe and cavity
cross-sections exceeding a factor of a few.

It may also be that the cavity ages are smaller than is inferred from
using the gas sound speed. Using the measured radio lobe volumes and
pressure profiles, outburst ages were calculated that satisfied the
$1\sigma$ \pcav-\prad\ criterion. We found outburst ages ranging
between $0.5-1.0$ Myr were needed to make the jetted systems
consistent with the \pcav-\prad\ relations. If the cavities were
excavated on these, or slightly longer, time scales, then the implied
outflow velocities should result in gas shocking with large Mach
numbers, possibly similar to what is occuring in Centaurus A
\citep{2009MNRAS.395.1999C}.

We conclude that for the jetted systems to lie within $1\sigma$ of the
best-fit \pcav-\prad\ relations, unlikely physical scenarios are
required. Thus, if there are larger bubbles coincident with the radio
lobes, it is unlikely that the associated \pcav\ values would move the
jetted systems to a location where they are consistent with the
\pcav-\prad\ trend. For this reason, jetted systems, which are
included in the figures for completeness, are not included in any of
the fitting because it appears they are not representative of the
\pcav-\prad\ relation under study. As mentioned in Section
\ref{sec:relation}, dramatic deviation toward higher radio powers for
a given cavity power may result from environmental effects.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Conclusions}
\label{sec:summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We have presented analysis of the jet power-cavity power scaling
relation for a sample of \samp\ giant elliptical galaxies observed
with the \cxo. Cavity powers, \pcav, were calculated for each set of
cavities using similar methods to those outlined in
\citet{rafferty06}. Each set of cavities was graded from `A' to `C,'
with `A' being the most reliable cavities and `C' being the least
reliable. Monochromatic radio powers at 1.4 GHz and between 200-400
MHz were calculated using measurements from the NVSS and SUMSS
surveys, and the CATS database. We also determined which of the gE
systems were jet dominated by using jet and lobe fluxes taken from
archival, high-resolution VLA observations.

After incorporating the BCG \pcav\ and \prad\ data from
\citet{birzan08}, we find a continuous power-law relation between
\pcav-\prad\ covering 6 decades in \prad\ and 8 decades in \pcav for
high and low radio frequencies (see Figure \ref{fig:pcav}). From
individual log-space \bces\ fits, we find similar forms for the power
laws describing the \pcav-\prad\ trend with the form $\pcav \propto
\prad^{0.7}$. This relation comes with the caveat of $\sim 1.0$ dex
cosmic scatter about the best-fit relations, and we point out that the
relation is weakly applicable for determining {\it{total}} AGN energy
output. We also note the good agreement of our best-fit relations with
theoretical models, specifically the model of
\citet{1979ApJ...232...34B} which predicts a slope of $\approx 0.71$.

Of interest in our study are the jetted sources which lie far from the
best-fit relations and are not representative of the scaling relation
under study. We suggest these outliers may result from AGN jets which
are not confined by the surrounding gaseous halo. One possible
explanation for a lack of confinement in these systems is that jet
pressure does not fall below the ambient gas pressure (or some
critical pressure), and jet destabilization is then no longer a
function of environment but is a function of intrinsic jet
properties. One other possible explanation is that the mass of
material entrained by a jet before it reaches a radius where the
ambient pressure becomes significant, \eg\ $p_{jet} \sim p_{gas}$, is
insufficient to slow or destabilize a jet within the halo. In either
case, the result is a radio source which appears to have
``broken-out'' of the X-ray halo. However, the connection between
properties of radio galaxies and the host environment is still unclear
\citep[\eg][]{2008MNRAS.386.1709C}.

Several groups have applied the \birzan\ scaling relations to study
the effects of feedback from elliptical galaxies, most notably
\citet{best07} and \citet{2007MNRAS.379..260M}, with some groups now
suggesting that distributed low-power radio galaxies may dominate
heating of the ICM, \eg\ \citet{2009arXiv0908.3158H}. Up to now, the
available observational evidence did not clearly suggest if one end of
a \pjet-\prad\ relation contributed more than the other, and if a
relation derived using data for BCGs would be continuous, or of
comparable scatter, for lower power radio sources. Assuming there is
no redshift evolution of \pjet-\prad, the steepness of our relation
suggests higher mass galaxies contribute more to the process of
heating over cosmic time than do lower mass systems. But, the
formation of massive galaxies and the dense gaseous environments in
which many reside are relatively recent events. So the direct
connection between feedback, heating, environment, and epoch is not
clear, and requires further study.

%%%%%%%%%%%%%%%%%
\acknowledgements
%%%%%%%%%%%%%%%%%

KWC and BRM acknowledge generous support from the Canadian National
Science and Engineering Research Council and \cxo\ grants. The
\chandra\ X-ray Observatory Center is operated by the Smithsonian
Astrophysical Observatory for and on behalf of NASA under contract
NAS8-03060. The National Radio Astronomy Observatory is a facility of
the National Science Foundation operated under cooperative agreement
by Associated Universities, Inc.

%%%%%%%%%%%%%%
% Facilities %
%%%%%%%%%%%%%%

{\it Facilities:} \facility{CXO (ACIS)} \facility{VLA}

%%%%%%%%%%%%%%%%
% Bibliography %
%%%%%%%%%%%%%%%%

\bibliography{cavagnolo}

%%%%%%%%%%%%%%%%%%%%%%
% Figures  and Tables%
%%%%%%%%%%%%%%%%%%%%%%

\input{figs.tex}

%%%%%%%%%%%%%%%%%%%%
% End the document %
%%%%%%%%%%%%%%%%%%%%
\end{document}
