%%%%%%%%%%%%%%%%%%%
% Custom commands %
%%%%%%%%%%%%%%%%%%%

\newcommand{\bces}{{\textsc{BCES}}}
\newcommand{\birzan}{B\^irzan}
\newcommand{\samp}{21}
\newcommand{\ecav}{\ensuremath{E_{\mathrm{cav}}}}
\newcommand{\pjet}{\ensuremath{P_{\mathrm{jet}}}}
\newcommand{\pcav}{\ensuremath{P_{\mathrm{cav}}}}
\newcommand{\prad}{\ensuremath{L_{\mathrm{radio}}}}
\newcommand{\phigh}{\ensuremath{L_{\mathrm{1.4}}}}
\newcommand{\pthree}{\ensuremath{L_{\mathrm{327}}}}
\newcommand{\plow}{\ensuremath{L_{\mathrm{200-400}}}}
\newcommand{\shigh}{\ensuremath{\sigma_{\mathrm{1.4}}}}
\newcommand{\sthree}{\ensuremath{\sigma_{\mathrm{327}}}}
\newcommand{\slow}{\ensuremath{\sigma_{\mathrm{200-400}}}}
\newcommand{\rhigh}{\ensuremath{r_{\mathrm{1.4}}}}
\newcommand{\rlow}{\ensuremath{r_{\mathrm{200-400}}}}
\newcommand{\mytitle}{A RELATIONSHIP BETWEEN AGN JET POWER AND RADIO LUMINOSITY}
\newcommand{\mystitle}{AGN \pjet-\prad\ Relation}

%%%%%%%%%%
% Header %
%%%%%%%%%%

%\documentclass[12pt, preprint]{aastex}
%\documentclass{aastex}
\documentclass{emulateapj}
\usepackage{apjfonts,graphicx,here,common,longtable,ifthen,amsmath,amssymb,natbib}
%% \usepackage[pagebackref,
%%   pdftitle={\mytitle},
%%   pdfauthor={Kenneth W. Cavagnolo},
%%   pdfsubject={ApJ},
%%   pdfkeywords={},
%%   pdfproducer={LaTeX with hyperref},
%%   pdfcreator={LaTeX}
%%   pdfdisplaydoctitle=true,
%%   colorlinks=true,
%%   citecolor=blue,
%%   linkcolor=blue,
%%   urlcolor=blue]{hyperref}
\bibliographystyle{apj}
\begin{document}
\title{\mytitle}
\shorttitle{\mystitle}
\author{
K. W. Cavagnolo\altaffilmark{1,7},
B. R. McNamara\altaffilmark{1,2,3},
P. E. J. Nulsen\altaffilmark{3},\\
C. L. Carilli\altaffilmark{4},
C. Jones\altaffilmark{3},
W. Forman\altaffilmark{3},\\
L. \birzan\altaffilmark{5,6},
S. Murray\altaffilmark{3}, \&
M. W. Wise\altaffilmark{6}
}
\altaffiltext{1}{Department of Physics and Astronomy, University of
  Waterloo, Waterloo, ON N2L 3G1, Canada.}
\altaffiltext{2}{Perimeter Institute for Theoretical Physics, 31
  Caroline Street N, Waterloo, ON N2L 2Y5, Canada.}
\altaffiltext{3}{Harvard-Smithsonian Center for Astrophysics, 60
  Garden Street, Cambridge, MA 01238, USA.}
\altaffiltext{4}{National Radio Astronomy Observatory, P.O. Box 0,
  Socorro, NM 87801-0387, USA.}
\altaffiltext{5}{Department of Astronomy and Astrophysics,
  Pennsylvania State University, 525 Davey Lab, University Park, PA
  16802, USA.}
\altaffiltext{6}{Astronomical Institute Anton Pannekoek, University of
  Amsterdam, Kruislaan 403, 1098 SJ Amsterdam, Netherlands.}
\altaffiltext{7}{kcavagno@uwaterloo.ca}
\shortauthors{K. W. Cavagnolo et al.}
\journalinfo{}
\slugcomment{For submission to ApJ}

%%%%%%%%%%%%
% Abstract %
%%%%%%%%%%%%

\begin{abstract}
  Using X-ray data collected with the \cxo\ and multi-frequency VLA
  radio data, we investigate the scaling relationship between active
  galactic nucleus (AGN) jet power (\pjet) and observed radio
  luminosity (\prad). We seek to determine if the \pjet-\prad\ scaling
  relations presented in \citet{birzan08} for primarily brightest
  cluster galaxies (BCGs) are continuous in form and scatter from
  isolated giant elliptical galaxies (gEs) up to BCGs. We expand the
  sample used in \citet{birzan08} to lower radio power by
  incorporating measurements for \samp\ relatively isolated
  gEs. Combining our results with those presented in \citet{birzan08},
  we find a mean scaling relation of $\pjet \approx 4\times10^{16}~
  \prad^{0.68} \lum$ with a scatter of $\approx 0.7$ dex. We briefly
  comment on the consistency of our results with theoretical models,
  specifically those of \citet{1979ApJ...232...34B} and
  \citet{1999MNRAS.309.1017W}. Our results are consistent with models
  for confined radio sources that are close to minimum energy density
  with jet hadron to lepton energy ratios of $\ga 100$. We also
  discuss the importance of environment when measuring a
  \pjet-\prad\ relation, and a possible connection to the process of
  entrainment. A brief discussion of the implications and utility of
  our results for large-scale strucuture formation models is also
  included.
\end{abstract} 

%%%%%%%%%%%%
% Keywords %
%%%%%%%%%%%%

\keywords{galaxies: active -- galaxies: clusters: general -- X-rays:
  galaxies -- radio continuum: galaxies}

%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%

Invoking energetic feedback from AGN in numerical simulations has been
shown to bring the shape and normalization of $\Lambda$CDM galaxy
luminosity functions into better agreement with observations
\citep{croton06, bower06, saro06, sijacki07}. Observational studies
have also proven that AGN mechanical feedback supplies the necessary
energy to influence the formation and evolution of large-scale
structure \citep{birzan04, 2005MNRAS.364.1343D, rafferty06, dunn08,
  birzan08}. However, the details of how AGN feedback is coupled to
the thermodynamics of an environment are still being debated
\citep{2008ASPC..386..343D, 2009arXiv0910.3691M}. One long-standing
barrier to a better theoretical and observational understanding of
heating via AGN is reliably estimating total AGN kinetic output
\citep[\eg][]{1973MNRAS.164..243L, 1991Natur.349..138R,
  1996AJ....112....9L}.

Advancement in studying AGN feedback occurred when the
\cxo\ \citep{chandra} unambiguously revealed cavities excavated by AGN
in the X-ray emitting gas surrounding many massive galaxies
\citep[\eg][]{2000ApJ...534L.135M, perseus1, schindler01}. It was
recognized that the morphology and location of cavities are useful for
estimating the $pV$ work done by the AGN on the environment. In
conjunction with estimates of the cavity ages, the $pV$ measurements
yield an estimate of integrated AGN jet power \citep[see][for a
  review]{mcnamrev}. Unlike model-dependant calculations of AGN
kinetic power \citep[\eg][]{1999MNRAS.309.1017W}, the cavity method of
estimating jet power is more robust because the intracluster medium
acts as a bolometer, keeping an integrated, physical record of AGN
energetics.

The systematic study of large samples using the X-ray cavity technique
is limited by the capabilities of the current generation of X-ray
telescopes \citep{2009arXiv0909.0397B}. Therefore, measuring and
calibrating correlations between simple observables, like AGN radio
power (\prad), and AGN energetics becomes even more vital to
circumvent the need for deep X-ray observing programs. These types of
scaling relations can also be applied to measurements from all-sky
radio surveys (\eg\ NVSS, SUMSS, LOFAR, ALMA) to study the growth of
black holes, their accretion histories, and the mechanical heating of
the Universe over much of its lifetime \citep{croton06,
  2006MNRAS.366..397S, 2009MNRAS.395..518C}.

Using X-ray cavities to estimate \pjet, an observational
\pjet-\prad\ relationship for a sample of primarily BCGs was presented
in \citet{birzan04} and \citet[][hereafter B08]{birzan08}. In B08,
scaling relations between \pjet\ and 327 MHz, 1.4 GHz, and bolometric
radio luminosities were presented. B08 showed that $\pjet \propto
\prad^{0.5-0.7}$ depending on the choice of frequency. However, there
are few objects in the B08 study with $\prad \lesssim 10^{38} \lum$
and $\pcav \lesssim 10^{43} \lum$, \ie\ the region populated by
low-power radio galaxies like isolated gEs. In this paper we re-visit
the B08 \pjet-\prad\ study with the inclusion of \samp\ gEs. Combining
the B08 results and the results in this paper, we find a relationship
between jet power and radio power which is similar at high and low
radio frequencies. The relationships span 6-8 orders of magnitude in
\pjet\ and \prad, and have the general form $\pjet \sim 10^{43}
(\prad/10^{40})^{0.7} \lum$ with dominantly intrinsic scatter of $\sim
0.7$ dex. We also find encouraging similarity between our best-fit
relations, previous studies, and theoretical AGN models.

This paper is structured as follows: \S\ref{sec:sample} outlines the
sample of selected gEs. X-ray and radio data reduction is discussed in
\S\ref{sec:data}. Results and discussion are presented in
\S\ref{sec:r&d}. The summary and concluding remarks are given in
\S\ref{sec:summary}. \LCDM\ All quoted uncertainties are 68\%
confidence. Hereafter, the terminology cavity power and jet power are
used interchangeably, and are denoted as \pcav\ and \pjet,
respectively.

%%%%%%%%%%%%%%%%%%
\section{Sample}
\label{sec:sample}
%%%%%%%%%%%%%%%%%%

Our sample of \samp\ gEs is taken from the sample of 160 gEs compiled
by Jones et al. \citetext{in preparation}. The B08 sample is taken
from \citet[][hereafter R06]{rafferty06}. Information regarding our gE
sample is listed in Table \ref{tab:sample}. The Jones et
al. compilation is drawn from the samples of
\citet{1999MNRAS.302..209B} and \citet{2003MNRAS.340.1375O} using the
criteria that $L_K > 10^{10}~\Lsol$ and the object has been observed
with \chandra. Of the 160 gEs, extended X-ray emission was detected in
109 objects. AGN activity was suspected in 27 objects based solely on
the presence of surface brightness depressions in the X-ray emitting
gas. We have further excluded dwarf galaxies ($M_V < -19.5$) from the
sample since it is not clear that the substructure in the X-ray gas is
associated with an AGN, leaving \samp\ objects. The \samp\ gEs in our
sample are in relatively low density environments, \ie\ these are not
the central dominant or brightest galaxies in clusters or groups. The
X-ray emission associated with the gEs in our sample is dominated by
the gas gravitationally bound to the gE halo and not a diffuse,
ambient atmosphere.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Observations and Data Analysis}
\label{sec:data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%
\subsection{X-ray}
\label{sec:xray}
%%%%%%%%%%%%%%%%%%

Details of the X-ray data analysis will be presented in Nulsen et
al. \citetext{in preparation}. \chandra\ data was reduced following
standard procedures: gain correction, CTI correction, bad grade
filtering, flare filtering, and point source exclusion. Background
spectral analysis was performed using the \caldb\ blank-sky
observations included in the CALDB and tailored to match each targeted
observation. Measurement of cavity power is performed similarly to
R06. For each observation, an azimuthally averaged deprojected gas
density and temperature profile were used to calculate the total gas
pressure at each radius. Then, using cavity volumes calculated from a
visual measurement of a cavity's projected cross-section, the total
energy contained in each cavity is estimated as $\ecav =
pV[\gamma/(\gamma-1)]$ where $p$ is pressure, $V$ is volume, and we
assume $\gamma = 4/3$ for the ratio of specific heat capacities. The
total cavity energy is then divided by the buoyancy age estimate for
the cavities, yielding $\pcav = \ecav/t_{\mathrm{buoy}}$ (see
\citet{birzan04} for discussion of how buoyancy ages are
estimated). Uncertainties for each calculation were determined by
propagating errors and summing in quadrature.

%%%%%%%%%%%%%%%%%%
\subsection{Radio}
\label{sec:radio}
%%%%%%%%%%%%%%%%%%

Bolometric radio luminosities were estimated using the relation $\nu
L_{\nu} = 4 \pi D_L^2 (1+z)^{\alpha-1} S_{\nu} \nu_0$ where $S_{\nu}$
is integrated flux density at frequency $\nu_0$, $z$ is redshift,
$D_L$ is luminosity distance, $\nu_0$ is central beam frequency of the
measurements, and $\alpha$ is radio spectral index. We have assumed
the radio spectra behave as $S_{\nu} \propto \nu^{\alpha}$ with a
spectral index of $\alpha = -0.8$, typical for optically-thin,
non-thermal extragalactic radio galaxies
\citep{1992ARA&A..30..575C}. The radio luminosities estimated using
200-400 MHz and 1.4 GHz fluxes are denoted as \plow\ and \phigh,
respectively.

The 1.4 GHz continuum radio flux for each source was taken from the
flux-limited NRAO VLA Sky Survey (NVSS, \citealt{nvss}). For NGC 1553,
which is outside the NVSS survey area, the 843 MHz continuum radio
flux was taken from the flux-limited Sydney University Molonglo Sky
Survey (SUMSS, \citealt{sumss1, sumss2}). The 1.4 GHz flux for N1553
was estimated using $\alpha = 0.89$, which was calculated from the 843
MHz SUMSS flux and 5 GHz Parkes flux \citep{1970ApL.....5...29W}.

The radio morphologies for our sample are heterogeneous, some sources
are large and extended, while some sources are compact. To ensure the
entire radio source was measured, a fixed physical aperture of 1 Mpc
was searched around the X-ray centroid of each target. For each target
field, all detected radio sources were overlaid on a composite image
of X-ray, optical (DSS I/II\footnote{http://archive.stsci.edu/dss/}),
and infrared emission
(2MASS\footnote{http://www.ipac.caltech.edu/2mass/}). When available,
the deeper and higher resolution radio data from VLA
FIRST\footnote{http://sundog.stsci.edu} was included. A visual
inspection was then performed to establish which detected radio
sources were associated with the target gE. After confirming which
radio sources within the search region were associated with the target
gE, the fluxes of the individual sources were added and the associated
uncertainties summed in quadrature.

Archival VLA data for each source in the sample was also reduced and
analyzed. In the cases where high-resolution VLA archival data is
available, multifrequency images were used to confirm the connection
between NVSS detected radio sources and the host gE. Images at 1.4 GHz
were further used to check NVSS fluxes. We found flux agreement for
most sources, the exceptions being IC 4296 and NGC 4782 where the NVSS
flux is approximately a factor of 2 lower. These sources are unique
because the radio lobes contain significant power in diffuse, extended
emission which is not detected in NVSS. For these sources, the fluxes
measured from the archival VLA data are used in our analysis. The
additional data analysis step was also used to investigate the poorly
confined sources discussed in Section \S\ref{sec:r&d}. For the systems
where nuclear radio emission was resolved, we found, on average
$S_{\nu,\mathrm{nucleus}}/S_{\nu,\mathrm{total}} \la 0.1$, suggesting
the nuclear contribution to the low-resolution NVSS measurements has a
negligible impact on our results.

B08 found that using lower frequency radio data, \ie\ 327 MHz versus
1400 MHz, resulted in a lower scatter \pcav-\prad\ relation. For our
sample of gEs, the quality and availability of 327 MHz data were poor,
and thus we gathered low-frequency radio fluxes from the CATS
Database\footnote{http://www.sao.ru/cats/} \citep{cats}. CATS was
queried in the frequency range 200-400 MHz using the list of radio
source coordinates found from the NVSS and SUMSS searches. Of the
\samp\ gEs in our sample, 17 objects were found in the CATS database
with fluxes in the 200-400 MHz range. The approach used for searching
CATS means that low-frequency radio emission which does not have a 1.4
GHz counterpart is missed. Because CATS does not provide source images
for visual inspection, this method also ensures that non-relevant
detections are less likely to be included. Therefore, the 200-400 MHz
radio powers shown in Figure \ref{fig:pcav} likely underestimate the
200-400 MHz fluxes for these gEs. However, because of the large range
of radio powers, a systematic shift by a factor of a few along the
\prad\ axis for all the gE points only alters the best-fit slope
within the uncertainties.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and Discussion}
\label{sec:r&d}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\pjet-\prad\ Scaling Relation}
\label{sec:relation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The results from the X-ray and radio data analysis are shown in the
plots of \pcav-\phigh\ and \pcav-\plow\ presented in Figure
\ref{fig:pcav}. A subjective grade of quality was assigned to each set
of cavities -- shown as color coding in Figure \ref{fig:pcav} and
listed in Table \ref{tab:sample}. We assigned grades because,
currently, no standard algorithm for detecting cavities and
determining cavity morphology exists, and the grades quantify our
visual assessment. Grade A cavities are associated with AGN radio
activity and have well-defined boundaries; grade B cavities are
associated with AGN radio activity, but lack well-defined boundaries;
grade C cavities have poorly-defined boundaries, and their connection
to AGN radio activity is uncertain. Grade C cavities are excluded from
all fitting.

Figure \ref{fig:pcav} shows that a power law relationship between
cavity power and radio power is continuous over approximately 8 orders
of magnitude in radio power and 6 orders of magnitude in cavity
power. To determine the form of the power-law relation, we performed
linear fits in log-space for each frequency regime using the bivariate
correlated error and intrinsic scatter (\bces) algorithm
\citep{bces}. The orthogonal \bces\ algorithm takes in asymmetric
uncertainties for both variables, assumes the presence of intrinsic
scatter, and performs a linear least-squares regression which
minimizes the squared orthogonal distance to the best-fit
relation. This differs from the fitting approach in B08 which
minimized the distance in the \pcav\ coordinate. The best-fit
parameter uncertainties were calculated using $10,000$ Monte Carlo
bootstrap resampling trials.

The best-fit orthogonal BCES determined linear function in log-space
for the \pcav-\phigh\ and \pcav-\plow\ relations are:
\begin{eqnarray}
  \log~\pcav &=& 0.72~(\pm 0.13)~\log~\phigh + 1.92~(\pm 0.17) \label{eqn:high}\\
  \log~\pcav &=& 0.64~(\pm 0.08)~\log~\plow + 1.55~(\pm 0.12) \label{eqn:low}
\end{eqnarray}
where \pcav\ has units $10^{42} \lum$, and \phigh\ and \plow\ have
units $10^{40} \lum$. The scatter for each relation is $\shigh = 0.77$
dex and $\slow = 0.61$ dex, and the respective correlation
coefficients are \rhigh\ = 0.73 and \rlow\ = 0.81. We have quantified
the total scatter about the best-fit relation,
$\sigma_{\mathrm{total}}$, using a weighted estimate of the orthogonal
distances to the best-fit line:
\begin{eqnarray}
  \sigma_{\mathrm{total}} &=& \sqrt{\frac{\sum_{i=1}^N w_i (P_{\mathrm{cav},i}-m L_{\mathrm{radio},i}-b)^2}{N-2}} \nonumber \\
  w_i &=& \frac{N}{\sigma_i^2 \sum_{i=1}^N \sigma_i^{-2}} \nonumber \\
  \sigma_i^2 &=& \sigma_{\pcav,i}^2 + m^2 \sigma_{\prad,i}^2 \nonumber
\end{eqnarray}
where $m$ and $b$ are the best-fit slope and intercept in Equations
\ref{eqn:high} and \ref{eqn:low}. For comparison, the B08 scaling
relations are
\begin{eqnarray}
  \log~\pcav &=& 0.35~(\pm 0.07)~\log~\phigh + 1.85~(\pm 0.10) \label{eqn:err}\\
  \log~\pcav &=& 0.51~(\pm 0.07)~\log~\pthree + 1.51~(\pm 0.12)
\end{eqnarray}
where \pcav\ has units $10^{42} \lum$, and \phigh\ and \pthree\ have
units $10^{24}$ W Hz$^{-1}$ (or $\approx 10^{40} \lum$). The relations
have scatters of $\shigh = 0.85$ dex and $\sthree = 0.81$
dex. Equation \ref{eqn:err} and its scatter have been revised from the
B08 published values \citep{birzan08err}. Note that the B08 relations
have power-law indices which significantly differ from each other by a
factor of $\approx 1.5$. Inclusion of the new gE dataset shows that
the B08 1.4 GHz data had too few points, with large dispersion, at
$\pcav \la 10^{43} \lum$ to reveal a steeper relationship.

We also point out that for Cygnus A (point with largest \prad\ in
Figure \ref{fig:pcav}), where our \pjet-\prad\ relations appear to
overestimate the jet power by $\approx 40$, the total kinetic
luminosity of $\approx 2\times10^{46} \lum$ derived by
\citep{2006ApJ...644L...9W} using the shock is consistent with the
\pjet\ value of $\approx 5\times10^{46} \lum$ predicted by our
relations. Hercules A (which is not in the B08 sample) is a similar
case, with $\pcav = 310\times10^{42} \lum$ and $\phigh \approx
4100\times10^{40} \lum$, which places HercA in the same region of
Figure \ref{fig:pcav} as Cygnus A. But, the total kinetic luminosity
of $1.6\times10^{46} \lum$ derived in \citet{herca} using the shock
agrees with the prediction from our relations, $3.2\times10^{46}
\lum$.

The substantial scatter in these relations highlight that, for an
individual system, radio luminosity is a poor surrogate for accurately
determining the integrated AGN energy output. As seen in systems like
Hydra A \citep{hydraa} or MS 0735.6+7421 \citep{ms0735}, the
energetics of a system can be dominated by the effects of an AGN
outburst which is more powerful than average. This may be particularly
true for gEs, which have lower pressure halos and are more susceptible
to disruption by AGN outbursts \citep{2006MNRAS.372.1161W,
  2008ApJ...687L..53P}. However, B08 showed that correcting for the
effect of radio aging by including a scaling with break frequency does
reduce the scatter within the relations by $\approx 50\%$. We also
point out that for the gEs, the scatter in \prad\ is larger than the
scatter in \pcav, while the opposite is true for the B08 sample. This
may result from the influence of an environment on the properties of a
radio source.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with Models and Previous Studies}
\label{sec:models}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Owing to the importance of kinetic feedback in galaxy formation
models, specifically in the form of a late-time radio-mode extension
of the quasar era, reliably estimating total AGN kinetic output is
vital \citep{2007ApJ...658L...9H}. Thus, we compare our results with
previous observational studies and theoretical jet models. In this
section we use the parameterization for jet power favored by
theorists, namely $L_{\mathrm{kin}} = \eta \prad^{\alpha}$, where
$L_{\mathrm{kin}}$ is total kinetic jet power, $\eta$ is some
normalization, $\alpha$ is a scaling index, and \prad\ is emergent
synchrotron power.

For flat-spectrum compact radio cores (\eg\ small scale jets and not
radio lobes), the jet model by \citet{1979ApJ...232...34B} predicts
$\alpha = 12/17~(\approx 0.71)$. Starting with the
\citet{1979ApJ...232...34B} model, \citet{1995A&A...293..665F} found a
similar slope when assuming emergent jet power scales with accretion
power in a fully-conserved jet-disk system, and the more generalized
model for scale-invariant jets by \citet{2003MNRAS.343L..59H} also
predicts $\alpha = 12/17$. Utilizing a collection of objects from the
R06 sample and 5 GHz core luminosities corrected for relativistic
Doppler boosting, \citet{2007MNRAS.381..589M} found that $\alpha =
0.81$ with $\eta \approx 2\times10^{44} \lum$ when \prad\ is in units
of $10^{40} \lum$. Another study by \citet{2005ApJ...633..384H} using
5 GHz core luminosities, an estimate of $L_{\mathrm{kin}}$ from the
Galactic X-ray binary mass-radio-X-ray fundamental plane relation
\citep{2003MNRAS.344...60G, 2003MNRAS.345.1057M}, and fixing
$L_{\mathrm{kin}} \propto \prad^{12/17}$ found that $\eta \approx
6\times10^{44} \lum$ when \prad\ is in units of $10^{40} \lum$.

\citet[][hereafter W99]{1999MNRAS.309.1017W} derive $\alpha$ and
$\eta$ using the hypersonic jet model of \citet{1991MNRAS.250..581F}
and assuming radio lobes are at minimum energy density \citep[see][for
  details]{1980ARA&A..18..165M}. W99 derived $\alpha = 6/7$ with $\eta
\approx f^{3/2}~4.61\times10^{41} \lum$ where \prad\ is in units of
$10^{40} \lum$ and has been adjusted from 151 MHz to 1.4 GHz assuming
$\alpha = -0.8$. The factor $f$ consolidates a variety of unknowns
(see W99 for details). The fiducial W99 model ($f=1$) yields $\eta$
two orders of magnitude lower than our best-fit
normalizations. Because the W99 model has been widely used for
estimating jet power, the difference in $\eta$'s needs to explored.

The W99 normalization has a weak dependence on environmental
assumptions (\ie\ altering ambient gas density and outflow velocity
change $\eta$ by factors of $\sim 2-5$), but a critical dependence on
several unknown quantities, namely the fractional deviation from the
minimum-energy condition and the ratio of hadron to lepton energy in
the jets (this ratio is commonly denoted as $k$). As a test, we
recalculated $\eta$ assuming the deviation from minimum energy is 0.75
and $k = 100$, a roughly canonical value \citep{2005MNRAS.364.1343D,
  2006MNRAS.372.1741D, 2006ApJ...648..200D, birzan08}. Under these
assumptions, the W99 normalization is revised up by a factor of
$\approx 200$, bringing the W99 zero-point into closer agreement with
our work. Indeed, W99 find that to fit their model to narrow-line
luminosities (assuming $Q_{\mathrm{narrow}} = Q$) for sources in the
7C and 3CRR surveys, $f$ must equal 20, which has $k = 20$ and is the
upper-limit of $f$ in their model. Plotted in Figure \ref{fig:radeff}
are the W99 model for low-$k$ and high-$k$ values along with our
best-fit for the 1.4 GHz \pjet-\prad\ relation.

Our results do not suggest if any particular model is favored over
another for two reasons: (1) our best-fit values do not significantly
differ from any one model's predictions, and (2) the models and
studies we have compared with probe different physical scales and
environments. However, the similarity of our results with these models
and studies is encouraging. It is also interesting that the W99 model
with $k \gg 1$ yields better agreement with our data. One important
aspect of jet models, and observational studies, is the issue of radio
source confinement. We now turn our attention to the set of points
plotted in Figure \ref{fig:radeff} which represent sources we suspect
are poorly confined by the ambient medium.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Poorly Confined Sources}
\label{sec:jet}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Included in Figure \ref{fig:radeff} is a set of points highlighting
systems we have classified as being poorly confined (PC). The objects
are: IC 4296 \citep{1988ApJ...324..198K, 2003ApJ...585..677P}, NGC 315
\citep{1979ApJ...228L...9B, 1981A&A....95..250W}, NGC 4261
\citep{1997ApJ...484..186J, 2000ApJ...534..165J}, NGC 4782
\citep{2007ApJ...664..804M}, and NGC 7626 \citep{1985ApJ...291...32B}.
These objects were initially culled from the sample because the
morphologies of the X-ray surface brightness decrements are
reminiscent of tunnels rather than bubbles, and the radio morphologies
are distinctly different from the rest of the gE and B08
objects. X-ray cavities typically trace a substantial fraction of the
jet+lobe radio emission, see Figure \ref{fig:pics} for an example in
M84. However, for the PC sources, the only indication of gas
excavation in the X-ray halo is found near the base of the jets,
seemingly at the ``edge'' of the X-ray halo, see Figure \ref{fig:pics}
for an example in NGC 4261. This appearance of breaking-out from the
detected X-ray halo is our reason for calling these poorly confined
sources.

Defining the small voids as ``cavities'' is misleading. The
\pcav\ values used in this study are meant to be estimates of the
integrated jet power. This is not the case for the PC sources as the
small voids are clearly incomplete records of the total $p~dV$ work
being done by the jets. However, there may be proper cavities at
larger radii associated with the radio lobes, but for PC systems the
ambient medium at those radii is too faint to yield a cavity
detection.

We calculated \pcav\ values for the PC systems assuming radio lobe
morphology approximates the volume of cavities potentially at larger
radii. Pressure profiles were extrapolated to large radii using the
best-fit parameters of a $\beta$-model \citep{betamodel} fit to the
surface brightness profile, assuming the ambient atmosphere is
isothermal, and adding a background gas pressure\footnote{The assumed
  background gas pressure is based on the mean value observed in
  outskirts of clusters and groups. See
  http://www.pa.msu.edu/astro/MC2/accept for a catalog of such
  pressure profiles.} value of $10^{-13}$ dyne \pcmsq. Cavity ages
were calculated assuming expansion at the gas sound speed. As a result
of the radio lobes extending into regions where the pressure profiles
are very steep and approaching the background pressure, the large
volumes are offset by much lower pressures and longer ages, resulting
in modest values of \pcav.

Two of the PC sources, NGC 315 and NGC 4261, are part of a sample of
nine FR-I objects analyzed in detail by \citet[][hereafter
  C08]{2008MNRAS.386.1709C} using \xmm\ X-ray observations. Provided
in C08 are the $4pV$ enthalpies for each FR-I source (calculated using
the radio lobe volumes and the external thermal pressure at the lobe
mid-point), and the mean temperature of the group environments into
which the lobes are expanding. Assuming lobe expansion occurs at the
ambient gas sound speed, we calculated \pcav\ values for each of the
C08 FR-I sources. For N315 and N4261 we find no significant difference
between the \pcav\ values calculated using the \chandra\ data and the
\xmm\ data from C08. Using the NVSS search method outlined in Section
\ref{sec:radio} we calculated \phigh\ for each C08 FR-I source. Our PC
objects and the C08 FR-I objects are plotted in Figure
\ref{fig:radeff}.

Figure \ref{fig:radeff} shows that the PC and C08 FR-I sources reside
well below our best-fit relation. Because we do not have a robust
measurement of \pcav\ for the PC systems, they were excluded from the
preceding analysis of the \pjet-\prad\ relations. However, it is
doubtful that the jets in these systems have intrinsically lower
kinetic power per unit radio emission as their deviation from the mean
\pjet-\prad\ relation suggests. One reason is that the \pcav\ method
cannot account for jet energy which goes into shocks. On average,
shock energy is a small correction, factor of a few \citep{mcnamrev},
but the frequency and variety of AGN driven shocks is broad, ranging
from strong (Mach $\ga 2$) -- Centaurus A \citep{2003ApJ...592..129K,
  2009MNRAS.395.1999C}, NGC 3801 \citep{2007ApJ...660..191C} -- to
weak (Mach $\la 2$) -- 3C 31 \citep{2002MNRAS.336.1161L}, Cygnus A
\citep{2006ApJ...644L...9W}, Hydra A \citep{hydraa}, Hercules A
\citep{herca}, M87 \citep{2007ApJ...665.1057F}, MS 0735.6+7421
\citep{ms0735}, NGC 4552 \citep{2006ApJ...648..947M}, NGC 4636
\citep{2009arXiv0909.2942B}, NGC 4782 \citep[][shock attributed to
  merger, but also coincident with radio outflow]{2007ApJ...664..804M}
-- to definitively absent -- 3C 186 \citep{2008ApJ...684..811S}, 3C
388 \citep{2006ApJ...639..753K}, NGC 6764
\citep{2008ApJ...688..190C}. It is possible that for the PC and C08
FR-I sources, some fraction of jet energy went into shocks.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Conclusions}
\label{sec:summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We have presented analysis of the jet power-radio power scaling
relation for a sample of \samp\ giant elliptical galaxies observed
with the \cxo. Cavity powers, \pjet, were calculated for each set of
cavities using similar methods to those outlined in R06. Bolometric
radio luminosities were estimated using 1.4 GHz and 200-400 MHz fluxes
taken from the NVSS/SUMSS surveys and the CATS database.

Incorporating the data from B08, we find a continuous power-law
relation between \pjet-\prad\ covering 6 decades in \prad\ and 8
decades in \pjet\ for high and low radio frequencies (see Figure
\ref{fig:pcav}). From log-space orthogonal \bces\ fits, we find
similar forms for the power laws describing the \pjet-\prad\ trend
with the mean form $\pjet \approx 5.93\times10^{43}
(\prad/10^{40})^{0.68} \lum$. This relation comes with the caveat of
$\approx 0.7$ dex scatter about the best-fit relations, and we point
out that the relation is weakly applicable for determining
{\it{total}} AGN energy output. We also note the agreement of our
best-fit relations with predictions from theoretical models for how
kinetic jet power scales with emergent radio power.

Several groups have applied the \birzan\ scaling relations to study
the effects of AGN feedback on structure formation, most notably
\citet{best07} and \citet{2007MNRAS.379..260M}, with some groups now
suggesting that distributed low-power radio galaxies may dominate
heating of the ICM, \eg\ \citet{2009arXiv0908.3158H}. Up to now, the
available observational results, which were primarily calibrated to
high-power radio sources, did not clearly indicate if a
\pjet-\prad\ relation would be continuous, or of comparable scatter,
for lower power radio sources. Assuming there is no redshift evolution
of \pjet-\prad, the slope of our relations suggest higher mass
galaxies contribute more to the process of heating over cosmic time
than do lower mass galaxies.

We have also highlighted a subset of objects we classify as poorly
confined. These objects have \pjet/\prad\ ratios which are large
relative to the rest of our sample. In addition, the poorly confined
sources reside in the same region of the \pjet-\prad\ plane as the
FR-I sources taken from C08. An explanations for the behavior of these
sources lies in the long-standing effort to understand the connection
between properties of radio galaxies and their environment. One
possible explanation is mass entrainment by the jets.

We point out, that these sources reside on the underside of the
\pjet-\prad\ relation with M87 and Cygnus A, which are well-studied
systems known to have low hadron content \eg\ $k \approx 40$ and $k
\approx 5$, respectively \citep{birzan08}. Without assuming the W99
model is correct, and using it as a guide for how $k$ influences the
observed radio power per unit kinetic luminosity, low-$k$ sources
indeed reside on the underside of the \pjet-\prad\ relation (see
Figure \ref{fig:radeff}). The suggestion being that jets start out
light, entrain material as they move out, and become heavy on
large-scales, \eg\ $k$ and environment are connected.

galaxy formation models which include preheating or
  distributed heating.

%%%%%%%%%%%%%%%%%
\acknowledgements
%%%%%%%%%%%%%%%%%

KWC and BRM acknowledge generous support from the Canadian National
Science and Engineering Research Council and \cxo\ grants. KWC
sincerely thanks Judith Croston and Chris Willott for helpful
discussions. The \chandra\ X-ray Observatory Center is operated by the
Smithsonian Astrophysical Observatory for and on behalf of NASA under
contract NAS8-03060. The National Radio Astronomy Observatory is a
facility of the National Science Foundation operated under cooperative
agreement by Associated Universities, Inc.

%%%%%%%%%%%%%%
% Facilities %
%%%%%%%%%%%%%%

{\it Facilities:} \facility{CXO (ACIS)} \facility{VLA}

%%%%%%%%%%%%%%%%
% Bibliography %
%%%%%%%%%%%%%%%%

%\bibliography{cavagnolo}
\bibliography{test}

%%%%%%%%%%%%%%%%%%%%%%
% Figures  and Tables%
%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\input{sample.tex}
\input{figs.tex}

%%%%%%%%%%%%%%%%%%%%
% End the document %
%%%%%%%%%%%%%%%%%%%%
\end{document}

% LocalWords:  CTI
