%%%%%%%%%%%%%%%%%%%
% Custom commands %
%%%%%%%%%%%%%%%%%%%

\newcommand{\bces}{{\textsc{BCES}}}
\newcommand{\birzan}{B\^irzan}
\newcommand{\samp}{21}
\newcommand{\ecav}{\ensuremath{E_{\mathrm{cav}}}}
%\newcommand{\pjet}{\ensuremath{P_{\mathrm{jet}}}}
%\newcommand{\prad}{\ensuremath{L_{\mathrm{radio}}}}
\newcommand{\phigh}{\ensuremath{L_{\mathrm{1.4}}}}
\newcommand{\pthree}{\ensuremath{L_{\mathrm{327}}}}
\newcommand{\plow}{\ensuremath{L_{\mathrm{200-400}}}}
\newcommand{\shigh}{\ensuremath{\sigma_{\mathrm{1.4}}}}
\newcommand{\sthree}{\ensuremath{\sigma_{\mathrm{327}}}}
\newcommand{\slow}{\ensuremath{\sigma_{\mathrm{200-400}}}}
\newcommand{\rhigh}{\ensuremath{r_{\mathrm{1.4}}}}
\newcommand{\rlow}{\ensuremath{r_{\mathrm{200-400}}}}
\newcommand{\mytitle}{A RELATIONSHIP BETWEEN AGN JET POWER AND RADIO LUMINOSITY}
\newcommand{\mystitle}{AGN \pjet-\prad\ Relation}

%%%%%%%%%%
% Header %
%%%%%%%%%%

%\documentclass[12pt, preprint]{aastex}
%\documentclass{aastex}
\documentclass{emulateapj}
\usepackage{apjfonts,graphicx,here,common,longtable,ifthen,amsmath,amssymb,natbib}
\usepackage[pagebackref,
  pdftitle={\mytitle},
  pdfauthor={Dr. Kenneth W. Cavagnolo},
  pdfsubject={Astrophysical Journal},
  pdfkeywords={galaxies: active -- galaxies: clusters: general --
    X-rays: galaxies -- radio continuum: galaxies},
  pdfproducer={LaTeX with hyperref},
  pdfcreator={LaTeX with hyperref}
  pdfdisplaydoctitle=true,
  colorlinks=true,
  citecolor=blue,
  linkcolor=blue,
  urlcolor=blue]{hyperref}
\bibliographystyle{apj}
\begin{document}
\title{\mytitle}
\shorttitle{\mystitle}
\author{
K. Cavagnolo\altaffilmark{1,7},
B. McNamara\altaffilmark{1,2,3},
P. Nulsen\altaffilmark{3},\\
C. Carilli\altaffilmark{4},
C. Jones\altaffilmark{3},
W. Forman\altaffilmark{3},\\
L. \birzan\altaffilmark{5},
S. Murray\altaffilmark{3}, \&
M. Wise\altaffilmark{6}
}
\altaffiltext{1}{Department of Physics and Astronomy, University of
  Waterloo, Waterloo, ON N2L 3G1, Canada.}
\altaffiltext{2}{Perimeter Institute for Theoretical Physics, 31
  Caroline Street N, Waterloo, ON N2L 2Y5, Canada.}
\altaffiltext{3}{Harvard-Smithsonian Center for Astrophysics, 60
  Garden Street, Cambridge, MA 01238, USA.}
\altaffiltext{4}{National Radio Astronomy Observatory, P.O. Box 0,
  Socorro, NM 87801-0387, USA.}
\altaffiltext{5}{Leiden Observatory, University of Leiden, P.O. 9513,
  2300 RA Leiden, The Netherlands}
\altaffiltext{6}{Astronomical Institute Anton Pannekoek, University of
  Amsterdam, Kruislaan 403, 1098 SJ Amsterdam, Netherlands.}
\altaffiltext{7}{kcavagno@uwaterloo.ca}
\shortauthors{K. W. Cavagnolo et al.}
\journalinfo{}
\slugcomment{For submission to ApJ}

%%%%%%%%%%%%
% Abstract %
%%%%%%%%%%%%

\begin{abstract}
  Using X-ray data collected with the \cxo\ and multi-frequency VLA
  radio data, we investigate the scaling relationship between active
  galactic nucleus (AGN) jet power (\pjet) and observed radio
  luminosity (\prad). We seek to determine if the \pjet-\prad\ scaling
  relations presented in \citet{birzan08} for primarily brightest
  cluster galaxies (BCGs) are continuous in form and scatter from
  isolated giant elliptical galaxies (gEs) up to BCGs. We expand the
  sample used in \citet{birzan08} to lower radio power by
  incorporating measurements for \samp\ relatively isolated
  gEs. Combining our results with those presented in \citet{birzan08},
  we find a mean scaling relation of $\pjet \approx 4\times10^{16}~
  \prad^{0.68} \lum$ with a scatter of $\approx 0.7$ dex. We briefly
  comment on the consistency of our results with theoretical models,
  specifically those of \citet{1979ApJ...232...34B} and
  \citet{1999MNRAS.309.1017W}. Our results are consistent with models
  for confined radio sources that are close to minimum energy density
  with jet hadron to lepton energy ratios of $\ga 100$. We also
  discuss the importance of environment when measuring a
  \pjet-\prad\ relation, and a possible connection to the process of
  entrainment. A brief discussion of the implications and utility of
  our results for large-scale structure formation models is also
  included.
\end{abstract} 

%%%%%%%%%%%%
% Keywords %
%%%%%%%%%%%%

\keywords{galaxies: active -- galaxies: clusters: general -- X-rays:
  galaxies -- radio continuum: galaxies}

%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%

The current galaxy formation paradigm conforms to observational
findings that most galaxies harbor a centralized supermassive black
hole which has co-evolved with the host galaxy
\citep{1995ARA&A..33..581K, magorrian}. Additional observational
evidence supports the theory that the properties of host galaxies and
their environment depend strongly on the presence of an AGN
\citep[\ie][]{2005MNRAS.362...25B}. Invoking energetic feedback from
AGN in numerical simulations has been shown to bring the shape and
normalization of the galaxy luminosity function into better agreement
with observations \citep{croton06, bower06, saro06,
  sijacki07}. Observational studies have also proven that AGN
mechanical feedback supplies the necessary energy to influence the
formation and evolution of large-scale structure \citep{birzan04,
  2005MNRAS.364.1343D, rafferty06, dunn08, birzan08}. However, the
details of how AGN feedback is coupled to the thermodynamics of an
environment are still being debated \citep{2008ASPC..386..343D,
  2009arXiv0910.3691M}. One long-standing barrier to a better
theoretical and observational understanding of heating via AGN is
reliably estimating total AGN kinetic output
\citep[\eg][]{1991Natur.349..138R, 1996AJ....112....9L}.

The \cxo\ \citep{chandra} advanced the study of AGN feedback when
observations unambiguously revealed cavities excavated by AGN in the
X-ray emitting gas surrounding many massive galaxies
\citep[\eg][]{2000ApJ...534L.135M, perseus1, schindler01}. It was
recognized that the size and location of cavities are useful for
estimating the $pV$ work done by the AGN on the environment
\citep{2000ApJ...534L.135M}. In conjunction with estimates of cavity
age, the $pV$ measurements yield an estimate of integrated AGN jet
power, \pjet\ \citep[see][for a review]{mcnamrev}. Unlike
model-dependant calculations of AGN kinetic power
\citep[\eg][]{1999MNRAS.309.1017W}, cavity based estimates of
\pjet\ are more robust because the gaseous environments keep an
integrated, physical record of AGN energetics.

The systematic study of large samples using the X-ray cavity technique
is limited by factors such as cavity size, cavity projection on the
sky, ambient medium-cavity surface brightness contrast, and
observational parameters such as exposure time and angular resolution
\citep{2009arXiv0909.0397B}. Therefore, measuring and calibrating
correlations between simple observables, like AGN radio power, and AGN
energetics is vital to circumvent the need for deep X-ray observing
programs. These types of scaling relations can also be applied to
measurements from current and future all-sky radio surveys (\eg\ NVSS,
SUMSS, LOFAR, SKA) to study the formation history of black holes,
their accretion histories, and the resulting mechanical heating of the
Universe \citep{croton06, 2006MNRAS.366..397S}.

Using X-ray cavities to estimate \pjet, an observational
\pjet-\prad\ relationship for a sample of primarily BCGs was presented
in \citet[][hereafter B04]{birzan04} and \citet[][hereafter
  B08]{birzan08}. In B08, scaling relations between \pjet\ and 327
MHz, 1.4 GHz, and bolometric radio luminosities were presented. B08
showed that $\pjet \propto \prad^{0.5-0.7}$ depending on the choice of
frequency. However, there are few objects in the B08 study with $\prad
\lesssim 10^{38} \lum$ and $\pcav \lesssim 10^{43} \lum$, \ie\ the
region populated by low-power radio galaxies like isolated gEs. In
this paper we re-visit the B08 \pjet-\prad\ study with the inclusion
of \samp\ gEs. Combining the B08 results and the results in this
paper, we find a relationship between jet power and radio power which
is similar at high and low radio frequencies. The relationships span
6-8 orders of magnitude in \pjet\ and \prad, and have the general form
$\pjet \sim 10^{43} (\prad/10^{40})^{0.7} \lum$ with dominantly
intrinsic scatter of $\sim 0.7$ dex. We also find encouraging
similarity between our best-fit relations, previous studies, and
theoretical AGN models.

This paper is structured as follows: \S\ref{sec:sample} outlines the
sample of selected gEs. X-ray and radio data reduction is discussed in
\S\ref{sec:data}. Results and discussion are presented in
\S\ref{sec:r&d}. The summary and concluding remarks are given in
\S\ref{sec:summary}. \LCDM\ All quoted uncertainties are 68\%
confidence. Hereafter, the terminology cavity power and jet power are
used interchangeably, and are denoted as \pcav\ and \pjet,
respectively.

%%%%%%%%%%%%%%%%%%
\section{Sample}
\label{sec:sample}
%%%%%%%%%%%%%%%%%%

Our sample of \samp\ gEs is taken from the sample of 160 gEs compiled
by Jones et al. \citetext{in preparation}. The B08 sample is taken
from \citet[][hereafter R06]{rafferty06}. Information regarding our gE
sample is listed in Table \ref{tab:sample}. The Jones et
al. compilation is drawn from the samples of
\citet{1999MNRAS.302..209B} and \citet{2003MNRAS.340.1375O} using the
criteria that $L_K > 10^{10}~\Lsol$ and the object has been observed
with \chandra. Of the 160 gEs, extended X-ray emission was detected in
109 objects. AGN activity was suspected in 27 objects based solely on
the presence of surface brightness depressions in the X-ray emitting
gas. We have further excluded dwarf galaxies ($M_V < -19.5$) from the
sample since it is not clear that the substructure in the X-ray gas is
associated with an AGN, leaving \samp\ objects. The \samp\ gEs in our
sample are in relatively low density environments, \ie\ these are not
the central dominant or brightest galaxies in clusters or groups. The
gEs studied here have X-ray halos and radio sources with luminosities
lower than are typically found for cDs and BCGs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Observations and Data Analysis}
\label{sec:data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%
\subsection{X-ray}
\label{sec:xray}
%%%%%%%%%%%%%%%%%%

Outburst powers are determined in the usual manner from the X-ray data
(see B04 and R06). Gas properties used here are taken from the
analysis by Jones et al (in preparation). Cavity locations and sizes
are from Nulsen et al. (in preparation), with cavity volumes and their
errors calculated by the method of B04 which takes into account the
unknown cavity geometry. The enthalpy of each cavity is determined as
$H_{\mathrm{cav}} = [\gamma/(\gamma-1)] p V$, where $p$ is the gas
pressure at the radius of the projected center of the cavity, and $V$
is its volume, assuming $\gamma = 4/3$ for the ratio of specific heat
capacities. To estimate the average power of an outburst, the enthalpy
of each cavity is divided by an estimate of its age and these are
summed for all the cavities in each system to obtain an estimate of
the average outburst power of its AGN.  For compatibility with B08,
here we give results only for the buoyant age estimates,
$t_{\mathrm{buoy}}$ (B04). Because the uncertainties are large
(chiefly due to the volume estimates), errors are propagated in log
space, assuming that the errors in the main inputs are independent.

%%%%%%%%%%%%%%%%%%
\subsection{Radio}
\label{sec:radio}
%%%%%%%%%%%%%%%%%%

Bolometric radio luminosities were estimated using the relation $\nu
L_{\nu} = 4 \pi D_L^2 (1+z)^{\alpha-1} S_{\nu} \nu_0$ where $S_{\nu}$
is integrated flux density at frequency $\nu_0$, $z$ is redshift,
$D_L$ is luminosity distance, $\nu_0$ is central beam frequency of the
measurements, and $\alpha$ is radio spectral index. We have assumed
the radio spectra behave as $S_{\nu} \propto \nu^{-\alpha}$ with a
spectral index of $\alpha = 0.8$, typical for optically-thin,
non-thermal extragalactic radio galaxies
\citep{1992ARA&A..30..575C}. The radio luminosities estimated using
200-400 MHz and 1.4 GHz fluxes are denoted as \plow\ and \phigh,
respectively.

The 1.4 GHz continuum radio flux for each source was taken from the
flux-limited NRAO VLA Sky Survey (NVSS, \citealt{nvss}). For NGC 1553,
which is outside the NVSS survey area, the 843 MHz continuum radio
flux was taken from the flux-limited Sydney University Molonglo Sky
Survey (SUMSS, \citealt{sumss1, sumss2}). The 1.4 GHz flux for N1553
was estimated using $\alpha = 0.89$, which was calculated from the 843
MHz SUMSS flux and 5 GHz Parkes flux \citep{1970ApL.....5...29W}.

The radio morphologies for our sample are heterogeneous: some sources
are large and extended, while some sources are compact. To ensure the
entire radio source was measured, a fixed physical aperture of 1 Mpc
was searched around the X-ray centroid of each target. For each target
field, all detected radio sources were overlaid on a composite image
of X-ray, optical (DSS I/II\footnote{http://archive.stsci.edu/dss/}),
and infrared emission
(2MASS\footnote{http://www.ipac.caltech.edu/2mass/}). When available,
the deeper and higher resolution radio data from VLA
FIRST\footnote{http://sundog.stsci.edu} was included. A visual
inspection was then performed to establish which detected radio
sources were associated with the target gE. After confirming which
radio sources within the search region were associated with the target
gE, the fluxes of the individual sources were added and the associated
uncertainties summed in quadrature.

Archival VLA data for each source in the sample was also reduced and
analyzed. In the cases where high-resolution VLA archival data is
available, multifrequency images were used to confirm the connection
between NVSS detected radio sources and the host gE. Images at 1.4 GHz
were further used to check NVSS fluxes. We found flux agreement for
most sources, with the exceptions being IC 4296 and NGC 4782, where
the NVSS flux is approximately a factor of 2 lower. These sources are
unique because the radio lobes contain significant power in diffuse,
extended emission which is not detected in NVSS. For these sources,
the fluxes measured from the archival VLA data are used in our
analysis. The additional data analysis step was also used to
investigate the poorly confined sources discussed in Section
\S\ref{sec:r&d}. For the systems where nuclear radio emission was
resolved, we found, on average $S_{\nu,\mathrm{nucleus}} /
S_{\nu,\mathrm{total}} \la 0.1$, suggesting the nuclear contribution
to the low-resolution NVSS measurements has a negligible impact on our
results.

B08 found that using lower frequency radio data, \ie\ 327 MHz versus
1400 MHz, resulted in a lower scatter \pcav-\prad\ relation. For our
sample of gEs, the quality and availability of 327 MHz data were poor,
and thus we gathered low-frequency radio fluxes from the CATS
Database\footnote{http://www.sao.ru/cats/} \citep{cats}. CATS was
queried in the frequency range 200-400 MHz using the list of radio
source coordinates found from the NVSS and SUMSS searches. Of the
\samp\ gEs in our sample, 17 objects were found in the CATS database
with fluxes in the 200-400 MHz range. The approach used for searching
CATS means that low-frequency radio emission without a 1.4 GHz
counterpart will be missed. But, because CATS does not provide images
for visual inspection, the search method also ensures that spurious
detections are less likely to be included. Therefore, the 200-400 MHz
radio powers shown in Figure \ref{fig:pcav} might underestimate the
200-400 MHz fluxes for these gEs. However, because of the large range
of radio powers, a systematic shift by a factor of a few along the
\prad\ axis for all the gE points alters the best-fit slope within the
uncertainties.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and Discussion}
\label{sec:r&d}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\pjet-\prad\ Scaling Relation}
\label{sec:relation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The results from the X-ray and radio data analysis are shown in the
plots of \pcav-\phigh\ and \pcav-\plow\ presented in Figure
\ref{fig:pcav}. A subjective figure of merit (FOM) was assigned to
each set of cavities -- shown as color coding in Figure \ref{fig:pcav}
and listed in Table \ref{tab:sample}. We assigned figures because,
currently, no standard algorithm for detecting cavities and
determining their volumes exists, the FOMs represent our qualitative
visual assessment. FOM-A cavities are associated with AGN radio
activity and have well-defined boundaries; FOM-B cavities are
associated with AGN radio activity, but lack well-defined boundaries;
FOM-C cavities have poorly-defined boundaries, and their connection to
AGN radio activity is unclear. FOM-C cavities are excluded from all
fitting.

Figure \ref{fig:pcav} shows a continuous power law relationship
between cavity power and radio power over approximately 8 orders of
magnitude in radio power and 6 orders of magnitude in cavity power. To
determine the form of the power-law relation, we performed linear fits
in log-space for each frequency regime using the bivariate correlated
error and intrinsic scatter (\bces) algorithm \citep{bces}. The
orthogonal \bces\ algorithm takes in asymmetric uncertainties for both
variables, assumes the presence of intrinsic scatter, and performs a
linear least-squares regression which minimizes the squared orthogonal
distance to the best-fit relation. This differs from the fitting
approach in B08 which minimized the distance in the
\pcav\ coordinate. The best-fit parameter uncertainties were
calculated using $10,000$ Monte Carlo bootstrap resampling trials.

The best-fit orthogonal \bces\ determined linear function in log-space
for the \pcav-\phigh\ and \pcav-\plow\ relations are:
\begin{eqnarray}
  \log~\pcav &=& 0.72~(\pm 0.13)~\log~\phigh + 1.92~(\pm 0.17) \label{eqn:high}\\
  \log~\pcav &=& 0.64~(\pm 0.08)~\log~\plow + 1.55~(\pm 0.12) \label{eqn:low}
\end{eqnarray}
where \pcav\ has units $10^{42} \lum$, and \phigh\ and \plow\ have
units $10^{40} \lum$. The scatter for each relation is $\shigh = 0.77$
dex and $\slow = 0.61$ dex, and the respective correlation
coefficients are \rhigh\ = 0.73 and \rlow\ = 0.81. We have quantified
the total scatter about the best-fit relation using a weighted
estimate of the orthogonal distances to the best-fit line
\citep[see][for equations]{2009A&A...498..361P}. For comparison, the
B08 scaling relations are
\begin{eqnarray}
  \log~\pcav &=& 0.35~(\pm 0.07)~\log~\phigh + 1.85~(\pm 0.10) \\
  \log~\pcav &=& 0.51~(\pm 0.07)~\log~\pthree + 1.51~(\pm 0.12) \label{eqn:err}
\end{eqnarray}
where \pcav\ has units $10^{42} \lum$, and \phigh\ and \pthree\ have
units $10^{24}$ W Hz$^{-1}$ (or $\approx 10^{40} \lum$). The relations
have scatters of $\shigh = 0.85$ dex and $\sthree = 0.81$ dex. There
is an error in Equation 15 of B08 that has been corrected in Equation
\ref{eqn:err} \citep{birzan08err}.

Note that we find a steeper relationship at 1.4 GHz than B08, and the
slopes of the relations from this work agree within the
uncertainties. This difference in slope at 1.4 GHz between our work
and B08 is due to the additional data points at lower \pjet. The B08
points tend to be clumped in a fairly narrow power range, which gave
the few points at the upper and lower power extremes excessive
leverage over the slope. The new data extends to lower jet powers,
giving a more uniform sampling and a more robust measurement of the
slope and zero point.

As a simple check, we point out two systems with accurate estimates of
AGN jet power: Cygnus A and Hercules A. For Cygnus A (point with
largest \prad\ in Figure \ref{fig:pcav}), where our
\pjet-\prad\ relations appear to overestimate the jet power by
$\approx 40$, the total kinetic luminosity of $\sim 2\times10^{46}
\lum$ calculated by \citet{2006ApJ...644L...9W} using the shock is
consistent with the \pjet\ value of $\sim 5\times10^{46} \lum$
predicted by our relations. Hercules A (which is not in the B08
sample) is a similar case to Cygnus A, with $\pcav = 310\times10^{42}
\lum$ and $\phigh = 4100\times10^{40} \lum$, placing Hercules A in the
same region of Figure \ref{fig:pcav} as Cygnus A. But, the total
kinetic luminosity of $\sim 1.6\times10^{46} \lum$ calculated by
\citet{herca} using the shock agrees with the prediction from our
relations, $\sim 3.2\times10^{46} \lum$.

The substantial scatter in the \pjet-\prad\ relations highlight that
radio luminosity is an inaccurate surrogate for determining AGN power
in individual systems. As seen in systems like Hydra A \citep{hydraa}
or MS 0735.6+7421 \citep{ms0735}, the energetics can be dominated by
the effects of an AGN outburst which is more powerful than
average. This may be particularly true for gEs, which have lower
pressure halos and are more susceptible to disruption by AGN outbursts
\citep{2006MNRAS.372.1161W, 2008ApJ...687L..53P}. However, B08 showed
that correcting for the effect of radio aging by including a scaling
with break frequency does reduce the scatter within the relations by
$\approx 50\%$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with Models and Observational Studies}
\label{sec:models}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Owing to the importance of prescriptions for kinetic feedback in
galaxy formation models, specifically in the form of a late-time
radio-mode extension of the quasar era, establishing observational
constraints for the prescriptions is vital
\citep[\eg][]{2007ApJ...658L...9H}. There is a multitude of jet models
\citep[\ie][]{1973MNRAS.164..243L, 1974MNRAS.166..513S,
  1974MNRAS.169..395B, 1989ApJ...345L..21B, 2002ApJS..141..337C,
  2002ApJS..141..371C}, and we restrict our focus to models which
specifically discuss the \pjet-\prad\ relation. We also examine
previous observational studies of \pjet-\prad\ besides B08. In this
section we use the common parameterization for jet power
$L_{\mathrm{kin}} = \eta \prad^{\alpha}$, where $L_{\mathrm{kin}}$ is
total kinetic jet power, $\eta$ is some normalization, $\alpha$ is a
scaling index, and \prad\ is emergent synchrotron power.

For flat-spectrum compact radio cores (\eg\ small scale jets and not
radio lobes), the jet model by \citet{1979ApJ...232...34B} predicts
$\alpha = 12/17~(\approx 0.71)$. Starting with the
\citet{1979ApJ...232...34B} model, \citet{1995A&A...293..665F} found a
similar slope when assuming emergent jet power scales with accretion
power in a jet-disk system. The more generalized model for
scale-invariant jets by \citet{2003MNRAS.343L..59H} also predicts
$\alpha = 12/17$. Utilizing a collection of objects from the R06
sample and 5 GHz core luminosities corrected for relativistic Doppler
boosting, \citet{2007MNRAS.381..589M} found that $\alpha = 0.81$ with
$\eta \approx 2\times10^{44} \lum$ with \prad\ in units of $10^{40}
\lum$. The earlier study by \citet{2005ApJ...633..384H} using 5 GHz
core luminosities and an estimate of $L_{\mathrm{kin}}$ from the
Galactic X-ray binary mass-radio-X-ray fundamental plane relation
\citep{2003MNRAS.344...60G, 2003MNRAS.345.1057M} found, when
$L_{\mathrm{kin}} \propto \prad^{12/17}$ was held constant, $\eta
\approx 6\times10^{44} \lum$ with \prad\ in units of $10^{40} \lum$

\citet[][hereafter W99]{1999MNRAS.309.1017W} derive $\alpha$ and
$\eta$ using the hypersonic jet model of \citet{1991MNRAS.250..581F}
and assuming radio lobes are at minimum energy density \citep[see][for
  details]{1980ARA&A..18..165M}. W99 derived $\alpha = 6/7$ with $\eta
\approx f^{3/2}~4.61\times10^{41} \lum$ when \prad\ is in units of
$10^{40} \lum$. The normalization has been adjusted from 151 MHz to
1.4 GHz assuming $\alpha = 0.8$. The factor $f$ consolidates a variety
of unknowns (see W99 for details). The fiducial W99 model ($f=1$)
yields $\eta$ two orders of magnitude lower than our best-fit
normalizations. Because the W99 model has been widely used for
estimating jet power, the difference in $\eta$'s needs to be explored.

The W99 normalization has a weak dependence on ambient gas density.
Using shallower and lower density gas profiles consistent with
observations increases jet outflow velocities in the W99 model, which
in turn increases $\eta$ by factors of $\sim 2-5$. In addition, there
is a critical dependence on the fractional deviation from the
minimum-energy condition and $k$, which is the ratio of energy in
neutralizing species to electrons. We find that for $k$ lying in the
range of tens to hundreds, values consistent with observational
findings \citep{2005MNRAS.364.1343D, 2006MNRAS.372.1741D,
  2006ApJ...648..200D, birzan08}, brings the W99 normalization into
agreement with our work. Figure \ref{fig:radeff} shows that the W99
zero-point lies significantly below our best-fit
\pjet-\prad\ relations, but the slopes formally agree. W99 find that
to fit their model to narrow-line region luminosities (assuming
$L_{\mathrm{NLR}} \propto L_{\mathrm{kin}}$) for sources in the 7C and
3CRR surveys, $f$ must equal 20, which is the upper-limit of $f$ in
their model and implies $k \approx 20$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Poorly Confined Sources}
\label{sec:jet}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In Figure \ref{fig:radeff} is a set of points highlighting systems we
have classified as being poorly confined (PC). The objects are: IC
4296 \citep{1988ApJ...324..198K, 2003ApJ...585..677P}, NGC 315
\citep{1979ApJ...228L...9B, 1981A&A....95..250W}, NGC 4261
\citep{1997ApJ...484..186J, 2000ApJ...534..165J}, NGC 4782
\citep{2007ApJ...664..804M}, and NGC 7626 \citep{1985ApJ...291...32B}.
These objects were culled from the sample because the X-ray surface
brightness decrements are reminiscent of tunnels rather than bubbles,
and the radio morphologies are distinctly different from the rest of
the gE and B08 objects. X-ray cavities typically enclose the jet+lobe
radio emission, see Figure \ref{fig:pics} for an example in
M84. However, for the PC sources, the only indication of gas
excavation in the X-ray halo is found near the base of the jets,
seemingly at the ``edge'' of the X-ray halo, see Figure \ref{fig:pics}
for an example in NGC 4261. The appearance of breaking-out from the
X-ray halo is our reason for suggesting these sources are poorly
confined.

The observed small voids do not capture the total $p~dV$ work being
done by the jets. However, there may be cavities which are not imaged
extending to larger radii and enclosing the radio lobes. But, for PC
systems the ambient medium at those radii is too faint to yield a
cavity detection. We calculated \pcav\ values for the PC systems
assuming radio lobe morphology approximates the volume of cavities
potentially at larger radii. Pressure profiles were extrapolated to
large radii using the best-fit parameters of a $\beta$-model
\citep{betamodel} fit to the surface brightness profile, assuming the
ambient atmosphere is isothermal, and adding a background gas pressure
of $10^{-13}$ dyne \pcmsq. The assumed background gas pressure is
based on the mean value observed in the outskirts of clusters and
groups. See the
\accept\ database\footnote{http://www.pa.msu.edu/astro/MC2/accept} for
a catalog of such pressure profiles. Cavity ages were calculated
assuming expansion at the gas sound speed. As a result of the radio
lobes extending into regions where the pressure profiles are very
steep and approaching the background pressure, the large volumes are
offset by much lower pressures and longer ages, resulting in modest
values of \pcav. Because we do not have a robust measurement of
\pcav\ for the PC systems, they were excluded from the preceding
analysis of the \pjet-\prad\ relations.

Two of the PC sources, NGC 315 and NGC 4261, are part of a sample of
nine FR-I objects analyzed in detail by \citet[][hereafter
  C08]{2008MNRAS.386.1709C} using \xmm\ X-ray observations. Provided
in C08 are the $4pV$ enthalpies for each FR-I source (calculated using
the radio lobe volumes and the external thermal pressure at the lobe
mid-point), and the mean temperature of the group environments into
which the lobes are expanding. Assuming lobe expansion occurs at the
ambient gas sound speed, we calculated \pcav\ values for each of the
C08 FR-I sources. For N315 and N4261 we find no significant difference
between the \pcav\ values calculated using the \chandra\ data and the
\xmm\ data from C08. Using the NVSS search method outlined in Section
\ref{sec:radio} we calculated \phigh\ for each C08 FR-I source. Our PC
objects and the C08 FR-I objects are plotted in Figure
\ref{fig:radeff}.

Figure \ref{fig:radeff} shows that the PC and C08 FR-I sources reside
well below our best-fit relation. This discrepancy implies that these
sources have the lowest jet power per unit radio luminosity of all
objects in the sample. One explanation is that these sources have
lower $k$ values, possibly because there are intrinsic differences in
radio sources (light and heavy jets), or because all jets are born
light and become heavy on large scales due to entrainment. Another
explanation is that that PC sources are more powerful than our
measurements indicate due to energy being imparted to shocks. On
average, shock energy is a small correction to \pcav, factor of a few
in clusters \citep{mcnamrev}, but the frequency and variety of AGN
driven shocks is broad, ranging from strong (Mach $\ga 2$) --
Centaurus A \citep{2003ApJ...592..129K, 2009MNRAS.395.1999C}, NGC 3801
\citep{2007ApJ...660..191C} -- to weak (Mach $\la 2$) -- 3C 31
\citep{2002MNRAS.336.1161L}, Cygnus A \citep{2006ApJ...644L...9W},
Hydra A \citep{hydraa}, Hercules A \citep{herca}, M87
\citep{2007ApJ...665.1057F}, MS 0735.6+7421 \citep{ms0735}, NGC 4552
\citep{2006ApJ...648..947M}, NGC 4636 \citep{2009arXiv0909.2942B}, NGC
4782 \citep{2007ApJ...664..804M} -- to definitively absent -- 3C 186
\citep{2008ApJ...684..811S}, 3C 388 \citep{2006ApJ...639..753K}, NGC
6764 \citep{2008ApJ...688..190C}. However, this would require that the
fraction of jet power going into shocks is preferentially higher for
systems with relatively high implied radiative efficiencies
(\ie\ $\pjet/\prad < \eta$).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Conclusions}
\label{sec:summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We have presented analysis of the jet power-radio power scaling
relation for a sample of \samp\ giant elliptical galaxies observed
with the \cxo. Cavity powers, \pjet, were calculated for each set of
cavities using similar methods to those outlined in R06. Bolometric
radio luminosities, \prad, were estimated using 1.4 GHz and 200-400
MHz fluxes taken from the NVSS/SUMSS surveys and the CATS database.

Incorporating the data from B08, we find a continuous power-law
relation between \pjet-\prad\ covering 6 decades in \prad\ and 8
decades in \pjet\ (Figure \ref{fig:pcav}). Using log-space orthogonal
\bces\ fits, we find similar forms for the power laws describing the
\pjet-\prad\ trend with the mean form $\pjet \approx 5.93\times10^{43}
(\prad/10^{40})^{0.68} \lum$. This relation comes with the caveat of
$\approx 0.7$ dex scatter about the best-fit relations, and we point
out that the relation is weakly applicable for determining
{\it{total}} AGN energy output of an individual system. We also note
the general agreement of our best-fit relations with previous
observational studies and predictions from theoretical jet models.

Several groups have applied the \birzan\ scaling relations to study
the effects of AGN feedback on structure formation, most notably
\citet{best07} and \citet{2007MNRAS.379..260M}, with some groups now
suggesting that distributed low-power radio galaxies may dominate
heating of the intracluster medium,
\eg\ \citet{2009arXiv0908.3158H}. Up to now, the available
observational results, which were primarily calibrated to high-power
radio sources, did not clearly indicate if a \pjet-\prad\ relation
would be continuous, or of comparable scatter, for lower power radio
sources. Assuming there is no redshift evolution of \pjet-\prad, our
relations suggest higher mass galaxies dominate over lower mass
galaxies in the process of mechanical heating within clusters. The
next step is to study the process of mechanical heating in a
cosmological context, \eg\ evaluating the contribution of mechanically
dominated AGN on the bolometric AGN luminosity function over cosmic
time \citet{2009MNRAS.395..518C}.

We have also focused on a subset of objects we classify as being
poorly confined (PC) by their environments (Figure
\ref{fig:radeff}). These objects have \pjet/\prad\ ratios which are
large relative to the rest of our sample. In addition, PC sources
reside in the same region of the \pjet-\prad\ plane as the FR-I
sources taken from C08. Possible explanations for the nature of these
sources lie in the long-standing effort to understand the connection
between properties of radio galaxies and their environment. Processes
such as matter entrainment and gas shocking may be important for
determining true kinetic jet power for PC systems.

With tighter, self-consistent observational constraints on the
\pjet-\prad\ relation across several decades in both parameters, and
host system mass, the need for calculating jet kinetic power using
model-dependant formalisms (\ie\ $Q$) has weakened
significantly. Using \pjet-\prad\ as an aide, a better understanding
of the supermassive black hole power plants which underlie AGN
activity can be undertaken. Moreover, future AGN feedback models, when
used in simulations, must replicate the observed radio-mode relations
studied here.

%%%%%%%%%%%%%%%%%
\acknowledgements
%%%%%%%%%%%%%%%%%

KWC and BRM acknowledge generous support from the Natural Science and
Engineering Research Council of Canada and grants from the \cxo. KWC
sincerely thanks Judith Croston, David Rafferty, and Chris Willott for
helpful input. The \cxo\ Center is operated by the Smithsonian
Astrophysical Observatory for and on behalf of NASA under contract
NAS8-03060. The National Radio Astronomy Observatory is a facility of
the National Science Foundation operated under cooperative agreement
by Associated Universities, Inc. This research has made use of
software provided by the \chandra\ X-ray Center, the NASA/IPAC
Extragalactic Database operated by the California Institute of
Technology Jet Propulsion Laboratory, and NASA's Astrophysics Data
System. Some software was obtained from the High Energy Astrophysics
Science Archive Research Center, provided by NASA's Goddard Space
Flight Center.

%%%%%%%%%%%%%%
% Facilities %
%%%%%%%%%%%%%%

{\it Facilities:} \facility{CXO (ACIS)} \facility{VLA}

%%%%%%%%%%%%%%%%
% Bibliography %
%%%%%%%%%%%%%%%%

\bibliography{cavagnolo}

%%%%%%%%%%%%%%%%%%%%%%
% Figures  and Tables%
%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\input{sample.tex}
\input{figs.tex}

%%%%%%%%%%%%%%%%%%%%
% End the document %
%%%%%%%%%%%%%%%%%%%%
\end{document}

% LocalWords:  CTI
