%%%%%%%%%%%%%%%%
% New commands %
%%%%%%%%%%%%%%%%

\input{newcomm}

%%%%%%%%%%
% Header %
%%%%%%%%%%

\documentclass[final]{msuthesis}
%\documentclass[twoside]{msuthesis}
%\documentclass[draft]{msuthesis}
\usepackage{mathrsfs,common,setspace,longtable}
\allowlos{}
\bibliographystyle{apj}
\copyrightyear{2008}
\title{\mytitle}
\author{Kenneth W. Cavagnolo}
\subject{Astronomy \& Astrophysics}
\degree{Doctor of Philosophy}
\department{Department of Astronomy and Astrophysics}
\advisor{Dr. Megan Donahue}
\colorfigures
%\multivolume

%%%%%%%%%%%
% Symbols %
%%%%%%%%%%%

%%%%%%%%%%%%
% Abstract %
%%%%%%%%%%%%

\abstract{
\input{abstract.tex}
}

%%%%%%%%%%%%%%
% Dedication %
%%%%%%%%%%%%%%

\dedication{Dedicated to my mother: Miss Lorna Lorraine Cox.}

%%%%%%%%%%%%%%%%%%%
% Acknowledgments %
%%%%%%%%%%%%%%%%%%%
\acknowledgments{
\classack My dissertation would not have been possible without the
multitude of grants from NASA and the Chandra X-ray Center. I also
thank the MSU College of Natural Science for awarding me the
Dissertation Completion Fellowship which helped fund my final year at
MSU.

My deepest thanks to Megan Donahue and Mark Voit for their guidance,
wisdom, patience, and without whom I would be in quantum computing. I
can only say, ``Thank you, Megan,'' for allowing me the time and space
to find my bearings after my mother's passing, words are insufficient
to express my gratitude. Many thanks to my friend Ming Sun who always
listened, always had time for a question, and was never wrong. Thanks
also to Jack Baldwin who nutured my painfully slow development as a
research assistant -- a more soothing voice there has never been. On
behalf of everyone that has never said so, ``We love you, Shawna
Prater. MSU Astronomy and Astrophysics could not function without
you.''  And of course, Debbie Simmons, without whom I would have been
dropped from all courses and locked out of the building.

Every time I feel the warmth of the Sun on my skin, it is an
invigorating experience. Bathed in photons millions of years old from
an inconceivably large nuclear power plant over a hundred million
kilometers away, I feel connected to the Universe in a way that is
surreal. To feel purposely cared for by the feckless Sun, whose
existence and operation are arguably devoid of purpose, is quite
profound. For that I say, ``Thank you, Sun!''}

%%%%%%%%%%%
% Preface %
%%%%%%%%%%%

\preface{Our universe is predominantly an untold story. Within a
  larger, nested framework of complex mechanisms, humans evolved with
  minimal impact on the systems which support and nurture our
  existance. Yet, during the short epoch of global industrialization,
  we have compromised the effectiveness and function of the systems
  which formed the biodiversity which makes our planet such a
  wonderful place. As an acknowledgment of our species' appreciation
  for the Earth, and as a show of our understanding that humanity's
  presence on Earth is fleeting, let us strive to utilize the pursuit
  of knowledge, through application of reason and logic, such that our
  actions benefit ``all the children, of all species, for all of
  time'' \citep{2002c2c..book.....O}. Let us all exert effort such
  that the Earth and the Universe will be enriched by humanity, and
  that our actions -- local, global, and possibly interplanetary --
  will leave the places we inhabit and visit nourished from our
  presence.}

%%%%%%%%%%%%
% Initiate %
%%%%%%%%%%%%

\begin{document}
%\extracopies
\requirements

%%%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}
\label{ch:intro}
%%%%%%%%%%%%%%%%%%%%%%

\input{intro}

%%%%%%%%%%%%%%%%%%%%%%
% Reprint cover page %
%%%%%%%%%%%%%%%%%%%%%%

\newpage
\parbox[c][0.9\textheight][c]{\linewidth}{
\begin{center}
Chapter Two
\end{center}
\begin{spacing}{1.1}
Cavagnolo, Kenneth W., Donahue, Megan, Voit, G. Mark, Sun, Ming
(2008). Bandpass Dependence of X-ray Temperatures in Galaxy
Clusters. {\underline{The Astrophysical Journal}}. 682:821-830.
\end{spacing}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Bandpass Dependence of X-ray Temperatures in Galaxy Clusters}
\label{ch:eband}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{energy_band}

%%%%%%%%%%%%%%%%%%%%%%
% Reprint cover page %
%%%%%%%%%%%%%%%%%%%%%%

\newpage
\parbox[c][0.9\textheight][c]{\linewidth}{
\begin{center}
Chapter Three
\end{center}
\begin{spacing}{1.1}
Cavagnolo, Kenneth W., Donahue, Megan, Voit, G. Mark, Sun, Ming
(2008). Intracluster Medium Entropy Profiles For A Chandra Archival
Sample of Galaxy Clusters. {\underline{The Astrophysical Journal
Supplement Series}}. arXiv eprint 0902.1802.\\
\end{spacing}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Intracluster Medium Entropy Profiles For A Chandra Archival Sample of Galaxy Clusters}
\label{ch:ent_supp}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{ent_supp3}

%%%%%%%%%%%%%%%%%%%%%%
% Reprint cover page %
%%%%%%%%%%%%%%%%%%%%%%

\newpage
\parbox[c][0.9\textheight][c]{\linewidth}{
\begin{center}
Chapter Four
\end{center}
\begin{spacing}{1.1}
Cavagnolo, Kenneth W., Donahue, Megan, Voit, G. Mark, Sun, Ming
(2008). An Entropy Threshold for Strong \halpha\ and Radio Emission in
the Cores of Galaxy Clusters. {\underline{The Astrophysical
Journal Letters}}. 683:107-110.\\
\end{spacing}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{An Entropy Threshold for Strong \halpha\ and Radio Emission
in the Cores of Galaxy Clusters}
\label{ch:harad}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{haradent}

%%%%%%%%%%%%%%%%%%
\chapter{Summary}
\label{ch:summary}
%%%%%%%%%%%%%%%%%%

\input{summary}

%%%%%%%%%%%%%%%%
%% APPENDICES %%
%%%%%%%%%%%%%%%%

\appendix
\input{eband_tablecomm}
\input{eband_tables}
\input{ent_supp_tablecomm}
\input{ent_supp_tables}
\input{appendix}

%%%%%%%%%%%%%%%%%%
%% BIBLIOGRAPHY %%
%%%%%%%%%%%%%%%%%%

\bibliography{cavagnolo}

%%%%%%%%%%%%%%
\end{document}
%%%%%%%%%%%%%%
